### 2020-09-20 samplepaper.tex
Initial Overleaf Import

% This is samplepaper.tex, a sample chapter demonstrating the
% LLNCS macro package for Springer Computer Science proceedings;
% Version 2.20 of 2017/10/04
%
\documentclass[runningheads]{llncs}
%
\usepackage{graphicx}
% Used for displaying a sample figure. If possible, figure files should
% be included in EPS format.
%
% If you use the hyperref package, please uncomment the following line
% to display URLs in blue roman font according to Springer's eBook style:
% \renewcommand\UrlFont{\color{blue}\rmfamily}
\usepackage{booktabs}   %% For formal tables:
%% http://ctan.org/pkg/booktabs
\usepackage{subcaption} %% For complex figures with subfigures/subcaptions
%% http://ctan.org/pkg/subcaption
\usepackage{xcolor} %% For \color
\usepackage{todonotes} %% For \todo
\usepackage{mathtools} %% For \xRightarrow[sub]{sup}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{stmaryrd} %% For \llbracket etc.
\usepackage{semantic}
\usepackage[scaled]{beramono}
\usepackage[T1]{fontenc}
\usepackage{natbib} %% For more citation commames (\cite etc.)
\usepackage{listings} %% For typesetting code
\newcommand{\lstsetgrift}{
	\lstset{%
		language=Lisp,%
		basicstyle=\ttfamily\small,%
		keywordstyle=\ttfamily\bfseries\small,%
		columns=flexible,%
		aboveskip=\smallskipamount,%
		belowskip=\smallskipamount,%
		frame=single,%
		xleftmargin=2pt,%
		escapeinside={/+}{+/},%
		mathescape=true,%
		keywords=[1]{define,if,:,Int,Bool,-,=,open},
		literate=%
		{->}{{$\rightarrow$}}2%
		{=>}{{$\Rightarrow$}}2%
		{lambda}{{$\lambda$}}1%
		{→}{{$\rightarrow$ }}2%
		{Γ}{{$\Gamma$ }}1%
		{⊢}{{$\vdash$ }}1%
	}%
}%%
\lstsetgrift

% random stuff
\newcommand{\infr}[2]{\inference{#1}{#2}}
\newcommand{\highlight}[1]{{\color{red} #1}}
\newcommand{\sidecond}[1]{\text{if}\;#1}

% abbreviations in figures
\newcommand{\figreduceto}[3]{#1 & \longmapsto & #2 & #3 \\}
\newcommand{\figreducetoH}[3]{\highlight{#1} & \highlight{\longmapsto} & 
\highlight{#2} & \highlight{#3} \\}
\newcommand{\figequalto}[3]{#1 & = & #2 & #3 \\}
\newcommand{\figequaltoH}[3]{\highlight{#1} & \highlight{=} & \highlight{#2} & 
\highlight{#3} \\}
\newcommand{\stxinrule}[3]{\text{#2} & #1 & \in & #3\\}
\newcommand{\stxrule}[3]{\text{#2} & #1 & \Coloneqq & #3\\}
\newcommand{\stxrulecont}[1]{& & | & #1 \\}

% ref figures, sections, etc.
\newcommand{\figref}[1]{Fig.~\ref{#1}}
\newcommand{\secref}[1]{Section~\ref{#1}}
\newcommand{\chapref}[1]{Section~\ref{#1}}

% names
\newcommand{\LUD}{\ensuremath{\text{Lazy\;UD}}}
\newcommand{\LD}{\ensuremath{\text{Lazy\;D}}}
\newcommand{\CastADT}{\ensuremath{\text{Cast ADT}}}
\newcommand{\RMachine}[1]{\ensuremath{\mathcal{R}(#1)}}
\newcommand{\LDMachine}{\RMachine{\BLD}}
\newcommand{\LUDMachine}{\RMachine{\BLUD}}
\newcommand{\RBMachine}[0]{\RMachine{B}}
\newcommand{\SMachine}[1]{\ensuremath{\mathcal{S}(#1)}}

% error monad
\newcommand{\just}[1]{\ensuremath{#1}}
\newcommand{\error}[1]{\ensuremath{\Uparrow#1}}

% types
\newcommand{\Tdyn}[0]{\ensuremath{\star}}

%% pre-types
\newcommand{\Pbool}[0]{\ensuremath{\mathtt{Bool}}}
\newcommand{\Pfunc}[2]{\ensuremath{#1 \shortrightarrow #2}}
\newcommand{\Pprod}[2]{\ensuremath{#1 \times #2}}

% ground types
\newcommand{\Gbool}[0]{\Pbool}
\newcommand{\Gfunc}[0]{\Pfunc{\Tdyn}{\Tdyn}}
\newcommand{\Gprod}[0]{\Pprod{\Tdyn}{\Tdyn}}

%% expressions
\newcommand{\econ}[1]{#1}
\newcommand{\evar}[1]{#1}
\newcommand{\elam}[3]{\lambda#1:#2.\;#3}
\newcommand{\eapp}[2]{#1\;#2}
\newcommand{\etrue}[0]{\mathtt{true}}
\newcommand{\efalse}[0]{\mathtt{false}}
\newcommand{\eif}[3]{\mathtt{if}\;#1\;#2\;#3}
\newcommand{\econs}[2]{\mathtt{cons} \; #1 \; #2}
\newcommand{\ecar}[1]{\mathtt{car} \; #1}
\newcommand{\ecdr}[1]{\mathtt{cdr} \; #1}
%\newcommand{\ecast}[2]{#1 \langle #2 \rangle}
\newcommand{\ecast}[2]{\ensuremath{#1 : #2}}

% casts
\newcommand{\ccast}[3]{#1 \xRightarrow[]{\enskip #2 \enskip} #3}
% \Rightarrow^{#2}

% values
\newcommand{\vdyn}[2]{\mathtt{Dyn}_{#1}(#2)}
\newcommand{\vtrue}[0]{\mathtt{true}}
\newcommand{\vfalse}[0]{\mathtt{false}}
\newcommand{\vfunc}[4]{\langle\elam{#1}{#2}{#3},#4\rangle}
\newcommand{\vfuncc}[6]{\ecast{#1}{\ccast{\Pfunc{#2}{#3}}{#4}{\Pfunc{#5}{#6}}}}
\newcommand{\vcons}[2]{\econs{#1}{#2}}
\newcommand{\vconsc}[6]{\ecast{#1}{\ccast{\Pprod{#2}{#3}}{#4}{\Pprod{#5}{#6}}}}

% observables
\newcommand{\odyn}{\ensuremath{\mathtt{dynamic}}}
\newcommand{\otrue}[0]{\mathtt{true}}
\newcommand{\ofalse}[0]{\mathtt{false}}
\newcommand{\ofunc}[0]{\mathtt{function}}
\newcommand{\ocons}[0]{\mathtt{cons}}
\newcommand{\oerror}[1]{\error{#1}}

% blame strategies
\newcommand{\BLD}[0]{\ensuremath{\mathtt{LD}}}
\newcommand{\BLUD}[0]{\ensuremath{\mathtt{LUD}}}

% cast _r_esults
\newcommand{\rsucc}[1]{\mathtt{succ}\;#1}
\newcommand{\rfail}[1]{\mathtt{fail}\;#1}

% machine _s_tates
\newcommand{\sexpr}[3]{\ensuremath{\langle#1,#2,#3\rangle}}
\newcommand{\scont}[2]{\ensuremath{\langle#1,#2\rangle}}
\newcommand{\shalt}[1]{\ensuremath{\Downarrow #1}}

% continuations
\newcommand{\Knil}[0]{\Box}
\newcommand{\Kcons}[2]{[#1]#2}

% frames
\newcommand{\closure}[2]{\langle#1,#2\rangle}
\newcommand{\FappXO}[2]{\eapp{\square}{\closure{#1}{#2}}}
\newcommand{\FappOX}[1]{\eapp{#1}{\square}}
\newcommand{\Fif}[3]{\eif{\square}{\closure{#1}{#3}}{\closure{#2}{#3}}}
\newcommand{\FconsXO}[2]{\econs{\square}{\closure{#1}{#2}}}
\newcommand{\FconsOX}[1]{\econs{#1}{\square}}
\newcommand{\Fcar}[0]{\ecar{\square}}
\newcommand{\Fcdr}[0]{\ecdr{\square}}
\newcommand{\Fcast}[1]{\ecast{\square}{#1}}

% threesomes
\newcommand{\tscc}[3]{\ccast{#1}{#2}{#3}}
%\newcommand{\tsTp}[2]{({#1};{#2})}
\newcommand{\tsTp}[2]{{#2}^{#1}}
\newcommand{\tsTdyn}[0]{\Tdyn}
\newcommand{\tsPbool}[0]{\Pbool}
\newcommand{\tsPfunc}[2]{\Pfunc{#1}{#2}}
\newcommand{\tsPprod}[2]{\Pprod{#1}{#2}}
\newcommand{\tsPfail}[2]{\bot^{#1#2}}
\newcommand{\tsle}[0]{\epsilon}
%\newcommand{\tsll}[1]{\cnfproj{}{#1}}
\newcommand{\tsll}[1]{#1}

% coercions in normal form
\newcommand{\cnfproj}[2]{#1?^{#2}}
\newcommand{\cnfinj}[1]{#1!}
\newcommand{\cnfseq}[2]{#1;#2}
\newcommand{\cnffail}[1]{\bot^{#1}}
\newcommand{\cnffunc}[2]{\Pfunc{#1}{#2}}
\newcommand{\cnfprod}[2]{\Pprod{#1}{#2}}
\newcommand{\cnfid}[1]{\ensuremath{\mathtt{id}_{#1}}}

% hypercoercions
\newcommand{\hcci}[0]{\cnfid{\Tdyn}}
\newcommand{\hccc}[3]{\ensuremath{(#1;#2;#3)}}
\newcommand{\hche}[0]{\ensuremath{\epsilon}}
\newcommand{\hchp}[2]{\ensuremath{#1?^{#2}}}
\newcommand{\hcmbool}[0]{\Pbool}
\newcommand{\hcmfunc}[2]{\Pfunc{#1}{#2}}
\newcommand{\hcmprod}[2]{\Pprod{#1}{#2}}
\newcommand{\hcmfail}[1]{\ensuremath{\bot^l}}
\newcommand{\hcte}[0]{\ensuremath{\epsilon}}
\newcommand{\hcti}[1]{\ensuremath{#1!}}

% gaps
\newcommand{\gnone}{\ensuremath{\epsilon}}
\newcommand{\gsome}[3]{\ccast{#1}{#2}{#3}}

% operators
\newcommand{\mbind}[0]{\ensuremath{\;\gg=\;}}
\newcommand{\mcomp}[0]{\ensuremath{\;>=>\;}}

% functions
\newcommand{\meet}[2]{\ensuremath{#1 \sqcap #2}}
\newcommand{\denote}[1]{\ensuremath{\llbracket #1 \rrbracket}}
\newcommand{\proxy}[2]{\ensuremath{\mathit{proxy}(#1,#2)}}
\newcommand{\applyCast}[2]{\ensuremath{\mathit{applyCast}(#1,#2)}}
\newcommand{\project}[4]{\ensuremath{\mathit{project}(#1,#2,#3,#4)}}
\newcommand{\composegap}[3]{\ensuremath{#1 \fatsemi #2 \fatsemi #3}}
\newcommand{\mkhead}[2]{\ensuremath{\mathit{mkProj}(#1,#2)}}
\newcommand{\mktail}[2]{\ensuremath{\mathit{mkInj}(#1,#2)}}
\newcommand{\mkgap}[3]{\ensuremath{\mathit{mkGap}(#1,#2,#3)}}
\newcommand{\compose}[2]{\ensuremath{#1 \fatsemi #2}}
\newcommand{\translate}[1]{\ensuremath{\lceil#1\rceil}}
\newcommand{\castToDyn}[2]{\ensuremath{\mathit{castToDyn}(#1,#2)}}
\newcommand{\castFromDyn}[2]{\ensuremath{\mathit{castFromDyn}(#1,#2)}}
\newcommand{\dom}[1]{\ensuremath{\mathit{dom}(#1)}}
\newcommand{\cod}[1]{\ensuremath{\mathit{cod}(#1)}}
\newcommand{\car}[1]{\ensuremath{\mathit{car}(#1)}}
\newcommand{\cdr}[1]{\ensuremath{\mathit{cdr}(#1)}}
\newcommand{\id}[1]{\ensuremath{\mathit{id}(#1)}}
\newcommand{\idm}[1]{\ensuremath{\mathit{id}_m(#1)}}
\newcommand{\idc}[1]{\ensuremath{\mathit{id}_c(#1)}}
\newcommand{\mkCont}[1]{\ensuremath{\mathit{mkCont}(#1)}}
\newcommand{\extCont}[2]{\ensuremath{\mathit{extCont}(#1,#2)}}
\newcommand{\applyCont}[2]{\ensuremath{\langle\langle#1,#2\rangle\rangle}}

% other relations
\newcommand{\tailable}[2]{\ensuremath{\casttyping{!}{#1}{#2}}}
\newcommand{\consistent}[2]{\ensuremath{#1\sim#2}}
\newcommand{\shallowlyconsistent}[2]{\ensuremath{#1\smile#2}}
\newcommand{\notshallowlyconsistent}[2]{\ensuremath{#1\not\smile#2}}
\newcommand{\expressiontyping}[3]{\ensuremath{#1 \vdash #2 : #3}}
\newcommand{\matching}[2]{\ensuremath{#1 \triangleright #2}}
\newcommand{\valuetyping}[2]{\ensuremath{\vdash #1 : #2}}
\newcommand{\envtyping}[2]{\ensuremath{#1 \vdash #2}}
\newcommand{\casttyping}[3]{\ensuremath{\vdash #1 : #2 \Longrightarrow #3}}
\newcommand{\transitivelyreducetoM}[3]{\ensuremath{#2 \longmapsto_{#1}^{*} #3}}
\newcommand{\transitivelyreduceto}[2]{\ensuremath{#1 \longmapsto^{*} #2}}
\newcommand{\transitivelyreducetoD}[2]{
	\ensuremath{#1 \longmapsto_{\LDMachine}^{*} #2}}
\newcommand{\transitivelyreducetoUD}[2]{
	\ensuremath{#1 \longmapsto_{\LUDMachine}^{*} #2}}
\newcommand{\reduceto}[2]{\ensuremath{#1 \longmapsto #2}}
\newcommand{\reducetoR}[3]{\ensuremath{#2 \longmapsto_{\RMachine{#1}} #3}}
\newcommand{\reducetoD}[2]{\reducetoR{\BLD}{#1}{#2}}
\newcommand{\reducetoUD}[2]{\reducetoR{\BLUD}{#1}{#2}}
\newcommand{\reducetoS}[3]{\ensuremath{#2 \longmapsto_{\SMachine{#1}} #3}}
\newcommand{\evalto}[2]{\ensuremath{\mathit{eval}(#1)=#2}}
\newcommand{\withmachineevalto}[3]{\ensuremath{\mathit{eval}_{#1}(#2)=#3}}
\newcommand{\evaltoR}[3]{\ensuremath{\mathit{eval}_{\RMachine{#1}}(#2)=#3}}
\newcommand{\evaltoD}[2]{\evaltoR{\BLD}{#1}{#2}}
\newcommand{\evaltoUD}[2]{\evaltoR{\BLUD}{#1}{#2}}
\newcommand{\evaltoS}[3]{\ensuremath{\mathit{eval}_{\SMachine{#1}}(#2)=#3}}
\newcommand{\compatibletailhead}[2]{\ensuremath{#1\;\mathit{R}\;#2}}
\newcommand{\goodgap}[1]{\ensuremath{\mathit{good}(#1)}}
\newcommand{\compileto}[4]{\expressiontyping{#1}{#2\rightsquigarrow#3}{#4}}
\newcommand{\machineequiv}[2]{
	\ensuremath{
		\withmachineevalto{#1}{e}{o}	
		\text{ if and only if }
		\withmachineevalto{#2}{e}{o}
		\text{ for all }
		\expressiontyping{\emptyset}{e}{T}
		\text{ and }
		\valuetyping{o}{T}
	}}
\newcommand{\bisimE}[3]{\ensuremath{#1 \vdash #2 \approx #3}}
\newcommand{\bisimv}[3]{\valuetyping{#1 \approx #2}{#3}}
\newcommand{\bisimr}[3]{\valuetyping{#1 \approx #2}{#3}}
\newcommand{\bisimF}[4]{\casttyping{#1 \approx #2}{#3}{#4}}
\newcommand{\bisimc}[4]{\casttyping{#1 \approx #2}{#3}{#4}}
\newcommand{\bisimK}[4]{\casttyping{#1 \approx #2}{#3}{#4}}
\newcommand{\bisims}[3]{\valuetyping{\ensuremath{#1 \approx #2}}{#3}}

\begin{document}
%
\title{A Framework for Equivalence of Cast Calculi and a new Cast Representation}
%
%\titlerunning{Abbreviated paper title}
% If the paper title is too long for the running head, you can set
% an abbreviated paper title here
%
\author{Kuang-Chen Lu\inst{1} \and
Jeremy G. Siek\inst{1} \and
Andre Kuhlenschmidt\inst{1}
}
%
\authorrunning{F. Author et al.}
% First names are abbreviated in the running head.
% If there are more than two authors, 'et al.' is used.
%
\institute{Indiana University, Bloomington IN 47405, USA}
% \institute{Princeton University, Princeton NJ 08544, USA \and
% Springer Heidelberg, Tiergartenstr. 17, 69121 Heidelberg, Germany
% \email{lncs@springer.com}\\
% \url{http://www.springer.com/gp/computer-science/lncs} \and
% ABC Institute, Rupert-Karls-University Heidelberg, Heidelberg, Germany\\
% \email{\{abc,lncs\}@uni-heidelberg.de}}
%
\maketitle              % typeset the header of the contribution
%
\begin{abstract}
Gradual typing aims at combining dynamic typing and static typing in one 
language to provide the advantages of both typing disciplines. Implementing 
gradual typing with reasonable overhead, however, is not trivial. Casts might 
accumulate in higher-order values and continuations, thus change the overall 
space complexity. Several space-efficient cast representations have been 
proposed, including coercions in normal forms, threesomes, and supercoercions. 
Drawing an interface between a cast representation and the remaining parts of 
language implementations would likely help to understand the relation 
between these cast representations and potentially new ones. We present such an 
interface, Cast Abstract Data Type. The Cast ADT brings another 
benefit. Space-efficient cast representations shall be proved not changing the 
overall behavior of language implementations except saving space. Existing 
proofs typically go through a whole bisimulation proof between the standard and 
inefficient semantics and a space-efficient one. If a space-efficient semantics 
uses the Cast ADT, its behavior would depend solely on the properties of the 
interface functions. Thus a cast representation is correct if its interface 
functions work correctly. We present an abstract machine \SMachine{C} that uses 
Cast ADT to work with casts, a parameterized bisimulation proof, and two 
subsets of Cast ADT that specify the Lazy D and the Lazy UD blame strategies. We
also introduce a new cast representation, hypercoercions, that is better than 
the known cast representations in some aspects.

% The abstract should briefly summarize the contents of the paper in
% 15--250 words.

\keywords{Gradual Typing \and Blame \and Coercion.}
\end{abstract}
%
%
%

\section{Introduction}
Around 2006, several groups of researchers proposed ways to integrate
dynamic typing and static typing, notably gradual typing
\citep{siek2006gradual}, hybrid typing \citep{knowles2010hybrid},
migratory typing \citep{tobin2006interlanguage}, and multi-language
interoperability \citep{Gray:2005ij,Matthews:2007zr}.

\todo[inline]{Cite "Contracts for higher-order functions" for the proxy-based approach?}

Gradual typing \citep{siek2006gradual,siek2015refined} includes both static typing 
and dynamic typing in the same language, enables smooth transition between them, while
enforcing type soundness.
To allow the smooth transition, gradually typed languages are featuerd by a special type
typically written as \Tdyn\ or \lstinline|Dyn| or \lstinline|Any|, which enables 
imprecise type annotations. A gradual type checker would allow programmers to cast 
implicitly between types that have no conflicting type information.
Researchers usually define the semantics of gradually typed languages by
translation to an intermediate language with explicit casts, such as the blame
calculus \citep{wadler2009well} and other cast calculi \citep{siek2009exploring}.
At runtime, casts store or check type information to enforce type soundness.
% To allow the smooth transition, every gradually typed language
% has a special type typically written as \Tdyn\ or \lstinline|Dyn| or \lstinline|Any|,
% which enables imprecise type annotations.
% Programmers can use an expression of type \texttt{T} in any context that \texttt{T} 
% is consistent to.
% Two types are consistent if they have no conflicting type information.
% For instance, \lstinline|(->  Bool Int)| is consistent with \lstinline|(->  $\star$ Int)| but
% not consistent with \lstinline|(->  Int Int)|.
% When the type of an expression is consistent but not equal to the type of its 
% context, there would be a runtime computation (i.e. a cast) that store or check 
% type information to enforce type soundness.

Unfortunately, straightforward implementations of casts impose significant 
runtime overheads that can change the asymptotic space complexity of a program 
\citep{herman2010space}.
For instance, the following module define functions 
that check the parity of natural numbers. The terms are ordinary, while the 
type annotations are not -- the output type of \lstinline|even?| is 
imprecise.
\begin{lstlisting}
(define (even? [n : Int]) : $\star$
  (if (= n 0) #t (odd? (- n 1))))
(define (odd? [n : Int]) : Bool
  (if (= n 0) #f (even? (- n 1))))
\end{lstlisting}
These functions look tail-recursive, so it is natural to expect that they 
consumes constant space. This is not the case, however, in a straightforward 
implementation because there is a cast around each of the 
``tail call'', one from \lstinline|Bool| to 
\lstinline|$\star$|, the other goes the other way.
A straightforward implementation would cast the output of the recursive 
call \textit{before} returning it, which effectively breaks the tail recursion 
and thus changes the space complexity.

Continuation is not the only place where casts might accumulate. 
Consider a variant of the above program written in continuation-passing style. 
Here, both functions returns \lstinline|Bool| so there is not pending cast in 
continuations. The continuation argument \lstinline|k|, however, is wrapped in 
a cast in each recursive call because the type of \lstinline|k| is less 
precise in \lstinline|even?|.
\begin{lstlisting}
(define (even? [n : Int] [k : (-> $\star$ Bool)]) : Bool
  (if (= n 0) (k #t) (odd? (- n 1) k)))
(define (odd? [n : Int] [k : (-> Bool Bool)]) : Bool
  (if (= n 0) (k #f) (even? (- n 1) k)))
\end{lstlisting}
Our examples programs are inspired by the examples in \citep{herman2010space}.
We direct interested readers to their work for more examples and detailed explanation.

A solution to this space-efficiency problem is representing cast information 
more concisely. There are several known space-efficient cast representations
\citep{Siek:2015:BCT:2737924.2737968,Siek:2010:TWB:1706299.1706342,Garcia:2013:CTB:2500365.2500603,kuhlenschmidt2018efficient,siek2012interpretations,garcia2014deriving}.
The current state of the art includes
\begin{itemize}
	\item threesomes 
	\citep{Siek:2010:TWB:1706299.1706342,Garcia:2013:CTB:2500365.2500603},
	\item supercoercions \citep{Garcia:2013:CTB:2500365.2500603}, and
	\item coercions in normal form
	\citep{siek2012interpretations,Siek:2015:BCT:2737924.2737968}.
\end{itemize}

These cast representations are represented in their own dynamic semantics of a gradually typed language,
which make it harder to focus on key differences between these representations. 
Surprisingly, no one has published a dynamic semantics parameterized over cast representations.
We present in Section~\ref{sec:framework} first of such generic dynamic semantics in the form 
of a CEK abstract machine and formulate the interface between the machine and cast representations
as an abstract data type, namely Cast ADT.

Of course, an alternative cast representation must be proved
correct. That is, a language implementation should give the same output no 
matter whether it is using a cast representation to reduce space 
consumption. Our generic CEK machine comes with generic theorems (Section~\ref{sec:framework}),
with which researchers can prove a cast representation is correct by showing its corresponding
implementation of Cast ADT satisfies a bunch of properties. We believe this framework can reduce the burden
 of proving this kind of theorems and help people focusing on the cast representations.
For illustration, we apply the framework to Lazy UD coercions in normal form
and Lazy UD threesomes (Chapter~\ref{sec:framework-examples}). 
We believe the framework is also applicable to other cast representations.

\todo[inline]{Actuallythink twosome's composition is structurally recursive but threesomes' is not}
The published cast representations have various strengths and weaknesses.
The major insight of these systems is a compose operator for casts which compress cast information to
reduce space consumption.
Threesomes and supercoercions are good for mechanized
metatheory because their compose operators are structurally recursive,
making them easy to define in proof assistants such as Agda. In
contrast, the coercions in normal form have compose operators that are
not structurally recursive, which makes it more difficult to define in
Agda, requiring what amounts to an explicit proof of termination.
%
On the other hand, coercions in normal form are easier to understand
than threesomes (with a strange labeled bottom type), and
supercoercions (10 different kinds).

This paper presents a new cast representation 
(Section~\ref{chap:hypercoercions}), named
\emph{hypercoercions}, that is good for both mechanized metatheory and
good for implementation. The straightforward Agda translation of composition 
operator for hypercoercions is able to pass the termination check and 
hypercoercions are suggestive of a bit-level representation that minimizes the 
need for pointers and fits all first-order casts into 64 bits.
%
We present two flavors of hypercoercions to support the two blame
tracking strategies from the literature: \LD\ and
\LUD~\citep{siek2009exploring}. With the \LD\ strategy, only 
\textbf{d}own 
casts (casts from \Tdyn\ to some other types) are subject to blame. 
With the 
\LUD\
strategy, however, some \textbf{u}p casts are also blamable.
We are interested in the D blame
tracking strategy because it comes with a more straightforward notion of
safe cast compared to \LUD~\citep{siek2009exploring}, which is why \LD\ 
was
chosen in the Grift compiler~\citep{kuhlenschmidt2018efficient}. We are also 
interested in \LUD\ because it plays a
prominent role in the gradual typing literature
\citep{wadler2009well}.  The \LUD\ hypercoercions were inspired by the
supercoercions of \citep{Garcia:2013:CTB:2500365.2500603} (hence the name) and
the \LD\ hypercoercions were inspired by the normal forms of
\citep{siek2012interpretations}.
The semantics of casts can be lazy or
eager~\citep{siek2009exploring}. In this paper, we focus on lazy cast
strategies because we suspect that they are more efficient than eager
strategies and because \citet{new2019gradual} show that the eager
strategies are incompatible with $\eta$-equivalence of functions.

To summarize, the primary contributions of this paper are:
\begin{itemize}
    \item Cast ADT, an abstract data type for cast representations
    \item a CEK abstract machine parameterized over Cast ADT
	\item a framework in Agda for proving the correctness of \LD\ or \LUD\ 
	cast representations when plugging into the CEK machine
	\item a formal proof that \LUD\ threesomes are correct
	\item a formal proof that \LUD\ coercions in normal form are correct
	\item hypercoercions, a new cast representation, which
	has a more compact memory representation in comparison to coercions in 
	normal form.
	\item a formal proof that both \LUD\ hypercoercions are correct
	\item a formal proof that both \LD\ hypercoercions are correct
\end{itemize}

\section{Related Works}
\label{chap:related-works}

\todo[inline]{how to make citet work?}

\subsubsection{Coercions in normal form}

\citet{henglein1994dynamic} introduces coercions to study compilation from 
dynamic languages to static ones. \citet{herman2010space} proposes using 
coercions in normal forms to represent casts in gradual typing and proves space 
efficiency. 
However, they didn't show the coercion-based semantics is equivalent to the 
standard (and type-based) one. \citet{Siek:2015:BCT:2737924.2737968} improves 
the Lazy UD flavor of coercions in normal forms and proves that Lazy UD 
coercions in normal form is correct, using two bisimulation between three 
reduction semantics. The first semantics is similar to \LUDMachine, which 
bisimulates a 
reduction semantics using coercions (not necessarily in normal form). The last 
semantics uses coercions in normal form and bisimulates the coercions-based 
semantics.

\subsubsection{Threesomes}

\citet{Siek:2010:TWB:1706299.1706342} introduces Lazy UD threesomes and prove 
its correctness, using a bisimulation between two reduction semantics: one is 
similar to \LUDMachine; the other uses Lazy UD threesomes and is similar to the 
machine in Section~\ref{sec:framework}. 
\citet{Garcia:2013:CTB:2500365.2500603} introduces several other flavors of 
threesomes, including a Lazy D one. Their threesomes are derived from 
corresponding flavors of coercions in normal form, using correctness-preserving 
transformation. So the correctness of their threesomes relies on the 
corrections of the coercions-in-normal-form-based semantics defined in 
\citet{herman2010space}, which have not been proved correct.

\subsubsection{Parameterized cast calculi}

\citet{garcia2014deriving} presents a dynamic semantics for the Eager D blame 
strategy, using coercions. They claims that "the artefacts for coercions can be
replaced by other artefacts implementing different dynamic semantics".

\section{Background} \label{sec:background}

In this section, we first review lazy cast calculi (Section~\ref{sec:cast-calculus}), where
we present an abstract machine that is employed in our framework \ref{sec:framework}. Then
we review coercions and their normal forms (Section~\ref{sec:coercions-in-normal-form}), which
motivates and inspires the design of hypercoercions (Section~\ref{sec:hypercoercions}).

\subsection{Cast Calculi} \label{sec:cast-calculi}

\begin{figure}
Syntax
\[
\begin{array}{lrcl}
\text{Blame Labels} & l \\
\text{Variables} & x,y,z \\
\stxrule{S,T}{Types}{
	\Tdyn \mid{}
	P
}
\stxrule{P,Q}{Pre-types}{
	\Pbool \mid
	\Pfunc{T}{T} \mid
	\Pprod{T}{T}
}
\stxrule{G,H}{Ground types}{
	\Gbool  \mid
	\Gfunc  \mid
	\Gprod
}
\stxrule{e}{Expressions}{
	\evar{x}        \mid
	\elam{x}{S}{e}  \mid
	\eapp{e}{e}     \mid
	\econs{e}{e}  \mid
	\ecar{e}      \mid
	\ecdr{e}
}
\stxrulecont{
	\ecast{e}{\ccast{S}{l}{T}}  \mid
	\etrue         \mid
	\efalse        \mid
	\eif{e}{e}{e}
}
\end{array}
\]

	\fbox{\consistent{T}{T}} Consistency
	\begin{gather*}
	\infr{}{\consistent{\Tdyn}{\Tdyn}} \quad
	\infr{}{\consistent{\Tdyn}{P}    } \quad
	\infr{}{\consistent{P}{\Tdyn}    }
	\\[1ex]
	\infr{}{
		\consistent{\Pbool}{\Pbool}
	} \quad
	\infr{
		\consistent{S_1}{S_2} &
		\consistent{T_1}{T_2}
	}{
		\consistent{\Pfunc{S_1}{T_1}}{\Pfunc{S_2}{T_2}}
	} \quad
	\infr{
		\consistent{S_1}{S_2} &
		\consistent{T_1}{T_2}
	}{
		\consistent{\Pprod{S_1}{T_1}}{\Pprod{S_2}{T_2}}
	}
	\end{gather*}

	\fbox{\shallowlyconsistent{T}{T}} Shallow consistency
	\begin{gather*}
	\inference{}{
		\shallowlyconsistent{\Tdyn}{\Tdyn}
	} \quad
	\inference{}{
		\shallowlyconsistent{\Tdyn}{P}
	} \quad
	\inference{}{
		\shallowlyconsistent{P}{\Tdyn}
	} \\
	\inference{}{
		\shallowlyconsistent{\Pbool}{\Pbool}
	} \quad
	\inference{}{
		\shallowlyconsistent{\Pfunc{S_1}{T_1}}{\Pfunc{S_2}{T_2}}
	} \quad
	\inference{}{
		\shallowlyconsistent{\Pprod{S_1}{T_1}}{\Pprod{S_2}{T_2}}
	}
	\end{gather*}

\fbox{$\expressiontyping{\Gamma}{e}{T}$} Expression Typing
\begin{gather*}
\dots \quad
\infr{
	\expressiontyping{\Gamma}{e}{S}  &
	\consistent{S}{T}
}{
	\expressiontyping{\Gamma}{(\ecast{e}{\ccast{S}{l}{T}})}{T}
}
\end{gather*}

\caption{Syntax and static semantics of the Cast Calculus.}
\label{fig:statics}
\end{figure}

\paragraph{Syntax and Static Semantics}

The syntax and static semantics are the same for the \LD\ and
\LUD\ cast calculi. They are reviewed in \figref{fig:statics}.
As usual, the important features are the cast expressions,
$\ecast{e}{\ccast{S}{l}{T}}$, which are responsible for runtime type
checking. Polarities of blame labels is not treated but are straightforward to 
incorporate. The syntax and static semantics is the same as that of 
\citep{siek2009exploring} except for a few minor exceptions:

\begin{itemize}
\item We add product type.
\item We consider only one base type, Boolean, for simplicity.
\item We separate types into those with a type constructor at the top,
  the \emph{pre-types}, versus the dynamic type \Tdyn.
\end{itemize}
As usual, for every cast $\ecast{e}{\ccast{S}{l}{T}}$, the source type $S$ and 
the target $T$ must be consistent.

\paragraph{Dynamic Semantics}

The dynamic semantics of a cast calculus is typically defined with a
reduction semantics. Here we use a CEK machine
\citep{felleisen1986control} instead. One reason is that environments are 
easier 
to deal with than substitutions in formal proof. Also, a CEK machine is more
convenient to use for the space-efficient semantics in
\chapref{sec:framework} (recall that a major point of space-efficiency 
is about compressing continuations and that continuations are part of the CEK 
machine states). So using a CEK machine for the cast 
calculi in this section makes it easier to prove the equivalent of these 
machines. Of course, one should prove that the abstract machine
presented here is equivalent to the standard reduction semantics for
cast calculi, but we have not yet done so.

\begin{figure}
\[
\begin{array}{lrcl}
\stxrule{v,u}{Values}{
  	\vdyn{I}{v}  \mid
    \vtrue       \mid
    \vfalse                     
}
\stxrulecont{
    \vfunc{x}{S}{e}{E}  \mid
	\vfuncc{v}{S}{T}{l}{S}{T}
}
\stxrulecont{
    \vcons{v}{v}               \mid
	\vconsc{v}{S}{T}{l}{S}{T}
}
\stxrule{I,J}{Injectable types}{
	\text{a subset of $P$ defined by the blame strategy $B$}
}
\stxrule{E}{Environments}{
	\text{a partial function}\;\{\langle x , v \rangle , \dots \}
}
\stxrule{F}{Frames}{
	\FappXO{e}{E}  \mid
	\FappOX{v}               \mid
	\Fcast{\ccast{S}{l}{T}}                \mid
	\Fcar                    
}
\stxrulecont{
	\Fcdr           \mid
	\FconsXO{e}{E}  \mid
	\FconsOX{v}
}
\stxrule{K}{Continuations}{
	\Knil         \mid
	\Kcons{F}{K}
}
\stxrule{s}{States}{
	\sexpr{e}{E}{K}  \mid
	\scont{v}{K}     \mid
	\shalt{v}        \mid
	\error{l}
}
\stxrule{o}{Observables}{
    \odyn    \mid
    \otrue   \mid
    \ofalse  \mid
    \ofunc   \mid
    \ocons   \mid
    \error{l}
}
\stxrule{r}{Cast results}{
    v \mid
    \error{l}
}
\end{array}
\]

\fbox{\valuetyping{v}{T}} Value typing
\begin{gather*}
\dots \qquad
\inference{
	\valuetyping{v}{I}
}{
	\valuetyping{\vdyn{I}{v}}{\Tdyn}
} \\[1ex]
\inference{
	\valuetyping{v}{\Pfunc{S_1}{T_1}}
}{
	\valuetyping{(\vfuncc{v}{S_1}{T_1}{l}{S_2}{T_2})}{\Pfunc{S_2}{T_2}}
} \quad
\inference{
	\valuetyping{v}{\Pprod{S_1}{T_1}}
}{
	\valuetyping{(\vconsc{v}{S_1}{T_1}{l}{S_2}{T_2})}{\Pprod{S_2}{T_2}}
}
\end{gather*}

\fbox{$\proxy{v}{\ccast{S}{l}{T}}=v$}
\[
\begin{array}{rclr}
\figequalto{\proxy{v}{\ccast{\Pbool}{l}{\Pbool}}}{v}{}
\figequalto{\proxy{v}{\ccast{\Pfunc{S_1}{T_1}}{l}{\Pfunc{S_2}{T_2}}}}{
	\vfuncc{v}{S_1}{T_1}{l}{S_2}{T_2}
}{}
\figequalto{\proxy{v}{\ccast{\Pprod{S_1}{T_1}}{l}{\Pprod{S_2}{T_2}}}}{
	\vconsc{v}{S_1}{T_1}{l}{S_2}{T_2}
}{}
\end{array}
\]

\caption{Syntax of a CEK machine \RMachine{B} and auxiliary definitions.}
\label{fig:R-machine-syntax}
\end{figure}

Fig.~\ref{fig:R-machine-dynamics} defines the transition relation of the CEK
machine (\RMachine{B}) and Fig.~\ref{fig:R-machine-syntax} gives a grammar for machine 
states $s$, including a definition of values $v$ and value typing.
%
This machine is parameterized over blame strategy ($B$), which ranges over
Lazy D (Fig.~\ref{fig:blame-strategy-LazyD}) and Lazy UD 
(Fig.~\ref{fig:blame-strategy-LazyD}).
%
The transitions involving casts are highlighted in red and described in
more detail below. The other transitions are standard for a CEK
machine for an extended simply typed lambda calculus.
%
Recall that CEK machines involve two kinds of transitions, (1) those
that dive further into an expression (looking for a redex) and push an
entry onto the continuation, and (2) those that return a value to the
current continuation and possibly perform a computation.
Corresponding to (1) and (2), the machine state is either in an evaluating
$\sexpr{e}{E}{K}$ or returning $\scont{v}{K}$ configuration, 
respectively. Additionally, there are two halting configurations: \shalt{v} 
halts with a value, while \error{l} halts with a blame label. 
Observables include all value constructors and blame labels, as in 
\citep{siek2012interpretations}. 
The function converting values to observables ($observe(v) = o$) is defined in 
the obvious way.

Let $v$ range over values. The 
$\vdyn{I}{v}$ stands for values casted to the dynamic type, as in 
\citep{wadler2009well}. The inner value must be of an 
injectable type. The definition of injectable types depends on blame 
strategies:
%
for the \LD\ strategy, every pre-type is injectable 
(Fig.~\ref{fig:blame-strategy-LazyD});
%
for the \LUD\ strategy, only ground types are injectable 
(Fig.~\ref{fig:blame-strategy-LazyUD}).
%
Other kinds of values are either Boolean constants, functions, casted 
functions, pairs, or casted pairs.
% In earlier version of this work, 
% we were tempted to use a generic constructor for all casted value, and use 
% value typing rules to restrict the cast such that its source and target are 
% shallowly consistent pre-types. This approach unfortunately considers 
% $\ecast{\etrue}{\ccast{\Pbool}{l}{\Pbool}}$ as a value.

The syntax \error{l} occurs several times in the syntax definition, we shall 
view those nonterminals that have \error{l} case as error monads. We use 
the symbol \mbind as the monad bind operator, which is defined as follows:
\[
\begin{array}{rcll}
(\error{l}) \mbind f & = & \error{l} \\
          a \mbind f & = & f(a)      & \text{otherwise}
\end{array}
\]

\begin{figure}
	\fbox{\reducetoR{B}{s}{s}} Transition
	\[
	\begin{array}{rclr}
	\figreduceto{\sexpr{\evar{x}}{E}{K}}{\scont{E(x)}{K}}{}
	\figreduceto{\sexpr{\elam{x}{S}{e}}{E}{K}}{\scont{\vfunc{x}{S}{e}{E}}{K}}{}
	\figreduceto{\sexpr{\eapp{e_1}{e_2}}{E}{K}}{
		\sexpr{e_1}{E}{\Kcons{\FappXO{e_2}{E}}{K}}
	}{}
	\figreduceto{\sexpr{\etrue}{E}{K}}{\scont{\vtrue}{K}}{}
	\figreduceto{\sexpr{\efalse}{E}{K}}{\scont{\vfalse}{K}}{}
	\figreduceto{\sexpr{\eif{e_1}{e_2}{e_3}}{E}{K}}{
		\scont{e_1}{\Kcons{\Fif{e_2}{e_3}{E}}{K}}
	}{}
	\figreduceto{\sexpr{\econs{e_1}{e_2}}{E}{K}}{
		\sexpr{e_1}{E}{\Kcons{\FconsXO{e_2}{E}}{K}}
	}{}
	\figreduceto{\sexpr{\ecar{e}}{E}{K}}{\sexpr{e}{E}{\Kcons{\Fcar}{K}}}{}
	\figreduceto{\sexpr{\ecdr{e}}{E}{K}}{\sexpr{e}{E}{\Kcons{\Fcdr}{K}}}{}
	\figreducetoH{
		\sexpr{\ecast{e}{\ccast{S}{l}{T}}}{E}{K}
	}{
		\sexpr{e}{E}{\Kcons{\Fcast{\ccast{S}{l}{T}}}{K}}
	}{}
	\figreducetoH{\scont{v}{\Kcons{\Fcast{\ccast{S}{l}{T}}}{K}}}{
		\applyCast{v}{\ccast{S}{l}{T}} \; \mbind \; \lambda u. \scont{u}{K}
	}{}
	\figreduceto{\scont{v_1}{\Kcons{\FappXO{e_2}{E}}{K}}}{\sexpr{e_2}{E}{
			\Kcons{\FappOX{v_1}}{K}}
	}{}
	\figreduceto{\scont{v}{\Kcons{\FappOX{\vfunc{x}{S}{e}{E}}}{K}}}{
		\sexpr{e}{E[x:=v]}{K}
	}{}
	\figreducetoH{\scont{v}{\Kcons{\FappOX{(\vfuncc{u}{S_1}{T_1}{l}{S_2}{T_2})}}{K}}}{
		\scont{v}{
			\Kcons{\Fcast{\ccast{S_2}{l}{S_1}}}{
				\Kcons{\FappOX{u}}{
					\Kcons{\Fcast{\ccast{T_1}{l}{T_2}}}{K}}}}
	}{}
	\figreduceto{\scont{\vtrue}{\Kcons{\Fif{e_2}{e_3}{E}}{K}}}{\sexpr{e_2}{E}{K}}{}
	\figreduceto{\scont{\vfalse}{\Kcons{\Fif{e_2}{e_3}{E}}{K}}}{\sexpr{e_3}{E}{K}}{}
	\figreduceto{\scont{v_1}{\Kcons{\FconsXO{e_2}{E}}{K}}}{
		\sexpr{e_2}{E}{\Kcons{\FconsOX{v_1}}{K}}
	}{}
	\figreduceto{\scont{v_2}{\Kcons{\FconsOX{v_1}}{K}}}{
		\scont{\vcons{v_1}{v_2}}{K}
	}{}
	\figreduceto{\scont{\vcons{v_1}{v_2}}{\Kcons{\Fcar}{K}}}{\scont{v_1}{K}}{}
	\figreducetoH{\scont{\vconsc{u}{S_1}{T_1}{l}{S_2}{T_2}}{\Kcons{\Fcar}{K}}}{
		\scont{u}{
			\Kcons{\Fcar}{
				\Kcons{\Fcast{\ccast{S_1}{l}{S_2}}}{K}}}	
	}{}
	\figreduceto{\scont{\vcons{v_1}{v_2}}{\Kcons{\Fcdr}{K}}}{\scont{v_2}{K}}{}
	\figreducetoH{\scont{\vconsc{u}{S_1}{T_1}{l}{S_2}{T_2}}{\Kcons{\Fcdr}{K}}}{
		\scont{u}{
			\Kcons{\Fcdr}{
				\Kcons{\Fcast{\ccast{T_1}{l}{T_2}}}{K}}}	
	}{}
	\figreduceto{\scont{v}{\Knil}}{\shalt{v}}{}
	\end{array}
	\]

	\fbox{\evaltoR{B}{e}{o}} Evaluation
	\[
	\inference{
		\transitivelyreduceto{\sexpr{e}{\emptyset}{\Knil}}{\shalt{v}}
	}{
		\evalto{e}{observe(v)}
	} \quad
	\infr{
		\transitivelyreduceto{\sexpr{e}{\emptyset}{\Knil}}{\error{l}}
	}{
		\evalto{e}{\error{l}}}
	\]
	\caption{Dynamic semantics of the cast calculi as a CEK
		machine \RMachine{B}. The transitions that involve casts are highlighted
		in red.}
	\label{fig:R-machine-dynamics}
\end{figure}

The transition relation \reduceto{s}{s} invokes the cast application function, 
noted as $\applyCast{v}{\ccast{S}{l}{T}}$ to allow for the differences 
between blame strategies (Fig.~\ref{fig:blame-strategy-LazyD} and 
Fig.~\ref{fig:blame-strategy-LazyUD}).
%
When evaluating a cast expression, the machine moves the cast to the
continuation and evaluates the inner expression.
%
To cast a value, the machine invokes the cast application function on the 
value. The cast result is either a value or an error (\error{l}). If the cast 
succeeds, the machine returns the value to the next continuation.  If the cast 
fails, the machine halts with the blame label.
%
To apply a casted function, the machine first casts the argument $v$, then
applies the inner function $u$ to the casted argument, and finally
casts the return value.
%
To take out the first part of a casted pair, the machine takes out the 
first part of the inner pair $u$ and cast it.
%
Taking out the second part is similar.

The reflexive transitive closure of reduction (\transitivelyreduceto{s}{s}) 
and evaluation (${\evalto{e}{o}}$) are standard~\citep{felleisen03:_pllc}.

\begin{figure}
\[
\begin{array}{lrcl}
\stxrule{I,J}{Injectable types}{P}
\end{array}
\]

\fbox{$\mathit{applyCast}_{\BLD}(v,\ccast{S}{l}{T}) = r$}
\[
\begin{array}{rclr}
\figequalto{
	applyCast(v,\ccast{\Tdyn}{l}{\Tdyn})
}{
	\just{v}
}{}
\figequalto{
applyCast(v,\ccast{P}{l}{\Tdyn})
}{
	\just{\vdyn{P}{v}}
}{}
\figequalto{
	applyCast(\vdyn{P}{u},\ccast{\Tdyn}{l}{Q})
}{
	applyCast(u,\ccast{P}{l}{Q})
}{}
\figequalto{
	applyCast(v,\ccast{P}{l}{Q})
}{
	\just{\proxy{v}{\ccast{P}{l}{Q}}}
}{\sidecond{\shallowlyconsistent{P}{Q}}}
\figequalto{
	applyCast(v,\ccast{P}{l}{Q})
}{
	\error{l}
}{\sidecond{\notshallowlyconsistent{P}{Q}}}
\end{array}
\]
\caption{The \LD\ blame strategy (\BLD)}
\label{fig:blame-strategy-LazyD}
\end{figure}

\begin{definition}[\LD\ CEK Machine, \LDMachine]
The \LD\ CEK machine, written \LDMachine, is the CEK machine of
\figref{fig:R-machine-dynamics} using the \BLD\ blame strategy defined in 
\figref{fig:blame-strategy-LazyD}.  We write the transition relations of
this machine as \reducetoD{s}{s} and \transitivelyreducetoD{s}{s}
and the evaluator as \evaltoD{e}{o}.
\end{definition}

We conjecture that \LDMachine\ agrees with the \LD\ cast calculus
of \citep{siek2009exploring}.

\begin{proposition}[\LDMachine\ is deterministic]
	If \reducetoD{s}{s_1} and \reducetoD{s}{s_2} then $s_1 = s_2$.
\end{proposition}

Next, we define the CEK Machine for \LUD. The only differences with
respect to \LD\ are in the injectable types and in the definition of the 
${\mathit{applyCast}(v,\ccast{S}{l}{T})}$
function, in which a cast whose source or target is the dynamic type
\Tdyn\ is always split into two casts that go through a ground type, that is, a 
type in which all sub-components are the dynamic type, such as 
\Pfunc{\Tdyn}{\Tdyn}.
\begin{definition}[\LUD\ CEK Machine]
	The \LUD\ CEK machine, written \LUDMachine\, is the CEK machine of
	\figref{fig:R-machine-dynamics} using the \BLUD\ blame strategy defined in 
	\figref{fig:blame-strategy-LazyUD}.  We write the transition relations of
	this machine as \reducetoUD{s}{s} and \transitivelyreducetoUD{s}{s}
	and the evaluator as \evaltoUD{e}{o}.
\end{definition}

\begin{figure}
\[
\begin{array}{lrcl}
\stxrule{I,J}{Injectable types}{G}
\end{array}
\]

	\fbox{$\mathit{applyCast}_{\mathtt{\BLUD}}(v,\ccast{S}{l}{T}) = r$}
	\[
	\begin{array}{rclr}
	\mathit{applyCast}(v, \ccast{\Tdyn}{l}{\Tdyn}) &=& \just{v} \\
	\mathit{applyCast}(v, \ccast{G}{l}{\Tdyn}) &=&
	\just{\vdyn{G}{v}} \\
	\mathit{applyCast}(v, \ccast{P}{l}{\Tdyn}) &=&
	\just{\vdyn{G}{\proxy{v}{\ccast{P}{l}{G}}}}
	& \text{if } G \sim P, G \neq P \\  
	\mathit{applyCast}(\vdyn{G}{u}, \ccast{\Tdyn}{l}{H}) &=&          
	\project{u}{G}{l}{H}\\
	\mathit{applyCast}(\vdyn{G}{u}, \ccast{\Tdyn}{l}{Q}) &=&
	\project{u}{G}{l}{H} \mbind \lambda v. \proxy{v}{\ccast{H}{l}{Q}}
	& \text{if } H \sim Q, H \neq Q \\
	\mathit{applyCast}(v, \ccast{P}{l}{Q}) &=&
	\just{\proxy{v}{\ccast{P}{l}{Q}}}
	& \text{if } P \smile Q \\
	\mathit{applyCast}(v, \ccast{P}{l}{Q}) &=&
	\error{l}
	& \text{if } P \not\smile Q
	\end{array}
	\]

	\fbox{$\project{v}{G}{l}{H}=r$}
	\[
	\begin{array}{rclr}
	\figequalto{\project{v}{G}{l}{G}}{v}{}
	\figequalto{\project{v}{G}{l}{H}}{\error{l}}{\sidecond{G \neq H}}
	\end{array}
	\]

\caption{The \LUD\ blame strategy (\BLUD)}
	\label{fig:blame-strategy-LazyUD}
\end{figure}

We conjecture that \LUDMachine\ agrees with the \LUD\ cast
calculus of \citep{siek2009exploring}.

\begin{proposition}[\LUDMachine\ is deterministic]
	If $\reducetoUD{s}{s_1}$ and $\reducetoUD{s}{s_2}$ 
	then $s_1 = s_2$.
\end{proposition}

\subsection{Coercions and Normal Forms} 
\label{sec:coercion-calculus}

In this section, we review the
coercions~\citep{henglein1994dynamic,herman2010space} and the normal form of
\citet{siek2012interpretations} to motivate the design of hypercoercions.  We
omit sum types and product types in this section because
\citet{siek2012interpretations} did not discuss them. We assume a basic
familiarity with coercions, and suggest that readers unfamiliar with coercions
to familiarize themselves with \citet{siek2012interpretations} and
\citet{Siek:2015:BCT:2737924.2737968}.

\begin{figure}
	\[
	\begin{array}{lrcl}
	\stxrule{I,J}{Injectable types (\LD)}{
		\Pfunc{T}{T} \mid \Pbool}
	\stxrule{I,J}{Injectable types (\LUD)}{
		\Pfunc{\Tdyn}{\Tdyn} \mid \Pbool
	}
	\stxrule{c,d}{Coercions}{
		\cnfid{T}       \mid
		\cnffunc{c}{d}  \mid
		\cnfprod{c}{d}  \mid
		\cnffail{l}     \mid
		\cnfinj{I}      \mid
		\cnfproj{I}{l}  \mid
		\cnfseq{c}{d}
	}
	\stxrule{s,t}{Coercions in normal form}{
		\cnfid{\Tdyn}       \mid
		\cnfseq{\cnfproj{I}{l}}{i} \mid
		i
	}
	\stxrule{i}{Final Coercions}{
		\cnffail{l} \mid
		\cnfseq{g}{\cnfinj{I}} \mid
		g
	}
	\stxrule{g}{Middle Coercions}{
		\cnfid{\Pbool} \mid
		\cnffunc{s}{t} \mid
		\cnfprod{s}{t}
	}
	\end{array}
	\]
	\caption{Syntax of coercions and normal forms {\`a} la 
		\citep{siek2012interpretations}.}
	\label{fig:normal-coercion}
\end{figure}

\figref{fig:normal-coercion} reviews the grammar for coercions,
written $c$.
%
To review, an injection $\cnfinj{I}$ takes a value from an injectable type
$I$ to type $\Tdyn$. An injectable type is simply a type that can be
cast directly to and from $\Tdyn$. The
definition of injectable types depends on the blame strategy, as in 
Chapter~\ref{chap:background}.
%
A projection $I?^l$ takes a value from type $\Tdyn$ to type $I$, or
halts the program and blames $l$ if the value is inconsistent with 
the target type.
The coercion \cnfid{T} is the identity, $\bot^{l}$ is the coercion that
always fails and blames $l$, and $(\cnfseq{c}{d})$ applies $c$ and
then $d$ in sequence. The function coercion $\cnffunc{c}{d}$
applies $c$ to the argument of a function and $d$ to the return
value.

Coercions come with a reduction relation so it is natural to ask about
their normal forms. \figref{fig:normal-coercion} defines the syntax of
coercion in normal form, written $\hat{c}$. Conceptually, a coercion
in normal form has three parts, all of which are optional.  It may
start with a projection $I?^l$, followed by a function coercion, and
then concluded with an injection $I!$ or a failure $\bot^l$. While
this is a simple idea, there are 10 clauses in the definition for
$\hat{c}$!

\section{A Framework for Proving Correctness of Cast ADTs}
\label{sec:framework}

% All cast representation shall be proved correct, that is, besides reducing 
% space consumption, using a cast representation should not affect the results of 
% program execution.
In this section we present a framework for proving the 
correctness of cast representations. The framework includes an abstract data 
type named Cast ADT, which specifies the operators of cast representations, 
a CEK machine $\SMachine{C}$, which uses the cast operators implemented by 
$C$ to work with casts, and theorems relating $\SMachine{C}$ to $\RMachine{B}$.
%
Subsection~\ref{sec:cast-adt-and-space-efficient-cek} describes Cast ADT and the 
machine \SMachine{C}. We conjecture that the machine \SMachine{C} is 
space-efficient provided that the cast representation $C$ performs compression.
%
Subsection~\ref{sec:good-cast-adt} defines two subset of Cast ADT, namely Lazy D 
Cast ADT and Lazy UD Cast ADT. As their names suggest, if $C$ is a Lazy D Cast 
ADT, executing a program in $\SMachine{C}$ would give the same result as in 
$\LDMachine$. Similarly, if $C$ is a Lazy UD Cast ADT, executing a program in 
$\SMachine{C}$ would give the same result as in $\LUDMachine$.
%
We prove the theorems relating \SMachine{C} and \RMachine{B} in
Subsection~\ref{sec:S-correct}.
The framework is written in the Agda language~\citep{norell2008dependently}.

%In Section~\ref{chap:background} we have seen that the standard dynamic 
%semantic of the cast calculi has a space-efficiency problem 
%(Section~\ref{sec:space-efficiency-problem}): casts might accumulate in 
%higher-order values and continuations and consume unbounded space. The 
%solution 
%is space-efficient cast representations, such as coercions in normal form and 
%threesomes.
%%
%Every such cast representations shall be proved correct. Actually, 
%people have done such proofs several times, such as the \emph{Correctness of 
%the threesome calculus} in \citep{Siek:2010:TWB:1706299.1706342} and the 
%bisimulation theorems in \citep{Siek:2015:BCT:2737924.2737968}.
%%
%These theorems are similar -- conceptually the only difference is the cast 
%representation.
%%
%But having two proofs blurs the similarity between the proofs and the key 
%differences between cast representations. 
%%
%Furthermore, there might be more cast representations in the future.
%Actually we introduce a new one in Section~\ref{chap:hypercoercions}.
%%
%Consequently, it is desirable to have generic proofs that handles many cast 
%representations that implement a common interface.
%
%Our solution is an abstract data type (Cast ADT), which specifies the 
%operators 
%of cast representations and a CEK machine ($\SMachine{C}$) parameterized over 
%Cast ADT (Section~\ref{sec:cast-adt-and-space-efficient-cek}). Then we 
%prove that if $C$ is a Lazy D Cast ADT then \SMachine{C} is equivalent to 
%\LDMachine, and that if $C$ is a Lazy UD Cast ADT then \SMachine{C} is 
%equivalent to \LUDMachine.
%%
%We conjecture that the machine \SMachine{C} is space-efficient provided that 
%the cast representation $C$ performs compression. We will prove or 
%conjecture that all cast representations defined 
%in the literature are instances of this ADT. 
%In \secref{sec:LazyD-correct} we prove that, for any
%instance $C$ of the Cast ADT, if $C$ satisfies a more refined abstract
%data type for Lazy D casts, then \SMachine{C} is equivalent to
%\LDMachine, that is, 
%\[
%\machineequiv{\LDMachine}{\SMachine{C}}
%\]
%In Section~\ref{sec:LazyUD-correct} we prove a corresponding \LUD\ theorem, 
%that is, for any instance $C$ of the Cast ADT, if $C$ satisfies a more refined 
%abstract data type for \LUD\ casts
%\[
%\machineequiv{\LUDMachine}{\SMachine{C}}
%\]
%
%Finally, we prove that some cast representations in 
%the literature (\LD\ and \LUD\ coercions in normal form, and \LUD\ threesomes) 
%are either instances of the Lazy D Cast ADT or the Lazy UD Cast ADT 
%(\secref{sec:coercions-correct} and \secref{sec:threesomes-correct}).
%We conjecture that supercoercions also fit into the two category.

\subsection{Cast Abstract Data Type and a Space-efficient CEK Machine}
\label{sec:cast-adt-and-space-efficient-cek}

\begin{figure}
	\[
	\begin{array}{lrcl}
	\stxrule{c,d}{Runtime casts}{\text{a data type defined by the 
	instance of Cast ADT}}
	\stxrule{v,u}{Values}{
		\vdyn{I}{v}  \mid
		\vtrue       \mid
		\vfalse                     
	}
	\stxrulecont{
		\ecast{\vfunc{x}{S}{e}{E}}{\Pfunc{c}{c}} \mid
		\ecast{\vcons{v}{v}}{\Pprod{c}{c}}
	}
	\stxrule{I,J}{Injectable types (\LD)}{P}
	\stxrule{I,J}{Injectable types (\LUD)}{G}
	\stxrule{E}{Environments}{
		\text{a partial function}\;\{\langle x , v \rangle , \dots \}
	}
	\stxrule{F}{Frames}{
		\FappXO{e}{E}  \mid
		\FappOX{v}     \mid
		\Fcar          \mid
		\Fcdr
	}
	\stxrulecont{
		\FconsXO{e}{E}  \mid
		\FconsOX{v}
	}
	\stxrule{K}{Continuations}{
		\Kcons{\Fcast{c}}{k}
	}
	\stxrule{k}{Pre-continuations}{
		\Knil         \mid
		\Kcons{F}{K}
	}
	\stxrule{s}{States}{
		\sexpr{e}{E}{K}  \mid
		\scont{v}{K}     \mid
		\shalt{v}        \mid
		\error{l}
	}
	\stxrule{r}{Cast results}{
		v \mid
		\error{l}
	}
	\end{array}
	\]

	\caption{Syntax of the space-efficient machine \SMachine{C} and auxiliary 
	data structures.}
	\label{fig:SEMachine-state}
\end{figure}

\figref{fig:SEMachine-state} defines the syntax of the space-efficient CEK 
machine (\SMachine{C}). This machine is parameterized over Cast ADT $C$.
%
The key differences between \SMachine{C} and the \RMachine{B} machine are the 
places where casts can accumulate~(\secref{sec:space-efficiency-problem}), that 
is, values and continuations.

Let $u,v$ range over values.
%
Recall that in \RMachine{B} we have two value constructors for functions and 
another two for pairs. That setup allows zero-or-more layers of casts at the 
top of higher-order values, which might lead to space inefficiency. 
%
In \SMachine{C}, we instead have exactly one layer of cast. 
Thus non-casted values in \RMachine{B} correspond to values 
in \SMachine{C} where casts are identities ($\mathit{id}(T)$). The 
$\mathit{id}$ functions is provided by the Cast ADT.

Let $K$ ranges over continuations and $k$ ranges over pre-continuations.
%
Pre-continuations are like the continuations in \RMachine{B}, but their 
top-most frame must not be a cast frames.
%
A continuation is now a pre-continuation prefixed with a cast frame.
%
Recall that continuations in \RMachine{B} have zero or more casts at the top.
In \SMachine{C}, however, every continuation has exactly one cast at the 
top.
%
Continuations in \RMachine{B} that have no casts at the top correspond
to continuations in \SMachine{C}\ whose casts are identities constructed by 
$\id{T}$.
Continuations in \RMachine{B} that have many casts at the top 
correspond
to continuations in \SMachine{C}\ where those casts are composed by
$\compose{c}{c}$, another functions provided by the Cast ADT.
%
Injectable types ($I,J$), environments ($\mathcal{E}$), states ($s$), and cast 
results ($r$) are the same as in \RBMachine.

Value typing (\valuetyping{v}{T}), continuation typing 
(\casttyping{k}{S}{T} and \casttyping{K}{S}{T}), and environment typing 
(\envtyping{\Gamma}{E}) are defined in the obvious way. 
They rely on cast typing \casttyping{c}{S}{T}, which shall be provided by the 
Cast~ADT.

\begin{definition}[Cast Abstract Data Type (Cast ADT)]
	\label{def:cast-rep}
	A cast abstract data type is a set $Cast$, which is indexed by two types, 
	with four operators and two properties of operators:
\begin{itemize}
	\item $id(T)=c$: create an identity cast
	\item $\compose{c}{c}=c$: compose casts
	\item $\translate{\ccast{S}{l}{T}}=c$: translate cast in source 
		program to runtime casts
	\item $\denote{c}(v)=r$: apply a cast to a value
	\item If $ \valuetyping{v}{T} $ then $\denote{\id{T}}(v)=v$
	\item If $ \valuetyping{v}{T_1} $ and
		$ \casttyping{c}{T_1}{T_2} $ and
		$ \casttyping{d}{T_2}{T_3} $ 
		then 
		$ \denote{\compose{c}{d}}(v) = (\denote{c}(v)\mbind\denote{d})$
\end{itemize}
We use the syntax \casttyping{c}{S}{T} to mean $c$ is in the set 
$\textit{Cast}_{S,T}$.
\end{definition}

Before moving to the transition relation of \SMachine{C}, let's define two 
helper functions that manipulate continuations.
%
The function $\mathit{mkCont}$ construct a continuation from a pre-continuation 
by topping the pre-continuation with an identity cast. 
%
The function $\mathit{extCont}$ composes $c$ with the cast at the top of $K$ by 
using the composition operator 
$\fatsemi$.
\[
\begin{array}{rclr}
\figequalto{\mkCont{k}}{\Kcons{\Fcast{\id{S}}}{k}}{\sidecond{\casttyping{k}{S}{T}}}
\figequalto{\extCont{c}{\Kcons{\Fcast{d}}{k}}}{
	\Kcons{\Fcast{(\compose{c}{d})}}{k}
}{}
\end{array}
\]

\begin{figure}
	\fbox{\reducetoS{C}{s}{s}} Transition
	\[
	\begin{array}{rclr}
	\figreduceto{\sexpr{\evar{x}}{E}{K}}{\scont{E(x)}{K}}{}
	\figreducetoH{
		\sexpr{\elam{x}{S}{e}}{E}{K}
	}{
		\scont{\ecast{\vfunc{x}{S}{e}{E}}{\Pfunc{id(S)}{id(T)}}}{K}
	}{}
	& &
	\highlight{
	\sidecond{
		\expressiontyping{\Gamma,S}{e}{T}
		\text{ and }
		\Gamma \vdash E}
	}
	\\
	\figreduceto{\sexpr{\eapp{e_1}{e_2}}{E}{K}}{
		\sexpr{e_1}{E}{\mkCont{\Kcons{\FappXO{e_2}{E}}{K}}}
	}{}
	\figreduceto{\sexpr{\etrue}{E}{K}}{\scont{\vtrue}{K}}{}
	\figreduceto{\sexpr{\efalse}{E}{K}}{\scont{\vfalse}{K}}{}
	\figreduceto{\sexpr{\eif{e_1}{e_2}{e_3}}{E}{K}}{
		\sexpr{e_1}{E}{\mkCont{\Kcons{\Fif{e_2}{e_3}{E}}{K}}}
	}{}
	\figreduceto{\sexpr{\econs{e_1}{e_2}}{E}{K}}{
		\sexpr{e_1}{E}{\mkCont{\Kcons{\FconsXO{e_2}{E}}{K}}}
	}{}
	\figreduceto{\sexpr{\ecar{e}}{E}{K}}{
		\sexpr{e}{E}{\mkCont{\Kcons{\Fcar}{K}}}
	}{}
	\figreduceto{\sexpr{\ecdr{e}}{E}{K}}{
		\sexpr{e}{E}{\mkCont{\Kcons{\Fcdr}{K}}}
	}{}
	\figreducetoH{
		\sexpr{\ecast{e}{\ccast{S}{l}{T}}}{E}{K}
	}{
		\sexpr{e}{E}{\extCont{\translate{\ccast{S}{l}{T}}}{K}}
	}{}
	\figreducetoH{\scont{v}{\Kcons{\Fcast{c}}{k}}}{
		\denote{c}(v) \; \mbind \; \lambda u. \applyCont{u}{K}
	}{}
	\end{array}
	\]

	\fbox{$\applyCont{v}{k}=s$}
	\[
	\begin{array}{rclr}
	\figequalto{\applyCont{v_1}{\Kcons{\FappXO{e_2}{E}}{K}}}{\sexpr{e_2}{E}{
			\mkCont{\Kcons{\FappOX{v_1}}{K}}}
	}{}
	\figequaltoH{
		\applyCont{v}{\Kcons{\FappOX{(\ecast{\vfunc{x}{S}{e}{E}}{\Pfunc{c}{d}})}}{K}}
	}{
		\denote{c}(v) \mbind \lambda u. \
		\sexpr{e}{E[x:=u]}{\extCont{d}{K}}
	}{}
	\figequalto{\applyCont{\vtrue}{\Kcons{\Fif{e_2}{e_3}{E}}{K}}}{\sexpr{e_2}{E}{K}}{}
	\figequalto{\applyCont{\vfalse}{\Kcons{\Fif{e_2}{e_3}{E}}{K}}}{\sexpr{e_3}{E}{K}}{}
	\figequalto{\applyCont{v_1}{\Kcons{\FconsXO{e_2}{E}}{K}}}{
		\sexpr{e_2}{E}{\mkCont{\Kcons{\FconsOX{v_1}}{K}}}
	}{}
	\figequaltoH{\applyCont{v_2}{\Kcons{\FconsOX{v_1}}{K}}}{
		\scont{\ecast{\vcons{v_1}{v_2}}{\Pprod{\id{T_1}}{\id{T_2}}}}{K}
	}{}
	& & 
	\highlight{\sidecond{
%		\casttyping{K}{\Pprod{T_1}{T_2}}{T'}
		\valuetyping{v_1}{T_1}
		\text{ and }
		\valuetyping{v_2}{T_2}
	}}
	\\
	\figequaltoH{
		\applyCont{\ecast{\vcons{v_1}{v_2}}{\Pprod{c_1}{c_2}}}{\Kcons{\Fcar}{K}}
	}{
		\denote{c_1}(v_1) \mbind \lambda u.
		\scont{u}{K}
	}{}
	\figequaltoH{
		\applyCont{\ecast{\vcons{v_1}{v_2}}{\Pprod{c_1}{c_2}}}{\Kcons{\Fcdr}{K}}
	}{
		\denote{c_2}(v_2) \mbind \lambda u.
		\scont{u}{K}
	}{}
	\figequalto{\applyCont{v}{\Knil}}{\shalt{v}}{}
	\end{array}
	\]

	\fbox{\evalto{e}{o}} Evaluation
	\[
	\inference{
		\transitivelyreduceto{\sexpr{e}{\emptyset}{\mkCont{\Knil}}}{\shalt{v}}
	}{
		\evalto{e}{observe(v)}
	} \quad
	\infr{
		\transitivelyreduceto{\sexpr{e}{\emptyset}{\Knil}}{\error{l}}
	}{
		\evalto{e}{\error{l}}}
	\]
	\caption{Dynamic semantics of the cast calculi as a 
	space-efficient CEK	machine, \SMachine{C}. The transitions that involve 
	casts are highlighted
		in red.}
	\label{fig:semachine-dynamics}
\end{figure}

\figref{fig:semachine-dynamics} defines the transition relation 
$\reducetoS{C}{s}{s}$. They rely on functions provided 
by $C$ to work with casts.
%
To construct a function, the machine fills the casts with identities.
%
When evaluating a cast expression, the machine extends the continuation with 
cast \translate{\ccast{S}{l}{T}}.
%
To return a value to a continuation, the machine first applies the top cast to 
the value. If the cast application fails, the machine halts with the blame 
label from the failure. Otherwise, the machine handles the pre-continuation 
with the function $\applyCont{v}{k}$.
%
To apply a function, the machine applies the domain cast $c$ to the 
argument $v$ and evaluates the function body. The codomain cast $d$ is merged 
into the continuation with $\textit{extCont}$.
%
When the machine constructs a pair, it fills the casts with $id$s, just 
like how it did for functions. 
%
To take out the first part of a pair, the machine applies the first pending 
cast on the first value and returns the result to the continuation.
%
Taking out the second part of a pair is similar.

Reflexive transitive closure of reduction ($\reducetoS{C}{s}{s}$) and
evaluation ($\evaltoS{C}{e}{o}$) are the same as in \RMachine{B}.

\begin{proposition}[\SMachine{C} is deterministic]
	\label{prop:SEMachine-deterministic}
	If $\reducetoS{C}{s}{s_1}$ and $\reducetoS{C}{s}{s_2}$ 
	then $s_1 = s_2$.
\end{proposition}

\subsection{Specifying good instances of Cast ADT}
\label{sec:good-cast-adt}

Ultimately, we want to claim that if a $C$ satisfies a collection of 
properties, \SMachine{C} would be equivalent to \LDMachine\ or \LUDMachine. 
Cast ADT has specified the behavior of identities and composition, so the only 
remaining operator is translation.
%
Lazy D Cast ADT (Definition~\ref{def:LazyD-CastADT}) and Lazy UD Cast ADT 
(Definition~\ref{def:LazyUD-CastADT}) specify the behavior 
of \translate{\ccast{S}{l}{T}}. Readers are encouraged to compare them with the 
corresponding $\mathit{applyCast}$ functions 
(Fig.~\ref{fig:blame-strategy-LazyD} and 
Fig.~\ref{fig:blame-strategy-LazyUD}).

\begin{definition}[Lazy D Cast ADT]
	\label{def:LazyD-CastADT}
	A Cast is a Lazy D Cast if:
	\begin{enumerate}
		\item $\denote{\translate{\ccast{\Tdyn}{l}{\Tdyn}}}(v) = v$
		\item $\denote{\translate{\ccast{P}{l}{\Tdyn}}}(v) = \vdyn{P}{v}$
		\item $\denote{\translate{\ccast{\Tdyn}{l}{Q}}}(\vdyn{P}{u}) = 
		\denote{\translate{\ccast{P}{l}{Q}}}(u)$
		\item $\denote{\translate{\ccast{\Pbool}{l}{\Pbool}}}(v) = v$
		\item 
		$\denote{\translate{\ccast{\Pfunc{S_1}{T_1}}{l}{\Pfunc{S_2}{T_2}}}}(
			\ecast{\vfunc{x}{S}{e}{E}}{\Pfunc{c}{d}})$\\
		$=
		\ecast{\vfunc{x}{S}{e}{E}}{
			\Pfunc{
				(\compose{\translate{\ccast{S_2}{l}{S_1}}}{c})}{
				(\compose{d}{\translate{\ccast{T_1}{l}{T_2}}})}}$
		\item 
		$\denote{\translate{\ccast{\Pprod{S_1}{T_1}}{l}{\Pprod{S_2}{T_2}}}}(
		\ecast{\vcons{v_1}{v_2}}{\Pprod{c}{d}})$\\
		$=
		\ecast{\vcons{v_1}{v_2}}{
			\Pprod{
				(\compose{c}{\translate{\ccast{S_1}{l}{S_2}}})}{
				(\compose{d}{\translate{\ccast{T_1}{l}{T_2}}})}}$
		\item $\denote{\translate{\ccast{P}{l}{Q}}}(v) = \error{l}$\\
			if $\notshallowlyconsistent{P}{Q}$
	\end{enumerate}
\end{definition}

\begin{definition}[Lazy UD Cast ADT]
	\label{def:LazyUD-CastADT}
	A Cast is a Lazy UD Cast if:
	\begin{enumerate}
	\item $\denote{\translate{\ccast{\Tdyn}{l}{\Tdyn}}}(v) = v$
	\item $\denote{\translate{\ccast{G}{l}{\Tdyn}}}(v) = \vdyn{G}{v}$
	\item $\denote{\translate{\ccast{P}{l}{\Tdyn}}}(v) = 
		\denote{\translate{\ccast{P}{l}{G}}}(v) \mbind 
		\denote{\ccast{G}{l}{\Tdyn}}$\\
		if $G \sim P$ and $G \neq P$	
	\item $\denote{\translate{\ccast{\Tdyn}{l}{G}}}(\vdyn{G}{u}) = u$
	\item $\denote{\translate{\ccast{\Tdyn}{l}{H}}}(\vdyn{G}{u}) = \error{l}$\\
		if $G \neq H$
	\item $\denote{\translate{\ccast{\Tdyn}{l}{Q}}}(v) = 
		\denote{\translate{\ccast{\Tdyn}{l}{H}}}(v) \mbind
		\denote{\translate{\ccast{H}{l}{Q}}}$\\
		if $H \sim Q$ and $H \neq Q$
	\item $\denote{\translate{\ccast{\Pbool}{l}{\Pbool}}}(v) = v$
		\item 
		$\denote{\translate{\ccast{\Pfunc{S_1}{T_1}}{l}{\Pfunc{S_2}{T_2}}}}(
		\ecast{\vfunc{x}{S}{e}{E}}{\Pfunc{c}{d}})$\\
		$=
		\ecast{\vfunc{x}{S}{e}{E}}{
			\Pfunc{
				(\compose{\translate{\ccast{S_2}{l}{S_1}}}{c})}{
				(\compose{d}{\translate{\ccast{T_1}{l}{T_2}}})}}$
		\item 
		$\denote{\translate{\ccast{\Pprod{S_1}{T_1}}{l}{\Pprod{S_2}{T_2}}}}(
		\ecast{\vcons{v_1}{v_2}}{\Pprod{c}{d}})$\\
		$=
		\ecast{\vcons{v_1}{v_2}}{
			\Pprod{
				(\compose{c}{\translate{\ccast{S_1}{l}{S_2}}})}{
				(\compose{d}{\translate{\ccast{T_1}{l}{T_2}}})}}$
		\item $\denote{\translate{\ccast{P}{l}{Q}}}(v) = \error{l}$\\
			if $\notshallowlyconsistent{P}{Q}$
	\end{enumerate}
\end{definition}

\subsection{The Space-efficient CEK Machine is Correct}
\label{sec:S-correct}

In this section, we prove that if $C$ is a Lazy D Cast ADT then
\[
\machineequiv{\LDMachine}{\SMachine{C}}
\]
and if $C$ is a Lazy UD Cast ADT then
\[
\machineequiv{\LUDMachine}{\SMachine{C}}
\]
The proof is done via a weak bisimulation.

\begin{figure}

\fbox{\bisimc{\overline{\ccast{S}{l}{T}}}{c}{S}{T}}
\begin{gather*}
\infr{}{\bisimc{[]}{id(T)}{T}{T}} \quad
\infr{}{\bisimc{[\ccast{S}{l}{T}]}{\translate{\ccast{S}{l}{T}}}{S}{T}}
\\[1ex]
%\infr{
%	\bisimc{z_1}{c_1}{T_1}{T_2}\\
%	\bisimc{z_2}{c_2}{T_2}{T_3}
%}{
%	\bisimc{(z_1 + z_2)}{(\compose{c_1}{c_2})}{T_1}{T_n}
%}
\infr{
	\bisimc{
		(\ccast{T_1}{l_1}{T_2}\ldots\ccast{T_{i-1}}{l_{i-1}}{T_i})
	}{c_1}{T_1}{T_i}\\
	\bisimc{
		(\ccast{T_i}{l_i}{T_{i+1}}\ldots\ccast{T_{n-1}}{l_{n-1}}{T_n})
	}{c_2}{T_i}{T_n}
}{
	\bisimc{
		(\ccast{T_1}{l_1}{T_{2}}\ldots\ccast{T_{n-1}}{l_{n-1}}{T_n})
	}{
		(\compose{c_1}{c_2})
	}{T_1}{T_n}
}
\end{gather*}

\fbox{$\bisimK{K}{K}{S}{T}$}
\begin{gather*}
\infr{
	\bisimK{K}{k'}{S_n}{T} \qquad
	\bisimc{
		(\ccast{S_1}{l_1}{S_2} \ldots \ccast{S_{n-1}}{l_{n-1}}{S_n})
	}{c}{S_1}{S_n}
}{
	\bisimK{
		\Kcons{
			\Fcast{\ccast{S_1}{l_1}{S_2}}
		}{\ldots\Kcons{\Fcast{\ccast{S_{n-1}}{l_{n-1}}{S_n}}}{K}}
	}{
		\Kcons{\Fcast{c'}}{k'}
	}{S_1}{T}
}
\end{gather*}

\fbox{$\bisimv{v}{v}{T}$}
\begin{gather*}
\infr{
	\expressiontyping{\Gamma,x : S_1}{e}{T_1}
	\qquad
	\bisimE{\Gamma}{E}{E'}
	\\
	\bisimc{
		(\ccast{S_n}{l_{n-1}}{S_{n-1}} \ldots
		\ccast{S_2}{l_1}{S_1})
	}{c}{S_n}{S_1}
	\\
	\bisimc{
		(		\ccast{T_1}{l_{1}}{T_2} \ldots
		\ccast{T_{n-1}}{l_{n-1}}{T_n}
		)	}{d}{T_1}{T_n}
	\\
	v = \vfuncc{
		\vfuncc{
			\vfunc{x}{S_1}{e}{E}
		}{S_1}{T_1}{l_1}{S_2}{T_2}
		\ldots
	}{S_{n-1}}{T_{n-1}}{l_{n-1}}{S_n}{T_n}
}{
	\bisimv{v}{
		(\ecast{\vfunc{x}{S_1}{e}{E'}}{\Pfunc{c}{d}})
	}{
		\Pfunc{S_n}{T_n}}
}
\\[1ex]
\infr{
	\bisimv{v_1}{v_1'}{S_1} \qquad
	\bisimv{v_2}{v_2'}{T_1} \\
	\bisimc{
		(\ccast{S_1}{l_{1}}{S_2} \ldots
		\ccast{S_{n-1}}{l_{n-1}}{S_n})
	}{c}{S_1}{S_n} \\
	\bisimc{
		(\ccast{T_1}{l_{1}}{T_2} \ldots
		\ccast{T_{n-1}}{l_{n-1}}{T_n})
	}{d}{T_1}{T_n}
	\\ v = \vconsc{
		\vconsc{
			\vcons{v_1}{u_1}
		}{S_1}{T_1}{l_1}{S_2}{T_2}
		\ldots
	}{S_{n-1}}{T_{n-1}}{l_{n-1}}{S_n}{T_n}
}{
	\bisimv{
		v
	}{
		(\ecast{\vcons{v_2}{u_2}}{\Pprod{c}{d}})
	}{
		\Pprod{S_n}{T_n}}
}
\end{gather*}

\fbox{\bisimE{\Gamma}{E}{E}}
\begin{gather*}
\inference{
}{
	\bisimE{\emptyset}{\emptyset}{\emptyset}
}
\quad
\inference{
	\Gamma \vdash E \approx E' \qquad
	v \approx v' : T
}{
	\Gamma , x : T \vdash 
	E [ x := v' ] \approx E' [ x := v' ]
}
\end{gather*}

\fbox{\bisims{s}{s}{T}}
\begin{gather*}
\infr{}{\bisims{\error{l}}{\error{l}}{T}} \quad
\infr{
	\bisimv{v}{v'}{T}
}{
	\bisims{\shalt{v}}{\shalt{v'}}{T}
}
\\
\infr{
	\bisimv{v}{v'}{S} \\
	\bisimK{K}{K'}{S}{T}
}{
	\bisims{\scont{v}{K}}{\scont{v}{K'}}{T}
} \quad
\infr{
	\expressiontyping{\Gamma}{e}{S} \\
	\bisimE{\Gamma}{E}{E'}          \\
	\bisimK{K}{K'}{S}{T}
}{
	\bisims{\sexpr{e}{E}{K}}{\sexpr{e}{E'}{K'}}{T}
}
\end{gather*}

\caption{Bisimulation between \RBMachine\ and \SMachine{C}. It is the smallest 
congruence relation containing the shown rules. Everything to the left (resp. 
right) of the 
symbol $\approx$ is in \RBMachine\ (resp. \SMachine{C}).}
\label{fig:bisim-SC-D}
\end{figure}

Fig.~\ref{fig:bisim-SC-D} defines the bisimulation relation between \RBMachine\ 
and \SMachine{C}. It is the smallest congruence relation containing the rules 
in Fig.~\ref{fig:bisim-SC-D}.
%
The relation $\bisimc{\overline{\ccast{S}{l}{T}}}{c}{S}{T}$ relates a sequence 
of cast in \RBMachine\ with one cast in \SMachine{C}. This relation is designed 
to cover all possibly ways to construct a cast representation. The empty 
sequence is related to the identity cast. A \RBMachine\ cast is related 
to its translation. Finally, cast sequencing preserves the bisimulation 
relation.
%
We remark that this bisimulation relation is unusual in that it uses
some ADT operations in its definition, such as $\id{T}$, 
$\translate{\ccast{S}{l}{T}}$, and $\compose{c}{c}$, which is necessary because 
\SMachine{C} and the bisimulation is parameterized over the Cast ADT.

The bisimulation relation is mutually defined on continuations and pre-continuations,
written 
$\bisimK{K}{K}{S}{T}$ and $\bisimK{K}{k}{S}{T}$, where $S$ and $T$ are their 
source and target types respectively, values, written $\bisimv{v}{v}{T}$, 
where $T$ is their type, and environments, written $\bisimE{\Gamma}{E}{E}$, 
where $\Gamma$ is their type environment. The bisimulation relation for values 
is designed to make Lemma~\ref{lem:LazyD-apply-cast-preserve-bisim} and 
Lemma~\ref{lem:LazyUD-apply-cast-preserve-bisim} (described below) true, that 
is, if $\bisimv{v}{v'}{S}$
then
\[
\bisimr{
	\applyCast{v}{\ccast{S}{l}{T}}
}{
	\denote{\translate{\ccast{S}{l}{T}}}(v')
}{T}
\]
So if two values of type $I$ are related, injecting them to $\Tdyn$
gives related values.
%
To relate function closures, the domain and codomain casts should be related. 
Closures in \RMachine{B} are proxied with a sequence of function casts, which 
can be viewed as two cast sequences in the obvious way.
%
The rule for products is similar.

One nice aspect of using abstract machines for this proof is that
the expressions in the machine are simply related by syntactic equality.

\begin{lemma}[Lazy D $\mathit{applyCast}$ Preserves Bisimulation]
	\label{lem:LazyD-apply-cast-preserve-bisim}
	Assume $C$ is a Lazy D Cast ADT,
	$v$ is a value in \LDMachine,
	$v'$ is a value in \SMachine{C},
	and $\bisimv{v}{v'}{S}$
	\[
	\bisimr{
		\applyCast{v}{\ccast{S}{l}{T}}
	}{
		\denote{\translate{\ccast{S}{l}{T}}}(v')
	}{T}
	\]
\end{lemma}
\begin{proof}
	Case splitting whether $S$ is shallowly consistent with $T$.
	If yes, case splitting how they are shallowly consistent.
	Then apply properties of Lazy D Cast when applicable.
\end{proof}

\begin{lemma}[Lazy UD $\mathit{applyCast}$ Preserves Bisimulation]
	\label{lem:LazyUD-apply-cast-preserve-bisim}
	Assume $C$ implements Lazy UD Cast ADT,
	$v$ is a value in \LUDMachine,
	$v'$ is a value in \SMachine{C},
	and $\bisimv{v}{v'}{S}$
	\[
	\bisimr{
		\applyCast{v}{\ccast{S}{l}{T}}
	}{
		\denote{\translate{\ccast{S}{l}{T}}}(v')
	}{T}
	\]
\end{lemma}
\begin{proof}
	Case splitting whether $S$ is shallowly consistent with $T$.
	If yes, case splitting how they are shallowly consistent.
	Then apply properties of Lazy UD Cast when applicable.
\end{proof}
%
%
%Before moving to the bisimulation proof, let's introduce two lemmas that 
%manipulate continuations.
%\begin{lemma}[$\mathit{mkCont}$ Preserves Bisimulation]
%	If \bisimK{K}{k}{S}{T} then
%	\[
%	\bisimK{K}{\mkCont{k}}{S}{T}.
%	\]
%\end{lemma}
%\begin{lemma}[$\mathit{extCont}$ Preserves Bisimulation]
%	If $\bisimc{
%		(\ccast{S_1}{l_1}{S_2}\ldots\ccast{S_{n-1}}{l_{n-1}}{S_n})
%	}{c}{S_1}{S_n}$
%	and $\bisimK{K}{K'}{S_n}{T}$ then
%	\[
%	\bisimK{
%		\Kcons{
%			\Fcast{\ccast{S_1}{l_1}{S_2}}
%		}{\ldots\Kcons{\Fcast{\ccast{S_{n-1}}{l_{n-1}}{S_n}}}{K}}
%	}{
%		\extCont{c}{K'}
%	}{S_1}{T}
%	\]
%\end{lemma}

We now come to the main lemmas, the weak bisimulation between
\RBMachine\ and \SMachine{C}.

\begin{lemma}[Lazy D Weak Bisimulation between \LDMachine\ and \SMachine{C}]
	\label{lem:weak-bisim-SC-D}
	Assume $C$ implements Lazy D Cast ADT
	and $s_1$ is a state in \LDMachine\
	and $s_1'$ is a state in \SMachine{C}
	and $\bisims{s_1}{s_1'}{T}$
	then either
\begin{enumerate}
\item $s_1  = \error{l}$
  and $s_1' = \error{l}$
  for some $l$, or
\item $s_1 = \shalt{v}$
  and $s_1' = \shalt{v'}$
  and $\bisimv{v}{v'}{T}$
  for some $v$ and $v'$, or
\item $\reduceto{s_1}{^{+}s_2}$
  and $\reduceto{s_1'}{^{+}s_2'}$
  and $\bisims{s_2}{s_2'}{T}$
\end{enumerate}
\end{lemma}
%\begin{proof}
%We proceed by case analysis on $\bisims{s_1}{s_1'}{T}$. 
%\begin{description}
%\item[Case $\inference{
%}{
%	\bisims{\error{l}}{\error{l}}{T}
%}$]
%This is case (1).
%\item[Case $\inference{
%	\bisimv{v}{v'}{T}
%}{
%	\bisims{\shalt{v}}{\shalt{v'}}{T}
%}$]
%This is case (2).
%\item[Case $\inference{
%	\expressiontyping{\Gamma}{e}{T} \\
%	\bisimE{\Gamma}{E}{E'} \\
%	K \approx K' : T
%}{
%	\bisims{\sexpr{e}{E}{K}}{\sexpr{e}{E'}{K'}}{T}
%}$]
%This is case (3). By case analysis on $e$.
%\item[Case $\inference{
%	\bisimv{v}{v'}{S} \\
%	\bisimK{K}{K'}{S}{T}
%}{
%	\bisims{\scont{v}{K}}{\scont{v'}{K'}}{T}
%}$]
%This is case (3). By inversion on $\bisimK{K}{K'}{S}{T}$, we have
%\[
%\begin{array}{rcl}
%K  & = &
%\Kcons{
%	\Fcast{\ccast{S_1}{l_1}{S_2}}
%}{\ldots\Kcons{\Fcast{\ccast{S_{n-1}}{l_{n-1}}{S}}}{K_1}} \\
%K' & = &
%\Kcons{\Fcast{c'}}{k_1'}
%\end{array}
%\]
%After zero or more transition steps, $\scont{v}{K}$ will either transition to 
%$\scont{u}{K_1}$ for some $u$ or transition to $\error{l}$ for some $l$ if one 
%of the cast fail. On the \SMachine{C} side, $\scont{v'}{K'}$ will either 
%transition to $\applyCont{u'}{k_1'}$ for some $u'$ or transition to 
%$\error{l'}$ for some $l'$ if the cast fail. Because the sequence of casts in 
%$K$ bisimulates the cast in $K'$, we can show with  
%Lemma~\ref{lem:LazyD-apply-cast-preserve-bisim} that either
%\begin{itemize}
%	\item all casts succeed and	$\bisimv{u}{u'}{S}$, or
%	\item both machines transition to error state and $l = l'$
%\end{itemize}
%When all casts succeeded, we also have $\bisimK{K_1}{k_1'}{S}{T}$ and need to 
%show that $\reduceto{\scont{u}{K_1}}{s_2}$ and $\applyCont{u'}{k_1'} = s_2'$ 
%and $\bisims{s_2}{s_2'}{T}$ for some $s_2$ and $s_2'$.
%%
%We proceed by case analysis on $K$. The most interesting cases 
%are function application and pair projection. Due to space limitation, 
%we only illustrate the general idea with function applications
%
%\begin{description}
%\item[Subcase $\infr{
%	\bisimv{v_1}{v_1'}{\Pfunc{S}{T_1}} \qquad
%	\bisimK{K_2}{K_2'}{T_1}{T}
%}{
%	\bisimK{
%		\Kcons{\FappOX{v_1}}{K_2}
%	}{
%		\Kcons{\FappOX{v_1'}}{K_2'}
%	}{S}{T}
%}$] By inversion on $\bisimv{v_1}{v_1'}{\Pfunc{S}{T_1}}$ we know the proxies 
%in $v_1$ bisimulate the proxies in $v_1'$. After a reasoning similar to the 
%above one that we used to reason about casts in continuations, we know that 
%either both machines will transition to error states if the input proxies fail 
%in casting the argument, or both machines will transition to a state 
%evaluation 
%the function body.
%\todo{need to elaborate this part, or just delete it.}
%\end{description}
%\end{description}
%\end{proof}

\begin{lemma}[Lazy UD Weak Bisimulation between \LUDMachine\ and \SMachine{C}]
	\label{lem:weak-bisim-SC-UD}
	Assume $C$ implements Lazy UD Cast ADT
	and $\bisims{s_1}{s_1'}{T}$
	then either
	\begin{enumerate}
		\item $s_1  = \error{l}$
		and $s_1' = \error{l}$
		for some $l$, or
		\item $s_1 = \shalt{v}$
		and $s_1' = \shalt{v'}$
		and $\bisimv{v}{v'}{T}$
		for some $v$ and $v'$, or
		\item $\reduceto{s_1}{^{+}s_2}$
		and $\reduceto{s_1'}{^{+}s_2'}$
		and $\bisims{s_2}{s_2'}{T}$
	\end{enumerate}
\end{lemma}
%\begin{proof}
%	Similar to Lemma~\ref{lem:weak-bisim-SC-D}.
%\end{proof}

\begin{theorem}[Correctness of Lazy D \SMachine{C}]
	\label{thm:SD-equiv}
	Suppose $C$ is a Lazy D Cast ADT
	\[
	\machineequiv{\RBMachine}{\SMachine{C}}
	\]
\end{theorem}
\begin{proof}
	By the definitions of $\textit{eval}$, we need to show 
	\[
	\transitivelyreducetoM{\RMachine{B}}{\sexpr{e}{\emptyset}{\Knil}}{
		s
	}
	\;\text{if and only if}\;
	\transitivelyreducetoM{\SMachine{C}}{\sexpr{e}{\emptyset}{\mkCont{\Knil}}}{
		s'
	}
	\]
	where $s$ and $s'$ are bisimuated final states, i.e. of the form 
	$\shalt{v}$ or $\error{l}$. The initial states are related by the 
	bisimulation relation, so we can prove this theorem with 
	Lemma~\ref{lem:weak-bisim-SC-D}.
\end{proof}

\begin{theorem}[Correctness of Lazy UD \SMachine{C}]
	\label{thm:SUD-equiv}
	Suppose $C$ is a Lazy UD Cast ADT
	\[
	\machineequiv{\RBMachine}{\SMachine{C}}
	\]
\end{theorem}
\begin{proof}
	Similar to Theorem~\ref{thm:SD-equiv}.
\end{proof}

\section{Hypercoercions, a New Cast Representation} \label{sec:hypercoercions}

\begin{figure}
	Syntax of Hypercoercions
	\[
	\begin{array}{lrcl}
	\stxrule{c}{Hypercoercions}{
		\hcci           \mid
		\hccc{h}{m}{t}
	}
	\stxrule{h}{Heads}{
		\hche     \mid
		\hchp{I}{l}
	}
	\stxrule{m}{Middles}{
		\hcmbool       \mid
		\hcmfunc{c}{c} \mid
		\hcmprod{c}{c} \mid
		\hcmfail{l}    
	}
	\stxrule{t}{Tails}{
		\hcte     \mid
		\hcti{I}
	}
	\end{array}
	\]

	\fbox{$\mathit{id}( T ) = c$}
	\[
	\begin{array}{rclr}
	\figequalto{id(\star)}{
		\hcci
	}{}
	\figequalto{id(P)}{
		\hccc{\hche}{id(P)}{\hcte}
	}{}
	\end{array}
	\]

	\fbox{$\mathit{id}_m( P ) = m$}
	\[
	\begin{array}{rclr}
	\figequalto{id(\Pbool)}{\hcmbool}{}
	\figequalto{id(\Pfunc{S}{T})}{
		\hcmfunc{id(S)}{id(T)}
	}{}
	\figequalto{id(\Pprod{S}{T})}{
		\hcmprod{id(S)}{id(T)}
	}{}
	\end{array}
	\]

	\fbox{\casttyping{c}{S}{T}} Hypercoercion typing 
	\begin{gather*}
	\inference{}{\casttyping{\hcci}{\Tdyn}{\Tdyn}}
	\quad
	\inference{
		\casttyping{h}{S}{P} &
		\casttyping{m}{P}{Q} &
		\casttyping{t}{Q}{T}
	}{
		\casttyping{\hccc{h}{m}{t}}{S}{T}
	}
	\end{gather*}

	\fbox{\casttyping{h}{T}{P}} Head typing
	\begin{gather*}
	\inference{}{\casttyping{\hche}{P}{P}}
	\quad
	\inference{}{\casttyping{\hchp{I}{l}}{\Tdyn}{I}}
	\end{gather*}

	\fbox{$\casttyping{m}{T}{T}$} Middle typing
	\begin{gather*}
	\infr{}{\casttyping{\hcmfail{l}}{P}{Q}} \quad
	\inference{}{\casttyping{\hcmbool}{\Pbool}{\Pbool}} \\
	\inference{
		\casttyping{c}{S_2}{S_1} &
		\casttyping{d}{T_1}{T_2}
	}{
		\casttyping{\hcmfunc{c}{d}}{\Pfunc{S_1}{T_1}}{\Pfunc{S_2}{T_2}}
	}
	\quad
	\inference{
		\casttyping{c}{S_1}{S_2} &
		\casttyping{d}{T_1}{T_2}
	}{
		\casttyping{\hcmprod{c}{d}}{\Pprod{S_1}{T_1}}{\Pprod{S_2}{T_2}}
	}
	\end{gather*}

	\fbox{\casttyping{t}{P}{T}} Tail typing
	\begin{gather*}
	\inference{}{\casttyping{\hcte}{P}{P}} \quad
	\inference{}{\casttyping{\hcti{I}}{I}{\Tdyn}} \quad
	\end{gather*}

	\caption{Definition of hypercoercions}
	\label{fig:hypercoercion}
\end{figure}

In this section we present a new cast representation called hypercoercions. It 
comes with two flavors: Lazy D hypercoercions and Lazy UD one.  The design of 
hypercoercions is motivated by the observation that a normal coercion has at most three
parts. Hypercoercions make this structure explicit: a hypercoercion $c$ is
either \hcci, the identity cast for \Tdyn, or it contains
three parts: a head, middle, and tail, as defined in
\figref{fig:hypercoercion}.
\begin{itemize}
	\item a head is either a projection or the no-op;
	\item a middle $m$ involves coercions that preserve a type
	constructor, i.e., coercions between Boolean, function, and pair, and 
	failure coercions;
	\item a tail is either an injection or the no-op.
\end{itemize}

Subsection~\ref{sec:LazyD-Hypercoercions} implements the \CastADT\ with the \LD\ 
hypercoercions and proves that \LD\ hypercoercions is a Lazy D Cast ADT. 
Subsection~\ref{sec:LazyUD-Hypercoercions} does the \LUD\ counterparts.
Finally, we argue in Subsection~\ref{sec:hypercoercions-compact} that 
hypercoercions would consume less space than coercions in 
normal form and hence are more suitable for implementation.

\subsection{\LD\ Hypercoercions}
\label{sec:LazyD-Hypercoercions}

\begin{figure} %% composition 1
\[
\begin{array}{lrcl}
\stxrule{g}{Gaps}{
	\gnone           \mid
	\gsome{S}{l}{T}
}
\end{array}
\]

\fbox{$\compose{c}{c} = c$} Composition of \LD\ hypercoercions
\[
\begin{array}{rclr}
\figequalto{\compose{c_1}{c_2}}{\composegap{c_1}{\gnone}{c_2}}{}
\end{array}
\]

\fbox{$\composegap{c}{g}{c} = c$}
\[
\begin{array}{rcll}
\figequalto{\composegap{\hcci}{g}{\hcci}}{\hcci}{}
\figequalto{\composegap{\hcci}{g}{\hccc{h}{m}{t}}}{
	\hccc{\mkhead{g}{h}}{m}{t}
}{}
\figequalto{\composegap{\hccc{h}{m}{t}}{g}{\hcci}}{
	\hccc{h}{m}{\mktail{t}{g}}
}{}
\figequalto{\composegap{\hccc{h_1}{m_1}{t_1}}{g}{\hccc{h_2}{m_2}{t_2}}}{
	\hccc{h_1}{(\composegap{m_1}{\mkgap{t_1}{g}{h_2}}{m_2})}{t_2}
}{}
\end{array}
\]

\fbox{\mkhead{g}{h}}
\[
\begin{array}{rclr}
\figequalto{\mkhead{g}{\hchp{P}{l}}}{\hchp{P}{l}}{}
\figequalto{\mkhead{\gsome{\Tdyn}{l}{P}}{\hche}}{\hchp{P}{l}}{}
%\mathit{mkProj(}
%& g
%& ,
%& \hchp{P}{l}
%& )=
%& \hchp{P}{l} \\
%\mathit{mkProj(}
%& \gsome{\Tdyn}{l}{P}
%& ,
%& \hche
%& )=
%& \hchp{P}{l}
\end{array}
\]
%\[
%\begin{array}{rcll}
%\figequalto{\mkhead{g}{\hchp{P}{l}}}{\hchp{P}{l}}{}
%\figequalto{\mkhead{\gsome{\Tdyn}{l}{P}}{\hche}}{\hchp{P}{l}}{}
%\end{array}
%\]

\fbox{\mktail{t}{g}}
\[
\begin{array}{rcll}
\figequalto{\mktail{\hcti{P}}{g}}{\hcti{P}}{}
\figequalto{\mktail{\hcte}{\gsome{P}{l}{\Tdyn}}}{\hcti{P}}{}
\end{array}
\]

\fbox{\mkgap{t}{g}{h}}
\[
\begin{array}{rcll}
\figequalto{\mkgap{\hcte}{g}{\hche}}{g}{}
\figequalto{\mkgap{\hcte}{\gsome{P}{l'}{\Tdyn}}{\hchp{Q}{l}}}{
	\gsome{P}{l}{Q}
}{}
\figequalto{\mkgap{\hcti{P}}{g}{\hchp{Q}{l}}}{
	\gsome{P}{l}{Q}
}{}
\figequalto{\mkgap{\hcti{P}}{\gsome{\Tdyn}{l}{Q}}{\hche}}{
	\gsome{P}{l}{Q}
}{}
\end{array}
\]

\fbox{$\composegap{m}{g}{m} = m$}
\[ 
\begin{array}{rclr}
\figequalto{\composegap{\hcmfail{l}}{g}{m_2}}{
	\hcmfail{l}
}{}
\figequalto{\composegap{m_1}{\gsome{P}{l}{Q}}{m_2}}{
	\hcmfail{l}
}{\sidecond{
		\notshallowlyconsistent{P}{Q}
		\text{ and } \forall l. m_1 \neq \hcmfail{l}
}}
\figequalto{\composegap{m_1}{g}{\hcmfail{l}}}{
	\hcmfail{l}
}{\sidecond{
		\goodgap{g}
		\text{ and } \forall l. m_1 \neq \hcmfail{l}}}
\figequalto{\composegap{\hcmbool}{g}{\hcmbool}}{
	\hcmbool
}{}
\figequalto{
	\composegap{
		(\hcmfunc{c_1}{d_1})}{
		g}{
		(\hcmfunc{c_2}{d_2})}
}{
	\hcmfunc{
		(\composegap{c_2}{\dom{g}}{c_1})}{
		(\composegap{d_1}{\cod{g}}{d_2})}
}{}
\figequalto{
	\composegap{
		(\hcmprod{c_1}{d_1})}{
		g}{
		(\hcmprod{c_2}{d_2})}
}{
	\hcmprod{
		(\composegap{c_1}{\car{g}}{c_2})}{
		(\composegap{d_1}{\cdr{g}}{d_2})}
}{}
\end{array}
\]

\fbox{$\goodgap{g}$}
\begin{gather*}
\infr{}{\goodgap{\gnone}} \quad
\infr{\shallowlyconsistent{P}{Q}}{\goodgap{\gsome{P}{l}{Q}}}
\end{gather*}

\fbox{$\dom{g}=g$}
\[
\begin{array}{rclr}
\figequalto{\dom{\gnone}}{\gnone}{}
\figequalto{\dom{\gsome{\Pfunc{S_1}{T_1}}{l}{\Pfunc{S_2}{T_2}}}}{
	\gsome{S_2}{l}{S_1}
}{}
\end{array}
\]

\fbox{$\cod{g}=g$}
\[
\begin{array}{rclr}
\figequalto{\cod{\gnone}}{\gnone}{}
\figequalto{\cod{\gsome{\Pfunc{S_1}{T_1}}{l}{\Pfunc{S_2}{T_2}}}}{
	\gsome{T_1}{l}{T_2}
}{}
\end{array}
\]

\fbox{$\car{g}=g$}
\[
\begin{array}{rclr}
\figequalto{\car{\gnone}}{\gnone}{}
\figequalto{\car{\gsome{\Pprod{S_1}{T_1}}{l}{\Pprod{S_2}{T_2}}}}{
	\gsome{S_1}{l}{S_2}
}{}
\end{array}
\]

\fbox{$\cdr{g}=g$}
\[
\begin{array}{rclr}
\figequalto{\cdr{\gnone}}{\gnone}{}
\figequalto{\cdr{\gsome{\Pprod{S_1}{T_1}}{l}{\Pprod{S_2}{T_2}}}}{
	\gsome{T_1}{l}{T_2}
}{}
\end{array}
\]

	\caption{Composition of \LD\ Hypercoercions}
	\label{fig:LazyD-Hypercoercions-composition}
\end{figure}

\figref{fig:LazyD-Hypercoercions-composition} defines the functions 
\compose{c}{c} that compose \LD\ hypercoercions. We use these functions to 
implement the \CastADT.

\todo[inline]{KC: Should we mention KC and Deyaa as citation?
(something like in private communication with KC and Deyaa)}

The \compose{c}{c} operator is the key to compressing coercions and maintaining 
space-efficiency. The composition operator for Coercions in Normal Form 
requires the target type of the first coercion to match the source type of the 
second. This requirement, however, imposes a considerable difficulty in 
termination proof of the composition of \LD\ Coercions in Normal Form, reported 
by Kuang-Chen Lu and Deyaaeldeen Almahallawi. So it is useful to relax this 
restriction for the \LD\ tracking strategy.
%
We shall need optional source cast, written $g$, that range over
$\gnone$ or $\gsome{S}{l}{T}$, to maintain the gap between the hypercoercions 
to be composed. The source cast is mandatory when the target
type of the first hypercoercion does not match the source type of the second. 
Then we write the composition of hypercoercions as \composegap{c_1}{g}{c_2}.
%  
When both $c_1$ and $c_2$ are \hcci, their composition is also \hcci. 
%
When the first hypercoercion is the \hcci, the output must start with a 
projection, in which case we invoke the helper function \textit{mkProj}. In 
\textit{mkProj}, if the head of $c_2$ is a projection, the result is $c_2$.  
Otherwise, we need a label to build the projection. Since the head of $c_2$ is 
the no-op, its source type must be a pretype. Thus we know $g$ must be a 
source cast and we use it to construct the projection.
%
Going back to $\composegap{c}{g}{c}$, when the second hypercoercion is the 
\hcci, the output must end with an injection, in which case we invoke the 
helper function \textit{mkInj}.
%
Finally, when both inputs are of the form \hccc{h}{m}{t}, we compose the middle 
with an updated gap.
%
The second and third cases of \mkgap{t}{g}{h} is interesting, where we choose 
the label in projection to be responsible for potential inconsistency.

Another interesting operator is the middle composition \composegap{m}{g}{m}. 
%
When the first middle is a failure (\hcmfail{l}), the result is the second
middle. In all the remaining cases, the first middle is not a failure.
%
When the gap is a cast between shallowly inconsistent types (i.e. having 
different top-most constructors). the output is a failure.
%
When the gap is good but the second middle is a failure, the output is the same 
failure. A gap $g$ is good if and only if there is not $P$ and $l$ 
and $Q$ such that $g = \gsome{P}{l}{Q}$ and \notshallowlyconsistent{P}{Q}.
%
The remaining cases are straightforward recursion.

Agda is able to understand that \composegap{c}{g}{c} is terminating. The reason 
might be that in \composegap{c}{g}{c} both casts become smaller in recursive 
calls, although their position is swapped in the function case. Readers who
hate non-structural recursion might add a Boolean parameter to indicate the order
of composition.

\begin{figure}
	\fbox{$\translate{\ccast{S}{l}{T}} = c$} Translation of \LD\ hypercoercions
	\[
	\begin{array}{rclr}
	\figequalto{\translate{\ccast{S}{l}{T}}}{\composegap{id(S)}{(\gsome{S}{l}{T})}{id(T)}}{}
	\end{array}
	\]
	\caption{Translatin of \LD\ Hypercoercions}
	\label{fig:LazyD-Hypercoercions-translation}
\end{figure}

The definition of translation \translate{\ccast{S}{l}{T}} is straightforward 
(\figref{fig:LazyD-Hypercoercions-translation}).

\begin{figure}
\fbox{$\denote{c}(v)=r$}
\[
\begin{array}{rclr}
\figequalto{\denote{\hcci}(v)}{v}{}
\figequalto{\denote{\hccc{h}{m}{t}}(v)}{
	(\denote{h}_h(v) \mbind \denote{m}_m)
	\mbind \denote{t}_t
}{}
\end{array}
\]

\fbox{$\denote{h}_h(v)=r$}
\[
\begin{array}{rclr}
\figequalto{\denote{\hche}(v)}{v}{}
\figequalto{\denote{\hchp{Q}{l}}(\vdyn{P}{u})}{
	\denote{\composegap{\idm{P}}{\gsome{P}{l}{Q}}{\idm{Q}}}_m(u)
}{}
\end{array}
\]

\fbox{$\denote{m}_m(v)=r$}
\[
\begin{array}{rclr}
\figequalto{\denote{\hcmfail{l}}(v)}{\error{l}}{}
\figequalto{\denote{\hcmbool}(v)}{v}{}
\figequalto{\denote{\hcmfunc{d_1}{d_2}}(\ecast{\vfunc{x}{S}{e}{E}}{\Pfunc{c_1}{c_2}})}{
	\ecast{\vfunc{x}{S}{e}{E}}{\Pfunc{(\compose{d_1}{c_1})}{(\compose{c_2}{d_2})}}
}{}
\figequalto{\denote{\hcmprod{d_1}{d_2}}(\ecast{\vcons{v_1}{v_2}}{\Pprod{c_1}{c_2}})}{
	\ecast{\vcons{v_1}{v_2}}{\Pprod{(\compose{c_1}{d_1})}{(\compose{c_2}{d_2})}}
}{}
\end{array}
\]

\fbox{$\denote{t}_t(v)=r$}
\[
\begin{array}{rclr}
\figequalto{\denote{\hcte}(v)}{v}{}
\figequalto{\denote{\hcti{P}}(v)}{\vdyn{P}{v}}{}
\end{array}
\]
\caption{Application of \LD\ Hypercoercions}
\label{fig:LazyD-Hypercoercions-application}
\end{figure}

Fig.~\ref{fig:LazyD-Hypercoercions-application} defines the cast application 
function for \LD\ hypercoercions.
Applying the identity cast for the dynamic type succeeds immediately. 
Otherwise, we apply head, middle, and tail in sequence. 
%
In projection case of head application, a new middle is constructed and applied 
to the injected value.
%
Middle applications raises an error if the middle is a failure and extend value 
proxies otherwise.

\begin{proposition} Lazy D Hypercoercions implement the Lazy D Cast ADT
\end{proposition}
\begin{theorem}[Lazy D Hypercoercions are Correct] Let $H$ be the Lazy D 
hypercoercions,
\[\machineequiv{\LDMachine}{\SMachine{H}}\]
\end{theorem}

\subsection{\LUD\ Hypercoercions} \label{sec:LazyUD-Hypercoercions}

Hypercoercions for the \LUD\ blame tracking strategy have the same syntax
as for \LD\ (\figref{fig:hypercoercion}), but the definitions of $\id{T}$ and
$\translate{\ccast{S}{l}{T}}$ and $\compose{c}{c}$, differ from \LD. Here 
composition $\compose{c_1}{c_2}$ makes the usual assumption that the
target type of $c_1$ matches the source type of $c_2$. 
%
The definition of composition for \LUD\ is particularly straightforward.
The first two lines say that \hcci\ acts as the identity on both the left
and right.
The third line handles the case when both hypercoercions have three parts. 
%
The first three lines of the middle composition $m \fatsemi t \fatsemi h 
\fatsemi m$ function match its arguments in sequential order to determine which 
label to blame. The forth and last line is straightforward recursion.

\todo[inline]{KC: I need a better name for \compatibletailhead{t}{h}}

%The third line handles the case when both the tail of $c_1$
%and the head of $c_2$ are no-ops, in which case the middles types
%$m_1$ and $m_2$ are composed via an auxiliary composition
%operator. This compose operator for middle coercions assumes that its
%inputs are shallowly consistent.  The fourth line handles the
%important case when the tail of $c_1$ is an injection and the head of
%$c_2$ is a projection. If the two middle coercions are shallowly
%consistent, then they can be composed. If not, the tail of the result
%is a failure coercion with the projection's label.  The last line
%handles the case when the tail of $c_1$ is a failure, in which case
%the result of composition is $c_1$. The definition of $id$ is straightforward.

\begin{figure}
	\fbox{$c \fatsemi c = c$}
	\[
	\begin{array}{rclcl}
		\hcci          
		& \fatsemi & d
		& = & d \\
		\hccc{h}{m}{t}
		& \fatsemi & \hcci
		& = & \hccc{h}{m}{t} \\
		\hccc{h_1}{m_1}{t_1}
		& \fatsemi & \hccc{h_2}{m_2}{t_2}
		& = & \hccc{h_1}{(m_1 \fatsemi t_1 \fatsemi h_2 \fatsemi m_2)}{t_2}
	\end{array}
	\]

	\fbox{$m \fatsemi t \fatsemi h \fatsemi m = m$}
	\[
	\begin{array}{rccccclclr}
	\hcmfail{l} 
	& \fatsemi & t
	& \fatsemi & h
	& \fatsemi & m_2
	& = & \hcmfail{l} \\
	m_1
	& \fatsemi & \hcti{G}
	& \fatsemi & \hchp{H}{l}
	& \fatsemi & m_2
	& = & \hcmfail{l}
	& \sidecond{G \neq H \text{ and } \forall l. m_1 \neq \hcmfail{l}} \\
	m_1
	& \fatsemi & t
	& \fatsemi & h
	& \fatsemi & \hcmfail{l}
	& = & \hcmfail{l}
	& \sidecond{\compatibletailhead{t}{h}
		\text{ and } \forall l. m_1 \neq \hcmfail{l}} \\
	m_1
	& \fatsemi & t
	& \fatsemi & h
	& \fatsemi & m_2
	& = & m_1 \fatsemi m_2
	& \sidecond{
		\forall l. m_2 \neq \hcmfail{l}
		\text{ and } \compatibletailhead{t}{h}
		\text{ and } \forall l. m_1 \neq \hcmfail{l}} \\
	\end{array}
	\]

	\fbox{$m \fatsemi m = m$}
	\[
	\begin{array}{rclcl}
	\hcmbool
	& \fatsemi & \hcmbool
	& = & \hcmbool \\
	\hcmfunc{c_1}{d_1}
	& \fatsemi & \hcmfunc{c_2}{d_2}
	& = & \hcmfunc{c_2 \fatsemi c_1}{d_1 \fatsemi d_2} \\
	\hcmprod{c_1}{d_1}
	& \fatsemi & \hcmprod{c_2}{d_2}
	& = & \hcmprod{c_2 \fatsemi c_1}{d_1 \fatsemi d_2} \\
	\end{array}
	\]

	\fbox{\compatibletailhead{t}{h}}
	\begin{gather*}
	\infr{}{\compatibletailhead{\hcte}{\hche}}
	\quad
	\infr{}{\compatibletailhead{\hcti{G}}{\hchp{G}{l}}}
	\end{gather*}

\caption{\LUD\ Hypercoercions (1): composition}
\label{fig:LazyUD-Hypercoercions-composition}
\end{figure}

\begin{figure}
	\fbox{$\translate{\ccast{S}{l}{T}} = c$}
	\[
	\begin{array}{rcll}
	\figequalto{\translate{\ccast{\Tdyn}{l}{\Tdyn}}}{\hcci}{}
	\figequalto{\translate{\ccast{\Tdyn}{l}{Q}}}{\castFromDyn{l}{Q}}{}
	\figequalto{\translate{\ccast{P}{l}{\Tdyn}}}{\castToDyn{P}{l}}{}
	\figequalto{\translate{\ccast{P}{l}{Q}}}{
		\hccc{\hche}{\hcmfail{l}}{\hcte}
	}{\sidecond{\notshallowlyconsistent{P}{Q}}}
	\figequalto{\translate{\ccast{\Pbool}{l}{\Pbool}}}{
		\hccc{\hche}{\hcmbool}{\hcte}
	}{}
	\figequalto{\translate{\ccast{\Pfunc{S_1}{T_1}}{l}{\Pfunc{S_2}{T_2}}}}{
		\hccc{\hche}{
			\hcmfunc{
				\translate{\ccast{S_2}{l}{S_1}}}{
				\translate{\ccast{T_1}{l}{T_2}}}
		}{\hcte}
	}{}
	\figequalto{\translate{\ccast{\Pprod{S_1}{T_1}}{l}{\Pprod{S_2}{T_2}}}}{
		\hccc{\hche}{
			\hcmprod{
				\translate{\ccast{S_1}{l}{S_2}}}{
				\translate{\ccast{T_1}{l}{T_2}}}
		}{\hcte}
	}{}
	\end{array}
	\]

	\fbox{$\castFromDyn{Q}{l}$}
	\[
	\begin{array}{rcll}
\figequalto{\castFromDyn{\Tdyn}{l}}{\hcci}{}
\figequalto{\castFromDyn{\Pbool}{l}}{
	\hccc{\hchp{\Gbool}{l}}{
		\hcmbool
	}{\hcte}
}{}
\figequalto{\castFromDyn{\Pfunc{S}{T}}{l}}{
	\hccc{\hchp{\Gfunc}{l}}{
		\hcmfunc{\castToDyn{S}{l}}{\castFromDyn{T}{l}}
	}{\hcte}
}{}
\figequalto{\castFromDyn{\Pprod{S}{T}}{l}}{
	\hccc{\hchp{\Gprod}{l}}{
		\hcmprod{\castFromDyn{S}{l}}{\castFromDyn{T}{l}}
	}{\hcte}
}{}
	\end{array}
	\]

	\fbox{$\castToDyn{Q}{l}$}
	\[
	\begin{array}{rcll}
\figequalto{\castToDyn{\Tdyn}{l}}{\hcci}{}
\figequalto{\castToDyn{\Pbool}{l}}{
	\hccc{\hche}{
		\hcmbool
	}{\hcti{\Gbool}}
}{}
\figequalto{\castToDyn{\Pfunc{S}{T}}{l}}{
	\hccc{\hche}{
		\hcmfunc{\castFromDyn{S}{l}}{\castToDyn{T}{l}}
	}{\hcti{\Gfunc}}
}{}
\figequalto{\castToDyn{\Pprod{S}{T}}{l}}{
	\hccc{\hche}{
		\hcmprod{\castToDyn{S}{l}}{\castToDyn{T}{l}}
	}{\hcti{\Gprod}}
}{}
	\end{array}
	\]
\caption{\LUD\ Hypercoercions (2): translation}
\label{fig:LazyUD-Hypercoercions-translation}
\end{figure}

The translation function \translate{\ccast{S}{l}{T}} is defined in 
\figref{fig:LazyUD-Hypercoercions-translation}.  Prior
presentations of this function do not use auxiliary functions, as we
do here. The reason that we introduce the auxiliary functions
$\mathit{castToDyn}$ and $\mathit{castFromDyn}$, is to ensure that each of them 
is structurally recursive, which makes them straightforward to define in
Agda.

\begin{figure}
	\fbox{$\denote{c}_c(v)=r$}
	\[
	\begin{array}{rclr}
	\figequalto{\denote{\hcci}(v)}{v}{}
	\figequalto{\denote{\hccc{h}{m}{t}}(v)}{
		(\denote{h}(v) \mbind \denote{m})
		\mbind \denote{t}
	}{}
	\end{array}
	\]

	\fbox{$\denote{h}_h(v)=r$}
	\[
	\begin{array}{rclr}
	\figequalto{\denote{\hche}(v)}{v}{}
	\figequalto{\denote{\hchp{G}{l}}(\vdyn{G}{u})}{u}{}
	\figequalto{\denote{\hchp{H}{l}}(\vdyn{G}{u})}{\error{l}}{
		\sidecond{G \neq H}
	}
	\end{array}
	\]

	\fbox{$\denote{m}_m(v)=r$}
	\[
	\begin{array}{rclr}
	\figequalto{\denote{\hcmfail{l}}(v)}{\error{l}}{}
	\figequalto{\denote{\hcmbool}(v)}{v}{}
	\figequalto{\denote{\hcmfunc{d_1}{d_2}}(\ecast{\vfunc{x}{S}{e}{E}}{\Pfunc{c_1}{c_2}})}{
		\ecast{\vfunc{x}{S}{e}{E}}{\Pfunc{(\compose{d_1}{c_1})}{(\compose{c_2}{d_2})}}
	}{}
	\figequalto{\denote{\hcmprod{d_1}{d_2}}(\ecast{\vcons{v_1}{v_2}}{\Pprod{c_1}{c_2}})}{
		\ecast{\vcons{v_1}{v_2}}{\Pprod{(\compose{c_1}{d_1})}{(\compose{c_2}{d_2})}}
	}{}
	\end{array}
	\]

	\fbox{$\denote{t}_t(v)=r$}
	\[
	\begin{array}{rclr}
	\figequalto{\denote{\hcte}(v)}{v}{}
	\figequalto{\denote{\hcti{G}}(v)}{\vdyn{G}{v}}{}
	\end{array}
	\]
	\caption{Application of \LUD\ Hypercoercions}
	\label{fig:LazyUD-Hypercoercions-application}
\end{figure}

Fig.~\ref{fig:LazyUD-Hypercoercions-application} defines the cast application 
function for \LUD\ hypercoercions.
Applying the identity cast for the dynamic type succeeds immediately. 
Otherwise, we apply head, middle, and tail in sequence. 
%
In the two projection cases of head application, the result depends on whether 
the source ground type ($G$) is the same as the target ($H$).
%
Middle applications raises an error if the middle is a failure and extend value 
proxies otherwise.

\begin{proposition} Lazy UD Hypercoercions implement the Lazy UD Cast ADT
\end{proposition}
\begin{theorem}[Lazy UD Hypercoercions are Correct] Let $H$ be the Lazy UD 
	hypercoercions,
	\[\machineequiv{\LDMachine}{\SMachine{H}}\]
\end{theorem}

\subsection{Compact Representation of Hypercoercions} \label{sec:hypercoercions-compact}

Hypercoercions enable a bit-level representation that is particularly
compact for identity coercions and coercions that project from base
types or inject to base types.  (Here \Pbool\ is the only base
type, but in a real language the base types would include integers,
Booleans, etc.)  We conjecture that such coercions occur more
frequently than the more complex coercions (e.g. between function
types), especially because such coercions appear in the leaves of
complex coercions.

Furthermore, values of base types are often stored in CPU registers, so
it would be nice for coercions on base types to also fit in registers,
that is, in 64 bits, so that applying a coercion to a value of base
type would not require access to main memory, which is an order of
magnitude slower than accessing registers on a modern CPU.
%
Coercions involving non-base types, such as function types, may be
arbitrarily deep, so in those cases, the hypercoercion representation
has to be a pointer to a heap-allocated structure.

Here is a sketch for the bit-level representation for hypercoercions.

\begin{itemize}
\item 1 bit to differentiate between \hcci\ and three-part coercions.

\item 1 bit to differentiate between middle coercions of base type
versus non-base type.

\item If the middle is a non-base type or bottom ($\hcmfail{l}$), then 61 bits 
represent a
pointer to a heap-allocated structure. Heap allocated structures are
usually 8-byte aligned, so there are 3 unused bits in a pointer.

\item If the middle is of base types, then the remaining 62 bits are
used to represent the head (51 bits), middle (10 bit), and tail (1
bit).
\begin{itemize}
\item The head requires 1 bit to differentiate between $\hche$
and $\hchp{P}{l}$ and then 50 bits could be used for the label $l$.
\item The middle would use 10 bits to differentiate all the base types.
\item The tail requires 1 bits to differentiate between $\hcte$ and $\hcti{P}$, 
where $P$ must be equal to the middle type.
\end{itemize}
The bits for blame labels represent an index into a table of blame information.
In the event that a program requires too many blame labels, then the 
implementation
can fallback to using the heap-allocated structure for more
coercions.
\end{itemize}

\section{Conclusion} \label{sec:conclusion}

We present steps toward the first framework for proving the
correctness of cast representations.
%
The framework includes abstract data types for cast representations
(Cast ADT and its refinements Lazy D Cast ADT and \LUD\ \CastADT), 
a parameterized abstract machine \effCEK{C}, 
a theorem which states that \SMachine{C} is equivalent
to \LDMachine\ when $C$ is a Lazy D Cast ADT, and
a theorem which states that \SMachine{C} is equivalent
to \LUDMachine\ when $C$ is a Lazy UD Cast ADT.
%
%The Lazy D Cast ADT refines the Cast ADT. 
%
We applied this framework to Lazy UD coercions in normal form,
Lazy UD threesomes, and hypercoercions and conjecture that
this framework is also applicable to other cast representations.

We also presented hypercoercions, a cast representation that has a 
theorem-prover-friendly compose operator and a more compact memory
representation in comparison with coercions in normal forms.

%
% ---- Bibliography ----
%
% BibTeX users should specify bibliography style 'splncs04'.
% References will then be sorted and formatted in the correct style.
%
% \bibliographystyle{splncs04}
% \bibliography{mybibliography}
%
\bibliographystyle{splncs04}
\bibliography{bibfile,all-modified}{}

\begin{thebibliography}{8}
\bibitem{ref_article1}
Author, F.: Article title. Journal \textbf{2}(5), 99--110 (2016)

\bibitem{ref_lncs1}
Author, F., Author, S.: Title of a proceedings paper. In: Editor,
F., Editor, S. (eds.) CONFERENCE 2016, LNCS, vol. 9999, pp. 1--13.
Springer, Heidelberg (2016). \doi{10.10007/1234567890}

\bibitem{ref_book1}
Author, F., Author, S., Author, T.: Book title. 2nd edn. Publisher,
Location (1999)

\bibitem{ref_proc1}
Author, A.-B.: Contribution title. In: 9th International Proceedings
on Proceedings, pp. 1--2. Publisher, Location (2010)

\bibitem{ref_url1}
LNCS Homepage, \url{http://www.springer.com/lncs}. Last accessed 4
Oct 2017
\end{thebibliography}
\end{document}

### 2020-09-21 samplepaper.tex
changes to pdflatex without errors
Updates from Overleaf

@@
 \newcommand{\denote}[1]{\ensuremath{\llbracket #1 \rrbracket}}
-\newcommand{\proxy}[2]{\ensuremath{\mathit{proxy}(#1,#2)}}
-\newcommand{\applyCast}[2]{\ensuremath{\mathit{applyCast}(#1,#2)}}
-\newcommand{\project}[4]{\ensuremath{\mathit{project}(#1,#2,#3,#4)}}
+\newcommand{\proxy}[2]{\ensuremath{\mathrm{proxy}(#1,#2)}}
+\newcommand{\applyCast}[2]{\ensuremath{\mathrm{applyCast}(#1,#2)}}
+\newcommand{\project}[4]{\ensuremath{\mathrm{project}(#1,#2,#3,#4)}}
 \newcommand{\composegap}[3]{\ensuremath{#1 \fatsemi #2 \fatsemi #3}}
-\newcommand{\mkhead}[2]{\ensuremath{\mathit{mkProj}(#1,#2)}}
-\newcommand{\mktail}[2]{\ensuremath{\mathit{mkInj}(#1,#2)}}
-\newcommand{\mkgap}[3]{\ensuremath{\mathit{mkGap}(#1,#2,#3)}}
+\newcommand{\mkhead}[2]{\ensuremath{\mathrm{mkProj}(#1,#2)}}
+\newcommand{\mktail}[2]{\ensuremath{\mathrm{mkInj}(#1,#2)}}
+\newcommand{\mkgap}[3]{\ensuremath{\mathrm{mkGap}(#1,#2,#3)}}
 \newcommand{\compose}[2]{\ensuremath{#1 \fatsemi #2}}
 \newcommand{\translate}[1]{\ensuremath{\lceil#1\rceil}}
-\newcommand{\castToDyn}[2]{\ensuremath{\mathit{castToDyn}(#1,#2)}}
-\newcommand{\castFromDyn}[2]{\ensuremath{\mathit{castFromDyn}(#1,#2)}}
-\newcommand{\dom}[1]{\ensuremath{\mathit{dom}(#1)}}
-\newcommand{\cod}[1]{\ensuremath{\mathit{cod}(#1)}}
-\newcommand{\car}[1]{\ensuremath{\mathit{car}(#1)}}
-\newcommand{\cdr}[1]{\ensuremath{\mathit{cdr}(#1)}}
-\newcommand{\id}[1]{\ensuremath{\mathit{id}(#1)}}
-\newcommand{\idm}[1]{\ensuremath{\mathit{id}_m(#1)}}
-\newcommand{\idc}[1]{\ensuremath{\mathit{id}_c(#1)}}
-\newcommand{\mkCont}[1]{\ensuremath{\mathit{mkCont}(#1)}}
-\newcommand{\extCont}[2]{\ensuremath{\mathit{extCont}(#1,#2)}}
-\newcommand{\applyCont}[2]{\ensuremath{\langle\langle#1,#2\rangle\rangle}}
+\newcommand{\castToDyn}[2]{\ensuremath{\mathrm{castToDyn}(#1,#2)}}
+\newcommand{\castFromDyn}[2]{\ensuremath{\mathrm{castFromDyn}(#1,#2)}}
+\newcommand{\dom}[1]{\ensuremath{\mathrm{dom}(#1)}}
+\newcommand{\cod}[1]{\ensuremath{\mathrm{cod}(#1)}}
+\newcommand{\car}[1]{\ensuremath{\mathrm{fst}(#1)}}
+\newcommand{\cdr}[1]{\ensuremath{\mathrm{snd}(#1)}}
+\newcommand{\id}[1]{\ensuremath{\mathrm{id}(#1)}}
+\newcommand{\idm}[1]{\ensuremath{\mathrm{id}_m(#1)}}
+\newcommand{\idc}[1]{\ensuremath{\mathrm{id}_c(#1)}}
+\newcommand{\mkCont}[1]{\ensuremath{\mathrm{mkK}(#1)}}
+\newcommand{\extCont}[2]{\ensuremath{\mathrm{extK}(#1,#2)}}
+% \newcommand{\applyCont}[2]{\ensuremath{\langle\langle#1,#2\rangle\rangle}}
+\newcommand{\applyCont}[2]{\ensuremath{\mathrm{applyK}(#1,#2)}}
 
@@
 \author{Kuang-Chen Lu\inst{1} \and
-Jeremy G. Siek\inst{1} \and
-Andre Kuhlenschmidt\inst{1}
+Jeremy G. Siek\inst{2} \and
+Andre Kuhlenschmidt\inst{2}
 }
@@
 %
-\institute{Indiana University, Bloomington IN 47405, USA}
+\institute{Brown University, Providence RI 02912, USA \and
+Indiana University, Bloomington IN 47405, USA}
 % \institute{Princeton University, Princeton NJ 08544, USA \and
@@
 space complexity. Several space-efficient cast representations have been 
-proposed, including coercions in normal forms, threesomes, and supercoercions. 
-Drawing an interface between a cast representation and the remaining parts of 
-language implementations would likely help to understand the relation 
-between these cast representations and potentially new ones. We present such an 
-interface, Cast Abstract Data Type. The Cast ADT brings another 
-benefit. Space-efficient cast representations shall be proved not changing the 
-overall behavior of language implementations except saving space. Existing 
-proofs typically go through a whole bisimulation proof between the standard and 
-inefficient semantics and a space-efficient one. If a space-efficient semantics 
-uses the Cast ADT, its behavior would depend solely on the properties of the 
-interface functions. Thus a cast representation is correct if its interface 
-functions work correctly. We present an abstract machine \SMachine{C} that uses 
-Cast ADT to work with casts, a parameterized bisimulation proof, and two 
-subsets of Cast ADT that specify the Lazy D and the Lazy UD blame strategies. We
-also introduce a new cast representation, hypercoercions, that is better than 
-the known cast representations in some aspects.
+proposed, notably coercions in normal forms and threesomes. But they are
+presented in different dynamic semantics, which make it difficult to compare
+the key differences between the cast representations. We present a abstrat
+data type, namely Cast ADT, that captures interface functions a cast representations
+typically includes, and an abstract machine parameterized over Cast ADTs.
+The Cast ADT brings another benefit: space-efficient cast representations 
+shall be proved not changing the 
+overall behavior of language implementations except saving space.
+With our generic abstract machine, these proofs can be done by proving properties
+of a specific Cast ADT, which is simpler than going through a bisimulation proof 
+between a space-efficient dynamic semantics and the definitional dynamic semantics.
+We have successfully applied our new approach of proving the correctness of cast 
+representations to several known cast representations and believe this framework
+is also applicable to other cast representations.
+We also present a new cast representation, hypercoercions, that is more friendly
+to mechanized meta-theory and hypothetically consume less memory than coercions
+in normal forms.
 
@@
 
-\todo[inline]{Cite "Contracts for higher-order functions" for the proxy-based approach?}
+\todo[inline]{KC: Cite "Contracts for higher-order functions" for the proxy-based approach maybe?}
 
@@
 typically written as \Tdyn\ or \lstinline|Dyn| or \lstinline|Any|, which enables 
-imprecise type annotations. A gradual type checker would allow programmers to cast 
+imprecise type annotations. A gradual type checker allows programmers to cast 
 implicitly between types that have no conflicting type information.
@@
 For illustration, we apply the framework to Lazy UD coercions in normal form
-and Lazy UD threesomes (Chapter~\ref{sec:framework-examples}). 
+and Lazy UD threesomes. 
 We believe the framework is also applicable to other cast representations.
-
-\todo[inline]{Actuallythink twosome's composition is structurally recursive but threesomes' is not}
+\todo[inline]{KC: (about the p above) I want to put the illustration part on the same github repo, adding description as
+Agda comments. }
+
+\todo[inline]{KC: (about the p below) Actually I think twosome's composition is structurally recursive but threesomes' is not}
 The published cast representations have various strengths and weaknesses.
@@
 This paper presents a new cast representation 
-(Section~\ref{chap:hypercoercions}), named
+(Section~\ref{sec:hypercoercions}), named
 \emph{hypercoercions}, that is good for both mechanized metatheory and
@@
 
-\todo[inline]{how to make citet work?}
+\todo[inline]{KC: how to make \textbackslash citet work?}
 
@@
 
-In this section, we first review lazy cast calculi (Section~\ref{sec:cast-calculus}), where
-we present an abstract machine that is employed in our framework \ref{sec:framework}. Then
-we review coercions and their normal forms (Section~\ref{sec:coercions-in-normal-form}), which
-motivates and inspires the design of hypercoercions (Section~\ref{sec:hypercoercions}).
+In this section, we first review lazy cast calculi (Subsection~\ref{sec:cast-calculi}), where
+we present an abstract machine that is employed in our framework. Then
+we review coercions and their normal forms (Subsection~\ref{sec:coercions-in-normal-form}), which
+motivates and inspires the design of hypercoercions.
 
@@
 easier 
-to deal with than substitutions in formal proof. Also, a CEK machine is more
+to deal with than substitutions in formal proofs. Also, a CEK machine is more
 convenient to use for the space-efficient semantics in
@@
 machine states). So using a CEK machine for the cast 
-calculi in this section makes it easier to prove the equivalent of these 
-machines. Of course, one should prove that the abstract machine
+calculi in this section makes it easier to prove these machines are equivalent.
+Of course, one should also prove that the abstract machine
 presented here is equivalent to the standard reduction semantics for
@@
 	\Fcast{\ccast{S}{l}{T}} \mid
-	\Fcar                    
+	\Fif{e}{e}{E}
 }
 \stxrulecont{
+	\Fcar \mid
 	\Fcdr \mid
@@
 %
-Recall that CEK machines involve two kinds of transitions, (1) those
+Recall that CEK machines involve two kinds of transitions: those
 that dive further into an expression (looking for a redex) and push an
-entry onto the continuation, and (2) those that return a value to the
+entry onto the continuation and those that return a value to the
 current continuation and possibly perform a computation.
-Corresponding to (1) and (2), the machine state is either in an evaluating
+That is, the machine state is either in an evaluating
 $\sexpr{e}{E}{K}$ or returning $\scont{v}{K}$ configuration, 
@@
 functions, pairs, or casted pairs.
+%
+The \proxy{v}{\ccast{S}{l}{T}} partial function applies the cast to $v$, which must
+have type $S$. This function is handy when we describe the dynamic semantics.
 % In earlier version of this work, 
@@
 
-The reflexive transitive closure of reduction (\transitivelyreduceto{s}{s}) 
-and evaluation (${\evalto{e}{o}}$) are standard~\citep{felleisen03:_pllc}.
+The reflexive transitive closure of reduction \transitivelyreduceto{s}{s}
+and evaluation partial function ${\evalto{e}{o}}$ are standard~\citep{felleisen03:_pllc}.
 
@@
 	\just{\vdyn{G}{\proxy{v}{\ccast{P}{l}{G}}}}
-	& \text{if } G \sim P, G \neq P \\  
+	\\ && \text{if } G \sim P, G \neq P \\  
+% 	& \text{if } G \sim P, G \neq P \\  
 	\mathit{applyCast}(\vdyn{G}{u}, \ccast{\Tdyn}{l}{H}) &=&          
@@
 	\project{u}{G}{l}{H} \mbind \lambda v. \proxy{v}{\ccast{H}{l}{Q}}
-	& \text{if } H \sim Q, H \neq Q \\
+	\\
+	&& \text{if } H \sim Q, H \neq Q \\
+% 	& \text{if } H \sim Q, H \neq Q \\
 	\mathit{applyCast}(v, \ccast{P}{l}{Q}) &=&
 	\just{\proxy{v}{\ccast{P}{l}{Q}}}
-	& \text{if } P \smile Q \\
+	\\&& \text{if } P \smile Q \\
 	\mathit{applyCast}(v, \ccast{P}{l}{Q}) &=&
 	\error{l}
-	& \text{if } P \not\smile Q
+	\\&& \text{if } P \not\smile Q
 	\end{array}
@@
 type named Cast ADT, which specifies the operators of cast representations, 
-a CEK machine $\SMachine{C}$, which uses the cast operators implemented by 
-$C$ to work with casts, and theorems relating $\SMachine{C}$ to $\RMachine{B}$.
+a CEK machine $\SMachine{C}$ parameterized over a Cast ADT,
+which uses the cast operators implemented by $C$ to work with casts, 
+and theorems relating $\SMachine{C}$ to $\RMachine{B}$.
 %
@@
 		\FappOX{v}     \mid
+		\Fif{e}{e}{E}
+	}
+	\stxrulecont{
 		\Fcar \mid
-		\Fcdr
-	}
-	\stxrulecont{
+		\Fcdr \mid
 		\FconsXO{e}{E}  \mid
@@
 \figref{fig:SEMachine-state} defines the syntax of the space-efficient CEK 
-machine (\SMachine{C}). This machine is parameterized over Cast ADT $C$.
-%
-The key differences between \SMachine{C} and the \RMachine{B} machine are the 
-places where casts can accumulate~(\secref{sec:space-efficiency-problem}), that 
-is, values and continuations.
+machine \SMachine{C}.
+The key differences between \SMachine{C} and \RMachine{B} are in the definitions
+of values and continuations, that is, places where casts can accumulate.
 
@@
 another two for pairs. That setup allows zero-or-more layers of casts at the 
-top of higher-order values, which might lead to space inefficiency. 
-%
-In \SMachine{C}, we instead have exactly one layer of cast. 
-Thus non-casted values in \RMachine{B} correspond to values 
-in \SMachine{C} where casts are identities ($\mathit{id}(T)$). The 
+top of higher-order values, which might consume unbounded space. 
+%
+\SMachine{C} instead has exactly one layer of cast.
+Thus non-casted values in \RMachine{B} correspond to \SMachine{C} values
+where casts are identities ($\mathit{id}(T)$). The 
 $\mathit{id}$ functions is provided by the Cast ADT.
@@
 Let $K$ ranges over continuations and $k$ ranges over pre-continuations.
-%
-Pre-continuations are like the continuations in \RMachine{B}, but their 
-top-most frame must not be a cast frames.
-%
-A continuation is now a pre-continuation prefixed with a cast frame.
-%
-Recall that continuations in \RMachine{B} have zero or more casts at the top.
-In \SMachine{C}, however, every continuation has exactly one cast at the 
-top.
-%
-Continuations in \RMachine{B} that have no casts at the top correspond
-to continuations in \SMachine{C}\ whose casts are identities constructed by 
-$\id{T}$.
-Continuations in \RMachine{B} that have many casts at the top 
-correspond
-to continuations in \SMachine{C}\ where those casts are composed by
+This setup is essentially saying that cast frames and non-cast frames should
+appear alternatively in continuations, and that a continuation always start
+with a cast frame.
+% %
+% Pre-continuations are like the continuations in \RMachine{B}, but their 
+% top-most frame must not be a cast frames.
+% %
+% A continuation is now a pre-continuation prefixed with a cast frame.
+% %
+% Recall that continuations in \RMachine{B} have zero or more casts at the top.
+% In \SMachine{C}, however, every continuation has exactly one cast at the 
+% top.
+% %
+\RMachine{B} continuations that have no casts at the top correspond
+to \SMachine{C} continuations whose casts are identities.
+\RMachine{B} continuations that have many casts at the top correspond
+to \SMachine{C} continuations in where those casts are composed by
 $\compose{c}{c}$, another functions provided by the Cast ADT.
 %
-Injectable types ($I,J$), environments ($\mathcal{E}$), states ($s$), and cast 
-results ($r$) are the same as in \RBMachine.
+Injectable types, environments, states, and cast results are the same as in \RBMachine.
 
@@
 
+\todo[inline]{KC: I changed some wording in the following definition:
+"a family"; translate a cast ...}
 \begin{definition}[Cast Abstract Data Type (Cast ADT)]
 	\label{def:cast-rep}
-	A cast abstract data type is a set $Cast$, which is indexed by two types, 
+	A cast abstract data type is a family, namely $Cast$, indexed by two types, 
 	with four operators and two properties of operators:
 \begin{itemize}
-	\item $id(T)=c$: create an identity cast
+	\item $\id{T}=c$: create an identity cast
 	\item $\compose{c}{c}=c$: compose casts
-	\item $\translate{\ccast{S}{l}{T}}=c$: translate cast in source 
-		program to runtime casts
+	\item $\translate{\ccast{S}{l}{T}}=c$: translate a cast in source 
+		program to a $\textit{Cast}_{S,T}$
 	\item $\denote{c}(v)=r$: apply a cast to a value
@@
 %
-To construct a function, the machine fills the casts with identities.
+To construct a function value, the machine fills the casts with identities.
 %
 When evaluating a cast expression, the machine extends the continuation with 
-cast \translate{\ccast{S}{l}{T}}.
+\translate{\ccast{S}{l}{T}}.
 %
@@
 argument $v$ and evaluates the function body. The codomain cast $d$ is merged 
-into the continuation with $\textit{extCont}$.
-%
-When the machine constructs a pair, it fills the casts with $id$s, just 
-like how it did for functions. 
+into the continuation with $\mathrm{extK}$.
+%
+When the machine constructs a pair, it fills the casts with identities, just 
+like how it does for function values. 
 %
@@
 Taking out the second part of a pair is similar.
-
-Reflexive transitive closure of reduction ($\reducetoS{C}{s}{s}$) and
-evaluation ($\evaltoS{C}{e}{o}$) are the same as in \RMachine{B}.
+\todo[inline]{KC: I want to give a brief discussion on inert v.s. active pairs.}
+
+Reflexive transitive closure of reduction $\reducetoS{C}{s}{s}$ and
+the evaluation partial function $\evaltoS{C}{e}{o}$ are the same as in \RMachine{B}.
 
@@
 
-\subsection{Specifying good instances of Cast ADT}
-\label{sec:good-cast-adt}
-
-Ultimately, we want to claim that if a $C$ satisfies a collection of 
-properties, \SMachine{C} would be equivalent to \LDMachine\ or \LUDMachine. 
-Cast ADT has specified the behavior of identities and composition, so the only 
+\subsection{Specifying good instances of Cast ADT} \label{sec:good-cast-adt}
+
+Recall that our goal is to prove that \SMachine{C} would be equivalent to
+\LDMachine\ or \LUDMachine\ when $C$ satisfies some properties.
+Cast ADT has fixed the behavior of identities and composition, so the only 
 remaining operator is translation.
@@
 of \translate{\ccast{S}{l}{T}}. Readers are encouraged to compare them with the 
-corresponding $\mathit{applyCast}$ functions 
+corresponding $\mathrm{applyCast}$ functions 
 (Fig.~\ref{fig:blame-strategy-LazyD} and 
@@
 	\label{def:LazyD-CastADT}
-	A Cast is a Lazy D Cast if:
+	A Cast ADT is a Lazy D Cast ADT if:
 	\begin{enumerate}
@@
 
-In this section, we prove that if $C$ is a Lazy D Cast ADT then
+Now we are ready to prove that if $C$ is a Lazy D Cast ADT then
 \[
@@
 \]
-and if $C$ is a Lazy UD Cast ADT then
+and that if $C$ is a Lazy UD Cast ADT then
 \[
@@
 \]
-The proof is done via a weak bisimulation.
+
+\todo[inline]{KC: In the latex file, below are two versions of a figure.
+One is the same as in our WGT paper. The other uses Z as the meta variable of sequences of 
+source-code casts, which is similar to the blame-and-coercion paper.}
 
@@
 congruence relation containing the shown rules. Everything to the left (resp. 
-right) of the 
-symbol $\approx$ is in \RBMachine\ (resp. \SMachine{C}).}
+right) of $\approx$ is in \RBMachine\ (resp. in \SMachine{C}).}
 \label{fig:bisim-SC-D}
@@
 
-Fig.~\ref{fig:bisim-SC-D} defines the bisimulation relation between \RBMachine\ 
-and \SMachine{C}. It is the smallest congruence relation containing the rules 
+\begin{figure}
+
+\fbox{\bisimc{Z}{c}{S}{T}}
+\begin{gather*}
+\infr{}{\bisimc{[]}{id(T)}{T}{T}} \quad
+\infr{}{\bisimc{[\ccast{S}{l}{T}]}{\translate{\ccast{S}{l}{T}}}{S}{T}}
+\\[1ex]
+\infr{
+	\bisimc{Z_1}{c_1}{T_1}{T_2}\\
+	\bisimc{Z_2}{c_2}{T_2}{T_3}
+}{
+	\bisimc{(Z_1 \mathrm{++} Z_2)}{(\compose{c_1}{c_2})}{T_1}{T_3}
+}
+\end{gather*}
+
+\fbox{$\bisimK{K}{K}{S}{T}$}
+\begin{gather*}
+\infr{
+	\bisimK{K}{k'}{S_n}{T} \qquad
+	\bisimc{Z}{c}{S_1}{S_n}
+}{
+	\bisimK{
+		\Kcons{\Fcast{Z}}{K}
+	}{
+		\Kcons{\Fcast{c'}}{k'}
+	}{S_1}{T}
+}
+\end{gather*}
+
+\fbox{$\bisimv{v}{v}{T}$}
+\begin{gather*}
+\infr{
+	\expressiontyping{\Gamma,x : S_1}{e}{T_1}
+	\qquad
+	\bisimE{\Gamma}{E}{E'}
+	\\
+	\bisimc{
+		(\ccast{S_n}{l_{n-1}}{S_{n-1}} \ldots
+		\ccast{S_2}{l_1}{S_1})
+	}{c}{S_n}{S_1}
+	\\
+	\bisimc{
+		(		\ccast{T_1}{l_{1}}{T_2} \ldots
+		\ccast{T_{n-1}}{l_{n-1}}{T_n}
+		)	}{d}{T_1}{T_n}
+	\\
+	v = \vfuncc{
+		\vfuncc{
+			\vfunc{x}{S_1}{e}{E}
+		}{S_1}{T_1}{l_1}{S_2}{T_2}
+		\ldots
+	}{S_{n-1}}{T_{n-1}}{l_{n-1}}{S_n}{T_n}
+}{
+	\bisimv{v}{
+		(\ecast{\vfunc{x}{S_1}{e}{E'}}{\Pfunc{c}{d}})
+	}{
+		\Pfunc{S_n}{T_n}}
+}
+\\[1ex]
+\infr{
+	\bisimv{v_1}{v_1'}{S_1} \qquad
+	\bisimv{v_2}{v_2'}{T_1} \\
+	\bisimc{
+		(\ccast{S_1}{l_{1}}{S_2} \ldots
+		\ccast{S_{n-1}}{l_{n-1}}{S_n})
+	}{c}{S_1}{S_n} \\
+	\bisimc{
+		(\ccast{T_1}{l_{1}}{T_2} \ldots
+		\ccast{T_{n-1}}{l_{n-1}}{T_n})
+	}{d}{T_1}{T_n}
+	\\ v = \vconsc{
+		\vconsc{
+			\vcons{v_1}{u_1}
+		}{S_1}{T_1}{l_1}{S_2}{T_2}
+		\ldots
+	}{S_{n-1}}{T_{n-1}}{l_{n-1}}{S_n}{T_n}
+}{
+	\bisimv{
+		v
+	}{
+		(\ecast{\vcons{v_2}{u_2}}{\Pprod{c}{d}})
+	}{
+		\Pprod{S_n}{T_n}}
+}
+\end{gather*}
+
+\fbox{\bisimE{\Gamma}{E}{E}}
+\begin{gather*}
+\inference{
+}{
+	\bisimE{\emptyset}{\emptyset}{\emptyset}
+}
+\quad
+\inference{
+	\Gamma \vdash E \approx E' \qquad
+	v \approx v' : T
+}{
+	\Gamma , x : T \vdash 
+	E [ x := v' ] \approx E' [ x := v' ]
+}
+\end{gather*}
+
+\fbox{\bisims{s}{s}{T}}
+\begin{gather*}
+\infr{}{\bisims{\error{l}}{\error{l}}{T}} \quad
+\infr{
+	\bisimv{v}{v'}{T}
+}{
+	\bisims{\shalt{v}}{\shalt{v'}}{T}
+}
+\\
+\infr{
+	\bisimv{v}{v'}{S} \\
+	\bisimK{K}{K'}{S}{T}
+}{
+	\bisims{\scont{v}{K}}{\scont{v}{K'}}{T}
+} \quad
+\infr{
+	\expressiontyping{\Gamma}{e}{S} \\
+	\bisimE{\Gamma}{E}{E'}          \\
+	\bisimK{K}{K'}{S}{T}
+}{
+	\bisims{\sexpr{e}{E}{K}}{\sexpr{e}{E'}{K'}}{T}
+}
+\end{gather*}
+
+\caption{Bisimulation between \RBMachine\ and \SMachine{C}. It is the smallest 
+congruence relation containing the shown rules. Everything to the left (resp. 
+right) of $\approx$ is in \RBMachine\ (resp. in \SMachine{C}).}
+\label{fig:bisim-SC-D}
+\end{figure}
+
+The central part of the proofs is a weak bisimulation between \RMachine{B} and \SMachine{C}.
+Fig.~\ref{fig:bisim-SC-D} defines the bisimulation relation.
+It is the smallest congruence relation containing the rules 
 in Fig.~\ref{fig:bisim-SC-D}.
@@
 
-\begin{lemma}[Lazy D $\mathit{applyCast}$ Preserves Bisimulation]
+\begin{lemma}[Lazy D $\denote{c}(v)$ Preserves Bisimulation]
 	\label{lem:LazyD-apply-cast-preserve-bisim}
@@
 
-\begin{lemma}[Lazy UD $\mathit{applyCast}$ Preserves Bisimulation]
+\begin{lemma}[Lazy UD $\denote{c}(v)$ Preserves Bisimulation]
 	\label{lem:LazyUD-apply-cast-preserve-bisim}
@@
 
-\begin{lemma}[Lazy D Weak Bisimulation between \LDMachine\ and \SMachine{C}]
-	\label{lem:weak-bisim-SC-D}
-	Assume $C$ implements Lazy D Cast ADT
-	and $s_1$ is a state in \LDMachine\
-	and $s_1'$ is a state in \SMachine{C}
-	and $\bisims{s_1}{s_1'}{T}$
-	then either
+\begin{lemma}[Weak Bisimulation between \RMachine{B} and \SMachine{C}] \label{lem:weak-bisimulation}
+Assume
 \begin{enumerate}
-\item $s_1  = \error{l}$
-  and $s_1' = \error{l}$
-  for some $l$, or
-\item $s_1 = \shalt{v}$
-  and $s_1' = \shalt{v'}$
-  and $\bisimv{v}{v'}{T}$
-  for some $v$ and $v'$, or
+    \item the blame strategy $B$ and $C$ agrees on the set of injectable types and
+    \item $\denote{c}(v)$ preserves the bisimulation relation (e.g. Lemma~\ref{lem:LazyD-apply-cast-preserve-bisim} and \ref{lem:LazyUD-apply-cast-preserve-bisim}) and
+    \item $s_1$ is a state in \RMachine{B} and
+    \item $s_1'$ is a state in \SMachine{C} and
+    \item $\bisims{s_1}{s_1'}{T}$
+\end{enumerate}	then either
+\begin{enumerate}
+\item $s_1  \text{ final}$ and $s_1' \text{ final}$ or
 \item $\reduceto{s_1}{^{+}s_2}$
@@
 \end{enumerate}
+where
+\begin{gather*}
+\infr{}{(\error{l})\text{ final}} \quad
+\infr{}{(\shalt{v})\text{ final}}
+\end{gather*}
 \end{lemma}
-%\begin{proof}
-%We proceed by case analysis on $\bisims{s_1}{s_1'}{T}$. 
-%\begin{description}
-%\item[Case $\inference{
-%}{
-%	\bisims{\error{l}}{\error{l}}{T}
-%}$]
-%This is case (1).
-%\item[Case $\inference{
-%	\bisimv{v}{v'}{T}
-%}{
-%	\bisims{\shalt{v}}{\shalt{v'}}{T}
-%}$]
-%This is case (2).
-%\item[Case $\inference{
-%	\expressiontyping{\Gamma}{e}{T} \\
-%	\bisimE{\Gamma}{E}{E'} \\
-%	K \approx K' : T
-%}{
-%	\bisims{\sexpr{e}{E}{K}}{\sexpr{e}{E'}{K'}}{T}
-%}$]
-%This is case (3). By case analysis on $e$.
-%\item[Case $\inference{
-%	\bisimv{v}{v'}{S} \\
-%	\bisimK{K}{K'}{S}{T}
-%}{
-%	\bisims{\scont{v}{K}}{\scont{v'}{K'}}{T}
-%}$]
-%This is case (3). By inversion on $\bisimK{K}{K'}{S}{T}$, we have
-%\[
-%\begin{array}{rcl}
-%K  & = &
-%\Kcons{
-%	\Fcast{\ccast{S_1}{l_1}{S_2}}
-%}{\ldots\Kcons{\Fcast{\ccast{S_{n-1}}{l_{n-1}}{S}}}{K_1}} \\
-%K' & = &
-%\Kcons{\Fcast{c'}}{k_1'}
-%\end{array}
-%\]
-%After zero or more transition steps, $\scont{v}{K}$ will either transition to 
-%$\scont{u}{K_1}$ for some $u$ or transition to $\error{l}$ for some $l$ if one 
-%of the cast fail. On the \SMachine{C} side, $\scont{v'}{K'}$ will either 
-%transition to $\applyCont{u'}{k_1'}$ for some $u'$ or transition to 
-%$\error{l'}$ for some $l'$ if the cast fail. Because the sequence of casts in 
-%$K$ bisimulates the cast in $K'$, we can show with  
-%Lemma~\ref{lem:LazyD-apply-cast-preserve-bisim} that either
-%\begin{itemize}
-%	\item all casts succeed and	$\bisimv{u}{u'}{S}$, or
-%	\item both machines transition to error state and $l = l'$
-%\end{itemize}
-%When all casts succeeded, we also have $\bisimK{K_1}{k_1'}{S}{T}$ and need to 
-%show that $\reduceto{\scont{u}{K_1}}{s_2}$ and $\applyCont{u'}{k_1'} = s_2'$ 
-%and $\bisims{s_2}{s_2'}{T}$ for some $s_2$ and $s_2'$.
-%%
-%We proceed by case analysis on $K$. The most interesting cases 
-%are function application and pair projection. Due to space limitation, 
-%we only illustrate the general idea with function applications
-%
-%\begin{description}
-%\item[Subcase $\infr{
-%	\bisimv{v_1}{v_1'}{\Pfunc{S}{T_1}} \qquad
-%	\bisimK{K_2}{K_2'}{T_1}{T}
-%}{
-%	\bisimK{
-%		\Kcons{\FappOX{v_1}}{K_2}
-%	}{
-%		\Kcons{\FappOX{v_1'}}{K_2'}
-%	}{S}{T}
-%}$] By inversion on $\bisimv{v_1}{v_1'}{\Pfunc{S}{T_1}}$ we know the proxies 
-%in $v_1$ bisimulate the proxies in $v_1'$. After a reasoning similar to the 
-%above one that we used to reason about casts in continuations, we know that 
-%either both machines will transition to error states if the input proxies fail 
-%in casting the argument, or both machines will transition to a state 
-%evaluation 
-%the function body.
-%\todo{need to elaborate this part, or just delete it.}
-%\end{description}
-%\end{description}
-%\end{proof}
-
-\begin{lemma}[Lazy UD Weak Bisimulation between \LUDMachine\ and \SMachine{C}]
-	\label{lem:weak-bisim-SC-UD}
-	Assume $C$ implements Lazy UD Cast ADT
-	and $\bisims{s_1}{s_1'}{T}$
-	then either
-	\begin{enumerate}
-		\item $s_1  = \error{l}$
-		and $s_1' = \error{l}$
-		for some $l$, or
-		\item $s_1 = \shalt{v}$
-		and $s_1' = \shalt{v'}$
-		and $\bisimv{v}{v'}{T}$
-		for some $v$ and $v'$, or
-		\item $\reduceto{s_1}{^{+}s_2}$
-		and $\reduceto{s_1'}{^{+}s_2'}$
-		and $\bisims{s_2}{s_2'}{T}$
-	\end{enumerate}
-\end{lemma}
-%\begin{proof}
+\todo[inline]{KC: wouldn't it be great if I can describe the main ideas of the proof?}
+
+% \begin{lemma}[Lazy D Weak Bisimulation between \LDMachine\ and \SMachine{C}]
+% 	\label{lem:weak-bisim-SC-D}
+% 	Assume $C$ implements Lazy D Cast ADT
+% 	and $s_1$ is a state in \LDMachine\
+% 	and $s_1'$ is a state in \SMachine{C}
+% 	and $\bisims{s_1}{s_1'}{T}$
+% 	then either
+% \begin{enumerate}
+% \item $s_1  = \error{l}$
+%   and $s_1' = \error{l}$
+%   for some $l$, or
+% \item $s_1 = \shalt{v}$
+%   and $s_1' = \shalt{v'}$
+%   and $\bisimv{v}{v'}{T}$
+%   for some $v$ and $v'$, or
+% \item $\reduceto{s_1}{^{+}s_2}$
+%   and $\reduceto{s_1'}{^{+}s_2'}$
+%   and $\bisims{s_2}{s_2'}{T}$
+% \end{enumerate}
+% \end{lemma}
+% %\begin{proof}
+% %We proceed by case analysis on $\bisims{s_1}{s_1'}{T}$. 
+% %\begin{description}
+% %\item[Case $\inference{
+% %}{
+% %	\bisims{\error{l}}{\error{l}}{T}
+% %}$]
+% %This is case (1).
+% %\item[Case $\inference{
+% %	\bisimv{v}{v'}{T}
+% %}{
+% %	\bisims{\shalt{v}}{\shalt{v'}}{T}
+% %}$]
+% %This is case (2).
+% %\item[Case $\inference{
+% %	\expressiontyping{\Gamma}{e}{T} \\
+% %	\bisimE{\Gamma}{E}{E'} \\
+% %	K \approx K' : T
+% %}{
+% %	\bisims{\sexpr{e}{E}{K}}{\sexpr{e}{E'}{K'}}{T}
+% %}$]
+% %This is case (3). By case analysis on $e$.
+% %\item[Case $\inference{
+% %	\bisimv{v}{v'}{S} \\
+% %	\bisimK{K}{K'}{S}{T}
+% %}{
+% %	\bisims{\scont{v}{K}}{\scont{v'}{K'}}{T}
+% %}$]
+% %This is case (3). By inversion on $\bisimK{K}{K'}{S}{T}$, we have
+% %\[
+% %\begin{array}{rcl}
+% %K  & = &
+% %\Kcons{
+% %	\Fcast{\ccast{S_1}{l_1}{S_2}}
+% %}{\ldots\Kcons{\Fcast{\ccast{S_{n-1}}{l_{n-1}}{S}}}{K_1}} \\
+% %K' & = &
+% %\Kcons{\Fcast{c'}}{k_1'}
+% %\end{array}
+% %\]
+% %After zero or more transition steps, $\scont{v}{K}$ will either transition to 
+% %$\scont{u}{K_1}$ for some $u$ or transition to $\error{l}$ for some $l$ if one 
+% %of the cast fail. On the \SMachine{C} side, $\scont{v'}{K'}$ will either 
+% %transition to $\applyCont{u'}{k_1'}$ for some $u'$ or transition to 
+% %$\error{l'}$ for some $l'$ if the cast fail. Because the sequence of casts in 
+% %$K$ bisimulates the cast in $K'$, we can show with  
+% %Lemma~\ref{lem:LazyD-apply-cast-preserve-bisim} that either
+% %\begin{itemize}
+% %	\item all casts succeed and	$\bisimv{u}{u'}{S}$, or
+% %	\item both machines transition to error state and $l = l'$
+% %\end{itemize}
+% %When all casts succeeded, we also have $\bisimK{K_1}{k_1'}{S}{T}$ and need to 
+% %show that $\reduceto{\scont{u}{K_1}}{s_2}$ and $\applyCont{u'}{k_1'} = s_2'$ 
+% %and $\bisims{s_2}{s_2'}{T}$ for some $s_2$ and $s_2'$.
+% %%
+% %We proceed by case analysis on $K$. The most interesting cases 
+% %are function application and pair projection. Due to space limitation, 
+% %we only illustrate the general idea with function applications
+% %
+% %\begin{description}
+% %\item[Subcase $\infr{
+% %	\bisimv{v_1}{v_1'}{\Pfunc{S}{T_1}} \qquad
+% %	\bisimK{K_2}{K_2'}{T_1}{T}
+% %}{
+% %	\bisimK{
+% %		\Kcons{\FappOX{v_1}}{K_2}
+% %	}{
+% %		\Kcons{\FappOX{v_1'}}{K_2'}
+% %	}{S}{T}
+% %}$] By inversion on $\bisimv{v_1}{v_1'}{\Pfunc{S}{T_1}}$ we know the proxies 
+% %in $v_1$ bisimulate the proxies in $v_1'$. After a reasoning similar to the 
+% %above one that we used to reason about casts in continuations, we know that 
+% %either both machines will transition to error states if the input proxies fail 
+% %in casting the argument, or both machines will transition to a state 
+% %evaluation 
+% %the function body.
+% %\todo{need to elaborate this part, or just delete it.}
+% %\end{description}
+% %\end{description}
+% %\end{proof}
+
+% \begin{lemma}[Lazy UD Weak Bisimulation between \LUDMachine\ and \SMachine{C}]
+% 	\label{lem:weak-bisim-SC-UD}
+% 	Assume $C$ implements Lazy UD Cast ADT
+% 	and $\bisims{s_1}{s_1'}{T}$
+% 	then either
+% 	\begin{enumerate}
+% 		\item $s_1  = \error{l}$
+% 		and $s_1' = \error{l}$
+% 		for some $l$, or
+% 		\item $s_1 = \shalt{v}$
+% 		and $s_1' = \shalt{v'}$
+% 		and $\bisimv{v}{v'}{T}$
+% 		for some $v$ and $v'$, or
+% 		\item $\reduceto{s_1}{^{+}s_2}$
+% 		and $\reduceto{s_1'}{^{+}s_2'}$
+% 		and $\bisims{s_2}{s_2'}{T}$
+% 	\end{enumerate}
+% \end{lemma}
+% \begin{proof}
 % 	Similar to Lemma~\ref{lem:weak-bisim-SC-D}.
-%\end{proof}
+% \end{proof}
 
@@
 \end{theorem}
-\begin{proof}
-	By the definitions of $\textit{eval}$, we need to show 
-	\[
-	\transitivelyreducetoM{\RMachine{B}}{\sexpr{e}{\emptyset}{\Knil}}{
-		s
-	}
-	\;\text{if and only if}\;
-	\transitivelyreducetoM{\SMachine{C}}{\sexpr{e}{\emptyset}{\mkCont{\Knil}}}{
-		s'
-	}
-	\]
-	where $s$ and $s'$ are bisimuated final states, i.e. of the form 
-	$\shalt{v}$ or $\error{l}$. The initial states are related by the 
-	bisimulation relation, so we can prove this theorem with 
-	Lemma~\ref{lem:weak-bisim-SC-D}.
-\end{proof}
+% \begin{proof}
+% 	By the definitions of $\textit{eval}$, we need to show 
+% 	\[
+% 	\transitivelyreducetoM{\RMachine{B}}{\sexpr{e}{\emptyset}{\Knil}}{
+% 		s
+% 	}
+% 	\;\text{if and only if}\;
+% 	\transitivelyreducetoM{\SMachine{C}}{\sexpr{e}{\emptyset}{\mkCont{\Knil}}}{
+% 		s'
+% 	}
+% 	\]
+% 	where $s$ and $s'$ are bisimuated final states, i.e. of the form 
+% 	$\shalt{v}$ or $\error{l}$. The initial states are related by the 
+% 	bisimulation relation, so we can prove this theorem with 
+% 	Lemma~\ref{lem:weak-bisim-SC-D}.
+% \end{proof}
 
@@
 \end{theorem}
-\begin{proof}
-	Similar to Theorem~\ref{thm:SD-equiv}.
-\end{proof}
+% \begin{proof}
+% 	Similar to Theorem~\ref{thm:SD-equiv}.
+% \end{proof}
 
@@
 
-\todo[inline]{KC: Should we mention KC and Deyaa as citation?
+\todo[inline]{KC: (About the following paragraph) Should we mention KC and Deyaa as citation?
 (something like in private communication with KC and Deyaa)}
@@
 (Cast ADT and its refinements Lazy D Cast ADT and \LUD\ \CastADT), 
-a parameterized abstract machine \effCEK{C}, 
+a parameterized abstract machine \SMachine{C}, 
 a theorem which states that \SMachine{C} is equivalent
@@
 
-\begin{thebibliography}{8}
-\bibitem{ref_article1}
-Author, F.: Article title. Journal \textbf{2}(5), 99--110 (2016)
-
-\bibitem{ref_lncs1}
-Author, F., Author, S.: Title of a proceedings paper. In: Editor,
-F., Editor, S. (eds.) CONFERENCE 2016, LNCS, vol. 9999, pp. 1--13.
-Springer, Heidelberg (2016). \doi{10.10007/1234567890}
-
-\bibitem{ref_book1}
-Author, F., Author, S., Author, T.: Book title. 2nd edn. Publisher,
-Location (1999)
-
-\bibitem{ref_proc1}
-Author, A.-B.: Contribution title. In: 9th International Proceedings
-on Proceedings, pp. 1--2. Publisher, Location (2010)
-
-\bibitem{ref_url1}
-LNCS Homepage, \url{http://www.springer.com/lncs}. Last accessed 4
-Oct 2017
-\end{thebibliography}
 \end{document}

### 2020-09-27 paper.tex
label polarity renaming "car" to "fst" renaming "cdr" to "snd"

--- 2020-09-21 samplepaper.tex
@@
-% This is samplepaper.tex, a sample chapter demonstrating the
-% LLNCS macro package for Springer Computer Science proceedings;
 % Version 2.20 of 2017/10/04
@@
 %% http://ctan.org/pkg/booktabs
-\usepackage{subcaption} %% For complex figures with subfigures/subcaptions
+%\usepackage{subcaption} %% For complex figures with subfigures/subcaptions
 %% http://ctan.org/pkg/subcaption
@@
 \usepackage[T1]{fontenc}
-\usepackage{natbib} %% For more citation commames (\cite etc.)
+\usepackage[numbers]{natbib} %% For more citation commames (\cite etc.)
 \usepackage{listings} %% For typesetting code
@@
 \newcommand{\SMachine}[1]{\ensuremath{\mathcal{S}(#1)}}
+\newcommand{\effCEK}[1]{\ensuremath{\mathcal{S}(#1)}}
 
@@
 \newcommand{\econs}[2]{\mathtt{cons} \; #1 \; #2}
-\newcommand{\ecar}[1]{\mathtt{car} \; #1}
-\newcommand{\ecdr}[1]{\mathtt{cdr} \; #1}
+\newcommand{\efst}[1]{\mathtt{fst} \; #1}
+\newcommand{\esnd}[1]{\mathtt{snd} \; #1}
 %\newcommand{\ecast}[2]{#1 \langle #2 \rangle}
@@
 \newcommand{\FconsOX}[1]{\econs{#1}{\square}}
-\newcommand{\Fcar}[0]{\ecar{\square}}
-\newcommand{\Fcdr}[0]{\ecdr{\square}}
+\newcommand{\Ffst}[0]{\efst{\square}}
+\newcommand{\Fsnd}[0]{\esnd{\square}}
 \newcommand{\Fcast}[1]{\ecast{\square}{#1}}
@@
 \newcommand{\cod}[1]{\ensuremath{\mathrm{cod}(#1)}}
-\newcommand{\car}[1]{\ensuremath{\mathrm{fst}(#1)}}
-\newcommand{\cdr}[1]{\ensuremath{\mathrm{snd}(#1)}}
+\newcommand{\fst}[1]{\ensuremath{\mathrm{fst}(#1)}}
+\newcommand{\snd}[1]{\ensuremath{\mathrm{snd}(#1)}}
 \newcommand{\id}[1]{\ensuremath{\mathrm{id}(#1)}}
@@
 we present an abstract machine that is employed in our framework. Then
-we review coercions and their normal forms (Subsection~\ref{sec:coercions-in-normal-form}), which
+we review coercions and their normal forms (Subsection~\ref{sec:coercions}), which
 motivates and inspires the design of hypercoercions.
@@
 \begin{array}{lrcl}
-\text{Blame Labels} & l \\
+\text{Blame Labels} & l,\bar{l} \\
 \text{Variables} & x,y,z \\
@@
 	\econs{e}{e}  \mid
-	\ecar{e}      \mid
-	\ecdr{e}
+	\efst{e}      \mid
+	\esnd{e}
 }
@@
 $\ecast{e}{\ccast{S}{l}{T}}$, which are responsible for runtime type
-checking. Polarities of blame labels is not treated but are straightforward to 
-incorporate. The syntax and static semantics is the same as that of 
+checking. Blame labels can be positive (blaming the expression inside the cast)
+or negative (blaming the context outside the cast), as in \cite{Wadler:2009qv,Siek:2015ab}.
+The syntax and static semantics is the same as that of 
 \citep{siek2009exploring} except for a few minor exceptions:
@@
 \stxrulecont{
-	\Fcar \mid
-	\Fcdr \mid
+	\Ffst \mid
+	\Fsnd \mid
 	\FconsXO{e}{E}  \mid
@@
 	}{}
-	\figreduceto{\sexpr{\ecar{e}}{E}{K}}{\sexpr{e}{E}{\Kcons{\Fcar}{K}}}{}
-	\figreduceto{\sexpr{\ecdr{e}}{E}{K}}{\sexpr{e}{E}{\Kcons{\Fcdr}{K}}}{}
+	\figreduceto{\sexpr{\efst{e}}{E}{K}}{\sexpr{e}{E}{\Kcons{\Ffst}{K}}}{}
+	\figreduceto{\sexpr{\esnd{e}}{E}{K}}{\sexpr{e}{E}{\Kcons{\Fsnd}{K}}}{}
 	\figreducetoH{
@@
 		\scont{v}{
-			\Kcons{\Fcast{\ccast{S_2}{l}{S_1}}}{
+			\Kcons{\Fcast{\ccast{S_2}{\bar{l}}{S_1}}}{
 				\Kcons{\FappOX{u}}{
@@
 	}{}
-	\figreduceto{\scont{\vcons{v_1}{v_2}}{\Kcons{\Fcar}{K}}}{\scont{v_1}{K}}{}
-	\figreducetoH{\scont{\vconsc{u}{S_1}{T_1}{l}{S_2}{T_2}}{\Kcons{\Fcar}{K}}}{
+	\figreduceto{\scont{\vcons{v_1}{v_2}}{\Kcons{\Ffst}{K}}}{\scont{v_1}{K}}{}
+	\figreducetoH{\scont{\vconsc{u}{S_1}{T_1}{l}{S_2}{T_2}}{\Kcons{\Ffst}{K}}}{
 		\scont{u}{
-			\Kcons{\Fcar}{
+			\Kcons{\Ffst}{
 				\Kcons{\Fcast{\ccast{S_1}{l}{S_2}}}{K}}}	
 	}{}
-	\figreduceto{\scont{\vcons{v_1}{v_2}}{\Kcons{\Fcdr}{K}}}{\scont{v_2}{K}}{}
-	\figreducetoH{\scont{\vconsc{u}{S_1}{T_1}{l}{S_2}{T_2}}{\Kcons{\Fcdr}{K}}}{
+	\figreduceto{\scont{\vcons{v_1}{v_2}}{\Kcons{\Fsnd}{K}}}{\scont{v_2}{K}}{}
+	\figreducetoH{\scont{\vconsc{u}{S_1}{T_1}{l}{S_2}{T_2}}{\Kcons{\Fsnd}{K}}}{
 		\scont{u}{
-			\Kcons{\Fcdr}{
+			\Kcons{\Fsnd}{
 				\Kcons{\Fcast{\ccast{T_1}{l}{T_2}}}{K}}}	
@@
 \subsection{Coercions and Normal Forms} 
-\label{sec:coercion-calculus}
+\label{sec:coercions}
 
@@
 	\begin{array}{lrcl}
-	\stxrule{I,J}{Injectable types (\LD)}{
-		\Pfunc{T}{T} \mid \Pbool}
-	\stxrule{I,J}{Injectable types (\LUD)}{
-		\Pfunc{\Tdyn}{\Tdyn} \mid \Pbool
-	}
+	\stxrule{I,J}{Injectable types (\LD)}{P}
+	\stxrule{I,J}{Injectable types (\LUD)}{G}
 	\stxrule{c,d}{Coercions}{
@@
 definition of injectable types depends on the blame strategy, as in 
-Chapter~\ref{chap:background}.
+Subsection~\ref{sec:cast-calculi}.
 %
@@
 	\stxrulecont{
-		\Fcar \mid
-		\Fcdr \mid
+		\Ffst \mid
+		\Fsnd \mid
 		\FconsXO{e}{E}  \mid
@@
 	}{}
-	\figreduceto{\sexpr{\ecar{e}}{E}{K}}{
-		\sexpr{e}{E}{\mkCont{\Kcons{\Fcar}{K}}}
-	}{}
-	\figreduceto{\sexpr{\ecdr{e}}{E}{K}}{
-		\sexpr{e}{E}{\mkCont{\Kcons{\Fcdr}{K}}}
+	\figreduceto{\sexpr{\efst{e}}{E}{K}}{
+		\sexpr{e}{E}{\mkCont{\Kcons{\Ffst}{K}}}
+	}{}
+	\figreduceto{\sexpr{\esnd{e}}{E}{K}}{
+		\sexpr{e}{E}{\mkCont{\Kcons{\Fsnd}{K}}}
 	}{}
@@
 	\figequaltoH{
-		\applyCont{\ecast{\vcons{v_1}{v_2}}{\Pprod{c_1}{c_2}}}{\Kcons{\Fcar}{K}}
+		\applyCont{\ecast{\vcons{v_1}{v_2}}{\Pprod{c_1}{c_2}}}{\Kcons{\Ffst}{K}}
 	}{
@@
 	\figequaltoH{
-		\applyCont{\ecast{\vcons{v_1}{v_2}}{\Pprod{c_1}{c_2}}}{\Kcons{\Fcdr}{K}}
+		\applyCont{\ecast{\vcons{v_1}{v_2}}{\Pprod{c_1}{c_2}}}{\Kcons{\Fsnd}{K}}
 	}{
@@
 			\Pfunc{
-				(\compose{\translate{\ccast{S_2}{l}{S_1}}}{c})}{
+				(\compose{\translate{\ccast{S_2}{\bar{l}}{S_1}}}{c})}{
 				(\compose{d}{\translate{\ccast{T_1}{l}{T_2}}})}}$
@@
 	\bisimc{
-		(\ccast{S_n}{l_{n-1}}{S_{n-1}} \ldots
-		\ccast{S_2}{l_1}{S_1})
+		(\ccast{S_n}{\bar{l}_{n-1}}{S_{n-1}} \ldots
+		\ccast{S_2}{\bar{l}_1}{S_1})
 	}{c}{S_n}{S_1}
@@
 	\hcmprod{
-		(\composegap{c_1}{\car{g}}{c_2})}{
-		(\composegap{d_1}{\cdr{g}}{d_2})}
+		(\composegap{c_1}{\fst{g}}{c_2})}{
+		(\composegap{d_1}{\snd{g}}{d_2})}
 }{}
@@
 
-\fbox{$\car{g}=g$}
+\fbox{$\fst{g}=g$}
 \[
 \begin{array}{rclr}
-\figequalto{\car{\gnone}}{\gnone}{}
-\figequalto{\car{\gsome{\Pprod{S_1}{T_1}}{l}{\Pprod{S_2}{T_2}}}}{
+\figequalto{\fst{\gnone}}{\gnone}{}
+\figequalto{\fst{\gsome{\Pprod{S_1}{T_1}}{l}{\Pprod{S_2}{T_2}}}}{
 	\gsome{S_1}{l}{S_2}
@@
 
-\fbox{$\cdr{g}=g$}
+\fbox{$\snd{g}=g$}
 \[
 \begin{array}{rclr}
-\figequalto{\cdr{\gnone}}{\gnone}{}
-\figequalto{\cdr{\gsome{\Pprod{S_1}{T_1}}{l}{\Pprod{S_2}{T_2}}}}{
+\figequalto{\snd{\gnone}}{\gnone}{}
+\figequalto{\snd{\gsome{\Pprod{S_1}{T_1}}{l}{\Pprod{S_2}{T_2}}}}{
 	\gsome{T_1}{l}{T_2}

### 2020-09-27 paper.tex
minor changes

@@
 \newcommand{\sidecond}[1]{\text{if}\;#1}
+\newcommand{\urlFrameworkAndIllustration}{
+	\url{https://github.com/LuKC1024/esop-2020}
+}
 
@@
 implicitly between types that have no conflicting type information.
+At runtime, casts store or check type information to enforce type soundness.
 Researchers usually define the semantics of gradually typed languages by
@@
 calculus \citep{wadler2009well} and other cast calculi \citep{siek2009exploring}.
-At runtime, casts store or check type information to enforce type soundness.
 % To allow the smooth transition, every gradually typed language
@@
 We believe the framework is also applicable to other cast representations.
-\todo[inline]{KC: (about the p above) I want to put the illustration part on the same github repo, adding description as
-Agda comments. }
+The framework and the illustration are available at the following URL:
+\[\text{\urlFrameworkAndIllustration}\]
 
@@
 Next, we define the CEK Machine for \LUD. The only differences with
-respect to \LD\ are in the injectable types and in the definition of the 
-${\mathit{applyCast}(v,\ccast{S}{l}{T})}$
-function, in which a cast whose source or target is the dynamic type
-\Tdyn\ is always split into two casts that go through a ground type, that is, a 
+respect to \LD\ are in the injectable types and in 
+${\mathit{applyCast}(v,\ccast{S}{l}{T})}$, in which a cast whose source or
+target is the dynamic type \Tdyn\ is always split into two casts that
+go through a ground type, that is, a 
 type in which all sub-components are the dynamic type, such as 
@@
 Taking out the second part of a pair is similar.
-\todo[inline]{KC: I want to give a brief discussion on inert v.s. active pairs.}
 
@@
 
-\todo[inline]{KC: In the latex file, below are two versions of a figure.
-One is the same as in our WGT paper. The other uses Z as the meta variable of sequences of 
-source-code casts, which is similar to the blame-and-coercion paper.}
-
 \begin{figure}
@@
 		}{\ldots\Kcons{\Fcast{\ccast{S_{n-1}}{l_{n-1}}{S_n}}}{K}}
-	}{
-		\Kcons{\Fcast{c'}}{k'}
-	}{S_1}{T}
-}
-\end{gather*}
-
-\fbox{$\bisimv{v}{v}{T}$}
-\begin{gather*}
-\infr{
-	\expressiontyping{\Gamma,x : S_1}{e}{T_1}
-	\qquad
-	\bisimE{\Gamma}{E}{E'}
-	\\
-	\bisimc{
-		(\ccast{S_n}{l_{n-1}}{S_{n-1}} \ldots
-		\ccast{S_2}{l_1}{S_1})
-	}{c}{S_n}{S_1}
-	\\
-	\bisimc{
-		(		\ccast{T_1}{l_{1}}{T_2} \ldots
-		\ccast{T_{n-1}}{l_{n-1}}{T_n}
-		)	}{d}{T_1}{T_n}
-	\\
-	v = \vfuncc{
-		\vfuncc{
-			\vfunc{x}{S_1}{e}{E}
-		}{S_1}{T_1}{l_1}{S_2}{T_2}
-		\ldots
-	}{S_{n-1}}{T_{n-1}}{l_{n-1}}{S_n}{T_n}
-}{
-	\bisimv{v}{
-		(\ecast{\vfunc{x}{S_1}{e}{E'}}{\Pfunc{c}{d}})
-	}{
-		\Pfunc{S_n}{T_n}}
-}
-\\[1ex]
-\infr{
-	\bisimv{v_1}{v_1'}{S_1} \qquad
-	\bisimv{v_2}{v_2'}{T_1} \\
-	\bisimc{
-		(\ccast{S_1}{l_{1}}{S_2} \ldots
-		\ccast{S_{n-1}}{l_{n-1}}{S_n})
-	}{c}{S_1}{S_n} \\
-	\bisimc{
-		(\ccast{T_1}{l_{1}}{T_2} \ldots
-		\ccast{T_{n-1}}{l_{n-1}}{T_n})
-	}{d}{T_1}{T_n}
-	\\ v = \vconsc{
-		\vconsc{
-			\vcons{v_1}{u_1}
-		}{S_1}{T_1}{l_1}{S_2}{T_2}
-		\ldots
-	}{S_{n-1}}{T_{n-1}}{l_{n-1}}{S_n}{T_n}
-}{
-	\bisimv{
-		v
-	}{
-		(\ecast{\vcons{v_2}{u_2}}{\Pprod{c}{d}})
-	}{
-		\Pprod{S_n}{T_n}}
-}
-\end{gather*}
-
-\fbox{\bisimE{\Gamma}{E}{E}}
-\begin{gather*}
-\inference{
-}{
-	\bisimE{\emptyset}{\emptyset}{\emptyset}
-}
-\quad
-\inference{
-	\Gamma \vdash E \approx E' \qquad
-	v \approx v' : T
-}{
-	\Gamma , x : T \vdash 
-	E [ x := v' ] \approx E' [ x := v' ]
-}
-\end{gather*}
-
-\fbox{\bisims{s}{s}{T}}
-\begin{gather*}
-\infr{}{\bisims{\error{l}}{\error{l}}{T}} \quad
-\infr{
-	\bisimv{v}{v'}{T}
-}{
-	\bisims{\shalt{v}}{\shalt{v'}}{T}
-}
-\\
-\infr{
-	\bisimv{v}{v'}{S} \\
-	\bisimK{K}{K'}{S}{T}
-}{
-	\bisims{\scont{v}{K}}{\scont{v}{K'}}{T}
-} \quad
-\infr{
-	\expressiontyping{\Gamma}{e}{S} \\
-	\bisimE{\Gamma}{E}{E'}          \\
-	\bisimK{K}{K'}{S}{T}
-}{
-	\bisims{\sexpr{e}{E}{K}}{\sexpr{e}{E'}{K'}}{T}
-}
-\end{gather*}
-
-\caption{Bisimulation between \RBMachine\ and \SMachine{C}. It is the smallest 
-congruence relation containing the shown rules. Everything to the left (resp. 
-right) of $\approx$ is in \RBMachine\ (resp. in \SMachine{C}).}
-\label{fig:bisim-SC-D}
-\end{figure}
-
-\begin{figure}
-
-\fbox{\bisimc{Z}{c}{S}{T}}
-\begin{gather*}
-\infr{}{\bisimc{[]}{id(T)}{T}{T}} \quad
-\infr{}{\bisimc{[\ccast{S}{l}{T}]}{\translate{\ccast{S}{l}{T}}}{S}{T}}
-\\[1ex]
-\infr{
-	\bisimc{Z_1}{c_1}{T_1}{T_2}\\
-	\bisimc{Z_2}{c_2}{T_2}{T_3}
-}{
-	\bisimc{(Z_1 \mathrm{++} Z_2)}{(\compose{c_1}{c_2})}{T_1}{T_3}
-}
-\end{gather*}
-
-\fbox{$\bisimK{K}{K}{S}{T}$}
-\begin{gather*}
-\infr{
-	\bisimK{K}{k'}{S_n}{T} \qquad
-	\bisimc{Z}{c}{S_1}{S_n}
-}{
-	\bisimK{
-		\Kcons{\Fcast{Z}}{K}
 	}{
@@
 \end{figure}
+
+% \begin{figure}
+
+% \fbox{\bisimc{Z}{c}{S}{T}}
+% \begin{gather*}
+% \infr{}{\bisimc{[]}{id(T)}{T}{T}} \quad
+% \infr{}{\bisimc{[\ccast{S}{l}{T}]}{\translate{\ccast{S}{l}{T}}}{S}{T}}
+% \\[1ex]
+% \infr{
+% 	\bisimc{Z_1}{c_1}{T_1}{T_2}\\
+% 	\bisimc{Z_2}{c_2}{T_2}{T_3}
+% }{
+% 	\bisimc{(Z_1 \mathrm{++} Z_2)}{(\compose{c_1}{c_2})}{T_1}{T_3}
+% }
+% \end{gather*}
+
+% \fbox{$\bisimK{K}{K}{S}{T}$}
+% \begin{gather*}
+% \infr{
+% 	\bisimK{K}{k'}{S_n}{T} \qquad
+% 	\bisimc{Z}{c}{S_1}{S_n}
+% }{
+% 	\bisimK{
+% 		\Kcons{\Fcast{Z}}{K}
+% 	}{
+% 		\Kcons{\Fcast{c'}}{k'}
+% 	}{S_1}{T}
+% }
+% \end{gather*}
+
+% \fbox{$\bisimv{v}{v}{T}$}
+% \begin{gather*}
+% \infr{
+% 	\expressiontyping{\Gamma,x : S_1}{e}{T_1}
+% 	\qquad
+% 	\bisimE{\Gamma}{E}{E'}
+% 	\\
+% 	\bisimc{
+% 		(\ccast{S_n}{\bar{l}_{n-1}}{S_{n-1}} \ldots
+% 		\ccast{S_2}{\bar{l}_1}{S_1})
+% 	}{c}{S_n}{S_1}
+% 	\\
+% 	\bisimc{
+% 		(		\ccast{T_1}{l_{1}}{T_2} \ldots
+% 		\ccast{T_{n-1}}{l_{n-1}}{T_n}
+% 		)	}{d}{T_1}{T_n}
+% 	\\
+% 	v = \vfuncc{
+% 		\vfuncc{
+% 			\vfunc{x}{S_1}{e}{E}
+% 		}{S_1}{T_1}{l_1}{S_2}{T_2}
+% 		\ldots
+% 	}{S_{n-1}}{T_{n-1}}{l_{n-1}}{S_n}{T_n}
+% }{
+% 	\bisimv{v}{
+% 		(\ecast{\vfunc{x}{S_1}{e}{E'}}{\Pfunc{c}{d}})
+% 	}{
+% 		\Pfunc{S_n}{T_n}}
+% }
+% \\[1ex]
+% \infr{
+% 	\bisimv{v_1}{v_1'}{S_1} \qquad
+% 	\bisimv{v_2}{v_2'}{T_1} \\
+% 	\bisimc{
+% 		(\ccast{S_1}{l_{1}}{S_2} \ldots
+% 		\ccast{S_{n-1}}{l_{n-1}}{S_n})
+% 	}{c}{S_1}{S_n} \\
+% 	\bisimc{
+% 		(\ccast{T_1}{l_{1}}{T_2} \ldots
+% 		\ccast{T_{n-1}}{l_{n-1}}{T_n})
+% 	}{d}{T_1}{T_n}
+% 	\\ v = \vconsc{
+% 		\vconsc{
+% 			\vcons{v_1}{u_1}
+% 		}{S_1}{T_1}{l_1}{S_2}{T_2}
+% 		\ldots
+% 	}{S_{n-1}}{T_{n-1}}{l_{n-1}}{S_n}{T_n}
+% }{
+% 	\bisimv{
+% 		v
+% 	}{
+% 		(\ecast{\vcons{v_2}{u_2}}{\Pprod{c}{d}})
+% 	}{
+% 		\Pprod{S_n}{T_n}}
+% }
+% \end{gather*}
+
+% \fbox{\bisimE{\Gamma}{E}{E}}
+% \begin{gather*}
+% \inference{
+% }{
+% 	\bisimE{\emptyset}{\emptyset}{\emptyset}
+% }
+% \quad
+% \inference{
+% 	\Gamma \vdash E \approx E' \qquad
+% 	v \approx v' : T
+% }{
+% 	\Gamma , x : T \vdash 
+% 	E [ x := v' ] \approx E' [ x := v' ]
+% }
+% \end{gather*}
+
+% \fbox{\bisims{s}{s}{T}}
+% \begin{gather*}
+% \infr{}{\bisims{\error{l}}{\error{l}}{T}} \quad
+% \infr{
+% 	\bisimv{v}{v'}{T}
+% }{
+% 	\bisims{\shalt{v}}{\shalt{v'}}{T}
+% }
+% \\
+% \infr{
+% 	\bisimv{v}{v'}{S} \\
+% 	\bisimK{K}{K'}{S}{T}
+% }{
+% 	\bisims{\scont{v}{K}}{\scont{v}{K'}}{T}
+% } \quad
+% \infr{
+% 	\expressiontyping{\Gamma}{e}{S} \\
+% 	\bisimE{\Gamma}{E}{E'}          \\
+% 	\bisimK{K}{K'}{S}{T}
+% }{
+% 	\bisims{\sexpr{e}{E}{K}}{\sexpr{e}{E'}{K'}}{T}
+% }
+% \end{gather*}
+
+% \caption{Bisimulation between \RBMachine\ and \SMachine{C}. It is the smallest 
+% congruence relation containing the shown rules. Everything to the left (resp. 
+% right) of $\approx$ is in \RBMachine\ (resp. in \SMachine{C}).}
+% \label{fig:bisim-SC-D}
+% \end{figure}
 
@@
 	\hcmfail{l}
-}{\sidecond{
+}{\\&&\sidecond{
 		\notshallowlyconsistent{P}{Q}
@@
 	\hcmfail{l}
-}{\sidecond{
+}{\\&&\sidecond{
 		\goodgap{g}

### 2020-09-30 paper.tex
edits to section 1

@@
 \todo[inline]{KC: Cite "Contracts for higher-order functions" for the proxy-based approach maybe?}
+\todo[inline]{JS: That paper doesn't exactly fit into what you're talking about in the above
+sentence. It might be appopriate to cite it elsewhere in the paper. Also,
+there are earlier papers about coercive subtyping (Computing with coercions by Breazu-Tannen et al)
+that use a proxy-based approach. The contracts paper may be the first to propose blame tracking.}
 
 Gradual typing \citep{siek2006gradual,siek2015refined} includes both static typing 
-and dynamic typing in the same language, enables smooth transition between them, while
+and dynamic typing in the same language and enables a smooth transition between them while
 enforcing type soundness.
-To allow the smooth transition, gradually typed languages are featuerd by a special type
-typically written as \Tdyn\ or \lstinline|Dyn| or \lstinline|Any|, which enables 
-imprecise type annotations. A gradual type checker allows programmers to cast 
+To enable a smooth transition, gradually typed languages feature a special type
+typically written as \Tdyn{}, \lstinline|Dyn|, or \lstinline|Any|, which
+provides a way to write imprecise type annotations. A gradual type checker allows programmers to cast 
 implicitly between types that have no conflicting type information.
-At runtime, casts store or check type information to enforce type soundness.
-Researchers usually define the semantics of gradually typed languages by
+At runtime, casts record and check type information to enforce type soundness.
+Researchers often define the semantics of gradually typed languages by
 translation to an intermediate language with explicit casts, such as the blame
@@
 \citep{herman2010space}.
-For instance, the following module define functions 
+For instance, consider the following functions 
 that check the parity of natural numbers. The terms are ordinary, while the 
@@
 \end{lstlisting}
-These functions look tail-recursive, so it is natural to expect that they 
-consumes constant space. This is not the case, however, in a straightforward 
-implementation because there is a cast around each of the 
-``tail call'', one from \lstinline|Bool| to 
-\lstinline|$\star$|, the other goes the other way.
-A straightforward implementation would cast the output of the recursive 
-call \textit{before} returning it, which effectively breaks the tail recursion 
-and thus changes the space complexity.
-
-Continuation is not the only place where casts might accumulate. 
-Consider a variant of the above program written in continuation-passing style. 
-Here, both functions returns \lstinline|Bool| so there is not pending cast in 
-continuations. The continuation argument \lstinline|k|, however, is wrapped in 
-a cast in each recursive call because the type of \lstinline|k| is less 
-precise in \lstinline|even?|.
+These functions look tail-recursive, so it is natural to expect that
+they consumes constant space. This is not the case, however, in a
+straightforward implementation because there is an implicit cast
+around each of the recursive calls, one from \lstinline|Bool| to
+\lstinline|$\star$| and the other from \lstinline|$\star$| to
+\lstinline|Bool|.  A straightforward implementation would perform this
+cast after the recursive calls but \textit{before} returning from the
+current function. So the calls are not in fact tail calls and the
+space complexity is linear instead of constant.
+
+Continuations are not the only place where casts can accumulate.
+Consider a variant of the above program written in
+continuation-passing style.  Here, both functions returns
+\lstinline|Bool| so there is no implicit cast in tail position.
+However, the argument \lstinline|k| is wrapped in a cast in each
+recursive call because the type of \lstinline|k| is less precise in
+\lstinline|even?| than it is in \lstinline|odd?|.
 \begin{lstlisting}
@@
 \end{lstlisting}
-Our examples programs are inspired by the examples in \citep{herman2010space}.
-We direct interested readers to their work for more examples and detailed explanation.
-
-A solution to this space-efficiency problem is representing cast information 
-more concisely. There are several known space-efficient cast representations
+These example programs are adapted from those of Herman et al.~\citep{herman2010space}.
+We direct readers to their work for more examples and a detailed explanation.
+
+One solution to this space-efficiency problem is to represent cast
+information more concisely. There are several known space-efficient
+cast representations
 \citep{Siek:2015:BCT:2737924.2737968,Siek:2010:TWB:1706299.1706342,Garcia:2013:CTB:2500365.2500603,kuhlenschmidt2018efficient,siek2012interpretations,garcia2014deriving}.
@@
 
-These cast representations are represented in their own dynamic semantics of a gradually typed language,
-which make it harder to focus on key differences between these representations. 
-Surprisingly, no one has published a dynamic semantics parameterized over cast representations.
-We present in Section~\ref{sec:framework} first of such generic dynamic semantics in the form 
-of a CEK abstract machine and formulate the interface between the machine and cast representations
-as an abstract data type, namely Cast ADT.
-
-Of course, an alternative cast representation must be proved
-correct. That is, a language implementation should give the same output no 
-matter whether it is using a cast representation to reduce space 
-consumption. Our generic CEK machine comes with generic theorems (Section~\ref{sec:framework}),
-with which researchers can prove a cast representation is correct by showing its corresponding
-implementation of Cast ADT satisfies a bunch of properties. We believe this framework can reduce the burden
- of proving this kind of theorems and help people focusing on the cast representations.
-For illustration, we apply the framework to Lazy UD coercions in normal form
-and Lazy UD threesomes. 
-We believe the framework is also applicable to other cast representations.
-The framework and the illustration are available at the following URL:
+The semantics of these cast representations are defined in many
+different papers with separate reduction rules, which makes it
+difficult to isolate the key differences between them.  In this paper
+we present the first set of reduction rules for a cast calculus that
+is parameterized over the cast representation
+(Section~\ref{sec:framework}). The semantics takes the form of a CEK
+abstract machine and it formulates the interface between the machine
+and the different cast representations as an abstract data type,
+namely the \emph{Cast ADT}.
+
+Of course, a space-efficient cast representation must be proved
+correct. That is, a language implementation that uses space-efficient
+casts should give the same output as the language semantics. Our
+generic CEK machine comes with generic theorems
+(Section~\ref{sec:framework}) that researchers can use to prove a cast
+representation correct.  We believe this framework can reduce the
+burden of proving correctness theorems and help people focus on the
+cast representations.  For illustration, we apply the framework to
+Lazy UD coercions in normal form~\citep{Siek:2015:BCT:2737924.2737968}
+and Lazy UD threesomes~\citep{Siek:2010:TWB:1706299.1706342}. We
+believe the framework is also applicable to other cast
+representations.  The framework and illustrations are available at the
+following URL:
 \[\text{\urlFrameworkAndIllustration}\]
 
-\todo[inline]{KC: (about the p below) Actually I think twosome's composition is structurally recursive but threesomes' is not}
-The published cast representations have various strengths and weaknesses.
-The major insight of these systems is a compose operator for casts which compress cast information to
-reduce space consumption.
-Threesomes and supercoercions are good for mechanized
-metatheory because their compose operators are structurally recursive,
-making them easy to define in proof assistants such as Agda. In
-contrast, the coercions in normal form have compose operators that are
-not structurally recursive, which makes it more difficult to define in
-Agda, requiring what amounts to an explicit proof of termination.
+\todo[inline]{KC: (about the p below) Actually I think twosome's
+  composition is structurally recursive but threesomes' is not}
+
+The published space-efficient cast representations have various
+strengths and weaknesses.  The major insight of these systems is a
+compose operator for casts which compresses cast information to reduce
+space consumption.  Threesomes and supercoercions are good for
+mechanized metatheory because their compose operators are structurally
+recursive, making them easy to define in proof assistants such as
+Agda. In contrast, the coercions in normal form have compose operators
+that are not structurally recursive, which makes it more difficult to
+define in Agda, requiring what amounts to an explicit proof of
+termination.
 %
 On the other hand, coercions in normal form are easier to understand
-than threesomes (with a strange labeled bottom type), and
+than threesomes (with their strange labeled bottom type), and
 supercoercions (10 different kinds).
 
-This paper presents a new cast representation 
-(Section~\ref{sec:hypercoercions}), named
+This paper presents a new cast representation named
 \emph{hypercoercions}, that is good for both mechanized metatheory and
-good for implementation. The straightforward Agda translation of composition 
-operator for hypercoercions is able to pass the termination check and 
-hypercoercions are suggestive of a bit-level representation that minimizes the 
-need for pointers and fits all first-order casts into 64 bits.
+good for implementation (Section~\ref{sec:hypercoercions}). The
+straightforward Agda translation of the composition operator for
+hypercoercions is able to pass Agda's termination check and
+hypercoercions are suggestive of a bit-level representation that
+minimizes the need for pointers and fits all first-order casts into 64
+bits.
 %
@@
 \LUD\
-strategy, however, some \textbf{u}p casts are also blamable.
+strategy, however, some \textbf{u}p casts may also be blamed.
 We are interested in the D blame
@@
 the \LD\ hypercoercions were inspired by the normal forms of
-\citep{siek2012interpretations}.
+Siek and Garcia~\citep{siek2012interpretations}.
 The semantics of casts can be lazy or
@@
 strategies because we suspect that they are more efficient than eager
-strategies and because \citet{new2019gradual} show that the eager
+strategies and because New et al.~\citep{new2019gradual} show that the eager
 strategies are incompatible with $\eta$-equivalence of functions.
@@
 
-\section{Related Works}
+\section{Related Work}
 \label{chap:related-works}
@@
 \todo[inline]{KC: how to make \textbackslash citet work?}
+\todo[inline]{JS: Good question! I would like to use citet as well.}
 

### 2020-10-01 paper.tex
Updates from Overleaf
switched to a bib style that works with author-year
edits and comments in sec 2

@@
 \usepackage[T1]{fontenc}
-\usepackage[numbers]{natbib} %% For more citation commames (\cite etc.)
+%\usepackage[numbers]{natbib} %% For more citation commames (\cite etc.)
+\usepackage{natbib} %% For more citation commames (\cite etc.)
 \usepackage{listings} %% For typesetting code
@@
 the \LD\ hypercoercions were inspired by the normal forms of
-Siek and Garcia~\citep{siek2012interpretations}.
+\citet{siek2012interpretations}.
 The semantics of casts can be lazy or
@@
 strategies because we suspect that they are more efficient than eager
-strategies and because New et al.~\citep{new2019gradual} show that the eager
+strategies and because \citet{new2019gradual} show that the eager
 strategies are incompatible with $\eta$-equivalence of functions.
@@
 
-\todo[inline]{KC: how to make \textbackslash citet work?}
-\todo[inline]{JS: Good question! I would like to use citet as well.}
+We review closely related work in three areas: coercions in normal
+form, threesomes, and parameterized cast calculi.
 
@@
 
-\citet{henglein1994dynamic} introduces coercions to study compilation from 
-dynamic languages to static ones. \citet{herman2010space} proposes using 
-coercions in normal forms to represent casts in gradual typing and proves space 
-efficiency. 
-However, they didn't show the coercion-based semantics is equivalent to the 
-standard (and type-based) one. \citet{Siek:2015:BCT:2737924.2737968} improves 
-the Lazy UD flavor of coercions in normal forms and proves that Lazy UD 
-coercions in normal form is correct, using two bisimulation between three 
-reduction semantics. The first semantics is similar to \LUDMachine, which 
-bisimulates a 
-reduction semantics using coercions (not necessarily in normal form). The last 
-semantics uses coercions in normal form and bisimulates the coercions-based 
-semantics.
+\citet{henglein1994dynamic} introduces coercions to study compilation
+from dynamic languages to statically typed
+ones. \citet{herman2010space} proposes using coercions in normal forms
+to represent casts in gradual typing and proves space efficiency.
+However, they did not prove that the coercion-based semantics is
+equivalent to the standard (and type-based)
+one. \citet{Siek:2015:BCT:2737924.2737968} improve the Lazy UD style
+of coercions in normal forms and prove that Lazy UD coercions in
+normal form are correct, using two bisimulation between three
+reduction semantics. The first semantics is similar to \LUDMachine,
+which bisimulates a reduction semantics using coercions (not
+necessarily in normal form). The last semantics uses coercions in
+normal form and bisimulates the coercions-based semantics.
+
+\todo[inline]{JS: say something about the difference between the above
+  and what is in this paper. That's the whole point of the related work
+  section from the eyes of the reviewer.}
 
@@
 
-\citet{Siek:2010:TWB:1706299.1706342} introduces Lazy UD threesomes and prove 
-its correctness, using a bisimulation between two reduction semantics: one is 
-similar to \LUDMachine; the other uses Lazy UD threesomes and is similar to the 
-machine in Section~\ref{sec:framework}. 
-\citet{Garcia:2013:CTB:2500365.2500603} introduces several other flavors of 
-threesomes, including a Lazy D one. Their threesomes are derived from 
-corresponding flavors of coercions in normal form, using correctness-preserving 
+\citet{Siek:2010:TWB:1706299.1706342} introduce Lazy UD threesomes and
+prove them correct, using a bisimulation between two reduction
+semantics: one is analogous to the \LUDMachine; the other uses Lazy UD
+threesomes and is analogous to the machine in
+Section~\ref{sec:framework}.  \citet{Garcia:2013:CTB:2500365.2500603}
+introduces several other flavors of threesomes, including a Lazy D
+one. Their threesomes are derived from the corresponding styles of
+coercions in normal form, using correctness-preserving
 transformation. So the correctness of their threesomes relies on the
-corrections of the coercions-in-normal-form-based semantics defined in 
-\citet{herman2010space}, which have not been proved correct.
+correctness of the coercions-in-normal-form-based semantics defined in
+\citet{herman2010space}, which has not been proved correct.
+
+\todo[inline]{JS: again, say something about the difference between
+  the above and what is in this paper.}
 
@@
 
-\citet{garcia2014deriving} presents a dynamic semantics for the Eager D blame 
-strategy, using coercions. They claims that "the artefacts for coercions can be
-replaced by other artefacts implementing different dynamic semantics".
+\citet{garcia2014deriving} presents a dynamic semantics for the Eager
+D blame strategy, using coercions. They claim that ``the artefacts for
+coercions can be replaced by other artefacts implementing different
+dynamic semantics''.
+
+\todo[inline]{JS: The above is too short of a description of that related
+work.}
 
@@
 %
-\bibliographystyle{splncs04}
+%\bibliographystyle{splncs04}
+\bibliographystyle{splncsnat}
 \bibliography{bibfile,all-modified}{}

### 2020-10-01 paper.tex
reorganization of the summary of contributions

@@
 \begin{itemize}
-    \item Cast ADT, an abstract data type for cast representations
-    \item a CEK abstract machine parameterized over Cast ADT
-	\item a framework in Agda for proving the correctness of \LD\ or \LUD\ 
-	cast representations when plugging into the CEK machine
-	\item a formal proof that \LUD\ threesomes are correct
-	\item a formal proof that \LUD\ coercions in normal form are correct
-	\item hypercoercions, a new cast representation, which
-	has a more compact memory representation in comparison to coercions in 
-	normal form.
-	\item a formal proof that both \LUD\ hypercoercions are correct
-	\item a formal proof that both \LD\ hypercoercions are correct
+\item Cast ADT, an abstract data type for cast representations, and a
+  CEK abstract machine parameterized over the Cast ADT,
+\item a framework in Agda for proving the correctness of cast
+  representations,
+\item hypercoercions, a new cast representation with a more compact
+  memory representation compared to coercions in normal form, and
+\item proofs of correctness in Agda for \LUD\ threesomes,
+  \LUD\ coercions in normal form, \LUD\ hypercoercions, and
+  \LD\ hypercoercions.
 \end{itemize}

### 2020-10-01 paper.tex
comments

@@
 burden of proving correctness theorems and help people focus on the
-cast representations.  For illustration, we apply the framework to
+cast representations.
+\todo[inline]{JS: Say the framework is in Agda.}
+For illustration, we apply the framework to
 Lazy UD coercions in normal form~\citep{Siek:2015:BCT:2737924.2737968}
@@
   representations,
-\item hypercoercions, a new cast representation with a more compact
-  memory representation compared to coercions in normal form, and
 \item proofs of correctness in Agda for \LUD\ threesomes,
   \LUD\ coercions in normal form, \LUD\ hypercoercions, and
-  \LD\ hypercoercions.
+  \LD\ hypercoercions, 
+\item hypercoercions, a new cast representation with a more compact
+  memory representation compared to coercions in normal form.
 \end{itemize}

### 2020-10-02 paper.tex
more comments

@@
 is parameterized over the cast representation
-(Section~\ref{sec:framework}). The semantics takes the form of a CEK
+(Section~\ref{sec:framework}).
+\todo[inline]{JS: First? What about \url{https://arxiv.org/abs/2001.11560}?}
+The semantics takes the form of a CEK
 abstract machine and it formulates the interface between the machine
@@
 checking. Blame labels can be positive (blaming the expression inside the cast)
-or negative (blaming the context outside the cast), as in \cite{Wadler:2009qv,Siek:2015ab}.
+or negative (blaming the context outside the cast), as in \cite{wadler2009well}.
 The syntax and static semantics is the same as that of 
@@
 \begin{itemize}
-\item We add product type.
 \item We consider only one base type, Boolean, for simplicity.
+\item We add the product type.
 \item We separate types into those with a type constructor at the top,
@@
 \end{itemize}
-As usual, for every cast $\ecast{e}{\ccast{S}{l}{T}}$, the source type $S$ and 
-the target $T$ must be consistent.
+As usual, in a cast $\ecast{e}{\ccast{S}{l}{T}}$, the source type $S$
+and the target $T$ must be consistent.
 
@@
 reduction semantics. Here we use a CEK machine
-\citep{felleisen1986control} instead. One reason is that environments are 
-easier 
-to deal with than substitutions in formal proofs. Also, a CEK machine is more
-convenient to use for the space-efficient semantics in
-\chapref{sec:framework} (recall that a major point of space-efficiency 
-is about compressing continuations and that continuations are part of the CEK 
-machine states). So using a CEK machine for the cast 
-calculi in this section makes it easier to prove these machines are equivalent.
-Of course, one should also prove that the abstract machine
-presented here is equivalent to the standard reduction semantics for
-cast calculi, but we have not yet done so.
+\citep{felleisen1986control} instead. One reason is that environments
+are easier to deal with than substitutions in formal proofs. Also, a
+CEK machine is more convenient to use for the space-efficient
+semantics in \chapref{sec:framework} because continuations need to be
+compressed and continuations are an explicit part of the CEK machine
+states.  So also using a CEK machine for the cast calculi in this
+section makes it easier to prove these machines are equivalent.  Of
+course, one should also prove that the abstract machine presented here
+is equivalent to the standard reduction semantics for cast calculi,
+but we have not yet done so.
+
+\todo[inline]{JS: We might cite the proof of correctness for CEK in the
+  PLT Redex book and conjecture that it would be straightforward to
+  adapt.}
 
@@
 states $s$, including a definition of values $v$ and value typing.
-%
-This machine is parameterized over blame strategy ($B$), which ranges over
+\todo[inline]{JS: explain the name choice of $\mathcal{R}$.}
+%
+This machine is parameterized over blame strategy $B$, which ranges over
 Lazy D (Fig.~\ref{fig:blame-strategy-LazyD}) and Lazy UD 
-(Fig.~\ref{fig:blame-strategy-LazyD}).
+(Fig.~\ref{fig:blame-strategy-LazyUD}).
+\todo[inline]{JS: I don't think $B$ is restricted to just those two.
+Can't it be any blame strategy that satisfies certain conditions?}
 %

### 2020-10-05 paper.tex
reply to some comments

@@
 difficult to isolate the key differences between them.  In this paper
-we present the first set of reduction rules for a cast calculus that
+we present a set of reduction rules for a cast calculus that
 is parameterized over the cast representation
@@
 \todo[inline]{JS: First? What about \url{https://arxiv.org/abs/2001.11560}?}
+\todo[inline]{KC: My bad. I don't remember how this word gets in but I
+definitely should be more careful about these kind of words. BTW, should
+the arxiv paper go into Related Work?}
 The semantics takes the form of a CEK
@@
 \todo[inline]{JS: Say the framework is in Agda.}
+\todo[inline]{KC: Has said, at the end of this paragraph}
 For illustration, we apply the framework to
@@
 believe the framework is also applicable to other cast
-representations.  The framework and illustrations are available at the
-following URL:
+representations.  The framework and illustrations (written in Agda)
+are available at the following URL:
 \[\text{\urlFrameworkAndIllustration}\]
@@
 \todo[inline]{JS: explain the name choice of $\mathcal{R}$.}
+\todo[inline]{KC: I want to space-efficient machine to be S, so ... B might be a better name 
+because it reminds people of the $\lambda B$ calculus.
+Or $T$ for type-based cast?
+Or $C$ for cast-calculus?
+Or $D$ for definitional semantic?
+How do you think?}
 %
@@
 Can't it be any blame strategy that satisfies certain conditions?}
+\todo[inline]{KC: Technically a $B$ should define a predicate over pretypes, which specifies
+what is injectable, and a apply-cast function. Of course, the set of values that the apply-cast
+function works with depends on the set of injectable types.
+\url{https://github.com/Gradual-Typing/Equivalence-of-Cast-Calculi/blob/master/equivalence-of-cast-calculi/R/BlameStrategies.agda}
+Do you want me to put these contraints in the paper?}
 %

### 2020-10-05 paper.tex
edits and comments in sec. 3

@@
 
-\todo[inline]{KC: Cite "Contracts for higher-order functions" for the proxy-based approach maybe?}
-\todo[inline]{JS: That paper doesn't exactly fit into what you're talking about in the above
-sentence. It might be appopriate to cite it elsewhere in the paper. Also,
-there are earlier papers about coercive subtyping (Computing with coercions by Breazu-Tannen et al)
-that use a proxy-based approach. The contracts paper may be the first to propose blame tracking.}
+%% \todo[inline]{KC: Cite "Contracts for higher-order functions" for the proxy-based approach maybe?}
+%% \todo[inline]{JS: That paper doesn't exactly fit into what you're talking about in the above
+%% sentence. It might be appopriate to cite it elsewhere in the paper. Also,
+%% there are earlier papers about coercive subtyping (Computing with coercions by Breazu-Tannen et al)
+%% that use a proxy-based approach. The contracts paper may be the first to propose blame tracking.}
 
@@
 the arxiv paper go into Related Work?}
+\todo[inline]{JS: Yes.}
 The semantics takes the form of a CEK
@@
 casts should give the same output as the language semantics. Our
-generic CEK machine comes with generic theorems
+generic CEK machine comes with generic theorems mechanized in Agda
 (Section~\ref{sec:framework}) that researchers can use to prove a cast
@@
 burden of proving correctness theorems and help people focus on the
-cast representations.
-\todo[inline]{JS: Say the framework is in Agda.}
-\todo[inline]{KC: Has said, at the end of this paragraph}
-For illustration, we apply the framework to
+cast representations. As a demonstration, we apply the framework to
 Lazy UD coercions in normal form~\citep{Siek:2015:BCT:2737924.2737968}
@@
 believe the framework is also applicable to other cast
-representations.  The framework and illustrations (written in Agda)
-are available at the following URL:
+representations. The framework and demonstrations are available at the
+following URL:
 \[\text{\urlFrameworkAndIllustration}\]
@@
   composition is structurally recursive but threesomes' is not}
+\todo[inline]{JS: Then please go ahead and fix it.}
 
@@
 
-\begin{figure}
+\begin{figure}[tp]
 Syntax
@@
 states.  So also using a CEK machine for the cast calculi in this
-section makes it easier to prove these machines are equivalent.  Of
-course, one should also prove that the abstract machine presented here
-is equivalent to the standard reduction semantics for cast calculi,
-but we have not yet done so.
-
-\todo[inline]{JS: We might cite the proof of correctness for CEK in the
-  PLT Redex book and conjecture that it would be straightforward to
-  adapt.}
-
-\begin{figure}
+section makes it easier to prove these machines are equivalent.  The
+equivalence of this CEK machine and reduction semantics for cast
+calculi could be proved by standard
+techniques~\citep{Felleisen:2009aa}.
+
+\begin{figure}[tp]
 \[
@@
 
+Fig.~\ref{fig:R-machine-syntax} defines machine 
+states $s$, including a definition of values $v$ and value typing.
 Fig.~\ref{fig:R-machine-dynamics} defines the transition relation of the CEK
-machine (\RMachine{B}) and Fig.~\ref{fig:R-machine-syntax} gives a grammar for machine 
-states $s$, including a definition of values $v$ and value typing.
+machine (\RMachine{B}). 
 \todo[inline]{JS: explain the name choice of $\mathcal{R}$.}
@@
 How do you think?}
+\todo[inline]{JS: B or C both sound like good choices for the reasons
+you give.}
 %
@@
 Do you want me to put these contraints in the paper?}
+\todo[inline]{JS: Yes.}
 %
@@
 more detail below. The other transitions are standard for a CEK
-machine for an extended simply typed lambda calculus.
-%
-Recall that CEK machines involve two kinds of transitions: those
-that dive further into an expression (looking for a redex) and push an
+machine for an extended simply typed lambda calculus~\citep{Felleisen:2009aa}.
+%
+Recall that CEK machines involve two kinds of transitions: those that
+dive further into an expression (looking for a redex) and push an
 entry onto the continuation and those that return a value to the
-current continuation and possibly perform a computation.
-That is, the machine state is either in an evaluating
-$\sexpr{e}{E}{K}$ or returning $\scont{v}{K}$ configuration, 
-respectively. Additionally, there are two halting configurations: \shalt{v} 
-halts with a value, while \error{l} halts with a blame label. 
-Observables include all value constructors and blame labels, as in 
-\citep{siek2012interpretations}. 
-The function converting values to observables ($observe(v) = o$) is defined in 
-the obvious way.
-
-Let $v$ range over values. The 
-$\vdyn{I}{v}$ stands for values casted to the dynamic type, as in 
-\citep{wadler2009well}. The inner value must be of an 
-injectable type. The definition of injectable types depends on blame 
-strategies:
+current continuation and possibly perform a computation.  That is, the
+machine state is either in an evaluating $\sexpr{e}{E}{K}$ or
+returning $\scont{v}{K}$ configuration, respectively. Additionally,
+there are two halting configurations: \shalt{v} halts with a value,
+while \error{l} halts with a blame label.  Observables include all the
+value constructors and blame labels, as in the work of
+\citet{siek2012interpretations}.  The function that converts values to
+observables ($observe(v) = o$) is defined in the obvious way.
+
+Let $v$ range over values. The $\vdyn{I}{v}$ stands for values casted
+to the dynamic type, as in the work of \citet{wadler2009well}. The
+inner value must be of an injectable type. The definition of
+injectable types depends on blame strategies:
 %
@@
 
-The syntax \error{l} occurs several times in the syntax definition, we shall 
-view those nonterminals that have \error{l} case as error monads. We use 
-the symbol \mbind as the monad bind operator, which is defined as follows:
+The syntax \error{l} occurs several times in the syntax definition. We shall 
+view those nonterminals that have an \error{l} case as error monads. We use 
+the symbol \mbind{} as the monad bind operator, which is defined as follows:
 \[
@@
 \]
+\todo[inline]{JS: why not use monadic let instead? That avoids
+  the need to also use meta-lambdas, which you would need to
+  explain, e.g., in the transition rule that uses applyCast.}
 
@@
 
-The transition relation \reduceto{s}{s} invokes the cast application function, 
-noted as $\applyCast{v}{\ccast{S}{l}{T}}$ to allow for the differences 
-between blame strategies (Fig.~\ref{fig:blame-strategy-LazyD} and 
+The transition relation \reduceto{s}{s} invokes the cast application
+function, noted as $\applyCast{v}{\ccast{S}{l}{T}}$ to capture the
+differences between blame strategies
+(Fig.~\ref{fig:blame-strategy-LazyD} and
 Fig.~\ref{fig:blame-strategy-LazyUD}).
@@
 %
-To cast a value, the machine invokes the cast application function on the 
-value. The cast result is either a value or an error (\error{l}). If the cast 
-succeeds, the machine returns the value to the next continuation.  If the cast 
-fails, the machine halts with the blame label.
+To cast a value, the machine invokes applyCast on the value. The cast
+result is either a value or an error (\error{l}). If the cast
+succeeds, the machine returns the value to the next continuation.  If
+the cast fails, the machine halts with the blame label.
 %
@@
 %
-To take out the first part of a casted pair, the machine takes out the 
-first part of the inner pair $u$ and cast it.
-%
-Taking out the second part is similar.
+To project the first element of a casted pair, the machine projects
+the first element of the inner pair $u$ and cast it.
+%
+Projecting the second element of a casted pair is similar.
 
@@
 
-We conjecture that \LDMachine\ agrees with the \LD\ cast calculus
-of \citep{siek2009exploring}.
+We conjecture that \LDMachine\ is equivalent to the \LD\ cast calculus
+of \citet{siek2009exploring}.
+
+The \LDMachine{} machine is deterministic.
 
@@
 respect to \LD\ are in the injectable types and in
-${\mathit{applyCast}(v,\ccast{S}{l}{T})}$, in which a cast whose source or
-target is the dynamic type \Tdyn\ is always split into two casts that
-go through a ground type, that is, a 
-type in which all sub-components are the dynamic type, such as 
-\Pfunc{\Tdyn}{\Tdyn}.
+${\mathit{applyCast}(v,\ccast{S}{l}{T})}$, in which a cast whose
+source or target is the dynamic type \Tdyn\ is always split into two
+casts that go through a ground type, that is, a type whose
+sub-components are the dynamic type, such as \Pfunc{\Tdyn}{\Tdyn}.
 \begin{definition}[\LUD\ CEK Machine]
@@
 
-\begin{figure}
+\begin{figure}[tp]
 \[
@@
 
-We conjecture that \LUDMachine\ agrees with the \LUD\ cast
-calculus of \citep{siek2009exploring}.
+We conjecture that \LUDMachine\ is equivalent to the \LUD\ cast
+calculus of \citet{siek2009exploring}.
+
+The \LUDMachine{} machine is deterministic.
 
@@
 
-In this section, we review the
-coercions~\citep{henglein1994dynamic,herman2010space} and the normal form of
-\citet{siek2012interpretations} to motivate the design of hypercoercions.  We
-omit sum types and product types in this section because
-\citet{siek2012interpretations} did not discuss them. We assume a basic
-familiarity with coercions, and suggest that readers unfamiliar with coercions
-to familiarize themselves with \citet{siek2012interpretations} and
-\citet{Siek:2015:BCT:2737924.2737968}.
-
-\begin{figure}
+In this section, we review the coercions
+of~\citet{henglein1994dynamic} and \citet{herman2010space} and the
+normal form of \citet{siek2012interpretations} to motivate the design
+of hypercoercions.  We omit sum types and product types in this
+section because the prior work did not include them.
+
+\begin{figure}[tp]
 	\[
@@
 	\caption{Syntax of coercions and normal forms {\`a} la 
-		\citep{siek2012interpretations}.}
+		\citet{siek2012interpretations}.}
 	\label{fig:normal-coercion}
@@
 their normal forms. \figref{fig:normal-coercion} defines the syntax of
-coercion in normal form, written $\hat{c}$. Conceptually, a coercion
+coercion in normal form, written $\hat{c}$.
+\todo[inline]{JS: In the figure, normal forms are written $s$ and $t$.}
+Conceptually, a coercion
 in normal form has three parts, all of which are optional.  It may

### 2020-10-05 paper.tex
rename R machine to C machine

@@
 \newcommand{\CastADT}{\ensuremath{\text{Cast ADT}}}
-\newcommand{\RMachine}[1]{\ensuremath{\mathcal{R}(#1)}}
-\newcommand{\LDMachine}{\RMachine{\BLD}}
-\newcommand{\LUDMachine}{\RMachine{\BLUD}}
-\newcommand{\RBMachine}[0]{\RMachine{B}}
+\newcommand{\CMachine}[1]{\ensuremath{\mathcal{C}(#1)}}
+\newcommand{\LDMachine}{\CMachine{\BLD}}
+\newcommand{\LUDMachine}{\CMachine{\BLUD}}
+\newcommand{\CBMachine}[0]{\CMachine{B}}
 \newcommand{\SMachine}[1]{\ensuremath{\mathcal{S}(#1)}}
@@
 \newcommand{\reduceto}[2]{\ensuremath{#1 \longmapsto #2}}
-\newcommand{\reducetoR}[3]{\ensuremath{#2 \longmapsto_{\RMachine{#1}} #3}}
+\newcommand{\reducetoR}[3]{\ensuremath{#2 \longmapsto_{\CMachine{#1}} #3}}
 \newcommand{\reducetoD}[2]{\reducetoR{\BLD}{#1}{#2}}
@@
 \newcommand{\withmachineevalto}[3]{\ensuremath{\mathit{eval}_{#1}(#2)=#3}}
-\newcommand{\evaltoR}[3]{\ensuremath{\mathit{eval}_{\RMachine{#1}}(#2)=#3}}
+\newcommand{\evaltoR}[3]{\ensuremath{\mathit{eval}_{\CMachine{#1}}(#2)=#3}}
 \newcommand{\evaltoD}[2]{\evaltoR{\BLD}{#1}{#2}}
@@
 (Section~\ref{sec:framework}).
-\todo[inline]{JS: First? What about \url{https://arxiv.org/abs/2001.11560}?}
-\todo[inline]{KC: My bad. I don't remember how this word gets in but I
-definitely should be more careful about these kind of words. BTW, should
-the arxiv paper go into Related Work?}
-\todo[inline]{JS: Yes.}
 The semantics takes the form of a CEK
@@
 \todo[inline]{JS: Then please go ahead and fix it.}
+\todo[inline]{KC: Fixed. 
+``Threesomes and supercoercions are good for
+mechanized metatheory because their compose operators 
+can be written in a structrually recursive form,''}
 
@@
 space consumption.  Threesomes and supercoercions are good for
-mechanized metatheory because their compose operators are structurally
-recursive, making them easy to define in proof assistants such as
+mechanized metatheory because their compose operators 
+can be written in a structrually recursive form,
+% are structurally recursive,
+making them easy to define in proof assistants such as
 Agda. In contrast, the coercions in normal form have compose operators
@@
 
+\todo[inline]{KC: KC, please add \url{https://arxiv.org/abs/2001.11560}
+to this section.}
+
 We review closely related work in three areas: coercions in normal
@@
 
-\caption{Syntax of a CEK machine \RMachine{B} and auxiliary definitions.}
+\caption{Syntax of a CEK machine \CMachine{B} and auxiliary definitions.}
 \label{fig:R-machine-syntax}
@@
 Fig.~\ref{fig:R-machine-dynamics} defines the transition relation of the CEK
-machine (\RMachine{B}). 
+machine (\CMachine{B}).
+We name the machine after \textbf{c}ast calculus.
 \todo[inline]{JS: explain the name choice of $\mathcal{R}$.}
@@
 you give.}
+\todo[inline]{KC: Let's go with C to avoid confusion with Blame strategy.}
 %
@@
 	\caption{Dynamic semantics of the cast calculi as a CEK
-		machine \RMachine{B}. The transitions that involve casts are highlighted
+		machine \CMachine{B}. The transitions that involve casts are highlighted
 		in red.}
@@
 which uses the cast operators implemented by $C$ to work with casts, 
-and theorems relating $\SMachine{C}$ to $\RMachine{B}$.
+and theorems relating $\SMachine{C}$ to $\CMachine{B}$.
 %
@@
 %
-We prove the theorems relating \SMachine{C} and \RMachine{B} in
+We prove the theorems relating \SMachine{C} and \CMachine{B} in
 Subsection~\ref{sec:S-correct}.
@@
 machine \SMachine{C}.
-The key differences between \SMachine{C} and \RMachine{B} are in the definitions
+The key differences between \SMachine{C} and \CMachine{B} are in the definitions
 of values and continuations, that is, places where casts can accumulate.
@@
 %
-Recall that in \RMachine{B} we have two value constructors for functions and 
+Recall that in \CMachine{B} we have two value constructors for functions and 
 another two for pairs. That setup allows zero-or-more layers of casts at the 
@@
 \SMachine{C} instead has exactly one layer of cast.
-Thus non-casted values in \RMachine{B} correspond to \SMachine{C} values
+Thus non-casted values in \CMachine{B} correspond to \SMachine{C} values
 where casts are identities ($\mathit{id}(T)$). The 
@@
 % %
-% Pre-continuations are like the continuations in \RMachine{B}, but their 
+% Pre-continuations are like the continuations in \CMachine{B}, but their 
 % top-most frame must not be a cast frames.
@@
 % %
-% Recall that continuations in \RMachine{B} have zero or more casts at the top.
+% Recall that continuations in \CMachine{B} have zero or more casts at the top.
 % In \SMachine{C}, however, every continuation has exactly one cast at the 
@@
 % %
-\RMachine{B} continuations that have no casts at the top correspond
+\CMachine{B} continuations that have no casts at the top correspond
 to \SMachine{C} continuations whose casts are identities.
-\RMachine{B} continuations that have many casts at the top correspond
+\CMachine{B} continuations that have many casts at the top correspond
 to \SMachine{C} continuations in where those casts are composed by
@@
 %
-Injectable types, environments, states, and cast results are the same as in \RBMachine.
+Injectable types, environments, states, and cast results are the same as in \CBMachine.
 
@@
 Reflexive transitive closure of reduction $\reducetoS{C}{s}{s}$ and
-the evaluation partial function $\evaltoS{C}{e}{o}$ are the same as in \RMachine{B}.
+the evaluation partial function $\evaltoS{C}{e}{o}$ are the same as in \CMachine{B}.
 
@@
 
-\caption{Bisimulation between \RBMachine\ and \SMachine{C}. It is the smallest 
+\caption{Bisimulation between \CBMachine\ and \SMachine{C}. It is the smallest 
 congruence relation containing the shown rules. Everything to the left (resp. 
-right) of $\approx$ is in \RBMachine\ (resp. in \SMachine{C}).}
+right) of $\approx$ is in \CBMachine\ (resp. in \SMachine{C}).}
 \label{fig:bisim-SC-D}
@@
 
-% \caption{Bisimulation between \RBMachine\ and \SMachine{C}. It is the smallest 
+% \caption{Bisimulation between \CBMachine\ and \SMachine{C}. It is the smallest 
 % congruence relation containing the shown rules. Everything to the left (resp. 
-% right) of $\approx$ is in \RBMachine\ (resp. in \SMachine{C}).}
+% right) of $\approx$ is in \CBMachine\ (resp. in \SMachine{C}).}
 % \label{fig:bisim-SC-D}
@@
 
-The central part of the proofs is a weak bisimulation between \RMachine{B} and \SMachine{C}.
+The central part of the proofs is a weak bisimulation between \CMachine{B} and \SMachine{C}.
 Fig.~\ref{fig:bisim-SC-D} defines the bisimulation relation.
@@
 The relation $\bisimc{\overline{\ccast{S}{l}{T}}}{c}{S}{T}$ relates a sequence 
-of cast in \RBMachine\ with one cast in \SMachine{C}. This relation is designed 
+of cast in \CBMachine\ with one cast in \SMachine{C}. This relation is designed 
 to cover all possibly ways to construct a cast representation. The empty 
-sequence is related to the identity cast. A \RBMachine\ cast is related 
+sequence is related to the identity cast. A \CBMachine\ cast is related 
 to its translation. Finally, cast sequencing preserves the bisimulation 
@@
 To relate function closures, the domain and codomain casts should be related. 
-Closures in \RMachine{B} are proxied with a sequence of function casts, which 
+Closures in \CMachine{B} are proxied with a sequence of function casts, which 
 can be viewed as two cast sequences in the obvious way.
@@
 We now come to the main lemmas, the weak bisimulation between
-\RBMachine\ and \SMachine{C}.
-
-\begin{lemma}[Weak Bisimulation between \RMachine{B} and \SMachine{C}] \label{lem:weak-bisimulation}
+\CBMachine\ and \SMachine{C}.
+
+\begin{lemma}[Weak Bisimulation between \CMachine{B} and \SMachine{C}] \label{lem:weak-bisimulation}
 Assume
@@
     \item $\denote{c}(v)$ preserves the bisimulation relation (e.g. Lemma~\ref{lem:LazyD-apply-cast-preserve-bisim} and \ref{lem:LazyUD-apply-cast-preserve-bisim}) and
-    \item $s_1$ is a state in \RMachine{B} and
+    \item $s_1$ is a state in \CMachine{B} and
     \item $s_1'$ is a state in \SMachine{C} and
@@
 	\[
-	\machineequiv{\RBMachine}{\SMachine{C}}
+	\machineequiv{\CBMachine}{\SMachine{C}}
 	\]
@@
 % 	\[
-% 	\transitivelyreducetoM{\RMachine{B}}{\sexpr{e}{\emptyset}{\Knil}}{
+% 	\transitivelyreducetoM{\CMachine{B}}{\sexpr{e}{\emptyset}{\Knil}}{
 % 		s

### 2020-10-05 paper.tex
more comments

--- 2020-10-05 paper.tex
@@
 How do you think?}
-\todo[inline]{JS: B or C both sound like good choices for the reasons
-you give.}
+\todo[inline]{JS: B is a good choices for the reason
+  you give. C is a bad choice because we later use C for the
+  Cast ADT parameter.}
 %
@@
 Fig.~\ref{fig:blame-strategy-LazyUD}).
+\todo[inline]{JS: be consistent with the font used for applyCast. Sometimes
+  you use roman and sometimes you used italic. Also, be consistent
+  for all the metafunctions (eval, observe, etc.).}
 %
@@
 section because the prior work did not include them.
+\todo[inline]{But Fig 6 includes product types.}
 
@@
 % program execution.
-In this section we present a framework for proving the 
-correctness of cast representations. The framework includes an abstract data 
-type named Cast ADT, which specifies the operators of cast representations, 
-a CEK machine $\SMachine{C}$ parameterized over a Cast ADT,
-which uses the cast operators implemented by $C$ to work with casts, 
-and theorems relating $\SMachine{C}$ to $\RMachine{B}$.
+In this section we present a framework for proving the correctness of
+space-efficient cast representations. The framework includes an
+abstract data type named Cast ADT, which specifies the operators of
+cast representations, a CEK machine $\SMachine{C}$ parameterized over
+a Cast ADT, which uses the cast operators implemented by $C$ to work
+with casts, and theorems relating $\SMachine{C}$ to $\RMachine{B}$.
 %

### 2020-10-05 paper.tex

--- 2020-10-05 paper.tex
@@
 We name the machine after \textbf{c}ast calculus.
-\todo[inline]{JS: explain the name choice of $\mathcal{R}$.}
-\todo[inline]{KC: I want to space-efficient machine to be S, so ... B might be a better name 
-because it reminds people of the $\lambda B$ calculus.
-Or $T$ for type-based cast?
-Or $C$ for cast-calculus?
-Or $D$ for definitional semantic?
-How do you think?}
-\todo[inline]{JS: B or C both sound like good choices for the reasons
-you give.}
-\todo[inline]{KC: Let's go with C to avoid confusion with Blame strategy.}
 %
@@
 In this section we present a framework for proving the 
-correctness of cast representations. The framework includes an abstract data 
+correctness of space-efficient cast representations.
+The framework includes an abstract data 
 type named Cast ADT, which specifies the operators of cast representations, 

### 2020-10-05 paper.tex
minor edits

@@
 casts should give the same output as the language semantics. Our
-generic CEK machine comes with generic theorems mechanized in Agda
+generic CEK machine comes with generic theorems mechanized in
+the Agda proof assistant~\citep{norell2008dependently}
 (Section~\ref{sec:framework}) that researchers can use to prove a cast
@@
 % program execution.
-In this section we present a framework for proving the 
-correctness of space-efficient cast representations.
-The framework includes an abstract data 
-type named Cast ADT, which specifies the operators of cast representations, 
-a CEK machine $\SMachine{C}$ parameterized over a Cast ADT,
-which uses the cast operators implemented by $C$ to work with casts, 
-and theorems relating $\SMachine{C}$ to $\CMachine{B}$.
-%
-Subsection~\ref{sec:cast-adt-and-space-efficient-cek} describes Cast ADT and the 
-machine \SMachine{C}. We conjecture that the machine \SMachine{C} is 
-space-efficient provided that the cast representation $C$ performs compression.
-%
-Subsection~\ref{sec:good-cast-adt} defines two subset of Cast ADT, namely Lazy D 
-Cast ADT and Lazy UD Cast ADT. As their names suggest, if $C$ is a Lazy D Cast 
-ADT, executing a program in $\SMachine{C}$ would give the same result as in 
-$\LDMachine$. Similarly, if $C$ is a Lazy UD Cast ADT, executing a program in 
-$\SMachine{C}$ would give the same result as in $\LUDMachine$.
+In this section we present a framework for proving the correctness of
+space-efficient cast representations.  The framework includes an
+abstract data type named Cast ADT, which specifies the operators
+required of a cast representation, a CEK machine $\SMachine{C}$
+parameterized over a Cast ADT $C$, and theorems relating
+$\SMachine{C}$ to $\CMachine{B}$.
+%
+Subsection~\ref{sec:cast-adt-and-space-efficient-cek} defines the Cast
+ADT and the machine \SMachine{C}. We conjecture that the machine
+\SMachine{C} is space-efficient provided that the cast representation
+$C$ performs compression.
+%
+Subsection~\ref{sec:good-cast-adt} defines two subsets of the Cast
+ADT, namely the Lazy D Cast ADT and the Lazy UD Cast ADT. As their
+names suggest, if $C$ is a Lazy D Cast ADT, executing a program in
+$\SMachine{C}$ would give the same result as in
+$\LDMachine$. Similarly, if $C$ is a Lazy UD Cast ADT, executing a
+program in $\SMachine{C}$ would give the same result as in
+$\LUDMachine$.
 %
@@
 Subsection~\ref{sec:S-correct}.
-The framework is written in the Agda language~\citep{norell2008dependently}.
 
@@
 
-\figref{fig:SEMachine-state} defines the syntax of the space-efficient CEK 
-machine \SMachine{C}.
-The key differences between \SMachine{C} and \CMachine{B} are in the definitions
-of values and continuations, that is, places where casts can accumulate.
+\figref{fig:SEMachine-state} defines the syntax of the space-efficient
+CEK machine \SMachine{C}.  The key differences between \SMachine{C}
+and \CMachine{B} are the places where casts can accumulate, that is,
+in the definitions of values and continuations.
 
@@
 %
-Recall that in \CMachine{B} we have two value constructors for functions and 
-another two for pairs. That setup allows zero-or-more layers of casts at the 
-top of higher-order values, which might consume unbounded space. 
+Recall that in \CMachine{B} we have two value constructors for
+functions and another two for pairs. That setup allows zero-or-more
+layers of casts at the top of higher-order values, which can consume
+unbounded space.
 %
@@
 
-Let $K$ ranges over continuations and $k$ ranges over pre-continuations.
-This setup is essentially saying that cast frames and non-cast frames should
-appear alternatively in continuations, and that a continuation always start
-with a cast frame.
+Let $K$ ranges over continuations and $k$ ranges over
+pre-continuations.  This setup requires cast frames and non-cast
+frames to alternate in continuations, and that a continuation always
+starts with a cast frame.
 % %
@@
 % %
-\CMachine{B} continuations that have no casts at the top correspond
-to \SMachine{C} continuations whose casts are identities.
-\CMachine{B} continuations that have many casts at the top correspond
-to \SMachine{C} continuations in where those casts are composed by
-$\compose{c}{c}$, another functions provided by the Cast ADT.
-%
-Injectable types, environments, states, and cast results are the same as in \CBMachine.
+A \CMachine{B} continuation that does not have a cast at the top
+corresponds to a \SMachine{C} continuation whose casts are identities.
+A \CMachine{B} continuation that has many casts at the top corresponds
+to a \SMachine{C} continuation in which those casts are composed by
+$\compose{c}{c}$, which is an operation provided by the Cast ADT.
+%
+Injectable types, environments, states, and cast results are the same
+as in \CBMachine.
 
 Value typing (\valuetyping{v}{T}), continuation typing
-(\casttyping{k}{S}{T} and \casttyping{K}{S}{T}), and environment typing 
-(\envtyping{\Gamma}{E}) are defined in the obvious way. 
-They rely on cast typing \casttyping{c}{S}{T}, which shall be provided by the 
+(\casttyping{k}{S}{T} and \casttyping{K}{S}{T}), and environment
+typing (\envtyping{\Gamma}{E}) are defined in the obvious way.  They
+rely on cast typing \casttyping{c}{S}{T}, which is provided by the
 Cast~ADT.

### 2020-10-05 paper.tex
Updates from Overleaf

--- 2020-10-05 paper.tex
@@
 
-%% \todo[inline]{KC: Cite "Contracts for higher-order functions" for the proxy-based approach maybe?}
-%% \todo[inline]{JS: That paper doesn't exactly fit into what you're talking about in the above
-%% sentence. It might be appopriate to cite it elsewhere in the paper. Also,
-%% there are earlier papers about coercive subtyping (Computing with coercions by Breazu-Tannen et al)
-%% that use a proxy-based approach. The contracts paper may be the first to propose blame tracking.}
+\todo[inline]{KC: Cite "Contracts for higher-order functions" for the proxy-based approach maybe?}
+\todo[inline]{JS: That paper doesn't exactly fit into what you're talking about in the above
+sentence. It might be appopriate to cite it elsewhere in the paper. Also,
+there are earlier papers about coercive subtyping (Computing with coercions by Breazu-Tannen et al)
+that use a proxy-based approach. The contracts paper may be the first to propose blame tracking.}
+\todo[inline]{KC: I think readers should be able to trace back history by following the pointers in the 
+intro section. I don't know whether my thought is correct. I would rather not giving misleading
+pointers. I also don't know how far should a pointer chases back. Readers can be directed to recently
+works which will eventually lead them back to the earliest possible paper. But wouldn't it be
+great if the author of a new paper shows reader all the milestones? After all we already know 
+pointer dereferencing is expensive.}
 
@@
   section from the eyes of the reviewer.}
+\todo[inline]{KC: I might have some misconcept about the related work
+section. You might have felt this, haha. Now I think this section is
+targeting the following scenarios:
+- ``I think someone has solved this problem ...''
+- ``This work looks similar to paper X, what is the difference?''
+- ``Is this work inspired by paper X?''
+Is my understanding correct?}
 
@@
 We name the machine after \textbf{c}ast calculus.
-%
-This machine is parameterized over blame strategy $B$, which ranges over
-Lazy D (Fig.~\ref{fig:blame-strategy-LazyD}) and Lazy UD 
-(Fig.~\ref{fig:blame-strategy-LazyUD}).
+\todo[inline]{JS: explain the name choice of $\mathcal{R}$.}
+\todo[inline]{KC: I want to space-efficient machine to be S, so ... B might be a better name 
+because it reminds people of the $\lambda B$ calculus.
+Or $T$ for type-based cast?
+Or $C$ for cast-calculus?
+Or $D$ for definitional semantic?
+How do you think?}
+\todo[inline]{JS: B or C both sound like good choices for the reasons
+you give.}
+\todo[inline]{KC: Let's go with C to avoid confusion with Blame strategy.}
+%
+% This machine is parameterized over blame strategy $B$, which ranges over
+% Lazy D (Fig.~\ref{fig:blame-strategy-LazyD}) and Lazy UD 
+% (Fig.~\ref{fig:blame-strategy-LazyUD}).
+This machine is parameterized over blame strategy $B$. We will describe
+the components of a blame strategy as we go through the machine definition.
+In this work we focus on Lazy D (Fig.~\ref{fig:blame-strategy-LazyD}) and Lazy UD 
+(Fig.~\ref{fig:blame-strategy-LazyUD}). Adding more blame strategies, 
+such as the ones defined in \cite{siek2009exploring}, is possible.
 \todo[inline]{JS: I don't think $B$ is restricted to just those two.
@@
 \todo[inline]{JS: Yes.}
+\todo[inline]{KC: The machine definition gives a nice context for blame strategy so I 
+define blame strategy later. You will find a todo near the blame strategy definition.}
 %
@@
 to the dynamic type, as in the work of \citet{wadler2009well}. The
-inner value must be of an injectable type. The definition of
-injectable types depends on blame strategies:
-%
-for the \LD\ strategy, every pre-type is injectable 
+inner value must be of an injectable type ($I$).
+% The definition of
+% injectable types depends on blame strategies:
+The set of injectable type, which is defined by specify blame strategies,
+must be a subset of pre-types.
+%
+For the \LD\ strategy, every pre-type is injectable 
 (Fig.~\ref{fig:blame-strategy-LazyD});
@@
   explain, e.g., in the transition rule that uses applyCast.}
+\todo[inline]{KC: 1. I will try to switch to monadic let. As you pointed out
+when we wrote the WGT paper, let is more friendly to readers who are not familiar
+with monads.
+2. Do you imply that monadic let doesn't need to be explained?
+}
 
@@
 The transition relation \reduceto{s}{s} invokes the cast application
-function, noted as $\applyCast{v}{\ccast{S}{l}{T}}$ to capture the
-differences between blame strategies
-(Fig.~\ref{fig:blame-strategy-LazyD} and
-Fig.~\ref{fig:blame-strategy-LazyUD}).
-\todo[inline]{JS: be consistent with the font used for applyCast. Sometimes
-  you use roman and sometimes you used italic. Also, be consistent
-  for all the metafunctions (eval, observe, etc.).}
+function, noted as $\applyCast{v}{\ccast{S}{l}{T}}$, which is also defined
+by specify blame strategies.
+% to capture the
+% differences between blame strategies
+% (Fig.~\ref{fig:blame-strategy-LazyD} and
+% Fig.~\ref{fig:blame-strategy-LazyUD}).
 %
@@
 \end{figure}
+
+\todo[inline]{KC: conditions of blame strategy}
+\begin{definition}[Blame Strategy, $B$]
+A blame strategy defines a subset of pre-types, written I, that is injectable,
+and a function, written applyCast, that applies cast to values.
+\end{definition}
 
@@
 normal form of \citet{siek2012interpretations} to motivate the design
-of hypercoercions.  We omit sum types and product types in this
-section because the prior work did not include them.
-\todo[inline]{But Fig 6 includes product types.}
+of hypercoercions.
+% We omit sum types and product types in this
+% section because the prior work did not include them.
 
@@
 their normal forms. \figref{fig:normal-coercion} defines the syntax of
-coercion in normal form, written $\hat{c}$.
+coercion in normal form, written $s$ and $t$.
 \todo[inline]{JS: In the figure, normal forms are written $s$ and $t$.}
+\todo[inline]{KC: you are absolutely right.}
 Conceptually, a coercion
@@
 then concluded with an injection $I!$ or a failure $\bot^l$. While
-this is a simple idea, there are 10 clauses in the definition for
-$\hat{c}$!
+this is a simple idea, 
+% there are 10 clauses in the definition for $s$!
+the three-part and symmetric structure is not obvious in the syntax definition.
 
@@
 In this section we present a framework for proving the 
-correctness of space-efficient cast representations.
-The framework includes an abstract data 
+correctness of cast representations. The framework includes an abstract data 
 type named Cast ADT, which specifies the operators of cast representations, 

### 2020-10-05 paper.tex

@@
 function, noted as $\applyCast{v}{\ccast{S}{l}{T}}$, which is also defined
-by specify blame strategies.
-% to capture the
-% differences between blame strategies
-% (Fig.~\ref{fig:blame-strategy-LazyD} and
-% Fig.~\ref{fig:blame-strategy-LazyUD}).
+by specify blame strategies (Fig.~\ref{fig:blame-strategy-LazyD} and
+Fig.~\ref{fig:blame-strategy-LazyUD}).
+\todo[inline]{JS: be consistent with the font used for applyCast. Sometimes
+  you use roman and sometimes you used italic. Also, be consistent
+  for all the metafunctions (eval, observe, etc.).}
 %
@@
 of hypercoercions.
-% We omit sum types and product types in this
-% section because the prior work did not include them.
 
@@
 % program execution.
-In this section we present a framework for proving the 
-correctness of cast representations. The framework includes an abstract data 
-type named Cast ADT, which specifies the operators of cast representations, 
-a CEK machine $\SMachine{C}$ parameterized over a Cast ADT,
-which uses the cast operators implemented by $C$ to work with casts, 
-and theorems relating $\SMachine{C}$ to $\CMachine{B}$.
-%
-Subsection~\ref{sec:cast-adt-and-space-efficient-cek} describes Cast ADT and the 
-machine \SMachine{C}. We conjecture that the machine \SMachine{C} is 
-space-efficient provided that the cast representation $C$ performs compression.
-%
-Subsection~\ref{sec:good-cast-adt} defines two subset of Cast ADT, namely Lazy D 
-Cast ADT and Lazy UD Cast ADT. As their names suggest, if $C$ is a Lazy D Cast 
-ADT, executing a program in $\SMachine{C}$ would give the same result as in 
-$\LDMachine$. Similarly, if $C$ is a Lazy UD Cast ADT, executing a program in 
-$\SMachine{C}$ would give the same result as in $\LUDMachine$.
+In this section we present a framework for proving the correctness of
+space-efficient cast representations.  The framework includes an
+abstract data type named Cast ADT, which specifies the operators
+required of a cast representation, a CEK machine $\SMachine{C}$
+parameterized over a Cast ADT $C$, and theorems relating
+$\SMachine{C}$ to $\CMachine{B}$.
+%
+Subsection~\ref{sec:cast-adt-and-space-efficient-cek} defines the Cast
+ADT and the machine \SMachine{C}. We conjecture that the machine
+\SMachine{C} is space-efficient provided that the cast representation
+$C$ performs compression.
+%
+Subsection~\ref{sec:good-cast-adt} defines two subsets of the Cast
+ADT, namely the Lazy D Cast ADT and the Lazy UD Cast ADT. As their
+names suggest, if $C$ is a Lazy D Cast ADT, executing a program in
+$\SMachine{C}$ would give the same result as in
+$\LDMachine$. Similarly, if $C$ is a Lazy UD Cast ADT, executing a
+program in $\SMachine{C}$ would give the same result as in
+$\LUDMachine$.
 %

### 2020-10-05 paper.tex
edits in sect. 4

@@
 \newcommand{\idc}[1]{\ensuremath{\mathrm{id}_c(#1)}}
-\newcommand{\mkCont}[1]{\ensuremath{\mathrm{mkK}(#1)}}
-\newcommand{\extCont}[2]{\ensuremath{\mathrm{extK}(#1,#2)}}
+\newcommand{\mkContName}[0]{\ensuremath{\mathrm{mkK}}}
+\newcommand{\mkCont}[1]{\ensuremath{\mkContName(#1)}}
+\newcommand{\extContName}[0]{\ensuremath{\mathrm{extK}}}
+\newcommand{\extCont}[2]{\ensuremath{\extContName(#1,#2)}}
 % \newcommand{\applyCont}[2]{\ensuremath{\langle\langle#1,#2\rangle\rangle}}
@@
 
-\begin{figure}
+\begin{figure}[tp]
 	\fbox{\reducetoR{B}{s}{s}} Transition
@@
 
-\begin{figure}
+\begin{figure}[tp]
 	\[
@@
 CEK machine \SMachine{C}.  The key differences between \SMachine{C}
-and \CMachine{B} are the places where casts can accumulate, that is,
-in the definitions of values and continuations.
+and \CMachine{B} are in the places where casts can accumulate, that
+is, in the definitions of values and continuations.
 
@@
 
-Before moving to the transition relation of \SMachine{C}, let's define two 
-helper functions that manipulate continuations.
-%
-The function $\mathit{mkCont}$ construct a continuation from a pre-continuation 
-by topping the pre-continuation with an identity cast. 
-%
-The function $\mathit{extCont}$ composes $c$ with the cast at the top of $K$ by 
-using the composition operator 
-$\fatsemi$.
-\[
-\begin{array}{rclr}
-\figequalto{\mkCont{k}}{\Kcons{\Fcast{\id{S}}}{k}}{\sidecond{\casttyping{k}{S}{T}}}
-\figequalto{\extCont{c}{\Kcons{\Fcast{d}}{k}}}{
-	\Kcons{\Fcast{(\compose{c}{d})}}{k}
-}{}
-\end{array}
-\]
-
-\begin{figure}
+Before discussing the transition relation of \SMachine{C}, we define
+two helper functions for manipulating continuations.
+%
+The function $\mkContName$ constructs a continuation from a
+pre-continuation by topping it with an identity cast.
+\begin{align*}
+  \mkCont{k} &= \Kcons{\Fcast{\id{S}}}{k} & \sidecond{\casttyping{k}{S}{T}}
+\end{align*}
+The function $\extContName$ composes $c$ with the cast at the top of
+$K$ by using the composition operator $\fatsemi$.
+\begin{align*}
+  \extCont{c}{\Kcons{\Fcast{d}}{k}} &= \Kcons{\Fcast{(\compose{c}{d})}}{k}
+\end{align*}
+
+\begin{figure}[tp]
 	\fbox{\reducetoS{C}{s}{s}} Transition
@@
 \figref{fig:semachine-dynamics} defines the transition relation
-$\reducetoS{C}{s}{s}$. They rely on functions provided 
-by $C$ to work with casts.
-%
-To construct a function value, the machine fills the casts with identities.
-%
-When evaluating a cast expression, the machine extends the continuation with 
-\translate{\ccast{S}{l}{T}}.
-%
-To return a value to a continuation, the machine first applies the top cast to 
-the value. If the cast application fails, the machine halts with the blame 
-label from the failure. Otherwise, the machine handles the pre-continuation 
-with the function $\applyCont{v}{k}$.
+$\reducetoS{C}{s}{s}$. It relies on the functions provided by the Cast
+ADT $C$.
+%
+We focus on the transition rules highlighted in red, which involve
+casts and the changes needed for space efficiency.
+%
+The rule for evaluating a function produces a function value, using
+identities for the casts on the function value's domain and range.
+%
+The rule for evaluating a cast expression extends the continuation
+with the cast \translate{\ccast{S}{l}{T}}.
+%
+The rule for returning a value to a continuation first applies the top
+cast of the continutation to the value. If the cast application fails,
+the machine halts with the blame label from the failure. Otherwise,
+the machine handles the pre-continuation with the function
+$\applyCont{v}{k}$.
 %
@@
 
-\begin{figure}
+\begin{figure}[tp]
 
@@
 
-\begin{figure}
+\begin{figure}[tp]
 	Syntax of Hypercoercions
@@
 
-\begin{figure} %% composition 1
+\begin{figure}[tp] %% composition 1
 \[
@@
 
-\begin{figure}
+\begin{figure}[tp]
 	\fbox{$\translate{\ccast{S}{l}{T}} = c$} Translation of \LD\ hypercoercions
@@
 
-\begin{figure}
+\begin{figure}[tp]
 \fbox{$\denote{c}(v)=r$}
@@
 
-\begin{figure}
+\begin{figure}[tp]
 	\fbox{$c \fatsemi c = c$}
@@
 
-\begin{figure}
+\begin{figure}[tp]
 	\fbox{$\translate{\ccast{S}{l}{T}} = c$}
@@
 
-\begin{figure}
+\begin{figure}[tp]
 	\fbox{$\denote{c}_c(v)=r$}

### 2020-10-05 paper.tex
more edits in sec 4, starting on 5

@@
 \newcommand{\scont}[2]{\ensuremath{\langle#1,#2\rangle}}
-\newcommand{\shalt}[1]{\ensuremath{\Downarrow #1}}
+\newcommand{\shalt}[1]{\ensuremath{\mathop{\Downarrow} #1}}
 
@@
 % \newcommand{\applyCont}[2]{\ensuremath{\langle\langle#1,#2\rangle\rangle}}
-\newcommand{\applyCont}[2]{\ensuremath{\mathrm{applyK}(#1,#2)}}
+\newcommand{\applyContName}[0]{\ensuremath{\mathrm{applyK}}}
+\newcommand{\applyCont}[2]{\ensuremath{\applyContName(#1,#2)}}
 
@@
 }
+\todo[inline]{JS: No, you should still define monadic let.}
 
@@
 their normal forms. \figref{fig:normal-coercion} defines the syntax of
-coercion in normal form, written $s$ and $t$.
-\todo[inline]{JS: In the figure, normal forms are written $s$ and $t$.}
-\todo[inline]{KC: you are absolutely right.}
-Conceptually, a coercion
-in normal form has three parts, all of which are optional.  It may
-start with a projection $I?^l$, followed by a function coercion, and
-then concluded with an injection $I!$ or a failure $\bot^l$. While
-this is a simple idea, 
-% there are 10 clauses in the definition for $s$!
-the three-part and symmetric structure is not obvious in the syntax definition.
+coercion in normal form, written $s$ and $t$.  Conceptually, a
+coercion in normal form has three parts, all of which are optional.
+It may start with a projection $I?^l$, followed by a function
+coercion, and then concluded with an injection $I!$ or a failure
+$\bot^l$. While this is a simple idea, the three-part symmetric
+structure is not obvious in the syntax definition.
 
@@
 	\]
-	\caption{Dynamic semantics of the cast calculi as a 
-	space-efficient CEK	machine, \SMachine{C}. The transitions that involve 
-	casts are highlighted
-		in red.}
+	\caption{The space-efficient CEK machine, \SMachine{C}.
+          The transitions involving casts are highlighted in red.}
 	\label{fig:semachine-dynamics}
@@
 $\applyCont{v}{k}$.
-%
-To apply a function, the machine applies the domain cast $c$ to the 
-argument $v$ and evaluates the function body. The codomain cast $d$ is merged 
-into the continuation with $\mathrm{extK}$.
-%
-When the machine constructs a pair, it fills the casts with identities, just 
-like how it does for function values. 
-%
-To take out the first part of a pair, the machine applies the first pending 
-cast on the first value and returns the result to the continuation.
-%
-Taking out the second part of a pair is similar.
-
-Reflexive transitive closure of reduction $\reducetoS{C}{s}{s}$ and
-the evaluation partial function $\evaltoS{C}{e}{o}$ are the same as in \CMachine{B}.
+
+Turning to the definion of $\applyContName{}$, we again focus on the
+cases that are specific to casts and space efficiency.  In the case
+for a function value, the machine applies the domain cast $c$ to the
+argument $v$ and then begins evaluation of the function body. To
+ensure space efficiency, the codomain cast $d$ is merged into the
+continuation with $\mathrm{extK}$.
+%
+In the case for constructing a pair, $\applyContName$ fills the casts
+in the pair value with identities, similar to its treatment of
+function values.
+%
+To project the first element of a pair, the machine applies the first
+pending cast on the first value and returns the result to the
+continuation.
+%
+Projecting the second element of a pair is similar.
+
+The reflexive transitive closure of reduction $\reducetoS{C}{s}{s}$
+and the evaluation partial function $\evaltoS{C}{e}{o}$ are defined in
+the standard way~\citep{felleisen03:_pllc}.
 
@@
 
-\subsection{Specifying good instances of Cast ADT} \label{sec:good-cast-adt}
-
-Recall that our goal is to prove that \SMachine{C} would be equivalent to
-\LDMachine\ or \LUDMachine\ when $C$ satisfies some properties.
-Cast ADT has fixed the behavior of identities and composition, so the only 
-remaining operator is translation.
+\subsection{Specifying good instances of the Cast ADT} \label{sec:good-cast-adt}
+
+Recall that our goal is to prove that \SMachine{C} is equivalent to
+\LDMachine\ or \LUDMachine\ when $C$ satisfies some properties. The
+Cast ADT specifies the behavior of identity casts and composition, so
+the only remaining operator to specify is translation:
+$\translate{\ccast{S}{l}{T}}$.
 %
@@
 Fig.~\ref{fig:blame-strategy-LazyUD}).
+\todo[inline]{JS: what does ``them'' refer to in the previous sentence?
+  Please replace with a specific noun. Also, why should the reader do
+  the comparison? What are they suppose to notice?}
+\todo[inline]{JS: say where the following equations come from.
+  They are the equations you needed for the proof of equivalence,
+  right?}
 
@@
 	\bisimc{
-		(\ccast{T_1}{l_1}{T_2}\ldots\ccast{T_{i-1}}{l_{i-1}}{T_i})
+		(\ccast{T_1}{l_1}{}\ldots\ccast{}{l_{i-1}}{T_i})
 	}{c_1}{T_1}{T_i}\\
 	\bisimc{
-		(\ccast{T_i}{l_i}{T_{i+1}}\ldots\ccast{T_{n-1}}{l_{n-1}}{T_n})
+		(\ccast{T_i}{l_i}{}\ldots\ccast{}{l_{n-1}}{T_n})
 	}{c_2}{T_i}{T_n}
@@
 	\bisimc{
-		(\ccast{T_1}{l_1}{T_{2}}\ldots\ccast{T_{n-1}}{l_{n-1}}{T_n})
+		(\ccast{T_1}{l_1}{}\ldots\ccast{}{l_{n-1}}{T_n})
 	}{
@@
 }{
-	\bisims{\scont{v}{K}}{\scont{v}{K'}}{T}
+	\bisims{\scont{v}{K}}{\scont{v'}{K'}}{T}
 } \quad
@@
 
-\caption{Bisimulation between \CBMachine\ and \SMachine{C}. It is the smallest 
-congruence relation containing the shown rules. Everything to the left (resp. 
-right) of $\approx$ is in \CBMachine\ (resp. in \SMachine{C}).}
+\caption{Bisimulation between \CBMachine\ and \SMachine{C}. It is the
+  smallest congruence relation containing the shown rules. Everything
+  to the left of $\approx$ is in \CBMachine{} and everything to the
+  right is in \SMachine{C}.}
 \label{fig:bisim-SC-D}
@@
 The central part of the proofs is a weak bisimulation between \CMachine{B} and \SMachine{C}.
-Fig.~\ref{fig:bisim-SC-D} defines the bisimulation relation.
-It is the smallest congruence relation containing the rules 
+Fig.~\ref{fig:bisim-SC-D} defines the bisimulation relation
+between a state $s$ of \CMachine{B} and a state $s'$
+of \SMachine{C}, written $\bisims{s}{s'}{T}$.
+This relation is the smallest congruence relation containing the rules 
 in Fig.~\ref{fig:bisim-SC-D}.
-%
-The relation $\bisimc{\overline{\ccast{S}{l}{T}}}{c}{S}{T}$ relates a sequence 
-of cast in \CBMachine\ with one cast in \SMachine{C}. This relation is designed 
-to cover all possibly ways to construct a cast representation. The empty 
-sequence is related to the identity cast. A \CBMachine\ cast is related 
-to its translation. Finally, cast sequencing preserves the bisimulation 
-relation.
-%
-We remark that this bisimulation relation is unusual in that it uses
-some ADT operations in its definition, such as $\id{T}$, 
-$\translate{\ccast{S}{l}{T}}$, and $\compose{c}{c}$, which is necessary because 
-\SMachine{C} and the bisimulation is parameterized over the Cast ADT.
-
-The bisimulation relation is mutually defined on continuations and pre-continuations,
-written 
-$\bisimK{K}{K}{S}{T}$ and $\bisimK{K}{k}{S}{T}$, where $S$ and $T$ are their 
-source and target types respectively, values, written $\bisimv{v}{v}{T}$, 
-where $T$ is their type, and environments, written $\bisimE{\Gamma}{E}{E}$, 
-where $\Gamma$ is their type environment. The bisimulation relation for values 
-is designed to make Lemma~\ref{lem:LazyD-apply-cast-preserve-bisim} and 
-Lemma~\ref{lem:LazyUD-apply-cast-preserve-bisim} (described below) true, that 
-is, if $\bisimv{v}{v'}{S}$
-then
+
+The auxiliary relation $\bisimc{\overline{\ccast{S}{l}{T}}}{c}{S}{T}$
+relates a sequence of cast in \CBMachine\ with one cast in
+\SMachine{C}. This relation is designed to cover all possibly ways to
+construct a cast representation. The empty sequence is related to the
+identity cast. A single \CBMachine\ cast is related to its
+translation. Appending two sequences of casts is related to the
+composition of the corresponding space-efficient casts.
+%
+We remark that this relation is unusual in that it uses some ADT
+operations in its definition, such as $\id{T}$,
+$\translate{\ccast{S}{l}{T}}$, and $\compose{c}{c}$, which is
+necessary because \SMachine{C} and the bisimulation is parameterized
+over the Cast ADT.
+
+The bisimulation relation is mutually defined on
+\begin{itemize}
+\item continuations and pre-continuations, written $\bisimK{K}{K}{S}{T}$ and
+  $\bisimK{K}{k}{S}{T}$, where $S$ and $T$ are their source and target
+  types respectively,
+\item values, written $\bisimv{v}{v}{T}$, where $T$ is
+  their type, and
+\item environments, written $\bisimE{\Gamma}{E}{E}$, where
+  $\Gamma$ is their type environment.
+\end{itemize}
+The bisimulation relation for values is designed to make
+Lemma~\ref{lem:LazyD-apply-cast-preserve-bisim} and
+Lemma~\ref{lem:LazyUD-apply-cast-preserve-bisim} (described below)
+true, that is, if $\bisimv{v}{v'}{S}$ then
 \[
@@
 \begin{proof}
-	Case splitting whether $S$ is shallowly consistent with $T$.
-	If yes, case splitting how they are shallowly consistent.
-	Then apply properties of Lazy D Cast when applicable.
+  Proceed by cases on whether $S$ is shallowly consistent with $T$.
+  If yes, proceed by cases regarding how they are shallowly consistent
+  and then apply equations of Lazy D Cast.
 \end{proof}
@@
 \begin{proof}
-	Case splitting whether $S$ is shallowly consistent with $T$.
-	If yes, case splitting how they are shallowly consistent.
-	Then apply properties of Lazy UD Cast when applicable.
+  Proceed by cases on whether $S$ is shallowly consistent with $T$.
+  If yes, further split on how they are shallowly consistent and then
+  apply equations of Lazy UD Cast.
 \end{proof}
@@
 
-We now come to the main lemmas, the weak bisimulation between
+We come to the main lemma, the weak bisimulation between
 \CBMachine\ and \SMachine{C}.
@@
 \end{enumerate}
-where
+where the final predicate on states is defined as follows
 \begin{gather*}
@@
 \todo[inline]{KC: wouldn't it be great if I can describe the main ideas of the proof?}
+\todo[inline]{JS: Yes, that would be great.}
 
@@
 
+\todo[inline]{There should be some text regarding the following
+two theorems.}
+
 \begin{theorem}[Correctness of Lazy D \SMachine{C}]
@@
 
-\begin{figure}[tp]
-	Syntax of Hypercoercions
-	\[
-	\begin{array}{lrcl}
-	\stxrule{c}{Hypercoercions}{
-		\hcci           \mid
-		\hccc{h}{m}{t}
-	}
-	\stxrule{h}{Heads}{
-		\hche     \mid
-		\hchp{I}{l}
-	}
-	\stxrule{m}{Middles}{
-		\hcmbool       \mid
-		\hcmfunc{c}{c} \mid
-		\hcmprod{c}{c} \mid
-		\hcmfail{l}    
-	}
-	\stxrule{t}{Tails}{
-		\hcte     \mid
-		\hcti{I}
-	}
-	\end{array}
-	\]
-
-	\fbox{$\mathit{id}( T ) = c$}
-	\[
-	\begin{array}{rclr}
-	\figequalto{id(\star)}{
-		\hcci
-	}{}
-	\figequalto{id(P)}{
-		\hccc{\hche}{id(P)}{\hcte}
-	}{}
-	\end{array}
-	\]
-
-	\fbox{$\mathit{id}_m( P ) = m$}
-	\[
-	\begin{array}{rclr}
-	\figequalto{id(\Pbool)}{\hcmbool}{}
-	\figequalto{id(\Pfunc{S}{T})}{
-		\hcmfunc{id(S)}{id(T)}
-	}{}
-	\figequalto{id(\Pprod{S}{T})}{
-		\hcmprod{id(S)}{id(T)}
-	}{}
-	\end{array}
-	\]
-
-	\fbox{\casttyping{c}{S}{T}} Hypercoercion typing 
-	\begin{gather*}
-	\inference{}{\casttyping{\hcci}{\Tdyn}{\Tdyn}}
-	\quad
-	\inference{
-		\casttyping{h}{S}{P} &
-		\casttyping{m}{P}{Q} &
-		\casttyping{t}{Q}{T}
-	}{
-		\casttyping{\hccc{h}{m}{t}}{S}{T}
-	}
-	\end{gather*}
-
-	\fbox{\casttyping{h}{T}{P}} Head typing
-	\begin{gather*}
-	\inference{}{\casttyping{\hche}{P}{P}}
-	\quad
-	\inference{}{\casttyping{\hchp{I}{l}}{\Tdyn}{I}}
-	\end{gather*}
-
-	\fbox{$\casttyping{m}{T}{T}$} Middle typing
-	\begin{gather*}
-	\infr{}{\casttyping{\hcmfail{l}}{P}{Q}} \quad
-	\inference{}{\casttyping{\hcmbool}{\Pbool}{\Pbool}} \\
-	\inference{
-		\casttyping{c}{S_2}{S_1} &
-		\casttyping{d}{T_1}{T_2}
-	}{
-		\casttyping{\hcmfunc{c}{d}}{\Pfunc{S_1}{T_1}}{\Pfunc{S_2}{T_2}}
-	}
-	\quad
-	\inference{
-		\casttyping{c}{S_1}{S_2} &
-		\casttyping{d}{T_1}{T_2}
-	}{
-		\casttyping{\hcmprod{c}{d}}{\Pprod{S_1}{T_1}}{\Pprod{S_2}{T_2}}
-	}
-	\end{gather*}
-
-	\fbox{\casttyping{t}{P}{T}} Tail typing
-	\begin{gather*}
-	\inference{}{\casttyping{\hcte}{P}{P}} \quad
-	\inference{}{\casttyping{\hcti{I}}{I}{\Tdyn}} \quad
-	\end{gather*}
-
-	\caption{Definition of hypercoercions}
-	\label{fig:hypercoercion}
-\end{figure}
-
 In this section we present a new cast representation called hypercoercions. It 
@@
 \end{itemize}
+
+\begin{figure}[tp]
+	Syntax of Hypercoercions
+	\[
+	\begin{array}{lrcl}
+	\stxrule{c}{Hypercoercions}{
+		\hcci           \mid
+		\hccc{h}{m}{t}
+	}
+	\stxrule{h}{Heads}{
+		\hche     \mid
+		\hchp{I}{l}
+	}
+	\stxrule{m}{Middles}{
+		\hcmbool       \mid
+		\hcmfunc{c}{c} \mid
+		\hcmprod{c}{c} \mid
+		\hcmfail{l}    
+	}
+	\stxrule{t}{Tails}{
+		\hcte     \mid
+		\hcti{I}
+	}
+	\end{array}
+	\]
+
+	\fbox{$\mathit{id}( T ) = c$}
+	\[
+	\begin{array}{rclr}
+	\figequalto{id(\star)}{
+		\hcci
+	}{}
+	\figequalto{id(P)}{
+		\hccc{\hche}{id(P)}{\hcte}
+	}{}
+	\end{array}
+	\]
+
+	\fbox{$\mathit{id}_m( P ) = m$}
+	\[
+	\begin{array}{rclr}
+	\figequalto{id(\Pbool)}{\hcmbool}{}
+	\figequalto{id(\Pfunc{S}{T})}{
+		\hcmfunc{id(S)}{id(T)}
+	}{}
+	\figequalto{id(\Pprod{S}{T})}{
+		\hcmprod{id(S)}{id(T)}
+	}{}
+	\end{array}
+	\]
+
+	\fbox{\casttyping{c}{S}{T}} Hypercoercion typing 
+	\begin{gather*}
+	\inference{}{\casttyping{\hcci}{\Tdyn}{\Tdyn}}
+	\quad
+	\inference{
+		\casttyping{h}{S}{P} &
+		\casttyping{m}{P}{Q} &
+		\casttyping{t}{Q}{T}
+	}{
+		\casttyping{\hccc{h}{m}{t}}{S}{T}
+	}
+	\end{gather*}
+
+	\fbox{\casttyping{h}{T}{P}} Head typing
+	\begin{gather*}
+	\inference{}{\casttyping{\hche}{P}{P}}
+	\quad
+	\inference{}{\casttyping{\hchp{I}{l}}{\Tdyn}{I}}
+	\end{gather*}
+
+	\fbox{$\casttyping{m}{T}{T}$} Middle typing
+	\begin{gather*}
+	\infr{}{\casttyping{\hcmfail{l}}{P}{Q}} \quad
+	\inference{}{\casttyping{\hcmbool}{\Pbool}{\Pbool}} \\
+	\inference{
+		\casttyping{c}{S_2}{S_1} &
+		\casttyping{d}{T_1}{T_2}
+	}{
+		\casttyping{\hcmfunc{c}{d}}{\Pfunc{S_1}{T_1}}{\Pfunc{S_2}{T_2}}
+	}
+	\quad
+	\inference{
+		\casttyping{c}{S_1}{S_2} &
+		\casttyping{d}{T_1}{T_2}
+	}{
+		\casttyping{\hcmprod{c}{d}}{\Pprod{S_1}{T_1}}{\Pprod{S_2}{T_2}}
+	}
+	\end{gather*}
+
+	\fbox{\casttyping{t}{P}{T}} Tail typing
+	\begin{gather*}
+	\inference{}{\casttyping{\hcte}{P}{P}} \quad
+	\inference{}{\casttyping{\hcti{I}}{I}{\Tdyn}} \quad
+	\end{gather*}
+
+	\caption{Definition of hypercoercions}
+	\label{fig:hypercoercion}
+\end{figure}
 

### 2020-10-05 paper.tex
comment

@@
 is also applicable to other cast representations.
+\todo[inline]{JS: cite which other cast representations}
 We also present a new cast representation, hypercoercions, that is more friendly
@@
 pointer dereferencing is expensive.}
+\todo[inline]{JS: Yes, citing the original paper for each idea is great.
+  I'm just saying 1) cite the correct paper for each idea and 2)
+  talk about the various ideas in an organized way with respect
+  to your sentence and paragraph structure.}
 

### 2020-10-05 paper.tex
removed old comment

@@
 
-\todo[inline]{KC: (about the p below) Actually I think twosome's
-  composition is structurally recursive but threesomes' is not}
-\todo[inline]{JS: Then please go ahead and fix it.}
-\todo[inline]{KC: Fixed. 
-``Threesomes and supercoercions are good for
-mechanized metatheory because their compose operators 
-can be written in a structrually recursive form,''}
-
 The published space-efficient cast representations have various
@@
 can be written in a structrually recursive form,
-% are structurally recursive,
 making them easy to define in proof assistants such as
@@
 On the other hand, coercions in normal form are easier to understand
-than threesomes (with their strange labeled bottom type), and
+than threesomes (which have a strange labeled bottom type), and
 supercoercions (10 different kinds).

### 2020-10-05 paper.tex
comment

@@
 \todo[inline]{JS: say something about the difference between the above
-  and what is in this paper. That's the whole point of the related work
-  section from the eyes of the reviewer.}
-\todo[inline]{KC: I might have some misconcept about the related work
-section. You might have felt this, haha. Now I think this section is
-targeting the following scenarios:
-- ``I think someone has solved this problem ...''
-- ``This work looks similar to paper X, what is the difference?''
-- ``Is this work inspired by paper X?''
-Is my understanding correct?}
+  and what is in this paper. That's the whole point of the related
+  work section from the eyes of the reviewer.}  \todo[inline]{KC: I
+  might have some misconcept about the related work section. You might
+  have felt this, haha. Now I think this section is targeting the
+  following scenarios: - ``I think someone has solved this problem
+  ...''  - ``This work looks similar to paper X, what is the
+  difference?''  - ``Is this work inspired by paper X?''  Is my
+  understanding correct?}  \todo[inline]{JS: yes, and make sure to
+  give very explicit answers to these questions. It should feel to you
+  like you're hitting the reader over the head with the most obvious
+  things (to you). The above paragraph is currently insufficient
+  because it doesn't emphasize what scientific constributions are new
+  to our paper compared to those prior papers on coercions in normal
+  form.}
 

### 2020-10-05 paper.tex
removed old comment

@@
 such as the ones defined in \cite{siek2009exploring}, is possible.
-\todo[inline]{JS: I don't think $B$ is restricted to just those two.
-Can't it be any blame strategy that satisfies certain conditions?}
-\todo[inline]{KC: Technically a $B$ should define a predicate over pretypes, which specifies
-what is injectable, and a apply-cast function. Of course, the set of values that the apply-cast
-function works with depends on the set of injectable types.
-\url{https://github.com/Gradual-Typing/Equivalence-of-Cast-Calculi/blob/master/equivalence-of-cast-calculi/R/BlameStrategies.agda}
-Do you want me to put these contraints in the paper?}
-\todo[inline]{JS: Yes.}
-\todo[inline]{KC: The machine definition gives a nice context for blame strategy so I 
-define blame strategy later. You will find a todo near the blame strategy definition.}
 %

### 2020-10-05 paper.tex
edits to sec 5

@@
 We also present a new cast representation, hypercoercions, that is more friendly
-to mechanized meta-theory and hypothetically consume less memory than coercions
+to mechanized meta-theory and consumes less memory than coercions
 in normal forms.
@@
 
-\todo[inline]{KC: I changed some wording in the following definition:
-"a family"; translate a cast ...}
 \begin{definition}[Cast Abstract Data Type (Cast ADT)]
@@
 \begin{itemize}
-	\item $\id{T}=c$: create an identity cast
-	\item $\compose{c}{c}=c$: compose casts
-	\item $\translate{\ccast{S}{l}{T}}=c$: translate a cast in source 
+	\item $\id{T}$: create an identity cast
+	\item $\compose{c}{c}$: compose two casts
+	\item $\translate{\ccast{S}{l}{T}}$: translate a cast in the source 
 		program to a $\textit{Cast}_{S,T}$
-	\item $\denote{c}(v)=r$: apply a cast to a value
+	\item $\denote{c}(v)$: apply a cast to a value
 	\item If $ \valuetyping{v}{T} $ then $\denote{\id{T}}(v)=v$
@@
 
-Subsection~\ref{sec:LazyD-Hypercoercions} implements the \CastADT\ with the \LD\ 
-hypercoercions and proves that \LD\ hypercoercions is a Lazy D Cast ADT. 
-Subsection~\ref{sec:LazyUD-Hypercoercions} does the \LUD\ counterparts.
-Finally, we argue in Subsection~\ref{sec:hypercoercions-compact} that 
-hypercoercions would consume less space than coercions in 
-normal form and hence are more suitable for implementation.
+Subsection~\ref{sec:LazyD-Hypercoercions} implements the \CastADT{}
+with the \LD{} hypercoercions and proves that \LD{} hypercoercions is
+a Lazy D Cast ADT.  Subsection~\ref{sec:LazyUD-Hypercoercions} does
+the same for \LUD{}.  Finally, we argue in
+Subsection~\ref{sec:hypercoercions-compact} that hypercoercions
+consume less space than coercions in normal form and hence are more
+suitable for implementation.
 
@@
 
+	\caption{Composition of \LD\ Hypercoercions}
+	\label{fig:LazyD-Hypercoercions-composition}
+\end{figure}
+
+\begin{figure}[tp]
 \fbox{$\goodgap{g}$}
@@
 \]
-
-	\caption{Composition of \LD\ Hypercoercions}
-	\label{fig:LazyD-Hypercoercions-composition}
+\caption{Auxilliary predicates and functions for hypercoercion composition.}
+\label{fig:aux-hypercoercion-composition}
 \end{figure}
 
-\figref{fig:LazyD-Hypercoercions-composition} defines the functions 
-\compose{c}{c} that compose \LD\ hypercoercions. We use these functions to 
-implement the \CastADT.
+\figref{fig:LazyD-Hypercoercions-composition} defines the composition
+operator \compose{c}{c} for \LD\ hypercoercions and
+\figref{fig:aux-hypercoercion-composition} defines some auxilliary
+predicates and functions.
 
@@
   (something like in private communication with KC and Deyaa)}
-
-The \compose{c}{c} operator is the key to compressing coercions and maintaining 
-space-efficiency. The composition operator for Coercions in Normal Form 
-requires the target type of the first coercion to match the source type of the 
-second. This requirement, however, imposes a considerable difficulty in 
-termination proof of the composition of \LD\ Coercions in Normal Form, reported 
-by Kuang-Chen Lu and Deyaaeldeen Almahallawi. So it is useful to relax this 
-restriction for the \LD\ tracking strategy.
-%
-We shall need optional source cast, written $g$, that range over
-$\gnone$ or $\gsome{S}{l}{T}$, to maintain the gap between the hypercoercions 
-to be composed. The source cast is mandatory when the target
-type of the first hypercoercion does not match the source type of the second. 
-Then we write the composition of hypercoercions as \composegap{c_1}{g}{c_2}.
+\todo[inline]{JS: Yes}
+
+The \compose{c}{c} operator is the key to compressing coercions and
+maintaining space-efficiency. The composition operator for Coercions
+in Normal Form requires the target type of the first coercion to match
+the source type of the second. This requirement, however, imposes
+considerable difficulty in the termination proof of the composition
+for \LD\ Coercions in Normal Form, reported by Kuang-Chen Lu and
+Deyaaeldeen Almahallawi. So it is useful to relax this restriction for
+the \LD\ tracking strategy.
+%
+We shall need an optional source cast, written $g$, that ranges over
+$\gnone$ or $\gsome{S}{l}{T}$, to maintain the gap between the two
+hypercoercions to be composed. The source cast is mandatory when the
+target type of the first hypercoercion does not match the source type
+of the second.  Then we write the composition of hypercoercions as
+\composegap{c_1}{g}{c_2}.
 %  
@@
 %
-When the first hypercoercion is the \hcci, the output must start with a 
-projection, in which case we invoke the helper function \textit{mkProj}. In 
-\textit{mkProj}, if the head of $c_2$ is a projection, the result is $c_2$.  
-Otherwise, we need a label to build the projection. Since the head of $c_2$ is 
-the no-op, its source type must be a pretype. Thus we know $g$ must be a 
-source cast and we use it to construct the projection.
+When the first hypercoercion is the \hcci, the output must start with
+a projection, in which case we invoke the helper function
+\textit{mkProj}. In \textit{mkProj}, if the head of $c_2$ is a
+projection, the result is $c_2$.  Otherwise, we need a label to build
+the projection. Since the head of $c_2$ is a no-op, its source type
+must be a pre-type. Thus we know $g$ must be a source cast and we use
+it to construct the projection.
 %
@@
 When the gap is a cast between shallowly inconsistent types (i.e. having 
-different top-most constructors). the output is a failure.
+different top-most constructors) the output is a failure.
 %
@@
 
-Agda is able to understand that \composegap{c}{g}{c} is terminating. The reason 
-might be that in \composegap{c}{g}{c} both casts become smaller in recursive 
-calls, although their position is swapped in the function case. Readers who
-hate non-structural recursion might add a Boolean parameter to indicate the order
-of composition.
+Agda is able to understand that \composegap{c}{g}{c} is
+terminating. The reason might be that in \composegap{c}{g}{c} both
+casts become smaller in recursive calls, although their position is
+swapped in the function case. Readers who dislike non-structural
+recursion could add a Boolean parameter to indicate the direction of
+composition.
 
@@
 	\]
-	\caption{Translatin of \LD\ Hypercoercions}
+	\caption{Translation of \LD\ Hypercoercions}
 	\label{fig:LazyD-Hypercoercions-translation}
@@
 
-The definition of translation \translate{\ccast{S}{l}{T}} is straightforward 
-(\figref{fig:LazyD-Hypercoercions-translation}).
+The definition of the translation function \translate{\ccast{S}{l}{T}}
+is straightforward (\figref{fig:LazyD-Hypercoercions-translation}).
 
@@
 %
-In projection case of head application, a new middle is constructed and applied 
-to the injected value.
-%
-Middle applications raises an error if the middle is a failure and extend value 
-proxies otherwise.
+In the projection case of applying a head coercion, a new middle is
+constructed and applied to the injected value.
+%
+Middle applications raise an error if the middle is a failure,
+otherwise they compose their coercions with those in the value.
 

### 2020-10-05 paper.tex
edits to sec 5 and 6

@@
 	$v'$ is a value in \SMachine{C},
-	and $\bisimv{v}{v'}{S}$
+	and $\bisimv{v}{v'}{S}$.
 	\[
@@
 	\label{thm:SD-equiv}
-	Suppose $C$ is a Lazy D Cast ADT
+	Suppose $C$ is a Lazy D Cast ADT.
 	\[
@@
 	\label{thm:SUD-equiv}
-	Suppose $C$ is a Lazy UD Cast ADT
+	Suppose $C$ is a Lazy UD Cast ADT.
 	\[
@@
 Middle applications raise an error if the middle is a failure,
-otherwise they compose their coercions with those in the value.
-
-\begin{proposition} Lazy D Hypercoercions implement the Lazy D Cast ADT
+otherwise they compose their sub-coercions with those in the value.
+
+\begin{proposition} Lazy D Hypercoercions implement the Lazy D Cast ADT.
 \end{proposition}
 \begin{theorem}[Lazy D Hypercoercions are Correct] Let $H$ be the Lazy D 
-hypercoercions,
+hypercoercions.
 \[\machineequiv{\LDMachine}{\SMachine{H}}\]
@@
 \subsection{\LUD\ Hypercoercions} \label{sec:LazyUD-Hypercoercions}
+
+\todo[inline]{JS: I'd recommend moving this subsection before that of
+  LazyD because a reader is more likely to be familiar with Lazy UD.}
 
@@
 %
-In the two projection cases of head application, the result depends on whether 
-the source ground type ($G$) is the same as the target ($H$).
-%
-Middle applications raises an error if the middle is a failure and extend value 
-proxies otherwise.
+In the two projection cases of applying a head coercion, the result
+depends on whether the source ground type ($G$) is the same as the
+target ($H$).
+%
+The application of a middle coercion raises an error if the middle is
+a failure and otherwise composes its sub-coercions with those in the
+value.
 
@@
 \begin{theorem}[Lazy UD Hypercoercions are Correct] Let $H$ be the Lazy UD 
-	hypercoercions,
+	hypercoercions.
 	\[\machineequiv{\LDMachine}{\SMachine{H}}\]
@@
 
-\subsection{Compact Representation of Hypercoercions} \label{sec:hypercoercions-compact}
+\subsection{A Compact Representation of Hypercoercions} \label{sec:hypercoercions-compact}
 
@@
 compact for identity coercions and coercions that project from base
-types or inject to base types.  (Here \Pbool\ is the only base
-type, but in a real language the base types would include integers,
-Booleans, etc.)  We conjecture that such coercions occur more
-frequently than the more complex coercions (e.g. between function
-types), especially because such coercions appear in the leaves of
-complex coercions.
+types or inject to base types.  (Here \Pbool\ is the only base type,
+but in a real language the base types would include integers,
+Booleans, etc.) Such coercions occur more frequently than the more
+complex coercions (e.g. between function types) because such coercions
+appear in the leaves of complex coercions.
 
@@
 
-We present steps toward the first framework for proving the
-correctness of cast representations.
+We present the first framework for mechanized proofs of correctness
+for space-efficient cast representations.
 %
 The framework includes abstract data types for cast representations
-(Cast ADT and its refinements Lazy D Cast ADT and \LUD\ \CastADT), 
-a parameterized abstract machine \SMachine{C}, 
-a theorem which states that \SMachine{C} is equivalent
-to \LDMachine\ when $C$ is a Lazy D Cast ADT, and
-a theorem which states that \SMachine{C} is equivalent
-to \LUDMachine\ when $C$ is a Lazy UD Cast ADT.
+(Cast ADT and its refinements Lazy D Cast ADT and \LUD\ \CastADT), a
+parameterized abstract machine \SMachine{C}, a theorem stating that
+\SMachine{C} is equivalent to \LDMachine\ when $C$ is a Lazy D Cast
+ADT, and a theorem which states that \SMachine{C} is equivalent to
+\LUDMachine\ when $C$ is a Lazy UD Cast ADT.
 %
@@
 %
-We applied this framework to Lazy UD coercions in normal form,
-Lazy UD threesomes, and hypercoercions and conjecture that
-this framework is also applicable to other cast representations.
-
-We also presented hypercoercions, a cast representation that has a 
-theorem-prover-friendly compose operator and a more compact memory
+We applied this framework to Lazy UD coercions in normal form, Lazy UD
+threesomes, and hypercoercions and expect that this framework is also
+applicable to many other cast representations.
+
+We also presented hypercoercions, a cast representation with a
+mechanization-friendly compose operator and a more compact memory
 representation in comparison with coercions in normal forms.

### 2020-10-06 paper.tex
reply to JS

@@
 
-\todo[inline]{KC: KC, please add \url{https://arxiv.org/abs/2001.11560}
+\todo[inline]{KC: [IMPORTANT] KC, please add \url{https://arxiv.org/abs/2001.11560}
 to this section.}
@@
 
+\todo[inline]{KC: [IMPORTANT]}
 \todo[inline]{JS: say something about the difference between the above
@@
   the above and what is in this paper.}
+\todo[inline]{KC: [IMPORTANT] will do.}
 
@@
   for all the metafunctions (eval, observe, etc.).}
+\todo[inline]{KC: [IMPORTANT] will do.}
 %
@@
 (Definition~\ref{def:LazyUD-CastADT}) specify the behavior 
-of \translate{\ccast{S}{l}{T}}. Readers are encouraged to compare them with the 
-corresponding $\mathrm{applyCast}$ functions 
+of \translate{\ccast{S}{l}{T}}. Readers are encouraged to compare these two
+definitions with the corresponding $\mathrm{applyCast}$ functions 
 (Fig.~\ref{fig:blame-strategy-LazyD} and 
@@
   right?}
+\todo[inline]{KC: [IMPORTANT] will do.}
 
@@
 
-\todo[inline]{There should be some text regarding the following
+\todo[inline]{JS: There should be some text regarding the following
 two theorems.}
@@
 \todo[inline]{JS: Yes}
+\todo[inline]{KC: Could you show me how to do this? I don't know exactly
+how to write this kind of citations.}
 
@@
 
-\todo[inline]{KC: I need a better name for \compatibletailhead{t}{h}}
+\todo[inline]{KC: I need a better name for \compatibletailhead{t}{h},
+any suggestion from Jeremy?}
 

### 2020-10-08 paper.tex
edits in related work

@@
 
-\todo[inline]{KC: [IMPORTANT] KC, please add \url{https://arxiv.org/abs/2001.11560}
-to this section.}
-
-We review closely related work in three areas: coercions in normal
-form, threesomes, and parameterized cast calculi.
+\citet{siek2020mechanized} defines two dynamic semantics for 
+cast calculi parameterized over cast representations, similar to
+our \CMachine{B}. The two corresponding interfaces, namely
+$\mathrm{CastStruct}$ and $\mathrm{EfficientCastStruct}$, give
+users more control over the structure of values. \CMachine{B} machine
+insists that the cast on the top of a value must be a function cast
+or a product cast. In contrast, users of their interfaces define
+a predicate on casts called $\mathrm{Inert}$ and any inert cast can
+be a part of a value. Their system doesn't include theorems relating
+space-inefficient cast calculi and space-efficient ones, which
+is one of the major goals of our framework.
+
+% We review closely related work in three areas: coercions in normal
+% form, threesomes, and parameterized cast calculi.
 
@@
   and what is in this paper. That's the whole point of the related
-  work section from the eyes of the reviewer.}  \todo[inline]{KC: I
-  might have some misconcept about the related work section. You might
-  have felt this, haha. Now I think this section is targeting the
-  following scenarios: - ``I think someone has solved this problem
-  ...''  - ``This work looks similar to paper X, what is the
-  difference?''  - ``Is this work inspired by paper X?''  Is my
-  understanding correct?}  \todo[inline]{JS: yes, and make sure to
+  work section from the eyes of the reviewer.}
+\todo[inline]{KC: I might have some misconcept about the related work section.
+You might have felt this, haha. Now I think this section is targeting the
+following scenarios: 
+- ``I think someone has solved this problem ...''
+- ``This work looks similar to paper X, what is the difference?''
+- ``Is this work inspired by paper X?''
+Is my understanding correct?}
+\todo[inline]{JS: yes, and make sure to
   give very explicit answers to these questions. It should feel to you

### 2020-10-09 paper.tex
Updates from Overleaf

@@
 \newcommand{\applyCont}[2]{\ensuremath{\applyContName(#1,#2)}}
+\newcommand{\applyCastName}[0]{\ensuremath{\mathrm{applyCast}}}
 
@@
 \newcommand{\reducetoS}[3]{\ensuremath{#2 \longmapsto_{\SMachine{#1}} #3}}
-\newcommand{\evalto}[2]{\ensuremath{\mathit{eval}(#1)=#2}}
-\newcommand{\withmachineevalto}[3]{\ensuremath{\mathit{eval}_{#1}(#2)=#3}}
-\newcommand{\evaltoR}[3]{\ensuremath{\mathit{eval}_{\CMachine{#1}}(#2)=#3}}
+\newcommand{\evalto}[2]{\ensuremath{\mathrm{eval}(#1)=#2}}
+\newcommand{\withmachineevalto}[3]{\ensuremath{\mathrm{eval}_{#1}(#2)=#3}}
+\newcommand{\evaltoR}[3]{\ensuremath{\mathrm{eval}_{\CMachine{#1}}(#2)=#3}}
 \newcommand{\evaltoD}[2]{\evaltoR{\BLD}{#1}{#2}}
 \newcommand{\evaltoUD}[2]{\evaltoR{\BLUD}{#1}{#2}}
-\newcommand{\evaltoS}[3]{\ensuremath{\mathit{eval}_{\SMachine{#1}}(#2)=#3}}
-\newcommand{\compatibletailhead}[2]{\ensuremath{#1\;\mathit{R}\;#2}}
-\newcommand{\goodgap}[1]{\ensuremath{\mathit{good}(#1)}}
+\newcommand{\evaltoS}[3]{\ensuremath{\mathrm{eval}_{\SMachine{#1}}(#2)=#3}}
+\newcommand{\compatibletailhead}[2]{\ensuremath{#1\;R\;#2}}
+\newcommand{\goodgap}[1]{\ensuremath{\mathrm{good}(#1)}}
 \newcommand{\compileto}[4]{\expressiontyping{#1}{#2\rightsquigarrow#3}{#4}}
@@
 \todo[inline]{JS: cite which other cast representations}
+\todo[inline]{KC: will do.}
 We also present a new cast representation, hypercoercions, that is more friendly
@@
 that use a proxy-based approach. The contracts paper may be the first to propose blame tracking.}
-\todo[inline]{KC: I think readers should be able to trace back history by following the pointers in the 
-intro section. I don't know whether my thought is correct. I would rather not giving misleading
-pointers. I also don't know how far should a pointer chases back. Readers can be directed to recently
-works which will eventually lead them back to the earliest possible paper. But wouldn't it be
-great if the author of a new paper shows reader all the milestones? After all we already know 
-pointer dereferencing is expensive.}
-\todo[inline]{JS: Yes, citing the original paper for each idea is great.
-  I'm just saying 1) cite the correct paper for each idea and 2)
-  talk about the various ideas in an organized way with respect
-  to your sentence and paragraph structure.}
+\todo[inline]{KC: How about citing the origin of the proxy-based approach when we talk
+about the CPSed even-odd example?
+I am confused about which paper to cite. \cite{herman2010space} seems to be citing
+\cite{findler2002contracts} for the proxy-based approach of casting function.
+Here is the relevant sentences from \cite{herman2010space}:
+``In general, it is not possible to check if an untyped function satisfies a
+particular static type. A natural solution is to wrap the function in a proxy that, whenever
+it is applied, casts its argument and result values appropriately, ensuring that the function
+is only observed with its expected type. This proxy-based approach was formalized by Findler
+and Felleisen [15] ...''
+I am \textit{not} trying to say I don't believe in your statements about the origins of
+the proxy-based approach and blame tracking in functions.
+I want to know whether \citet{herman2010space} is citing the right paper.
+Maybe both papers came up independently with a similar idea but \cite{findler2002contracts}
+is more related to our work.
+}
 
@@
 calculus \citep{wadler2009well} and other cast calculi \citep{siek2009exploring}.
-% To allow the smooth transition, every gradually typed language
-% has a special type typically written as \Tdyn\ or \lstinline|Dyn| or \lstinline|Any|,
-% which enables imprecise type annotations.
-% Programmers can use an expression of type \texttt{T} in any context that \texttt{T} 
-% is consistent to.
-% Two types are consistent if they have no conflicting type information.
-% For instance, \lstinline|(->  Bool Int)| is consistent with \lstinline|(->  $\star$ Int)| but
-% not consistent with \lstinline|(->  Int Int)|.
-% When the type of an expression is consistent but not equal to the type of its 
-% context, there would be a runtime computation (i.e. a cast) that store or check 
-% type information to enforce type soundness.
 
@@
 
+\todo[inline]{KC: This paragraph suggests that
+\cite{siek2009exploring} gives the definitional semantics.
+\cite{siek2009exploring}'s is coercion-based.
+It makes more sense to me to use a type-based semantics as the definition.
+Actually in my mind \cite{siek2012interpretations} is definitional.}
+
 To summarize, the primary contributions of this paper are:
@@
 
+\subsection{Dynamics parameterized over cast representations}
 \citet{siek2020mechanized} defines two dynamic semantics for 
-cast calculi parameterized over cast representations, similar to
-our \CMachine{B}. The two corresponding interfaces, namely
-$\mathrm{CastStruct}$ and $\mathrm{EfficientCastStruct}$, give
-users more control over the structure of values. \CMachine{B} machine
+cast calculi parameterized over cast representations. The first
+semantics, namely CC, is \textit{not} space-efficient and
+parameterized over $\mathrm{CastStruct}$. The author instantiates
+CC to obtain the blame calculus ($\lambda B$). 
+The resulting semantics is analogous to our \LUDMachine.
+The other semantics, namely SC, is designed to be space-efficient
+and parameterized over $\mathrm{EfficientCastStruct}$. SC is analogous
+to our \SMachine{C}. These two parameterized semantics give
+users more control over the structure of values. Our \CMachine{B} machine
 insists that the cast on the top of a value must be a function cast
@@
 
-% We review closely related work in three areas: coercions in normal
-% form, threesomes, and parameterized cast calculi.
-
-\subsubsection{Coercions in normal form}
-
-\citet{henglein1994dynamic} introduces coercions to study compilation
-from dynamic languages to statically typed
-ones. \citet{herman2010space} proposes using coercions in normal forms
-to represent casts in gradual typing and proves space efficiency.
-However, they did not prove that the coercion-based semantics is
-equivalent to the standard (and type-based)
-one. \citet{Siek:2015:BCT:2737924.2737968} improve the Lazy UD style
-of coercions in normal forms and prove that Lazy UD coercions in
-normal form are correct, using two bisimulation between three
-reduction semantics. The first semantics is similar to \LUDMachine,
-which bisimulates a reduction semantics using coercions (not
-necessarily in normal form). The last semantics uses coercions in
-normal form and bisimulates the coercions-based semantics.
-
-\todo[inline]{KC: [IMPORTANT]}
+\citet{garcia2014deriving} presents a dynamic semantics for the Eager
+D blame strategy, using coercions. They claim that ``the artefacts for
+coercions can be replaced by other artefacts implementing different
+dynamic semantics''.
+
+\todo[inline]{JS: The above is too short of a description of that related
+work.}
+\todo[inline]{KC: I am actually very confused by \citet{garcia2014deriving}.
+They stated that ``Theorems 8.1 and 8.3 can be generalised for other choices
+of dynamic semantics by applying the correspondence described
+through the paper starting with a different set of coercion artefacts.''.
+However they didn't give a generalization and it is unclear to me over what
+their system is parameterized (cast representations? apply-coercion and seq?.}
+
+\subsection{Correctness of cast representations}
+
 \todo[inline]{JS: say something about the difference between the above
@@
   form.}
-
-\subsubsection{Threesomes}
+\todo[inline]{KC: I rewrote this section. Please check again.}
 
 \citet{Siek:2010:TWB:1706299.1706342} introduce Lazy UD threesomes and
-prove them correct, using a bisimulation between two reduction
-semantics: one is analogous to the \LUDMachine; the other uses Lazy UD
-threesomes and is analogous to the machine in
-Section~\ref{sec:framework}.  \citet{Garcia:2013:CTB:2500365.2500603}
+prove the correctness of Lazy UD threesomes. To use threesomes for
+optimization, they define a translation from their cast calculus
+(the blame calculus) to a runtime language (threesome calculus).
+Then they define a bisimulation relation connecting the blame calculus
+and the threesome calculus and prove a bisimulation between them.
+In contrast, our \CMachine{B} is an interpreter of the cast calculus and 
+compiles casts to cast representations on the fly.
+
+\citet{Garcia:2013:CTB:2500365.2500603}
 introduces several other flavors of threesomes, including a Lazy D
 one. Their threesomes are derived from the corresponding styles of
-coercions in normal form, using correctness-preserving
-transformation. So the correctness of their threesomes relies on the
-correctness of the coercions-in-normal-form-based semantics defined in
-\citet{herman2010space}, which has not been proved correct.
-
-\todo[inline]{JS: again, say something about the difference between
-  the above and what is in this paper.}
-\todo[inline]{KC: [IMPORTANT] will do.}
-
-\subsubsection{Parameterized cast calculi}
-
-\citet{garcia2014deriving} presents a dynamic semantics for the Eager
-D blame strategy, using coercions. They claim that ``the artefacts for
-coercions can be replaced by other artefacts implementing different
-dynamic semantics''.
-
-\todo[inline]{JS: The above is too short of a description of that related
-work.}
+coercions in \citet{herman2010space}, using correctness-preserving
+transformation.
+
+\cite{Siek:2015:BCT:2737924.2737968} proves the correctness
+of \LUD\ coercions in normal form. Their approach is similar to
+that of \citet{Siek:2010:TWB:1706299.1706342}. They defines
+three calculi (i.e. $\lambda B$ (the blame calculus), $\lambda C$, and
+$\lambda S$). $\lambda C$ uses coercions but doesn't normalize coercions
+so is not space-efficient. $\lambda S$ uses coercions in normal form
+and is space-efficient. To establish the correctness of $\lambda S$,
+they prove a bisimulation relating $\lambda B$ to $\lambda C$
+and a bisimulation relating $\lambda C$ to $\lambda S$.
+Inspired by the approaches of \cite{Siek:2010:TWB:1706299.1706342}
+and \cite{Siek:2015:BCT:2737924.2737968}, 
+we also use the bisimulation technique.
 
@@
 \todo[inline]{JS: No, you should still define monadic let.}
+\todo[inline]{KC: will do.}
 
@@
   for all the metafunctions (eval, observe, etc.).}
-\todo[inline]{KC: [IMPORTANT] will do.}
+\todo[inline]{KC: Fixed.}
 %
@@
 
-\fbox{$\mathit{applyCast}_{\BLD}(v,\ccast{S}{l}{T}) = r$}
+\fbox{$\applyCastName_{\BLD}(v,\ccast{S}{l}{T}) = r$}
 \[
@@
 \figequalto{
-	applyCast(v,\ccast{\Tdyn}{l}{\Tdyn})
+\applyCast{v}{\ccast{\Tdyn}{l}{\Tdyn}}
 }{
@@
 \figequalto{
-applyCast(v,\ccast{P}{l}{\Tdyn})
+\applyCast{v}{\ccast{P}{l}{\Tdyn}}
 }{
@@
 \figequalto{
-	applyCast(\vdyn{P}{u},\ccast{\Tdyn}{l}{Q})
-}{
-	applyCast(u,\ccast{P}{l}{Q})
+\applyCast{\vdyn{P}{u}}{\ccast{\Tdyn}{l}{Q}}
+}{
+\applyCast{u}{\ccast{P}{l}{Q}}
 }{}
 \figequalto{
-	applyCast(v,\ccast{P}{l}{Q})
+\applyCast{v}{\ccast{P}{l}{Q}}
 }{
@@
 \figequalto{
-	applyCast(v,\ccast{P}{l}{Q})
+\applyCast{v}{\ccast{P}{l}{Q}}
 }{
@@
 
-\todo[inline]{KC: conditions of blame strategy}
+\todo[inline]{KC: conditions of blame strategy. Jeremy, please }
 \begin{definition}[Blame Strategy, $B$]
 A blame strategy defines a subset of pre-types, written I, that is injectable,
-and a function, written applyCast, that applies cast to values.
+and a function, written \applyCastName, that applies cast to values.
 \end{definition}
@@
 Next, we define the CEK Machine for \LUD. The only differences with
-respect to \LD\ are in the injectable types and in
-${\mathit{applyCast}(v,\ccast{S}{l}{T})}$, in which a cast whose
+respect to \LD\ are in the injectable types and in \applyCast{v}{\ccast{S}{l}{T}},
+in which a cast whose
 source or target is the dynamic type \Tdyn\ is always split into two
@@
 
-	\fbox{$\mathit{applyCast}_{\mathtt{\BLUD}}(v,\ccast{S}{l}{T}) = r$}
+	\fbox{$\applyCastName_{\mathtt{\BLUD}}(v,\ccast{S}{l}{T}) = r$}
 	\[
 	\begin{array}{rclr}
-	\mathit{applyCast}(v, \ccast{\Tdyn}{l}{\Tdyn}) &=& \just{v} \\
-	\mathit{applyCast}(v, \ccast{G}{l}{\Tdyn}) &=&
+	\applyCastName(v, \ccast{\Tdyn}{l}{\Tdyn}) &=& \just{v} \\
+	\applyCastName(v, \ccast{G}{l}{\Tdyn}) &=&
 	\just{\vdyn{G}{v}} \\
-	\mathit{applyCast}(v, \ccast{P}{l}{\Tdyn}) &=&
+	\applyCastName(v, \ccast{P}{l}{\Tdyn}) &=&
 	\just{\vdyn{G}{\proxy{v}{\ccast{P}{l}{G}}}}
@@
 % 	& \text{if } G \sim P, G \neq P \\  
-	\mathit{applyCast}(\vdyn{G}{u}, \ccast{\Tdyn}{l}{H}) &=&          
+	\applyCastName(\vdyn{G}{u}, \ccast{\Tdyn}{l}{H}) &=&          
 	\project{u}{G}{l}{H}\\
-	\mathit{applyCast}(\vdyn{G}{u}, \ccast{\Tdyn}{l}{Q}) &=&
+	\applyCastName(\vdyn{G}{u}, \ccast{\Tdyn}{l}{Q}) &=&
 	\project{u}{G}{l}{H} \mbind \lambda v. \proxy{v}{\ccast{H}{l}{Q}}
@@
 % 	& \text{if } H \sim Q, H \neq Q \\
-	\mathit{applyCast}(v, \ccast{P}{l}{Q}) &=&
+	\applyCastName(v, \ccast{P}{l}{Q}) &=&
 	\just{\proxy{v}{\ccast{P}{l}{Q}}}
 	\\&& \text{if } P \smile Q \\
-	\mathit{applyCast}(v, \ccast{P}{l}{Q}) &=&
+	\applyCastName(v, \ccast{P}{l}{Q}) &=&
 	\error{l}
@@
 Thus non-casted values in \CMachine{B} correspond to \SMachine{C} values
-where casts are identities ($\mathit{id}(T)$). The 
-$\mathit{id}$ functions is provided by the Cast ADT.
+where casts are identities ($\mathrm{id}(T)$). The 
+$\mathrm{id}$ functions is provided by the Cast ADT.
 
@@
 (Definition~\ref{def:LazyUD-CastADT}) specify the behavior 
-of \translate{\ccast{S}{l}{T}}. Readers are encouraged to compare these two
-definitions with the corresponding $\mathrm{applyCast}$ functions 
-(Fig.~\ref{fig:blame-strategy-LazyD} and 
-Fig.~\ref{fig:blame-strategy-LazyUD}).
+of \translate{\ccast{S}{l}{T}}. These two definitions are designed to
+make sure cast application preserves the bisimulation relation that we
+are to defined in the next subsection.
+
+% Readers are encouraged to compare these two
+% definitions with the corresponding $\applyCastName$ functions 
+% (Fig.~\ref{fig:blame-strategy-LazyD} and 
+% Fig.~\ref{fig:blame-strategy-LazyUD}).
+
+The first three cases and the last case of Lazy D Cast ADT correspond
+to the first three cases of the Lazy D \applyCastName\ function
+(Fig.~\ref{fig:blame-strategy-LazyD}).
+The 4-6 cases of Lazy D Cast ADT correspond the proxy case in \applyCastName.
+
 \todo[inline]{JS: what does ``them'' refer to in the previous sentence?
@@
   right?}
-\todo[inline]{KC: [IMPORTANT] will do.}
+\todo[inline]{KC: [Fixed.}
 
@@
 \end{definition}
+
+Similarly, cases 4 and 5 of Lazy UD Cast ADT correspond to the fourth
+case of Lazy UD \applyCastName (Fig.~\ref{fig:blame-strategy-LazyUD}).
+Cases 7-9 correspond to the sixth case of
+Lazy UD \applyCastName.
 
@@
 %manipulate continuations.
-%\begin{lemma}[$\mathit{mkCont}$ Preserves Bisimulation]
+%\begin{lemma}[$\mathrm{mkCont}$ Preserves Bisimulation]
 %	If \bisimK{K}{k}{S}{T} then
@@
 %\end{lemma}
-%\begin{lemma}[$\mathit{extCont}$ Preserves Bisimulation]
+%\begin{lemma}[$\mathrm{extCont}$ Preserves Bisimulation]
 %	If $\bisimc{
@@
 \todo[inline]{JS: Yes, that would be great.}
+\todo[inline]{KC: that is possibly only if we steal some pages from elsewhere.
+The paper limit is 25 (excluding bib) and we have used 30 now.
+https://etaps.org/2021/call-for-papers}
 
@@
 two theorems.}
+\todo[inline]{KC: will do}
 
@@
 
-	\fbox{$\mathit{id}( T ) = c$}
+	\fbox{$\mathrm{id}( T ) = c$}
 	\[
@@
 
-	\fbox{$\mathit{id}_m( P ) = m$}
+	\fbox{$\mathrm{id}_m( P ) = m$}
 	\[
@@
 \figequalto{\mkhead{\gsome{\Tdyn}{l}{P}}{\hche}}{\hchp{P}{l}}{}
-%\mathit{mkProj(}
+%\mathrm{mkProj(}
 %& g
@@
 %& \hchp{P}{l} \\
-%\mathit{mkProj(}
+%\mathrm{mkProj(}
 %& \gsome{\Tdyn}{l}{P}
@@
   LazyD because a reader is more likely to be familiar with Lazy UD.}
+\todo[inline]{KC: will do}
 
@@
 do here. The reason that we introduce the auxiliary functions
-$\mathit{castToDyn}$ and $\mathit{castFromDyn}$, is to ensure that each of them 
+$\mathrm{castToDyn}$ and $\mathrm{castFromDyn}$, is to ensure that each of them 
 is structurally recursive, which makes them straightforward to define in

### 2020-10-09 paper.tex
todo in abstract

@@
 We have successfully applied our new approach of proving the correctness of cast 
-representations to several known cast representations and believe this framework
-is also applicable to other cast representations.
+representations to several known cast representations
+(\cite{Siek:2010:TWB:1706299.1706342,siek2012interpretations,Siek:2015:BCT:2737924.2737968})
+and believe this framework
+is also applicable to other cast representations (\cite{Garcia:2013:CTB:2500365.2500603,siek2012interpretations}).
 \todo[inline]{JS: cite which other cast representations}
-\todo[inline]{KC: will do.}
+\todo[inline]{KC: I am citing \cite{siek2012interpretations} for Lazy D coercions
+in normal form, is this the right paper to cite?}
 We also present a new cast representation, hypercoercions, that is more friendly
@@
 
-\subsection{Dynamics parameterized over cast representations}
-\citet{siek2020mechanized} defines two dynamic semantics for 
-cast calculi parameterized over cast representations. The first
-semantics, namely CC, is \textit{not} space-efficient and
-parameterized over $\mathrm{CastStruct}$. The author instantiates
-CC to obtain the blame calculus ($\lambda B$). 
-The resulting semantics is analogous to our \LUDMachine.
-The other semantics, namely SC, is designed to be space-efficient
-and parameterized over $\mathrm{EfficientCastStruct}$. SC is analogous
-to our \SMachine{C}. These two parameterized semantics give
-users more control over the structure of values. Our \CMachine{B} machine
-insists that the cast on the top of a value must be a function cast
-or a product cast. In contrast, users of their interfaces define
-a predicate on casts called $\mathrm{Inert}$ and any inert cast can
-be a part of a value. Their system doesn't include theorems relating
-space-inefficient cast calculi and space-efficient ones, which
-is one of the major goals of our framework.
-
-\citet{garcia2014deriving} presents a dynamic semantics for the Eager
-D blame strategy, using coercions. They claim that ``the artefacts for
-coercions can be replaced by other artefacts implementing different
-dynamic semantics''.
-
-\todo[inline]{JS: The above is too short of a description of that related
-work.}
-\todo[inline]{KC: I am actually very confused by \citet{garcia2014deriving}.
-They stated that ``Theorems 8.1 and 8.3 can be generalised for other choices
-of dynamic semantics by applying the correspondence described
-through the paper starting with a different set of coercion artefacts.''.
-However they didn't give a generalization and it is unclear to me over what
-their system is parameterized (cast representations? apply-coercion and seq?.}
-
-\subsection{Correctness of cast representations}
-
 \todo[inline]{JS: say something about the difference between the above
@@
 
+\subsection{Dynamics semantics parameterized over cast representations}
+\citet{siek2020mechanized} defines two dynamic semantics for 
+cast calculi parameterized over cast representations. The first
+semantics, namely CC, is \textit{not} space-efficient and
+parameterized over $\mathrm{CastStruct}$. The author instantiates
+CC to obtain the blame calculus ($\lambda B$) in 
+\cite{Siek:2010:TWB:1706299.1706342}. 
+The resulting semantics is analogous to our \LUDMachine.
+The other semantics, namely SC, is designed to be space-efficient
+and parameterized over $\mathrm{EfficientCastStruct}$. SC is analogous
+to our \SMachine{C}. CC and SC give their users more control
+over the structure of values. Our \CMachine{B} machine
+insists that the cast on the top of a value must be a cast between
+compound types (specifically, functions and pairs).
+In contrast, users of their interfaces define
+a predicate on casts called $\mathrm{Inert}$ and any inert cast can
+be a part of a value. Their system doesn't include theorems relating
+space-inefficient cast calculi and space-efficient ones, which
+is one of the major goals of our framework.
+
+\citet{garcia2014deriving} presents a dynamic semantics for the Eager
+D blame strategy, using coercions. They claim that ``the artefacts for
+coercions can be replaced by other artefacts implementing different
+dynamic semantics''.
+
+\todo[inline]{JS: The above is too short of a description of that related
+work.}
+\todo[inline]{KC: I am actually very confused by \citet{garcia2014deriving}.
+They stated that ``Theorems 8.1 and 8.3 can be generalised for other choices
+of dynamic semantics by applying the correspondence described
+through the paper starting with a different set of coercion artefacts.''.
+However they didn't give a generalization and it is unclear to me over what
+their system is parameterized (cast representations? apply-coercion and seq?.}
+
+\subsection{Correctness of cast representations}
+
 \citet{Siek:2010:TWB:1706299.1706342} introduce Lazy UD threesomes and
-prove the correctness of Lazy UD threesomes. To use threesomes for
+prove the correctness of this cast representation. To use threesomes for
 optimization, they define a translation from their cast calculus
 (the blame calculus) to a runtime language (threesome calculus).
-Then they define a bisimulation relation connecting the blame calculus
-and the threesome calculus and prove a bisimulation between them.
+Then they prove a bisimulation between the blame calculus
+and the threesome calculus.
 In contrast, our \CMachine{B} is an interpreter of the cast calculus and 
@@
 that of \citet{Siek:2010:TWB:1706299.1706342}. They defines
-three calculi (i.e. $\lambda B$ (the blame calculus), $\lambda C$, and
-$\lambda S$). $\lambda C$ uses coercions but doesn't normalize coercions
+three calculi (i.e. $\lambda B$ and $\lambda C$ and $\lambda S$). 
+$\lambda B$ is the blame calculus. 
+$\lambda C$ uses coercions but doesn't normalize coercions
 so is not space-efficient. $\lambda S$ uses coercions in normal form
-and is space-efficient. To establish the correctness of $\lambda S$,
+and is space-efficient. To establish the correctness of
+their cast representation,
 they prove a bisimulation relating $\lambda B$ to $\lambda C$

### 2020-10-09 paper.tex
Updates from Overleaf
minor edits

@@
 \newcommand{\mbind}[0]{\ensuremath{\;\gg=\;}}
+\newcommand{\mlet}[3]{\ensuremath{
+\mathtt{let}\ #1\leftarrow#2\ \mathtt{in}\;#3}}
 \newcommand{\mcomp}[0]{\ensuremath{\;>=>\;}}
@@
 \[\text{\urlFrameworkAndIllustration}\]
+\todo[inline]{KC: is this the right place to mention that in Agda
+code we use de Bruijn indexes?}
 
@@
 The syntax \error{l} occurs several times in the syntax definition. We shall 
-view those nonterminals that have an \error{l} case as error monads. We use 
-the symbol \mbind{} as the monad bind operator, which is defined as follows:
+view those nonterminals that have an \error{l} case as error monads.
+That is, they raise an error with the error message $l$.
+The monadic \texttt{let} is defined as follows:
 \[
 \begin{array}{rcll}
-(\error{l}) \mbind f & = & \error{l} \\
-          a \mbind f & = & f(a)      & \text{otherwise}
-\end{array}
-\]
+    (\mlet{x}{(\error{l})}{e}) & = & \error{l} \\
+    (\mlet{x}{a}{e}) & = & [a/x]e & \text{otherwise} \\ 
+\end{array}
+\]
+In Agda code we use the monad bind operator instead.
+% We use 
+% the symbol \mbind{} as the monad bind operator, which is defined as follows:
+% \[
+% \begin{array}{rcll}
+% (\error{l}) \mbind f & = & \error{l} \\
+%           a \mbind f & = & f(a)      & \text{otherwise}
+% \end{array}
+% \]
 \todo[inline]{JS: why not use monadic let instead? That avoids
@@
 \todo[inline]{JS: No, you should still define monadic let.}
-\todo[inline]{KC: will do.}
+\todo[inline]{KC: KC, you need to replace all uses of monad bind to let.}
 
@@
   for all the metafunctions (eval, observe, etc.).}
-\todo[inline]{KC: Fixed.}
+\todo[inline]{KC: Fixed}
 %
@@
 
-\todo[inline]{KC: conditions of blame strategy. Jeremy, please }
 \begin{definition}[Blame Strategy, $B$]

### 2020-10-09 paper.tex
comment

@@
 is also applicable to other cast representations (\cite{Garcia:2013:CTB:2500365.2500603,siek2012interpretations}).
-\todo[inline]{JS: cite which other cast representations}
-\todo[inline]{KC: I am citing \cite{siek2012interpretations} for Lazy D coercions
-in normal form, is this the right paper to cite?}
 We also present a new cast representation, hypercoercions, that is more friendly
@@
 }
+
+\todo[inline]{JS: In the above you've lumped proxy-based and blame
+  tracking together, which is incorrect. AFAIK,
+  \cite{findler2002contracts} is the origin of blame tracking. AFAIK,
+  \citet{Breazu-Tannen:1990vc} is the origin of proxy-based
+  casts. (Who knows, there could be an even earlier paper for
+  proxy-based casts, but that's the earliest one I know.)
+  \citet{herman2010space} cited the wrong paper for function proxies,
+  perhaps because they didn't know about the decade earlier
+  \citet{Breazu-Tannen:1990vc}. Also, \cite{findler2002contracts}
+  should have cited \citet{Breazu-Tannen:1990vc} but did not. Perhaps
+  because they did not consider that papers about ``casts'' to be
+  closely related to their paper about ``contracts''.  Or perhaps they
+  too did not know about \citet{Breazu-Tannen:1990vc}.  Authors make
+  mistakes all the time regarding related work, and this is just yet
+  another example of that. For that matter, I should have cited
+  \citet{Breazu-Tannen:1990vc} in \citet{siek2006gradual} but did not,
+  probably because I had learned about it from the TAPL textbook
+  (section 15.6) and therefore thought it was so standard that it
+  didn't need a citation.  But it would have been better for me to
+  cite it.}
 

### 2020-10-09 paper.tex
comment edits

@@
   \cite{findler2002contracts} is the origin of blame tracking. AFAIK,
-  \citet{Breazu-Tannen:1990vc} is the origin of proxy-based
-  casts. (Who knows, there could be an even earlier paper for
-  proxy-based casts, but that's the earliest one I know.)
-  \citet{herman2010space} cited the wrong paper for function proxies,
-  perhaps because they didn't know about the decade earlier
-  \citet{Breazu-Tannen:1990vc}. Also, \cite{findler2002contracts}
-  should have cited \citet{Breazu-Tannen:1990vc} but did not. Perhaps
-  because they did not consider that papers about ``casts'' to be
-  closely related to their paper about ``contracts''.  Or perhaps they
-  too did not know about \citet{Breazu-Tannen:1990vc}.  Authors make
-  mistakes all the time regarding related work, and this is just yet
-  another example of that. For that matter, I should have cited
+  \citet{Breazu-Tannen:1990vc} is the origin of proxy-based casts.
+  You can read both papers for yourself and be the judge.  BTW, TAPL
+  (section 15.6) cites Breazu-Tannen.  So \citet{herman2010space}
+  cited the wrong paper for function proxies, perhaps because they
+  didn't know about \citet{Breazu-Tannen:1990vc}. Also,
+  \cite{findler2002contracts} should have cited
+  \citet{Breazu-Tannen:1990vc} but did not. Perhaps because they did
+  not consider that papers about ``casts'' to be closely related to
+  their paper about ``contracts''.  Or perhaps they too did not know
+  about \citet{Breazu-Tannen:1990vc}.  Authors make mistakes all the
+  time regarding related work, and this is just yet another example of
+  that. For that matter, I should have cited
   \citet{Breazu-Tannen:1990vc} in \citet{siek2006gradual} but did not,
-  probably because I had learned about it from the TAPL textbook
-  (section 15.6) and therefore thought it was so standard that it
-  didn't need a citation.  But it would have been better for me to
-  cite it.}
+  probably because I had learned about it from TAPL and therefore
+  thought it was so standard that it didn't need a citation.  But it
+  would have been better for me to cite it.}
 

### 2020-10-09 paper.tex
related work

@@
 code we use de Bruijn indexes?}
+\todo[inline]{JS: no, that's too deep into the details for the introduction
+   of a paper that is not about variable representations.}
 
@@
 Actually in my mind \cite{siek2012interpretations} is definitional.}
+\todo[inline]{JS: While I see what you're saying, its important
+  to give precendence to the definition that is earlier in time.}
 
@@
 
-\todo[inline]{JS: say something about the difference between the above
-  and what is in this paper. That's the whole point of the related
-  work section from the eyes of the reviewer.}
-\todo[inline]{KC: I might have some misconcept about the related work section.
-You might have felt this, haha. Now I think this section is targeting the
-following scenarios: 
-- ``I think someone has solved this problem ...''
-- ``This work looks similar to paper X, what is the difference?''
-- ``Is this work inspired by paper X?''
-Is my understanding correct?}
-\todo[inline]{JS: yes, and make sure to
-  give very explicit answers to these questions. It should feel to you
-  like you're hitting the reader over the head with the most obvious
-  things (to you). The above paragraph is currently insufficient
-  because it doesn't emphasize what scientific constributions are new
-  to our paper compared to those prior papers on coercions in normal
-  form.}
-\todo[inline]{KC: I rewrote this section. Please check again.}
+\todo[inline]{JS: add a sentence that summarizes this section,
+  mentioning the topics of the two subsections.}
 
 \subsection{Dynamics semantics parameterized over cast representations}
-\citet{siek2020mechanized} defines two dynamic semantics for 
-cast calculi parameterized over cast representations. The first
-semantics, namely CC, is \textit{not} space-efficient and
-parameterized over $\mathrm{CastStruct}$. The author instantiates
-CC to obtain the blame calculus ($\lambda B$) in 
-\cite{Siek:2010:TWB:1706299.1706342}. 
-The resulting semantics is analogous to our \LUDMachine.
-The other semantics, namely SC, is designed to be space-efficient
-and parameterized over $\mathrm{EfficientCastStruct}$. SC is analogous
-to our \SMachine{C}. CC and SC give their users more control
-over the structure of values. Our \CMachine{B} machine
-insists that the cast on the top of a value must be a cast between
-compound types (specifically, functions and pairs).
-In contrast, users of their interfaces define
-a predicate on casts called $\mathrm{Inert}$ and any inert cast can
-be a part of a value. Their system doesn't include theorems relating
-space-inefficient cast calculi and space-efficient ones, which
-is one of the major goals of our framework.
+
+\citet{siek2020mechanized} defines two reduction semantics for cast
+calculi parameterized over cast representations. The first semantics,
+namely CC, is not space-efficient and is parameterized over
+$\mathrm{CastStruct}$.  The reduction semantics for CC is analogous to
+our \LUDMachine.  The second semantics, namely SC, is designed to be
+space-efficient and parameterized over
+$\mathrm{EfficientCastStruct}$. SC is analogous to our \SMachine{C}.
+\citet{siek2020mechanized} does not prove the correctness of SC with
+respect to CC, whereas the main goal of the present paper is proving
+the correctness of \SMachine{C} with respect to \LUDMachine.
+
+%% The following details are less important. -Jeremy
+%% CC and SC give their users more control over the structure of
+%% values. Our \CMachine{B} machine insists that the cast on the top of a
+%% value must be a cast between compound types (specifically, functions
+%% and pairs).  In contrast, users of their interfaces define a predicate
+%% on casts called $\mathrm{Inert}$ and any inert cast can be a part of a
+%% value.
 
@@
 their system is parameterized (cast representations? apply-coercion and seq?.}
+\todo[inline]{JS: your comment above says what you should say
+  (except the part about your confusion). Say it in a matter-of-fact
+way, and not a derogitory way.}
 
@@
 one. Their threesomes are derived from the corresponding styles of
-coercions in \citet{herman2010space}, using correctness-preserving
+coercions in \citet{herman2010space}, using a correctness-preserving
 transformation.
@@
 we also use the bisimulation technique.
+\todo[inline]{JS: there is a least one interesting difference regarding
+  the bisimulation: your lemma 3 has an ``upto reduction'' flavor to it
+  which makes your $\approx$ relation simpler. }
 

### 2020-10-09 paper.tex
more comments

@@
 \newcommand{\just}[1]{\ensuremath{#1}}
-\newcommand{\error}[1]{\ensuremath{\Uparrow#1}}
+\newcommand{\error}[1]{\ensuremath{\mathop{\Uparrow}#1}}
 
@@
 \begin{array}{rcll}
-    (\mlet{x}{(\error{l})}{e}) & = & \error{l} \\
-    (\mlet{x}{a}{e}) & = & [a/x]e & \text{otherwise} \\ 
-\end{array}
-\]
-In Agda code we use the monad bind operator instead.
+  (\mlet{x}{r}{e}) & = &
+  \begin{cases}
+    \error{l} & \text{if } r = \error{l} \\
+    [r/x]e & \text{otherwise}
+  \end{cases}
+    %% (\mlet{x}{(\error{l})}{e}) & = & \error{l} \\
+    %% (\mlet{x}{a}{e}) & = & [a/x]e & \text{otherwise} \\ 
+\end{array}
+\]
+In the Agda code we use the monad bind operator instead.
 % We use 
@@
 % \]
-\todo[inline]{JS: why not use monadic let instead? That avoids
-  the need to also use meta-lambdas, which you would need to
-  explain, e.g., in the transition rule that uses applyCast.}
-\todo[inline]{KC: 1. I will try to switch to monadic let. As you pointed out
-when we wrote the WGT paper, let is more friendly to readers who are not familiar
-with monads.
-2. Do you imply that monadic let doesn't need to be explained?
-}
-\todo[inline]{JS: No, you should still define monadic let.}
 \todo[inline]{KC: KC, you need to replace all uses of monad bind to let.}
@@
 Fig.~\ref{fig:blame-strategy-LazyUD}).
-\todo[inline]{JS: be consistent with the font used for applyCast. Sometimes
-  you use roman and sometimes you used italic. Also, be consistent
-  for all the metafunctions (eval, observe, etc.).}
-\todo[inline]{KC: Fixed}
 %
@@
 
-\todo[inline]{JS: what does ``them'' refer to in the previous sentence?
-  Please replace with a specific noun. Also, why should the reader do
-  the comparison? What are they suppose to notice?}
-\todo[inline]{JS: say where the following equations come from.
-  They are the equations you needed for the proof of equivalence,
-  right?}
-\todo[inline]{KC: [Fixed.}
-
 \begin{definition}[Lazy D Cast ADT]
@@
 				(\compose{d}{\translate{\ccast{T_1}{l}{T_2}}})}}$
-		\item $\denote{\translate{\ccast{P}{l}{Q}}}(v) = \error{l}$\\
+		\item $\denote{\translate{\ccast{P}{l}{Q}}}(v) = \error{l}$ \qquad
 			if $\notshallowlyconsistent{P}{Q}$
@@
 	\item $\denote{\translate{\ccast{\Tdyn}{l}{G}}}(\vdyn{G}{u}) = u$
-	\item $\denote{\translate{\ccast{\Tdyn}{l}{H}}}(\vdyn{G}{u}) = \error{l}$\\
+	\item $\denote{\translate{\ccast{\Tdyn}{l}{H}}}(\vdyn{G}{u}) = \error{l}$ \qquad
 		if $G \neq H$
@@
 				(\compose{d}{\translate{\ccast{T_1}{l}{T_2}}})}}$
-		\item $\denote{\translate{\ccast{P}{l}{Q}}}(v) = \error{l}$\\
+		\item $\denote{\translate{\ccast{P}{l}{Q}}}(v) = \error{l}$\qquad
 			if $\notshallowlyconsistent{P}{Q}$
@@
 
-\todo[inline]{KC: (About the following paragraph) Should we mention KC and Deyaa as citation?
-  (something like in private communication with KC and Deyaa)}
-\todo[inline]{JS: Yes}
-\todo[inline]{KC: Could you show me how to do this? I don't know exactly
-how to write this kind of citations.}
-
 The \compose{c}{c} operator is the key to compressing coercions and
@@
 considerable difficulty in the termination proof of the composition
-for \LD\ Coercions in Normal Form, reported by Kuang-Chen Lu and
-Deyaaeldeen Almahallawi. So it is useful to relax this restriction for
-the \LD\ tracking strategy.
+for \LD\ Coercions in Normal Form~\citep{almahallawi19}. So it is
+useful to relax this restriction for the \LD\ tracking strategy.
 %
@@
   any suggestion from Jeremy?}
+\todo[inline]{JS: how about $\sim$}
 

### 2020-10-10 paper.tex
Updates from Overleaf

@@
 
+\todo[inline]{KC: I feel ``going through a bisimulation proof'' is too specific.
+There should be other ways to prove equivalence of two dynamic semantics.
+How does Jeremy think?}
+
 % The abstract should briefly summarize the contents of the paper in
@@
 
-\todo[inline]{KC: Cite "Contracts for higher-order functions" for the proxy-based approach maybe?}
-\todo[inline]{JS: That paper doesn't exactly fit into what you're talking about in the above
-sentence. It might be appopriate to cite it elsewhere in the paper. Also,
-there are earlier papers about coercive subtyping (Computing with coercions by Breazu-Tannen et al)
-that use a proxy-based approach. The contracts paper may be the first to propose blame tracking.}
-\todo[inline]{KC: How about citing the origin of the proxy-based approach when we talk
-about the CPSed even-odd example?
-I am confused about which paper to cite. \cite{herman2010space} seems to be citing
-\cite{findler2002contracts} for the proxy-based approach of casting function.
-Here is the relevant sentences from \cite{herman2010space}:
-``In general, it is not possible to check if an untyped function satisfies a
-particular static type. A natural solution is to wrap the function in a proxy that, whenever
-it is applied, casts its argument and result values appropriately, ensuring that the function
-is only observed with its expected type. This proxy-based approach was formalized by Findler
-and Felleisen [15] ...''
-I am \textit{not} trying to say I don't believe in your statements about the origins of
-the proxy-based approach and blame tracking in functions.
-I want to know whether \citet{herman2010space} is citing the right paper.
-Maybe both papers came up independently with a similar idea but \cite{findler2002contracts}
-is more related to our work.
-}
-
-\todo[inline]{JS: In the above you've lumped proxy-based and blame
-  tracking together, which is incorrect. AFAIK,
-  \cite{findler2002contracts} is the origin of blame tracking. AFAIK,
-  \citet{Breazu-Tannen:1990vc} is the origin of proxy-based casts.
-  You can read both papers for yourself and be the judge.  BTW, TAPL
-  (section 15.6) cites Breazu-Tannen.  So \citet{herman2010space}
-  cited the wrong paper for function proxies, perhaps because they
-  didn't know about \citet{Breazu-Tannen:1990vc}. Also,
-  \cite{findler2002contracts} should have cited
-  \citet{Breazu-Tannen:1990vc} but did not. Perhaps because they did
-  not consider that papers about ``casts'' to be closely related to
-  their paper about ``contracts''.  Or perhaps they too did not know
-  about \citet{Breazu-Tannen:1990vc}.  Authors make mistakes all the
-  time regarding related work, and this is just yet another example of
-  that. For that matter, I should have cited
-  \citet{Breazu-Tannen:1990vc} in \citet{siek2006gradual} but did not,
-  probably because I had learned about it from TAPL and therefore
-  thought it was so standard that it didn't need a citation.  But it
-  would have been better for me to cite it.}
+% \todo[inline]{KC: Cite "Contracts for higher-order functions" for the proxy-based approach maybe?}
+% \todo[inline]{JS: That paper doesn't exactly fit into what you're talking about in the above
+% sentence. It might be appopriate to cite it elsewhere in the paper. Also,
+% there are earlier papers about coercive subtyping (Computing with coercions by Breazu-Tannen et al)
+% that use a proxy-based approach. The contracts paper may be the first to propose blame tracking.}
+% \todo[inline]{KC: How about citing the origin of the proxy-based approach when we talk
+% about the CPSed even-odd example?
+% I am confused about which paper to cite. \cite{herman2010space} seems to be citing
+% \cite{findler2002contracts} for the proxy-based approach of casting function.
+% Here is the relevant sentences from \cite{herman2010space}:
+% ``In general, it is not possible to check if an untyped function satisfies a
+% particular static type. A natural solution is to wrap the function in a proxy that, whenever
+% it is applied, casts its argument and result values appropriately, ensuring that the function
+% is only observed with its expected type. This proxy-based approach was formalized by Findler
+% and Felleisen [15] ...''
+% I am \textit{not} trying to say I don't believe in your statements about the origins of
+% the proxy-based approach and blame tracking in functions.
+% I want to know whether \citet{herman2010space} is citing the right paper.
+% Maybe both papers came up independently with a similar idea but \cite{findler2002contracts}
+% is more related to our work.
+% }
+
+% \todo[inline]{JS: In the above you've lumped proxy-based and blame
+%   tracking together, which is incorrect. AFAIK,
+%   \cite{findler2002contracts} is the origin of blame tracking. AFAIK,
+%   \citet{Breazu-Tannen:1990vc} is the origin of proxy-based casts.
+%   You can read both papers for yourself and be the judge.  BTW, TAPL
+%   (section 15.6) cites Breazu-Tannen.  So \citet{herman2010space}
+%   cited the wrong paper for function proxies, perhaps because they
+%   didn't know about \citet{Breazu-Tannen:1990vc}. Also,
+%   \cite{findler2002contracts} should have cited
+%   \citet{Breazu-Tannen:1990vc} but did not. Perhaps because they did
+%   not consider that papers about ``casts'' to be closely related to
+%   their paper about ``contracts''.  Or perhaps they too did not know
+%   about \citet{Breazu-Tannen:1990vc}.  Authors make mistakes all the
+%   time regarding related work, and this is just yet another example of
+%   that. For that matter, I should have cited
+%   \citet{Breazu-Tannen:1990vc} in \citet{siek2006gradual} but did not,
+%   probably because I had learned about it from TAPL and therefore
+%   thought it was so standard that it didn't need a citation.  But it
+%   would have been better for me to cite it.}
 
@@
 strategies are incompatible with $\eta$-equivalence of functions.
-
-\todo[inline]{KC: This paragraph suggests that
-\cite{siek2009exploring} gives the definitional semantics.
-\cite{siek2009exploring}'s is coercion-based.
-It makes more sense to me to use a type-based semantics as the definition.
-Actually in my mind \cite{siek2012interpretations} is definitional.}
-\todo[inline]{JS: While I see what you're saying, its important
-  to give precendence to the definition that is earlier in time.}
 
@@
 	\begin{array}{rclr}
-	\figequalto{id(\star)}{
+	\figequalto{\id{\star}}{
 		\hcci
 	}{}
-	\figequalto{id(P)}{
-		\hccc{\hche}{id(P)}{\hcte}
+	\figequalto{\id{P}}{
+		\hccc{\hche}{\id{P}}{\hcte}
 	}{}
@@
 	\begin{array}{rclr}
-	\figequalto{id(\Pbool)}{\hcmbool}{}
-	\figequalto{id(\Pfunc{S}{T})}{
-		\hcmfunc{id(S)}{id(T)}
-	}{}
-	\figequalto{id(\Pprod{S}{T})}{
-		\hcmprod{id(S)}{id(T)}
+	\figequalto{\id{\Pbool}}{\hcmbool}{}
+	\figequalto{\id{\Pfunc{S}{T}}}{
+		\hcmfunc{\id{S}}{\id{T}}
+	}{}
+	\figequalto{\id{\Pprod{S}{T}}}{
+		\hcmprod{\id{S}}{\id{T}}
 	}{}

### 2020-10-11 paper.tex
get most todos done

--- 2020-10-09 paper.tex
@@
 \newcommand{\evaltoS}[3]{\ensuremath{\mathrm{eval}_{\SMachine{#1}}(#2)=#3}}
-\newcommand{\compatibletailhead}[2]{\ensuremath{#1\;R\;#2}}
+\newcommand{\compatibletailhead}[2]{\ensuremath{#1\sim#2}}
 \newcommand{\goodgap}[1]{\ensuremath{\mathrm{good}(#1)}}
@@
 }
-
 \todo[inline]{JS: In the above you've lumped proxy-based and blame
@@
 
+\todo[inline]{KC: in the next paragraph I cite \cite{breazu1991inheritance}}
 Continuations are not the only place where casts can accumulate.
@@
 \lstinline|Bool| so there is no implicit cast in tail position.
-However, the argument \lstinline|k| is wrapped in a cast in each
+% However, the argument \lstinline|k| is wrapped in a cast in each
+% recursive call because the type of \lstinline|k| is less precise in
+% \lstinline|even?| than it is in \lstinline|odd?|.
+However, the argument \lstinline|k| is casted in each
 recursive call because the type of \lstinline|k| is less precise in
 \lstinline|even?| than it is in \lstinline|odd?|. 
+Every time a function is casted we record a pieces of
+cast information for the input and another piece for
+the output, following the approach in \cite{breazu1991inheritance}
+and \cite{Breazu-Tannen:1990vc},
+so the space complexity is again linear.
 \begin{lstlisting}
@@
 \end{lstlisting}
-These example programs are adapted from those of Herman et al.~\citep{herman2010space}.
+These example programs are adapted from those of \cite{herman2010space}.
 We direct readers to their work for more examples and a detailed explanation.
@@
 \[\text{\urlFrameworkAndIllustration}\]
-\todo[inline]{KC: is this the right place to mention that in Agda
-code we use de Bruijn indexes?}
-\todo[inline]{JS: no, that's too deep into the details for the introduction
-   of a paper that is not about variable representations.}
 
@@
 
-\todo[inline]{KC: This paragraph suggests that
-\cite{siek2009exploring} gives the definitional semantics.
-\cite{siek2009exploring}'s is coercion-based.
-It makes more sense to me to use a type-based semantics as the definition.
-Actually in my mind \cite{siek2012interpretations} is definitional.}
-\todo[inline]{JS: While I see what you're saying, its important
-  to give precendence to the definition that is earlier in time.}
-
 To summarize, the primary contributions of this paper are:
@@
   mentioning the topics of the two subsections.}
+\todo[inline]{KC: fixed. I want to move this section to the end
+of the paper, how do you think?}
+
+In this section we review publications that contribute dynamic semantics
+applicable to a variety of cast representations
+(Subsection~\ref{subsec:parameterized-dynamics}),
+proofs of correctness of cast representations
+(Subsection~\ref{subsec:related-work-other-proofs}),
+and relationship between hypercoercions and other cast representations
+(Subsection~\ref{subsec:related-work-other-cast-reprs}).
 
 \subsection{Dynamics semantics parameterized over cast representations}
-
-\citet{siek2020mechanized} defines two reduction semantics for cast
-calculi parameterized over cast representations. The first semantics,
-namely CC, is not space-efficient and is parameterized over
-$\mathrm{CastStruct}$.  The reduction semantics for CC is analogous to
-our \LUDMachine.  The second semantics, namely SC, is designed to be
-space-efficient and parameterized over
-$\mathrm{EfficientCastStruct}$. SC is analogous to our \SMachine{C}.
-\citet{siek2020mechanized} does not prove the correctness of SC with
-respect to CC, whereas the main goal of the present paper is proving
-the correctness of \SMachine{C} with respect to \LUDMachine.
-
-%% The following details are less important. -Jeremy
-%% CC and SC give their users more control over the structure of
-%% values. Our \CMachine{B} machine insists that the cast on the top of a
-%% value must be a cast between compound types (specifically, functions
-%% and pairs).  In contrast, users of their interfaces define a predicate
-%% on casts called $\mathrm{Inert}$ and any inert cast can be a part of a
-%% value.
-
-\citet{garcia2014deriving} presents a dynamic semantics for the Eager
-D blame strategy, using coercions. They claim that ``the artefacts for
-coercions can be replaced by other artefacts implementing different
-dynamic semantics''.
+\label{subsec:parameterized-dynamics}
+
+\todo[inline]{KC: how can I forget the interpretation paper!}
+\cite{siek2012interpretations} presents a definitional interpreter
+and a variant of the ECD abstract machine \citep{siek2012ECD}.
+Both systems are parameterized over 4 flavors of coercions in normal
+forms: Lazy UD, Lazy D, Eager UD, Eager D.
+
+\citet{garcia2014deriving} proves the definitional interpreter
+in \cite{siek2012interpretations}
+is equivalent to the ECD machine in the same paper,
+which was left as a conjecture. 
+They claim that their system ``can be generalised for other choices
+of dynamic semantics by applying the correspondence described 
+through the paper starting with a different set of coercion artefacts.''.
+It is unclear to us whether their system is just applicable
+to other flavor of coercions or also to other cast representations.
 
@@
 way, and not a derogitory way.}
+\todo[inline]{KC: updated.}
+
+\citet{siek2020mechanized} defines two reduction semantics for cast
+calculi parameterized over cast representations. The first semantics,
+namely CC, is not space-efficient and is parameterized over
+$\mathrm{CastStruct}$.  The reduction semantics for CC is analogous to
+our \LUDMachine.  The second semantics, namely SC, is designed to be
+space-efficient and parameterized over
+$\mathrm{EfficientCastStruct}$. SC is analogous to our \SMachine{C}.
+\citet{siek2020mechanized} does not prove the correctness of SC with
+respect to CC, whereas the main goal of the present paper is proving
+the correctness of \SMachine{C} with respect to \LUDMachine.
+
+%% The following details are less important. -Jeremy
+%% CC and SC give their users more control over the structure of
+%% values. Our \CMachine{B} machine insists that the cast on the top of a
+%% value must be a cast between compound types (specifically, functions
+%% and pairs).  In contrast, users of their interfaces define a predicate
+%% on casts called $\mathrm{Inert}$ and any inert cast can be a part of a
+%% value.
 
 \subsection{Correctness of cast representations}
+\label{subsec:related-work-other-proofs}
 
@@
 and a bisimulation relating $\lambda C$ to $\lambda S$.
+
 Inspired by the approaches of \cite{Siek:2010:TWB:1706299.1706342}
 and \cite{Siek:2015:BCT:2737924.2737968}, 
-we also use the bisimulation technique.
+we also use the bisimulation technique. But our bisimulation have an
+important difference. Our bisimulation relation, unlike theirs, does
+not cover all possible states in the reduction. Instead, we ask both 
+sides of the bisimulation to reduce several steps before recovering
+the bisimulation relation (compare our Lemma~\ref{lem:weak-bisimulation}
+with Lemma~8 in \cite{Siek:2010:TWB:1706299.1706342}
+and Proposition~16 in \cite{Siek:2015:BCT:2737924.2737968}).
+This decision simplifies the bisimulation relation (Fig.~\ref{fig:bisim-SC-D})
+(compared to Figure~6 in \cite{Siek:2010:TWB:1706299.1706342} and
+Figure~6 in \cite{Siek:2015:BCT:2737924.2737968}).
+In particular, the function application case is a congruence
+(hence not shown in the figure) in our bisimulation relation
+but requires special rules in theirs.
+
 \todo[inline]{JS: there is a least one interesting difference regarding
@@
   which makes your $\approx$ relation simpler. }
+\todo[inline]{KC: updated.}
+
+\subsection{Other Cast Representations}
+\label{subsec:related-work-other-cast-reprs}
+
+Hypercoercions is inspired by coercions in normal form and supercoercions
+and ends up having a symmetrical definition similar to threesomes.
 
@@
 \paragraph{Syntax and Static Semantics}
+
+\todo[inline]{KC: is this the right place to mention that in Agda
+code we use de Bruijn indexes?}
 
@@
   smallest congruence relation containing the shown rules. Everything
-  to the left of $\approx$ is in \CBMachine{} and everything to the
+  to the left of $\approx$ is in \CMachine{B} and everything to the
   right is in \SMachine{C}.}
@@
 
-% \begin{lemma}[Lazy D Weak Bisimulation between \LDMachine\ and \SMachine{C}]
-% 	\label{lem:weak-bisim-SC-D}
-% 	Assume $C$ implements Lazy D Cast ADT
-% 	and $s_1$ is a state in \LDMachine\
-% 	and $s_1'$ is a state in \SMachine{C}
-% 	and $\bisims{s_1}{s_1'}{T}$
-% 	then either
-% \begin{enumerate}
-% \item $s_1  = \error{l}$
-%   and $s_1' = \error{l}$
-%   for some $l$, or
-% \item $s_1 = \shalt{v}$
-%   and $s_1' = \shalt{v'}$
-%   and $\bisimv{v}{v'}{T}$
-%   for some $v$ and $v'$, or
-% \item $\reduceto{s_1}{^{+}s_2}$
-%   and $\reduceto{s_1'}{^{+}s_2'}$
-%   and $\bisims{s_2}{s_2'}{T}$
-% \end{enumerate}
-% \end{lemma}
-% %\begin{proof}
-% %We proceed by case analysis on $\bisims{s_1}{s_1'}{T}$. 
-% %\begin{description}
-% %\item[Case $\inference{
-% %}{
-% %	\bisims{\error{l}}{\error{l}}{T}
-% %}$]
-% %This is case (1).
-% %\item[Case $\inference{
-% %	\bisimv{v}{v'}{T}
-% %}{
-% %	\bisims{\shalt{v}}{\shalt{v'}}{T}
-% %}$]
-% %This is case (2).
-% %\item[Case $\inference{
-% %	\expressiontyping{\Gamma}{e}{T} \\
-% %	\bisimE{\Gamma}{E}{E'} \\
-% %	K \approx K' : T
-% %}{
-% %	\bisims{\sexpr{e}{E}{K}}{\sexpr{e}{E'}{K'}}{T}
-% %}$]
-% %This is case (3). By case analysis on $e$.
-% %\item[Case $\inference{
-% %	\bisimv{v}{v'}{S} \\
-% %	\bisimK{K}{K'}{S}{T}
-% %}{
-% %	\bisims{\scont{v}{K}}{\scont{v'}{K'}}{T}
-% %}$]
-% %This is case (3). By inversion on $\bisimK{K}{K'}{S}{T}$, we have
-% %\[
-% %\begin{array}{rcl}
-% %K  & = &
-% %\Kcons{
-% %	\Fcast{\ccast{S_1}{l_1}{S_2}}
-% %}{\ldots\Kcons{\Fcast{\ccast{S_{n-1}}{l_{n-1}}{S}}}{K_1}} \\
-% %K' & = &
-% %\Kcons{\Fcast{c'}}{k_1'}
-% %\end{array}
-% %\]
-% %After zero or more transition steps, $\scont{v}{K}$ will either transition to 
-% %$\scont{u}{K_1}$ for some $u$ or transition to $\error{l}$ for some $l$ if one 
-% %of the cast fail. On the \SMachine{C} side, $\scont{v'}{K'}$ will either 
-% %transition to $\applyCont{u'}{k_1'}$ for some $u'$ or transition to 
-% %$\error{l'}$ for some $l'$ if the cast fail. Because the sequence of casts in 
-% %$K$ bisimulates the cast in $K'$, we can show with  
-% %Lemma~\ref{lem:LazyD-apply-cast-preserve-bisim} that either
-% %\begin{itemize}
-% %	\item all casts succeed and	$\bisimv{u}{u'}{S}$, or
-% %	\item both machines transition to error state and $l = l'$
-% %\end{itemize}
-% %When all casts succeeded, we also have $\bisimK{K_1}{k_1'}{S}{T}$ and need to 
-% %show that $\reduceto{\scont{u}{K_1}}{s_2}$ and $\applyCont{u'}{k_1'} = s_2'$ 
-% %and $\bisims{s_2}{s_2'}{T}$ for some $s_2$ and $s_2'$.
-% %%
-% %We proceed by case analysis on $K$. The most interesting cases 
-% %are function application and pair projection. Due to space limitation, 
-% %we only illustrate the general idea with function applications
-% %
-% %\begin{description}
-% %\item[Subcase $\infr{
-% %	\bisimv{v_1}{v_1'}{\Pfunc{S}{T_1}} \qquad
-% %	\bisimK{K_2}{K_2'}{T_1}{T}
-% %}{
-% %	\bisimK{
-% %		\Kcons{\FappOX{v_1}}{K_2}
-% %	}{
-% %		\Kcons{\FappOX{v_1'}}{K_2'}
-% %	}{S}{T}
-% %}$] By inversion on $\bisimv{v_1}{v_1'}{\Pfunc{S}{T_1}}$ we know the proxies 
-% %in $v_1$ bisimulate the proxies in $v_1'$. After a reasoning similar to the 
-% %above one that we used to reason about casts in continuations, we know that 
-% %either both machines will transition to error states if the input proxies fail 
-% %in casting the argument, or both machines will transition to a state 
-% %evaluation 
-% %the function body.
-% %\todo{need to elaborate this part, or just delete it.}
-% %\end{description}
-% %\end{description}
-% %\end{proof}
-
-% \begin{lemma}[Lazy UD Weak Bisimulation between \LUDMachine\ and \SMachine{C}]
-% 	\label{lem:weak-bisim-SC-UD}
-% 	Assume $C$ implements Lazy UD Cast ADT
-% 	and $\bisims{s_1}{s_1'}{T}$
-% 	then either
-% 	\begin{enumerate}
-% 		\item $s_1  = \error{l}$
-% 		and $s_1' = \error{l}$
-% 		for some $l$, or
-% 		\item $s_1 = \shalt{v}$
-% 		and $s_1' = \shalt{v'}$
-% 		and $\bisimv{v}{v'}{T}$
-% 		for some $v$ and $v'$, or
-% 		\item $\reduceto{s_1}{^{+}s_2}$
-% 		and $\reduceto{s_1'}{^{+}s_2'}$
-% 		and $\bisims{s_2}{s_2'}{T}$
-% 	\end{enumerate}
-% \end{lemma}
-% \begin{proof}
-% 	Similar to Lemma~\ref{lem:weak-bisim-SC-D}.
-% \end{proof}
-
 \todo[inline]{JS: There should be some text regarding the following
 two theorems.}
-\todo[inline]{KC: will do}
+\todo[inline]{KC: Fixed.}
+
+Lemma~\ref{lem:weak-bisimulation} implies that if a \CMachine{B} state $s_1$ transitions to a 
+final state $s_2$ and \bisims{s_1}{s'_1}{T}, the state $s_1'$
+will transition to a final state $s_2'$ that holds the same observable as $s_1'$. 
+Instantiating Lemma~\ref{lem:weak-bisimulation} with Lazy D and Lazy UD blame strategy leads
+to the next two theorems.
 
@@
 \end{theorem}
-% \begin{proof}
-% 	By the definitions of $\textit{eval}$, we need to show 
-% 	\[
-% 	\transitivelyreducetoM{\CMachine{B}}{\sexpr{e}{\emptyset}{\Knil}}{
-% 		s
-% 	}
-% 	\;\text{if and only if}\;
-% 	\transitivelyreducetoM{\SMachine{C}}{\sexpr{e}{\emptyset}{\mkCont{\Knil}}}{
-% 		s'
-% 	}
-% 	\]
-% 	where $s$ and $s'$ are bisimuated final states, i.e. of the form 
-% 	$\shalt{v}$ or $\error{l}$. The initial states are related by the 
-% 	bisimulation relation, so we can prove this theorem with 
-% 	Lemma~\ref{lem:weak-bisim-SC-D}.
-% \end{proof}
 
@@
 \end{theorem}
-% \begin{proof}
-% 	Similar to Theorem~\ref{thm:SD-equiv}.
-% \end{proof}
 
@@
 
-Subsection~\ref{sec:LazyD-Hypercoercions} implements the \CastADT{}
-with the \LD{} hypercoercions and proves that \LD{} hypercoercions is
-a Lazy D Cast ADT.  Subsection~\ref{sec:LazyUD-Hypercoercions} does
-the same for \LUD{}.  Finally, we argue in
+Subsection~\ref{sec:LazyUD-Hypercoercions} implements the \CastADT{}
+with the \LUD{} hypercoercions and proves that \LUD{} hypercoercions is
+a Lazy UD Cast ADT.  Subsection~\ref{sec:LazyUD-Hypercoercions} does
+the same for \LD{}.  Finally, we argue in
 Subsection~\ref{sec:hypercoercions-compact} that hypercoercions
@@
 
-\subsection{\LD\ Hypercoercions}
-\label{sec:LazyD-Hypercoercions}
-
-\begin{figure}[tp] %% composition 1
-\[
-\begin{array}{lrcl}
-\stxrule{g}{Gaps}{
-	\gnone           \mid
-	\gsome{S}{l}{T}
-}
-\end{array}
-\]
-
-\fbox{$\compose{c}{c} = c$} Composition of \LD\ hypercoercions
-\[
-\begin{array}{rclr}
-\figequalto{\compose{c_1}{c_2}}{\composegap{c_1}{\gnone}{c_2}}{}
-\end{array}
-\]
-
-\fbox{$\composegap{c}{g}{c} = c$}
-\[
-\begin{array}{rcll}
-\figequalto{\composegap{\hcci}{g}{\hcci}}{\hcci}{}
-\figequalto{\composegap{\hcci}{g}{\hccc{h}{m}{t}}}{
-	\hccc{\mkhead{g}{h}}{m}{t}
-}{}
-\figequalto{\composegap{\hccc{h}{m}{t}}{g}{\hcci}}{
-	\hccc{h}{m}{\mktail{t}{g}}
-}{}
-\figequalto{\composegap{\hccc{h_1}{m_1}{t_1}}{g}{\hccc{h_2}{m_2}{t_2}}}{
-	\hccc{h_1}{(\composegap{m_1}{\mkgap{t_1}{g}{h_2}}{m_2})}{t_2}
-}{}
-\end{array}
-\]
-
-\fbox{\mkhead{g}{h}}
-\[
-\begin{array}{rclr}
-\figequalto{\mkhead{g}{\hchp{P}{l}}}{\hchp{P}{l}}{}
-\figequalto{\mkhead{\gsome{\Tdyn}{l}{P}}{\hche}}{\hchp{P}{l}}{}
-%\mathrm{mkProj(}
-%& g
-%& ,
-%& \hchp{P}{l}
-%& )=
-%& \hchp{P}{l} \\
-%\mathrm{mkProj(}
-%& \gsome{\Tdyn}{l}{P}
-%& ,
-%& \hche
-%& )=
-%& \hchp{P}{l}
-\end{array}
-\]
-%\[
-%\begin{array}{rcll}
-%\figequalto{\mkhead{g}{\hchp{P}{l}}}{\hchp{P}{l}}{}
-%\figequalto{\mkhead{\gsome{\Tdyn}{l}{P}}{\hche}}{\hchp{P}{l}}{}
-%\end{array}
-%\]
-
-\fbox{\mktail{t}{g}}
-\[
-\begin{array}{rcll}
-\figequalto{\mktail{\hcti{P}}{g}}{\hcti{P}}{}
-\figequalto{\mktail{\hcte}{\gsome{P}{l}{\Tdyn}}}{\hcti{P}}{}
-\end{array}
-\]
-
-\fbox{\mkgap{t}{g}{h}}
-\[
-\begin{array}{rcll}
-\figequalto{\mkgap{\hcte}{g}{\hche}}{g}{}
-\figequalto{\mkgap{\hcte}{\gsome{P}{l'}{\Tdyn}}{\hchp{Q}{l}}}{
-	\gsome{P}{l}{Q}
-}{}
-\figequalto{\mkgap{\hcti{P}}{g}{\hchp{Q}{l}}}{
-	\gsome{P}{l}{Q}
-}{}
-\figequalto{\mkgap{\hcti{P}}{\gsome{\Tdyn}{l}{Q}}{\hche}}{
-	\gsome{P}{l}{Q}
-}{}
-\end{array}
-\]
-
-\fbox{$\composegap{m}{g}{m} = m$}
-\[ 
-\begin{array}{rclr}
-\figequalto{\composegap{\hcmfail{l}}{g}{m_2}}{
-	\hcmfail{l}
-}{}
-\figequalto{\composegap{m_1}{\gsome{P}{l}{Q}}{m_2}}{
-	\hcmfail{l}
-}{\\&&\sidecond{
-		\notshallowlyconsistent{P}{Q}
-		\text{ and } \forall l. m_1 \neq \hcmfail{l}
-}}
-\figequalto{\composegap{m_1}{g}{\hcmfail{l}}}{
-	\hcmfail{l}
-}{\\&&\sidecond{
-		\goodgap{g}
-		\text{ and } \forall l. m_1 \neq \hcmfail{l}}}
-\figequalto{\composegap{\hcmbool}{g}{\hcmbool}}{
-	\hcmbool
-}{}
-\figequalto{
-	\composegap{
-		(\hcmfunc{c_1}{d_1})}{
-		g}{
-		(\hcmfunc{c_2}{d_2})}
-}{
-	\hcmfunc{
-		(\composegap{c_2}{\dom{g}}{c_1})}{
-		(\composegap{d_1}{\cod{g}}{d_2})}
-}{}
-\figequalto{
-	\composegap{
-		(\hcmprod{c_1}{d_1})}{
-		g}{
-		(\hcmprod{c_2}{d_2})}
-}{
-	\hcmprod{
-		(\composegap{c_1}{\fst{g}}{c_2})}{
-		(\composegap{d_1}{\snd{g}}{d_2})}
-}{}
-\end{array}
-\]
-
-	\caption{Composition of \LD\ Hypercoercions}
-	\label{fig:LazyD-Hypercoercions-composition}
-\end{figure}
-
-\begin{figure}[tp]
-\fbox{$\goodgap{g}$}
-\begin{gather*}
-\infr{}{\goodgap{\gnone}} \quad
-\infr{\shallowlyconsistent{P}{Q}}{\goodgap{\gsome{P}{l}{Q}}}
-\end{gather*}
-
-\fbox{$\dom{g}=g$}
-\[
-\begin{array}{rclr}
-\figequalto{\dom{\gnone}}{\gnone}{}
-\figequalto{\dom{\gsome{\Pfunc{S_1}{T_1}}{l}{\Pfunc{S_2}{T_2}}}}{
-	\gsome{S_2}{l}{S_1}
-}{}
-\end{array}
-\]
-
-\fbox{$\cod{g}=g$}
-\[
-\begin{array}{rclr}
-\figequalto{\cod{\gnone}}{\gnone}{}
-\figequalto{\cod{\gsome{\Pfunc{S_1}{T_1}}{l}{\Pfunc{S_2}{T_2}}}}{
-	\gsome{T_1}{l}{T_2}
-}{}
-\end{array}
-\]
-
-\fbox{$\fst{g}=g$}
-\[
-\begin{array}{rclr}
-\figequalto{\fst{\gnone}}{\gnone}{}
-\figequalto{\fst{\gsome{\Pprod{S_1}{T_1}}{l}{\Pprod{S_2}{T_2}}}}{
-	\gsome{S_1}{l}{S_2}
-}{}
-\end{array}
-\]
-
-\fbox{$\snd{g}=g$}
-\[
-\begin{array}{rclr}
-\figequalto{\snd{\gnone}}{\gnone}{}
-\figequalto{\snd{\gsome{\Pprod{S_1}{T_1}}{l}{\Pprod{S_2}{T_2}}}}{
-	\gsome{T_1}{l}{T_2}
-}{}
-\end{array}
-\]
-\caption{Auxilliary predicates and functions for hypercoercion composition.}
-\label{fig:aux-hypercoercion-composition}
-\end{figure}
-
-\figref{fig:LazyD-Hypercoercions-composition} defines the composition
-operator \compose{c}{c} for \LD\ hypercoercions and
-\figref{fig:aux-hypercoercion-composition} defines some auxilliary
-predicates and functions.
-
-The \compose{c}{c} operator is the key to compressing coercions and
-maintaining space-efficiency. The composition operator for Coercions
-in Normal Form requires the target type of the first coercion to match
-the source type of the second. This requirement, however, imposes
-considerable difficulty in the termination proof of the composition
-for \LD\ Coercions in Normal Form~\citep{almahallawi19}. So it is
-useful to relax this restriction for the \LD\ tracking strategy.
-%
-We shall need an optional source cast, written $g$, that ranges over
-$\gnone$ or $\gsome{S}{l}{T}$, to maintain the gap between the two
-hypercoercions to be composed. The source cast is mandatory when the
-target type of the first hypercoercion does not match the source type
-of the second.  Then we write the composition of hypercoercions as
-\composegap{c_1}{g}{c_2}.
-%  
-When both $c_1$ and $c_2$ are \hcci, their composition is also \hcci. 
-%
-When the first hypercoercion is the \hcci, the output must start with
-a projection, in which case we invoke the helper function
-\textit{mkProj}. In \textit{mkProj}, if the head of $c_2$ is a
-projection, the result is $c_2$.  Otherwise, we need a label to build
-the projection. Since the head of $c_2$ is a no-op, its source type
-must be a pre-type. Thus we know $g$ must be a source cast and we use
-it to construct the projection.
-%
-Going back to $\composegap{c}{g}{c}$, when the second hypercoercion is the 
-\hcci, the output must end with an injection, in which case we invoke the 
-helper function \textit{mkInj}.
-%
-Finally, when both inputs are of the form \hccc{h}{m}{t}, we compose the middle 
-with an updated gap.
-%
-The second and third cases of \mkgap{t}{g}{h} is interesting, where we choose 
-the label in projection to be responsible for potential inconsistency.
-
-Another interesting operator is the middle composition \composegap{m}{g}{m}. 
-%
-When the first middle is a failure (\hcmfail{l}), the result is the second
-middle. In all the remaining cases, the first middle is not a failure.
-%
-When the gap is a cast between shallowly inconsistent types (i.e. having 
-different top-most constructors) the output is a failure.
-%
-When the gap is good but the second middle is a failure, the output is the same 
-failure. A gap $g$ is good if and only if there is not $P$ and $l$ 
-and $Q$ such that $g = \gsome{P}{l}{Q}$ and \notshallowlyconsistent{P}{Q}.
-%
-The remaining cases are straightforward recursion.
-
-Agda is able to understand that \composegap{c}{g}{c} is
-terminating. The reason might be that in \composegap{c}{g}{c} both
-casts become smaller in recursive calls, although their position is
-swapped in the function case. Readers who dislike non-structural
-recursion could add a Boolean parameter to indicate the direction of
-composition.
-
-\begin{figure}[tp]
-	\fbox{$\translate{\ccast{S}{l}{T}} = c$} Translation of \LD\ hypercoercions
-	\[
-	\begin{array}{rclr}
-	\figequalto{\translate{\ccast{S}{l}{T}}}{\composegap{id(S)}{(\gsome{S}{l}{T})}{id(T)}}{}
-	\end{array}
-	\]
-	\caption{Translation of \LD\ Hypercoercions}
-	\label{fig:LazyD-Hypercoercions-translation}
-\end{figure}
-
-The definition of the translation function \translate{\ccast{S}{l}{T}}
-is straightforward (\figref{fig:LazyD-Hypercoercions-translation}).
-
-\begin{figure}[tp]
-\fbox{$\denote{c}(v)=r$}
-\[
-\begin{array}{rclr}
-\figequalto{\denote{\hcci}(v)}{v}{}
-\figequalto{\denote{\hccc{h}{m}{t}}(v)}{
-	(\denote{h}_h(v) \mbind \denote{m}_m)
-	\mbind \denote{t}_t
-}{}
-\end{array}
-\]
-
-\fbox{$\denote{h}_h(v)=r$}
-\[
-\begin{array}{rclr}
-\figequalto{\denote{\hche}(v)}{v}{}
-\figequalto{\denote{\hchp{Q}{l}}(\vdyn{P}{u})}{
-	\denote{\composegap{\idm{P}}{\gsome{P}{l}{Q}}{\idm{Q}}}_m(u)
-}{}
-\end{array}
-\]
-
-\fbox{$\denote{m}_m(v)=r$}
-\[
-\begin{array}{rclr}
-\figequalto{\denote{\hcmfail{l}}(v)}{\error{l}}{}
-\figequalto{\denote{\hcmbool}(v)}{v}{}
-\figequalto{\denote{\hcmfunc{d_1}{d_2}}(\ecast{\vfunc{x}{S}{e}{E}}{\Pfunc{c_1}{c_2}})}{
-	\ecast{\vfunc{x}{S}{e}{E}}{\Pfunc{(\compose{d_1}{c_1})}{(\compose{c_2}{d_2})}}
-}{}
-\figequalto{\denote{\hcmprod{d_1}{d_2}}(\ecast{\vcons{v_1}{v_2}}{\Pprod{c_1}{c_2}})}{
-	\ecast{\vcons{v_1}{v_2}}{\Pprod{(\compose{c_1}{d_1})}{(\compose{c_2}{d_2})}}
-}{}
-\end{array}
-\]
-
-\fbox{$\denote{t}_t(v)=r$}
-\[
-\begin{array}{rclr}
-\figequalto{\denote{\hcte}(v)}{v}{}
-\figequalto{\denote{\hcti{P}}(v)}{\vdyn{P}{v}}{}
-\end{array}
-\]
-\caption{Application of \LD\ Hypercoercions}
-\label{fig:LazyD-Hypercoercions-application}
-\end{figure}
-
-Fig.~\ref{fig:LazyD-Hypercoercions-application} defines the cast application 
-function for \LD\ hypercoercions.
-Applying the identity cast for the dynamic type succeeds immediately. 
-Otherwise, we apply head, middle, and tail in sequence. 
-%
-In the projection case of applying a head coercion, a new middle is
-constructed and applied to the injected value.
-%
-Middle applications raise an error if the middle is a failure,
-otherwise they compose their sub-coercions with those in the value.
-
-\begin{proposition} Lazy D Hypercoercions implement the Lazy D Cast ADT.
-\end{proposition}
-\begin{theorem}[Lazy D Hypercoercions are Correct] Let $H$ be the Lazy D 
-hypercoercions.
-\[\machineequiv{\LDMachine}{\SMachine{H}}\]
-\end{theorem}
-
 \subsection{\LUD\ Hypercoercions} \label{sec:LazyUD-Hypercoercions}
@@
   LazyD because a reader is more likely to be familiar with Lazy UD.}
-\todo[inline]{KC: will do}
-
-Hypercoercions for the \LUD\ blame tracking strategy have the same syntax
-as for \LD\ (\figref{fig:hypercoercion}), but the definitions of $\id{T}$ and
-$\translate{\ccast{S}{l}{T}}$ and $\compose{c}{c}$, differ from \LD. Here 
-composition $\compose{c_1}{c_2}$ makes the usual assumption that the
-target type of $c_1$ matches the source type of $c_2$. 
-%
+\todo[inline]{KC: Updated.}
+
+% Hypercoercions for the \LUD\ blame tracking strategy have the same syntax
+% as for \LD\ (\figref{fig:hypercoercion}), but the definitions of $\id{T}$ and
+% $\translate{\ccast{S}{l}{T}}$ and $\compose{c}{c}$, differ from \LD. Here 
+% composition $\compose{c_1}{c_2}$ makes the usual assumption that the
+% target type of $c_1$ matches the source type of $c_2$. 
+% %
 The definition of composition for \LUD\ is particularly straightforward.
@@
 \todo[inline]{JS: how about $\sim$}
+\todo[inline]{KC: sounds good}
 
@@
 	& = & m_1 \fatsemi m_2
-	& \sidecond{
+	& \quad \sidecond{
 		\forall l. m_2 \neq \hcmfail{l}
@@
 
+\todo[inline]{KC: should we cite the place where ``Prior presentations'' locate?}
 The translation function \translate{\ccast{S}{l}{T}} is defined in 
@@
 \begin{theorem}[Lazy UD Hypercoercions are Correct] Let $H$ be the Lazy UD 
+	hypercoercions.
+	\[\machineequiv{\LDMachine}{\SMachine{H}}\]
+\end{theorem}
+
+\subsection{\LD\ Hypercoercions}
+\label{sec:LazyD-Hypercoercions}
+
+\begin{figure}[tp] %% composition 1
+\[
+\begin{array}{lrcl}
+\stxrule{g}{Gaps}{
+	\gnone           \mid
+	\gsome{S}{l}{T}
+}
+\end{array}
+\]
+
+\fbox{$\compose{c}{c} = c$} Composition of \LD\ hypercoercions
+\[
+\begin{array}{rclr}
+\figequalto{\compose{c_1}{c_2}}{\composegap{c_1}{\gnone}{c_2}}{}
+\end{array}
+\]
+
+\fbox{$\composegap{c}{g}{c} = c$}
+\[
+\begin{array}{rcll}
+\figequalto{\composegap{\hcci}{g}{\hcci}}{\hcci}{}
+\figequalto{\composegap{\hcci}{g}{\hccc{h}{m}{t}}}{
+	\hccc{\mkhead{g}{h}}{m}{t}
+}{}
+\figequalto{\composegap{\hccc{h}{m}{t}}{g}{\hcci}}{
+	\hccc{h}{m}{\mktail{t}{g}}
+}{}
+\figequalto{\composegap{\hccc{h_1}{m_1}{t_1}}{g}{\hccc{h_2}{m_2}{t_2}}}{
+	\hccc{h_1}{(\composegap{m_1}{\mkgap{t_1}{g}{h_2}}{m_2})}{t_2}
+}{}
+\end{array}
+\]
+
+\fbox{\mkhead{g}{h}}
+\[
+\begin{array}{rclr}
+\figequalto{\mkhead{g}{\hchp{P}{l}}}{\hchp{P}{l}}{}
+\figequalto{\mkhead{\gsome{\Tdyn}{l}{P}}{\hche}}{\hchp{P}{l}}{}
+%\mathrm{mkProj(}
+%& g
+%& ,
+%& \hchp{P}{l}
+%& )=
+%& \hchp{P}{l} \\
+%\mathrm{mkProj(}
+%& \gsome{\Tdyn}{l}{P}
+%& ,
+%& \hche
+%& )=
+%& \hchp{P}{l}
+\end{array}
+\]
+%\[
+%\begin{array}{rcll}
+%\figequalto{\mkhead{g}{\hchp{P}{l}}}{\hchp{P}{l}}{}
+%\figequalto{\mkhead{\gsome{\Tdyn}{l}{P}}{\hche}}{\hchp{P}{l}}{}
+%\end{array}
+%\]
+
+\fbox{\mktail{t}{g}}
+\[
+\begin{array}{rcll}
+\figequalto{\mktail{\hcti{P}}{g}}{\hcti{P}}{}
+\figequalto{\mktail{\hcte}{\gsome{P}{l}{\Tdyn}}}{\hcti{P}}{}
+\end{array}
+\]
+
+\fbox{\mkgap{t}{g}{h}}
+\[
+\begin{array}{rcll}
+\figequalto{\mkgap{\hcte}{g}{\hche}}{g}{}
+\figequalto{\mkgap{\hcte}{\gsome{P}{l'}{\Tdyn}}{\hchp{Q}{l}}}{
+	\gsome{P}{l}{Q}
+}{}
+\figequalto{\mkgap{\hcti{P}}{g}{\hchp{Q}{l}}}{
+	\gsome{P}{l}{Q}
+}{}
+\figequalto{\mkgap{\hcti{P}}{\gsome{\Tdyn}{l}{Q}}{\hche}}{
+	\gsome{P}{l}{Q}
+}{}
+\end{array}
+\]
+
+\fbox{$\composegap{m}{g}{m} = m$}
+\[ 
+\begin{array}{rclr}
+\figequalto{\composegap{\hcmfail{l}}{g}{m_2}}{
+	\hcmfail{l}
+}{}
+\figequalto{\composegap{m_1}{\gsome{P}{l}{Q}}{m_2}}{
+	\hcmfail{l}
+}{\\&&\sidecond{
+		\notshallowlyconsistent{P}{Q}
+		\text{ and } \forall l. m_1 \neq \hcmfail{l}
+}}
+\figequalto{\composegap{m_1}{g}{\hcmfail{l}}}{
+	\hcmfail{l}
+}{\\&&\sidecond{
+		\goodgap{g}
+		\text{ and } \forall l. m_1 \neq \hcmfail{l}}}
+\figequalto{\composegap{\hcmbool}{g}{\hcmbool}}{
+	\hcmbool
+}{}
+\figequalto{
+	\composegap{
+		(\hcmfunc{c_1}{d_1})}{
+		g}{
+		(\hcmfunc{c_2}{d_2})}
+}{
+	\hcmfunc{
+		(\composegap{c_2}{\dom{g}}{c_1})}{
+		(\composegap{d_1}{\cod{g}}{d_2})}
+}{}
+\figequalto{
+	\composegap{
+		(\hcmprod{c_1}{d_1})}{
+		g}{
+		(\hcmprod{c_2}{d_2})}
+}{
+	\hcmprod{
+		(\composegap{c_1}{\fst{g}}{c_2})}{
+		(\composegap{d_1}{\snd{g}}{d_2})}
+}{}
+\end{array}
+\]
+
+	\caption{Composition of \LD\ Hypercoercions}
+	\label{fig:LazyD-Hypercoercions-composition}
+\end{figure}
+
+\begin{figure}[tp]
+\fbox{$\goodgap{g}$}
+\begin{gather*}
+\infr{}{\goodgap{\gnone}} \quad
+\infr{\shallowlyconsistent{P}{Q}}{\goodgap{\gsome{P}{l}{Q}}}
+\end{gather*}
+
+\fbox{$\dom{g}=g$}
+\[
+\begin{array}{rclr}
+\figequalto{\dom{\gnone}}{\gnone}{}
+\figequalto{\dom{\gsome{\Pfunc{S_1}{T_1}}{l}{\Pfunc{S_2}{T_2}}}}{
+	\gsome{S_2}{l}{S_1}
+}{}
+\end{array}
+\]
+
+\fbox{$\cod{g}=g$}
+\[
+\begin{array}{rclr}
+\figequalto{\cod{\gnone}}{\gnone}{}
+\figequalto{\cod{\gsome{\Pfunc{S_1}{T_1}}{l}{\Pfunc{S_2}{T_2}}}}{
+	\gsome{T_1}{l}{T_2}
+}{}
+\end{array}
+\]
+
+\fbox{$\fst{g}=g$}
+\[
+\begin{array}{rclr}
+\figequalto{\fst{\gnone}}{\gnone}{}
+\figequalto{\fst{\gsome{\Pprod{S_1}{T_1}}{l}{\Pprod{S_2}{T_2}}}}{
+	\gsome{S_1}{l}{S_2}
+}{}
+\end{array}
+\]
+
+\fbox{$\snd{g}=g$}
+\[
+\begin{array}{rclr}
+\figequalto{\snd{\gnone}}{\gnone}{}
+\figequalto{\snd{\gsome{\Pprod{S_1}{T_1}}{l}{\Pprod{S_2}{T_2}}}}{
+	\gsome{T_1}{l}{T_2}
+}{}
+\end{array}
+\]
+\caption{Auxilliary predicates and functions for hypercoercion composition.}
+\label{fig:aux-hypercoercion-composition}
+\end{figure}
+
+Hypercoercions for the \LD\ blame tracking strategy have the same syntax
+as for \LUD\ (\figref{fig:hypercoercion}), but the definitions of $\id{T}$ and
+$\translate{\ccast{S}{l}{T}}$ and $\compose{c}{c}$ differ from \LUD.
+% Here composition $\compose{c_1}{c_2}$ makes the usual assumption that the
+% target type of $c_1$ matches the source type of $c_2$. 
+%
+\figref{fig:LazyD-Hypercoercions-composition} defines the composition
+operator \compose{c}{c} for \LD\ hypercoercions and
+\figref{fig:aux-hypercoercion-composition} defines some auxilliary
+predicates and functions.
+
+The \compose{c}{c} operator is the key to compressing coercions and
+maintaining space-efficiency. The composition operator for Coercions
+in Normal Form requires the target type of the first coercion to match
+the source type of the second. This requirement, however, imposes
+considerable difficulty in the termination proof of the composition
+for \LD\ Coercions in Normal Form~\citep{almahallawi19}. So it is
+useful to relax this restriction for the \LD\ tracking strategy.
+%
+We shall need an optional source cast, written $g$, that ranges over
+$\gnone$ or $\gsome{S}{l}{T}$, to maintain the gap between the two
+hypercoercions to be composed. The source cast is mandatory when the
+target type of the first hypercoercion does not match the source type
+of the second.  Then we write the composition of hypercoercions as
+\composegap{c_1}{g}{c_2}.
+%  
+When both $c_1$ and $c_2$ are \hcci, their composition is also \hcci. 
+%
+When the first hypercoercion is the \hcci, the output must start with
+a projection, in which case we invoke the helper function
+\textit{mkProj}. In \textit{mkProj}, if the head of $c_2$ is a
+projection, the result is $c_2$.  Otherwise, we need a label to build
+the projection. Since the head of $c_2$ is a no-op, its source type
+must be a pre-type. Thus we know $g$ must be a source cast and we use
+it to construct the projection.
+%
+Going back to $\composegap{c}{g}{c}$, when the second hypercoercion is the 
+\hcci, the output must end with an injection, in which case we invoke the 
+helper function \textit{mkInj}.
+%
+Finally, when both inputs are of the form \hccc{h}{m}{t}, we compose the middle 
+with an updated gap.
+%
+The second and third cases of \mkgap{t}{g}{h} is interesting, where we choose 
+the label in projection to be responsible for potential inconsistency.
+
+Another interesting operator is the middle composition \composegap{m}{g}{m}. 
+%
+When the first middle is a failure (\hcmfail{l}), the result is the second
+middle. In all the remaining cases, the first middle is not a failure.
+%
+When the gap is a cast between shallowly inconsistent types (i.e. having 
+different top-most constructors) the output is a failure.
+%
+When the gap is good but the second middle is a failure, the output is the same 
+failure. A gap $g$ is good if and only if there is not $P$ and $l$ 
+and $Q$ such that $g = \gsome{P}{l}{Q}$ and \notshallowlyconsistent{P}{Q}.
+%
+The remaining cases are straightforward recursion.
+
+Agda is able to understand that \composegap{c}{g}{c} is
+terminating. The reason might be that in \composegap{c}{g}{c} both
+casts become smaller in recursive calls, although their position is
+swapped in the function case. Readers who dislike non-structural
+recursion could add a Boolean parameter to indicate the direction of
+composition.
+
+\begin{figure}[tp]
+	\fbox{$\translate{\ccast{S}{l}{T}} = c$} Translation of \LD\ hypercoercions
+	\[
+	\begin{array}{rclr}
+	\figequalto{\translate{\ccast{S}{l}{T}}}{\composegap{id(S)}{(\gsome{S}{l}{T})}{id(T)}}{}
+	\end{array}
+	\]
+	\caption{Translation of \LD\ Hypercoercions}
+	\label{fig:LazyD-Hypercoercions-translation}
+\end{figure}
+
+The definition of the translation function \translate{\ccast{S}{l}{T}}
+is straightforward (\figref{fig:LazyD-Hypercoercions-translation}).
+
+\begin{figure}[tp]
+\fbox{$\denote{c}(v)=r$}
+\[
+\begin{array}{rclr}
+\figequalto{\denote{\hcci}(v)}{v}{}
+\figequalto{\denote{\hccc{h}{m}{t}}(v)}{
+	(\denote{h}_h(v) \mbind \denote{m}_m)
+	\mbind \denote{t}_t
+}{}
+\end{array}
+\]
+
+\fbox{$\denote{h}_h(v)=r$}
+\[
+\begin{array}{rclr}
+\figequalto{\denote{\hche}(v)}{v}{}
+\figequalto{\denote{\hchp{Q}{l}}(\vdyn{P}{u})}{
+	\denote{\composegap{\idm{P}}{\gsome{P}{l}{Q}}{\idm{Q}}}_m(u)
+}{}
+\end{array}
+\]
+
+\fbox{$\denote{m}_m(v)=r$}
+\[
+\begin{array}{rclr}
+\figequalto{\denote{\hcmfail{l}}(v)}{\error{l}}{}
+\figequalto{\denote{\hcmbool}(v)}{v}{}
+\figequalto{\denote{\hcmfunc{d_1}{d_2}}(\ecast{\vfunc{x}{S}{e}{E}}{\Pfunc{c_1}{c_2}})}{
+	\ecast{\vfunc{x}{S}{e}{E}}{\Pfunc{(\compose{d_1}{c_1})}{(\compose{c_2}{d_2})}}
+}{}
+\figequalto{\denote{\hcmprod{d_1}{d_2}}(\ecast{\vcons{v_1}{v_2}}{\Pprod{c_1}{c_2}})}{
+	\ecast{\vcons{v_1}{v_2}}{\Pprod{(\compose{c_1}{d_1})}{(\compose{c_2}{d_2})}}
+}{}
+\end{array}
+\]
+
+\fbox{$\denote{t}_t(v)=r$}
+\[
+\begin{array}{rclr}
+\figequalto{\denote{\hcte}(v)}{v}{}
+\figequalto{\denote{\hcti{P}}(v)}{\vdyn{P}{v}}{}
+\end{array}
+\]
+\caption{Application of \LD\ Hypercoercions}
+\label{fig:LazyD-Hypercoercions-application}
+\end{figure}
+
+Fig.~\ref{fig:LazyD-Hypercoercions-application} defines the cast application 
+function for \LD\ hypercoercions.
+Applying the identity cast for the dynamic type succeeds immediately. 
+Otherwise, we apply head, middle, and tail in sequence. 
+%
+In the projection case of applying a head coercion, a new middle is
+constructed and applied to the injected value.
+%
+Middle applications raise an error if the middle is a failure,
+otherwise they compose their sub-coercions with those in the value.
+
+\begin{proposition} Lazy D Hypercoercions implement the Lazy D Cast ADT.
+\end{proposition}
+\begin{theorem}[Lazy D Hypercoercions are Correct] Let $H$ be the Lazy D 
 hypercoercions.

### 2020-10-11 paper.tex
mbind to mlet

@@
 % operators
-\newcommand{\mbind}[0]{\ensuremath{\;\gg=\;}}
+% \newcommand{\mbind}[0]{\ensuremath{\;\gg=\;}}
+% \newcommand{\mcomp}[0]{\ensuremath{\;>=>\;}}
 \newcommand{\mlet}[3]{\ensuremath{
-\mathtt{let}\ #1\leftarrow#2\ \mathtt{in}\;#3}}
-\newcommand{\mcomp}[0]{\ensuremath{\;>=>\;}}
+\mathit{let}\ {#1\leftarrow#2}\ \mathit{in}\;#3}}
 
@@
 
-\todo[inline]{KC: in the next paragraph I cite \cite{breazu1991inheritance}}
+\todo[inline]{KC: in the next paragraph I cite \cite{breazu1991inheritance}
+and \cite{breazu1990computing}}
+
 Continuations are not the only place where casts can accumulate.
@@
 the output, following the approach in \cite{breazu1991inheritance}
-and \cite{Breazu-Tannen:1990vc},
+and \cite{breazu1990computing},
 so the space complexity is again linear.
@@
 % \]
-\todo[inline]{KC: KC, you need to replace all uses of monad bind to let.}
 
@@
 	\figreducetoH{\scont{v}{\Kcons{\Fcast{\ccast{S}{l}{T}}}{K}}}{
-		\applyCast{v}{\ccast{S}{l}{T}} \; \mbind \; \lambda u. \scont{u}{K}
+	    \mlet{u}{\applyCast{v}{\ccast{S}{l}{T}}}{\scont{u}{K}}
+% 		\applyCast{v}{\ccast{S}{l}{T}} \; \mbind \; \lambda u. \scont{u}{K}
 	}{}
@@
 	\applyCastName(\vdyn{G}{u}, \ccast{\Tdyn}{l}{Q}) &=&
-	\project{u}{G}{l}{H} \mbind \lambda v. \proxy{v}{\ccast{H}{l}{Q}}
+	\mlet{v}{\project{u}{G}{l}{H}}{\proxy{v}{\ccast{H}{l}{Q}}}
+% 	\project{u}{G}{l}{H} \mbind \lambda v. \proxy{v}{\ccast{H}{l}{Q}}
 	\\
@@
 		then 
-		$ \denote{\compose{c}{d}}(v) = (\denote{c}(v)\mbind\denote{d})$
+% 		$ \denote{\compose{c}{d}}(v) = (\denote{c}(v)\mbind\denote{d})$
+        $ \denote{\compose{c}{d}}(v) = \mlet{v}{\denote{c}(v)}{\denote{d}(v)}$
 \end{itemize}
@@
 	}{
-		\scont{\ecast{\vfunc{x}{S}{e}{E}}{\Pfunc{id(S)}{id(T)}}}{K}
+		\scont{\ecast{\vfunc{x}{S}{e}{E}}{\Pfunc{\id{S}}{\id{T}}}}{K}
 	}{}
@@
 	\figreducetoH{\scont{v}{\Kcons{\Fcast{c}}{k}}}{
-		\denote{c}(v) \; \mbind \; \lambda u. \applyCont{u}{K}
+	    \mlet{u}{\denote{c}(v)}{\applyCont{u}{K}}
+% 		\denote{c}(v) \; \mbind \; \lambda u. \applyCont{u}{K}
 	}{}
@@
 	}{
-		\denote{c}(v) \mbind \lambda u. \
-		\sexpr{e}{E[x:=u]}{\extCont{d}{K}}
+	    \mlet{u}{\denote{c}(v)}{\sexpr{e}{E[x:=u]}{\extCont{d}{K}}}
+% 		\denote{c}(v) \mbind \lambda u. \
+% 		\sexpr{e}{E[x:=u]}{\extCont{d}{K}}
 	}{}
@@
 	}{
-		\denote{c_1}(v_1) \mbind \lambda u.
-		\scont{u}{K}
+	    \mlet{u}{\denote{c_1}(v_1)}{\scont{u}{K}}
+% 		\denote{c_1}(v_1) \mbind \lambda u.
+% 		\scont{u}{K}
 	}{}
@@
 	}{
-		\denote{c_2}(v_2) \mbind \lambda u.
-		\scont{u}{K}
+	    \mlet{u}{\denote{c_2}(v_2)}{\scont{u}{K}}
+% 		\denote{c_2}(v_2) \mbind \lambda u.
+% 		\scont{u}{K}
 	}{}
@@
 	\item $\denote{\translate{\ccast{P}{l}{\Tdyn}}}(v) = 
-		\denote{\translate{\ccast{P}{l}{G}}}(v) \mbind 
-		\denote{\ccast{G}{l}{\Tdyn}}$\\
+	    \mlet{v}{\denote{\translate{\ccast{P}{l}{G}}}(v)}{\denote{\ccast{G}{l}{\Tdyn}}(v)}
+% 		\denote{\translate{\ccast{P}{l}{G}}}(v) \mbind 
+% 		\denote{\ccast{G}{l}{\Tdyn}}
+        $\\
 		if $G \sim P$ and $G \neq P$	
@@
 	\item $\denote{\translate{\ccast{\Tdyn}{l}{Q}}}(v) = 
-		\denote{\translate{\ccast{\Tdyn}{l}{H}}}(v) \mbind
-		\denote{\translate{\ccast{H}{l}{Q}}}$\\
+	    \mlet{v}{\denote{\translate{\ccast{\Tdyn}{l}{H}}}(v)}{\denote{\translate{\ccast{H}{l}{Q}}}(v)}
+% 		\denote{\translate{\ccast{\Tdyn}{l}{H}}}(v) \mbind
+% 		\denote{\translate{\ccast{H}{l}{Q}}}
+		$\\
 		if $H \sim Q$ and $H \neq Q$
@@
 \begin{gather*}
-\infr{}{\bisimc{[]}{id(T)}{T}{T}} \quad
+\infr{}{\bisimc{[]}{\id{T}}{T}{T}} \quad
 \infr{}{\bisimc{[\ccast{S}{l}{T}]}{\translate{\ccast{S}{l}{T}}}{S}{T}}
@@
 	}{
-		\Kcons{\Fcast{c'}}{k'}
+		\Kcons{\Fcast{c}}{k'}
 	}{S_1}{T}
@@
 \end{figure}
-
-% \begin{figure}
-
-% \fbox{\bisimc{Z}{c}{S}{T}}
-% \begin{gather*}
-% \infr{}{\bisimc{[]}{id(T)}{T}{T}} \quad
-% \infr{}{\bisimc{[\ccast{S}{l}{T}]}{\translate{\ccast{S}{l}{T}}}{S}{T}}
-% \\[1ex]
-% \infr{
-% 	\bisimc{Z_1}{c_1}{T_1}{T_2}\\
-% 	\bisimc{Z_2}{c_2}{T_2}{T_3}
-% }{
-% 	\bisimc{(Z_1 \mathrm{++} Z_2)}{(\compose{c_1}{c_2})}{T_1}{T_3}
-% }
-% \end{gather*}
-
-% \fbox{$\bisimK{K}{K}{S}{T}$}
-% \begin{gather*}
-% \infr{
-% 	\bisimK{K}{k'}{S_n}{T} \qquad
-% 	\bisimc{Z}{c}{S_1}{S_n}
-% }{
-% 	\bisimK{
-% 		\Kcons{\Fcast{Z}}{K}
-% 	}{
-% 		\Kcons{\Fcast{c'}}{k'}
-% 	}{S_1}{T}
-% }
-% \end{gather*}
-
-% \fbox{$\bisimv{v}{v}{T}$}
-% \begin{gather*}
-% \infr{
-% 	\expressiontyping{\Gamma,x : S_1}{e}{T_1}
-% 	\qquad
-% 	\bisimE{\Gamma}{E}{E'}
-% 	\\
-% 	\bisimc{
-% 		(\ccast{S_n}{\bar{l}_{n-1}}{S_{n-1}} \ldots
-% 		\ccast{S_2}{\bar{l}_1}{S_1})
-% 	}{c}{S_n}{S_1}
-% 	\\
-% 	\bisimc{
-% 		(		\ccast{T_1}{l_{1}}{T_2} \ldots
-% 		\ccast{T_{n-1}}{l_{n-1}}{T_n}
-% 		)	}{d}{T_1}{T_n}
-% 	\\
-% 	v = \vfuncc{
-% 		\vfuncc{
-% 			\vfunc{x}{S_1}{e}{E}
-% 		}{S_1}{T_1}{l_1}{S_2}{T_2}
-% 		\ldots
-% 	}{S_{n-1}}{T_{n-1}}{l_{n-1}}{S_n}{T_n}
-% }{
-% 	\bisimv{v}{
-% 		(\ecast{\vfunc{x}{S_1}{e}{E'}}{\Pfunc{c}{d}})
-% 	}{
-% 		\Pfunc{S_n}{T_n}}
-% }
-% \\[1ex]
-% \infr{
-% 	\bisimv{v_1}{v_1'}{S_1} \qquad
-% 	\bisimv{v_2}{v_2'}{T_1} \\
-% 	\bisimc{
-% 		(\ccast{S_1}{l_{1}}{S_2} \ldots
-% 		\ccast{S_{n-1}}{l_{n-1}}{S_n})
-% 	}{c}{S_1}{S_n} \\
-% 	\bisimc{
-% 		(\ccast{T_1}{l_{1}}{T_2} \ldots
-% 		\ccast{T_{n-1}}{l_{n-1}}{T_n})
-% 	}{d}{T_1}{T_n}
-% 	\\ v = \vconsc{
-% 		\vconsc{
-% 			\vcons{v_1}{u_1}
-% 		}{S_1}{T_1}{l_1}{S_2}{T_2}
-% 		\ldots
-% 	}{S_{n-1}}{T_{n-1}}{l_{n-1}}{S_n}{T_n}
-% }{
-% 	\bisimv{
-% 		v
-% 	}{
-% 		(\ecast{\vcons{v_2}{u_2}}{\Pprod{c}{d}})
-% 	}{
-% 		\Pprod{S_n}{T_n}}
-% }
-% \end{gather*}
-
-% \fbox{\bisimE{\Gamma}{E}{E}}
-% \begin{gather*}
-% \inference{
-% }{
-% 	\bisimE{\emptyset}{\emptyset}{\emptyset}
-% }
-% \quad
-% \inference{
-% 	\Gamma \vdash E \approx E' \qquad
-% 	v \approx v' : T
-% }{
-% 	\Gamma , x : T \vdash 
-% 	E [ x := v' ] \approx E' [ x := v' ]
-% }
-% \end{gather*}
-
-% \fbox{\bisims{s}{s}{T}}
-% \begin{gather*}
-% \infr{}{\bisims{\error{l}}{\error{l}}{T}} \quad
-% \infr{
-% 	\bisimv{v}{v'}{T}
-% }{
-% 	\bisims{\shalt{v}}{\shalt{v'}}{T}
-% }
-% \\
-% \infr{
-% 	\bisimv{v}{v'}{S} \\
-% 	\bisimK{K}{K'}{S}{T}
-% }{
-% 	\bisims{\scont{v}{K}}{\scont{v}{K'}}{T}
-% } \quad
-% \infr{
-% 	\expressiontyping{\Gamma}{e}{S} \\
-% 	\bisimE{\Gamma}{E}{E'}          \\
-% 	\bisimK{K}{K'}{S}{T}
-% }{
-% 	\bisims{\sexpr{e}{E}{K}}{\sexpr{e}{E'}{K'}}{T}
-% }
-% \end{gather*}
-
-% \caption{Bisimulation between \CBMachine\ and \SMachine{C}. It is the smallest 
-% congruence relation containing the shown rules. Everything to the left (resp. 
-% right) of $\approx$ is in \CBMachine\ (resp. in \SMachine{C}).}
-% \label{fig:bisim-SC-D}
-% \end{figure}
 
@@
 https://etaps.org/2021/call-for-papers}
+\todo[inline]{KC: [IMPORTANT]}
 
@@
 	\figequalto{\denote{\hccc{h}{m}{t}}(v)}{
-		(\denote{h}(v) \mbind \denote{m})
-		\mbind \denote{t}
+	    \mlet{v}{\denote{h}_h(v)}{
+	    \mlet{v}{\denote{m}_m(v)}{
+	    \denote{t}_t(v)}}
+	   % \mlet{v}{(\mlet{v}{\denote{h}(v)}{\denote{m}(v)})}{
+	   % \denote{t}(v)}
+% 		(\denote{h}(v) \mbind \denote{m})
+% 		\mbind \denote{t}
 	}{}
@@
 	\begin{array}{rclr}
-	\figequalto{\translate{\ccast{S}{l}{T}}}{\composegap{id(S)}{(\gsome{S}{l}{T})}{id(T)}}{}
+	\figequalto{\translate{\ccast{S}{l}{T}}}{\composegap{\id{S}}{(\gsome{S}{l}{T})}{\id{T}}}{}
 	\end{array}
@@
 \figequalto{\denote{\hccc{h}{m}{t}}(v)}{
-	(\denote{h}_h(v) \mbind \denote{m}_m)
-	\mbind \denote{t}_t
+    \mlet{v}{\denote{h}_h(v)}{
+    \mlet{v}{\denote{m}_m(v)}{\denote{t}_t(v)}}
+% 	(\denote{h}_h(v) \mbind \denote{m}_m)
+% 	\mbind \denote{t}_t
 }{}

### 2020-10-11 paper.tex
comment and edits to abstract

@@
 \begin{abstract}
-Gradual typing aims at combining dynamic typing and static typing in one 
-language to provide the advantages of both typing disciplines. Implementing 
-gradual typing with reasonable overhead, however, is not trivial. Casts might 
-accumulate in higher-order values and continuations, thus change the overall 
-space complexity. Several space-efficient cast representations have been 
-proposed, notably coercions in normal forms and threesomes. But they are
-presented in different dynamic semantics, which make it difficult to compare
-the key differences between the cast representations. We present a abstrat
-data type, namely Cast ADT, that captures interface functions a cast representations
-typically includes, and an abstract machine parameterized over Cast ADTs.
-The Cast ADT brings another benefit: space-efficient cast representations 
-shall be proved not changing the 
+Gradual typing combines dynamic typing and static typing in one
+language to provide the advantages of both typing
+disciplines. Implementing gradual typing with reasonable overhead,
+however, is not trivial. Casts accumulate on higher-order values and
+continuations, changing the overall space complexity. Several
+space-efficient cast representations have been proposed, notably
+coercions in normal forms and threesomes. But they are presented in
+different dynamic semantics, which make it difficult to compare the
+key differences between the cast representations. We present a
+abstract data type, namely Cast ADT, that captures interface functions
+a cast representations typically includes, and an abstract machine
+parameterized over Cast ADTs.  The Cast ADT brings another benefit:
+space-efficient cast representations shall be proved not changing the
 overall behavior of language implementations except saving space.
-With our generic abstract machine, these proofs can be done by proving properties
-of a specific Cast ADT, which is simpler than going through a bisimulation proof 
-between a space-efficient dynamic semantics and the definitional dynamic semantics.
-We have successfully applied our new approach of proving the correctness of cast 
-representations to several known cast representations
+With our generic abstract machine, these proofs can be done by proving
+properties of a specific Cast ADT, which is simpler than proofs
+regarding the entire dynamic semantics.
+\todo[inline]{JS: The stuff above about ``make it difficult to compare''
+  is a weak argument. I would recommend deleting that argument and
+  instead focus on the benefits regarding the proofs of correctness.}
+
+We have successfully applied our new approach to the proofs of
+correctness for two space-efficient cast representations from the
+literature
 (\cite{Siek:2010:TWB:1706299.1706342,siek2012interpretations,Siek:2015:BCT:2737924.2737968})
-and believe this framework
-is also applicable to other cast representations (\cite{Garcia:2013:CTB:2500365.2500603,siek2012interpretations}).
-We also present a new cast representation, hypercoercions, that is more friendly
-to mechanized meta-theory and consumes less memory than coercions
-in normal forms.
+and believe this framework is also applicable to other cast
+representations
+(\cite{Garcia:2013:CTB:2500365.2500603,siek2012interpretations}).  We
+also present a new cast representation, hypercoercions, that is more
+friendly to mechanized meta-theory and consumes less memory than
+coercions in normal forms. We prove correctness for two variants of
+hypercoercions.
 
@@
 How does Jeremy think?}
+\todo[inline]{JS: yes}
 

### 2020-10-11 paper.tex
saving space: moved some type systems to appendix, made some figures smaller

@@
 \usepackage{xcolor} %% For \color
-\usepackage{todonotes} %% For \todo
+\usepackage[disable]{todonotes} %% For \todo
 \usepackage{mathtools} %% For \xRightarrow[sub]{sup}
@@
 
-Inspired by the approaches of \cite{Siek:2010:TWB:1706299.1706342}
-and \cite{Siek:2015:BCT:2737924.2737968}, 
-we also use the bisimulation technique. But our bisimulation have an
-important difference. Our bisimulation relation, unlike theirs, does
-not cover all possible states in the reduction. Instead, we ask both 
-sides of the bisimulation to reduce several steps before recovering
-the bisimulation relation (compare our Lemma~\ref{lem:weak-bisimulation}
-with Lemma~8 in \cite{Siek:2010:TWB:1706299.1706342}
-and Proposition~16 in \cite{Siek:2015:BCT:2737924.2737968}).
-This decision simplifies the bisimulation relation (Fig.~\ref{fig:bisim-SC-D})
-(compared to Figure~6 in \cite{Siek:2010:TWB:1706299.1706342} and
-Figure~6 in \cite{Siek:2015:BCT:2737924.2737968}).
-In particular, the function application case is a congruence
-(hence not shown in the figure) in our bisimulation relation
-but requires special rules in theirs.
-
-\todo[inline]{JS: there is a least one interesting difference regarding
-  the bisimulation: your lemma 3 has an ``upto reduction'' flavor to it
-  which makes your $\approx$ relation simpler. }
-\todo[inline]{KC: updated.}
+Inspired by the approaches of \cite{Siek:2010:TWB:1706299.1706342} and
+\cite{Siek:2015:BCT:2737924.2737968}, we also use the bisimulation
+technique. But our bisimulation have an important difference. Our
+bisimulation relation does not cover all possible states in the
+reduction. Instead, we ask both sides of the bisimulation to reduce
+several steps before recovering the bisimulation relation (compare our
+Lemma~\ref{lem:weak-bisimulation} with Lemma~8 in
+\cite{Siek:2010:TWB:1706299.1706342} and Proposition~16 in
+\cite{Siek:2015:BCT:2737924.2737968}).  This decision simplifies the
+bisimulation relation (Fig.~\ref{fig:bisim-SC-D}) (compared to
+Figure~6 in \cite{Siek:2010:TWB:1706299.1706342} and Figure~6 in
+\cite{Siek:2015:BCT:2737924.2737968}).  In particular, the function
+application case is a congruence (hence not shown in the figure) in
+our bisimulation relation but requires special rules in theirs.
 
@@
 
-\begin{figure}[tp]
-Syntax
+\begin{figure}[t]
 \[
@@
 
-	\fbox{\consistent{T}{T}} Consistency
-	\begin{gather*}
-	\infr{}{\consistent{\Tdyn}{\Tdyn}} \quad
-	\infr{}{\consistent{\Tdyn}{P}    } \quad
-	\infr{}{\consistent{P}{\Tdyn}    }
-	\\[1ex]
-	\infr{}{
-		\consistent{\Pbool}{\Pbool}
-	} \quad
-	\infr{
-		\consistent{S_1}{S_2} &
-		\consistent{T_1}{T_2}
-	}{
-		\consistent{\Pfunc{S_1}{T_1}}{\Pfunc{S_2}{T_2}}
-	} \quad
-	\infr{
-		\consistent{S_1}{S_2} &
-		\consistent{T_1}{T_2}
-	}{
-		\consistent{\Pprod{S_1}{T_1}}{\Pprod{S_2}{T_2}}
-	}
-	\end{gather*}
-
-	\fbox{\shallowlyconsistent{T}{T}} Shallow consistency
-	\begin{gather*}
-	\inference{}{
-		\shallowlyconsistent{\Tdyn}{\Tdyn}
-	} \quad
-	\inference{}{
-		\shallowlyconsistent{\Tdyn}{P}
-	} \quad
-	\inference{}{
-		\shallowlyconsistent{P}{\Tdyn}
-	} \\
-	\inference{}{
-		\shallowlyconsistent{\Pbool}{\Pbool}
-	} \quad
-	\inference{}{
-		\shallowlyconsistent{\Pfunc{S_1}{T_1}}{\Pfunc{S_2}{T_2}}
-	} \quad
-	\inference{}{
-		\shallowlyconsistent{\Pprod{S_1}{T_1}}{\Pprod{S_2}{T_2}}
-	}
-	\end{gather*}
-
-\fbox{$\expressiontyping{\Gamma}{e}{T}$} Expression Typing
-\begin{gather*}
-\dots \quad
-\infr{
-	\expressiontyping{\Gamma}{e}{S}  &
-	\consistent{S}{T}
-}{
-	\expressiontyping{\Gamma}{(\ecast{e}{\ccast{S}{l}{T}})}{T}
-}
-\end{gather*}
-
-\caption{Syntax and static semantics of the Cast Calculus.}
+%% 	\fbox{\consistent{T}{T}} Consistency
+%% 	\begin{gather*}
+%% 	\infr{}{\consistent{\Tdyn}{\Tdyn}} \quad
+%% 	\infr{}{\consistent{\Tdyn}{P}    } \quad
+%% 	\infr{}{\consistent{P}{\Tdyn}    }
+%% 	\\[1ex]
+%% 	\infr{}{
+%% 		\consistent{\Pbool}{\Pbool}
+%% 	} \quad
+%% 	\infr{
+%% 		\consistent{S_1}{S_2} &
+%% 		\consistent{T_1}{T_2}
+%% 	}{
+%% 		\consistent{\Pfunc{S_1}{T_1}}{\Pfunc{S_2}{T_2}}
+%% 	} \quad
+%% 	\infr{
+%% 		\consistent{S_1}{S_2} &
+%% 		\consistent{T_1}{T_2}
+%% 	}{
+%% 		\consistent{\Pprod{S_1}{T_1}}{\Pprod{S_2}{T_2}}
+%% 	}
+%% 	\end{gather*}
+
+%% 	\fbox{\shallowlyconsistent{T}{T}} Shallow consistency
+%% 	\begin{gather*}
+%% 	\inference{}{
+%% 		\shallowlyconsistent{\Tdyn}{\Tdyn}
+%% 	} \quad
+%% 	\inference{}{
+%% 		\shallowlyconsistent{\Tdyn}{P}
+%% 	} \quad
+%% 	\inference{}{
+%% 		\shallowlyconsistent{P}{\Tdyn}
+%% 	} \\
+%% 	\inference{}{
+%% 		\shallowlyconsistent{\Pbool}{\Pbool}
+%% 	} \quad
+%% 	\inference{}{
+%% 		\shallowlyconsistent{\Pfunc{S_1}{T_1}}{\Pfunc{S_2}{T_2}}
+%% 	} \quad
+%% 	\inference{}{
+%% 		\shallowlyconsistent{\Pprod{S_1}{T_1}}{\Pprod{S_2}{T_2}}
+%% 	}
+%% 	\end{gather*}
+
+%% \fbox{$\expressiontyping{\Gamma}{e}{T}$} Expression Typing
+%% \begin{gather*}
+%% \dots \quad
+%% \infr{
+%% 	\expressiontyping{\Gamma}{e}{S}  &
+%% 	\consistent{S}{T}
+%% }{
+%% 	\expressiontyping{\Gamma}{(\ecast{e}{\ccast{S}{l}{T}})}{T}
+%% }
+%% \end{gather*}
+
+\caption{Syntax of the Cast Calculus.}
 \label{fig:statics}
@@
 
-\paragraph{Syntax and Static Semantics}
+\paragraph{Syntax}
 
@@
 
-The syntax and static semantics are the same for the \LD\ and
+The syntax is the same for the \LD\ and
 \LUD\ cast calculi. They are reviewed in \figref{fig:statics}.
@@
 \end{itemize}
-As usual, in a cast $\ecast{e}{\ccast{S}{l}{T}}$, the source type $S$
-and the target $T$ must be consistent.
+
+\noindent The static semantics of the cast calculi is reviewed in the
+Appendix, \figref{fig:statics2}.
 
@@
 
-\begin{figure}[tp]
+\begin{figure}[t]
 \[
@@
     \vtrue       \mid
-    \vfalse                     
+    \vfalse     \mid                    
+    \vfunc{x}{S}{e}{E}  
 }
 \stxrulecont{
-    \vfunc{x}{S}{e}{E}  \mid
-	\vfuncc{v}{S}{T}{l}{S}{T}
-}
-\stxrulecont{
+	\vfuncc{v}{S}{T}{l}{S}{T} \mid
         \vcons{v}{v}               \mid
@@
 \end{itemize}
+The static semantics of hypercoercions is defined in the Appendix,
+\figref{fig:hypercoercion-statics}.
 
@@
 
-	\fbox{\casttyping{c}{S}{T}} Hypercoercion typing 
-	\begin{gather*}
-	\inference{}{\casttyping{\hcci}{\Tdyn}{\Tdyn}}
-	\quad
-	\inference{
-		\casttyping{h}{S}{P} &
-		\casttyping{m}{P}{Q} &
-		\casttyping{t}{Q}{T}
-	}{
-		\casttyping{\hccc{h}{m}{t}}{S}{T}
-	}
-	\end{gather*}
-
-	\fbox{\casttyping{h}{T}{P}} Head typing
-	\begin{gather*}
-	\inference{}{\casttyping{\hche}{P}{P}}
-	\quad
-	\inference{}{\casttyping{\hchp{I}{l}}{\Tdyn}{I}}
-	\end{gather*}
-
-	\fbox{$\casttyping{m}{T}{T}$} Middle typing
-	\begin{gather*}
-	\infr{}{\casttyping{\hcmfail{l}}{P}{Q}} \quad
-	\inference{}{\casttyping{\hcmbool}{\Pbool}{\Pbool}} \\
-	\inference{
-		\casttyping{c}{S_2}{S_1} &
-		\casttyping{d}{T_1}{T_2}
-	}{
-		\casttyping{\hcmfunc{c}{d}}{\Pfunc{S_1}{T_1}}{\Pfunc{S_2}{T_2}}
-	}
-	\quad
-	\inference{
-		\casttyping{c}{S_1}{S_2} &
-		\casttyping{d}{T_1}{T_2}
-	}{
-		\casttyping{\hcmprod{c}{d}}{\Pprod{S_1}{T_1}}{\Pprod{S_2}{T_2}}
-	}
-	\end{gather*}
-
-	\fbox{\casttyping{t}{P}{T}} Tail typing
-	\begin{gather*}
-	\inference{}{\casttyping{\hcte}{P}{P}} \quad
-	\inference{}{\casttyping{\hcti{I}}{I}{\Tdyn}} \quad
-	\end{gather*}
-
-	\caption{Definition of hypercoercions}
+	\caption{Hypercoercions: syntax and $\mathrm{id}$ operations.}
 	\label{fig:hypercoercion}
@@
 
-	\fbox{$\castFromDyn{Q}{l}$}
+%	\fbox{$\castFromDyn{Q}{l}$}
 	\[
@@
 
-	\fbox{$\castToDyn{Q}{l}$}
+%	\fbox{$\castToDyn{Q}{l}$}
 	\[
@@
 \begin{figure}[tp]
-\fbox{$\goodgap{g}$}
+  % removing fbox's to save space -Jeremy
+%\fbox{$\goodgap{g}$}
 \begin{gather*}
@@
 
-\fbox{$\dom{g}=g$}
+%\fbox{$\dom{g}=g$}
 \[
@@
 
-\fbox{$\cod{g}=g$}
+%\fbox{$\cod{g}=g$}
 \[
@@
 
-\fbox{$\fst{g}=g$}
+%\fbox{$\fst{g}=g$}
 \[
@@
 
-\fbox{$\snd{g}=g$}
+%\fbox{$\snd{g}=g$}
 \[
@@
 
+\section{Appendix}
+
+Figure~\ref{fig:statics2} defines the static semantics of the cast
+calculus.
+As usual, in a cast $\ecast{e}{\ccast{S}{l}{T}}$, the source type $S$
+and the target $T$ must be consistent.
+
+\begin{figure}[tp]
+	\fbox{\consistent{T}{T}} Consistency
+	\begin{gather*}
+	\infr{}{\consistent{\Tdyn}{\Tdyn}} \quad
+	\infr{}{\consistent{\Tdyn}{P}    } \quad
+	\infr{}{\consistent{P}{\Tdyn}    }
+	\\[1ex]
+	\infr{}{
+		\consistent{\Pbool}{\Pbool}
+	} \quad
+	\infr{
+		\consistent{S_1}{S_2} &
+		\consistent{T_1}{T_2}
+	}{
+		\consistent{\Pfunc{S_1}{T_1}}{\Pfunc{S_2}{T_2}}
+	} \quad
+	\infr{
+		\consistent{S_1}{S_2} &
+		\consistent{T_1}{T_2}
+	}{
+		\consistent{\Pprod{S_1}{T_1}}{\Pprod{S_2}{T_2}}
+	}
+	\end{gather*}
+
+	\fbox{\shallowlyconsistent{T}{T}} Shallow consistency
+	\begin{gather*}
+	\inference{}{
+		\shallowlyconsistent{\Tdyn}{\Tdyn}
+	} \quad
+	\inference{}{
+		\shallowlyconsistent{\Tdyn}{P}
+	} \quad
+	\inference{}{
+		\shallowlyconsistent{P}{\Tdyn}
+	} \\
+	\inference{}{
+		\shallowlyconsistent{\Pbool}{\Pbool}
+	} \quad
+	\inference{}{
+		\shallowlyconsistent{\Pfunc{S_1}{T_1}}{\Pfunc{S_2}{T_2}}
+	} \quad
+	\inference{}{
+		\shallowlyconsistent{\Pprod{S_1}{T_1}}{\Pprod{S_2}{T_2}}
+	}
+	\end{gather*}
+
+\fbox{$\expressiontyping{\Gamma}{e}{T}$} Expression Typing
+\begin{gather*}
+\dots \quad
+\infr{
+	\expressiontyping{\Gamma}{e}{S}  &
+	\consistent{S}{T}
+}{
+	\expressiontyping{\Gamma}{(\ecast{e}{\ccast{S}{l}{T}})}{T}
+}
+\end{gather*}
+
+\caption{Static Semantics of the Cast Calculus.}
+\label{fig:statics2}
+\end{figure}
+
+\figref{fig:hypercoercion-statics} defines the static semantics of
+hypercoercions.
+
+\begin{figure}[tp]
+	\fbox{\casttyping{c}{S}{T}} Hypercoercion typing 
+	\begin{gather*}
+	\inference{}{\casttyping{\hcci}{\Tdyn}{\Tdyn}}
+	\quad
+	\inference{
+		\casttyping{h}{S}{P} &
+		\casttyping{m}{P}{Q} &
+		\casttyping{t}{Q}{T}
+	}{
+		\casttyping{\hccc{h}{m}{t}}{S}{T}
+	}
+	\end{gather*}
+
+	\fbox{\casttyping{h}{T}{P}} Head typing
+	\begin{gather*}
+	\inference{}{\casttyping{\hche}{P}{P}}
+	\quad
+	\inference{}{\casttyping{\hchp{I}{l}}{\Tdyn}{I}}
+	\end{gather*}
+
+	\fbox{$\casttyping{m}{T}{T}$} Middle typing
+	\begin{gather*}
+	\infr{}{\casttyping{\hcmfail{l}}{P}{Q}} \quad
+	\inference{}{\casttyping{\hcmbool}{\Pbool}{\Pbool}} \\
+	\inference{
+		\casttyping{c}{S_2}{S_1} &
+		\casttyping{d}{T_1}{T_2}
+	}{
+		\casttyping{\hcmfunc{c}{d}}{\Pfunc{S_1}{T_1}}{\Pfunc{S_2}{T_2}}
+	}
+	\quad
+	\inference{
+		\casttyping{c}{S_1}{S_2} &
+		\casttyping{d}{T_1}{T_2}
+	}{
+		\casttyping{\hcmprod{c}{d}}{\Pprod{S_1}{T_1}}{\Pprod{S_2}{T_2}}
+	}
+	\end{gather*}
+
+	\fbox{\casttyping{t}{P}{T}} Tail typing
+	\begin{gather*}
+	\inference{}{\casttyping{\hcte}{P}{P}} \quad
+	\inference{}{\casttyping{\hcti{I}}{I}{\Tdyn}} \quad
+	\end{gather*}
+
+	\caption{Static semantics of hypercoercions}
+	\label{fig:hypercoercion-statics}
+\end{figure}
+
 \end{document}

### 2020-10-12 paper.tex
Updates from Overleaf
a general description of the proof of lemma 3

@@
 \begin{abstract}
+% Background
 Gradual typing combines dynamic typing and static typing in one
@@
 space-efficient cast representations have been proposed, notably
-coercions in normal forms and threesomes. But they are presented in
-different dynamic semantics, which make it difficult to compare the
-key differences between the cast representations. We present a
-abstract data type, namely Cast ADT, that captures interface functions
-a cast representations typically includes, and an abstract machine
-parameterized over Cast ADTs.  The Cast ADT brings another benefit:
-space-efficient cast representations shall be proved not changing the
-overall behavior of language implementations except saving space.
-With our generic abstract machine, these proofs can be done by proving
-properties of a specific Cast ADT, which is simpler than proofs
-regarding the entire dynamic semantics.
+coercions in normal forms and threesomes.
+These cast representations shall be proved not changing the overall
+behavior of language implementations except saving space.
+Existing proofs typically go through a bisimulation between
+a space-efficient semantics, which use a specific cast representation,
+and the definitional but inefficient semantics \citep{Siek:2010:TWB:1706299.1706342,Siek:2015:BCT:2737924.2737968}.
+% Problem
+However, this technique imposes unnecessary burden to proof writer
+because a considerable portion of the semantics is irrelevant to
+casts.
+% Solution
+To isolate cast representations from the remaining part of 
+implementations, we present a abstract data type, namely Cast ADT,
+that captures interface functions a cast representations typically 
+includes, and an abstract machine parameterized over Cast ADTs.
+Our generic dynamic semantics comes with generic theorems,
+% Why is our solution a step forward
+with which the correctness proofs can be done by just proving 
+properties of a specific Cast ADT.
+% %
+% To isolate cast representations from the remaining part of 
+% implementations, we present a abstract data type, namely Cast ADT,
+% that captures interface functions a cast representations typically 
+% includes, and an abstract machine parameterized over Cast ADTs.
+% %
+% With our generic abstract machine, the correctness proofs can be
+% done by proving properties of a specific Cast ADT, which is simpler
+% than proofs regarding the entire dynamic semantics.
+%%%%%
+% %
+% But they are presented in
+% different dynamic semantics, which make it difficult to compare the
+% key differences between the cast representations.
+% %
+% We present a
+% abstract data type, namely Cast ADT, that captures interface functions
+% a cast representations typically includes, and an abstract machine
+% parameterized over Cast ADTs.
+% %
+% The Cast ADT brings another benefit:
+% space-efficient cast representations shall be proved not changing the
+% overall behavior of language implementations except saving space.
+% %
+% With our generic abstract machine, these proofs can be done by proving
+% properties of a specific Cast ADT, which is simpler than proofs
+% regarding the entire dynamic semantics.
 \todo[inline]{JS: The stuff above about ``make it difficult to compare''
@@
   instead focus on the benefits regarding the proofs of correctness.}
+\todo[inline]{KC: updated.}
 
@@
 literature
-(\cite{Siek:2010:TWB:1706299.1706342,siek2012interpretations,Siek:2015:BCT:2737924.2737968})
+\citep{Siek:2010:TWB:1706299.1706342,siek2012interpretations,Siek:2015:BCT:2737924.2737968}
 and believe this framework is also applicable to other cast
 representations
-(\cite{Garcia:2013:CTB:2500365.2500603,siek2012interpretations}).  We
+\citep{Garcia:2013:CTB:2500365.2500603,siek2012interpretations}.  We
 also present a new cast representation, hypercoercions, that is more
@@
 hypercoercions.
-
-\todo[inline]{KC: I feel ``going through a bisimulation proof'' is too specific.
-There should be other ways to prove equivalence of two dynamic semantics.
-How does Jeremy think?}
-\todo[inline]{JS: yes}
 
@@
 interoperability \citep{Gray:2005ij,Matthews:2007zr}.
-
-\todo[inline]{KC: Cite "Contracts for higher-order functions" for the proxy-based approach maybe?}
-\todo[inline]{JS: That paper doesn't exactly fit into what you're talking about in the above
-sentence. It might be appopriate to cite it elsewhere in the paper. Also,
-there are earlier papers about coercive subtyping (Computing with coercions by Breazu-Tannen et al)
-that use a proxy-based approach. The contracts paper may be the first to propose blame tracking.}
-\todo[inline]{KC: How about citing the origin of the proxy-based approach when we talk
-about the CPSed even-odd example?
-I am confused about which paper to cite. \cite{herman2010space} seems to be citing
-\cite{findler2002contracts} for the proxy-based approach of casting function.
-Here is the relevant sentences from \cite{herman2010space}:
-``In general, it is not possible to check if an untyped function satisfies a
-particular static type. A natural solution is to wrap the function in a proxy that, whenever
-it is applied, casts its argument and result values appropriately, ensuring that the function
-is only observed with its expected type. This proxy-based approach was formalized by Findler
-and Felleisen [15] ...''
-I am \textit{not} trying to say I don't believe in your statements about the origins of
-the proxy-based approach and blame tracking in functions.
-I want to know whether \citet{herman2010space} is citing the right paper.
-Maybe both papers came up independently with a similar idea but \cite{findler2002contracts}
-is more related to our work.
-}
-\todo[inline]{JS: In the above you've lumped proxy-based and blame
-  tracking together, which is incorrect. AFAIK,
-  \cite{findler2002contracts} is the origin of blame tracking. AFAIK,
-  \citet{Breazu-Tannen:1990vc} is the origin of proxy-based casts.
-  You can read both papers for yourself and be the judge.  BTW, TAPL
-  (section 15.6) cites Breazu-Tannen.  So \citet{herman2010space}
-  cited the wrong paper for function proxies, perhaps because they
-  didn't know about \citet{Breazu-Tannen:1990vc}. Also,
-  \cite{findler2002contracts} should have cited
-  \citet{Breazu-Tannen:1990vc} but did not. Perhaps because they did
-  not consider that papers about ``casts'' to be closely related to
-  their paper about ``contracts''.  Or perhaps they too did not know
-  about \citet{Breazu-Tannen:1990vc}.  Authors make mistakes all the
-  time regarding related work, and this is just yet another example of
-  that. For that matter, I should have cited
-  \citet{Breazu-Tannen:1990vc} in \citet{siek2006gradual} but did not,
-  probably because I had learned about it from TAPL and therefore
-  thought it was so standard that it didn't need a citation.  But it
-  would have been better for me to cite it.}
 
@@
 \todo[inline]{KC: in the next paragraph I cite \cite{breazu1991inheritance}
-and \cite{breazu1990computing}}
+and \cite{findler2002contracts}. My understanding is \cite{findler2002contracts}
+extends the approach in \cite{breazu1991inheritance} with
+blame labels.}
 
@@
 the output, following the approach in \cite{breazu1991inheritance}
-and \cite{breazu1990computing},
+and \cite{findler2002contracts},
 so the space complexity is again linear.
@@
 
-\todo[inline]{KC: how can I forget the interpretation paper!}
 \cite{siek2012interpretations} presents a definitional interpreter
@@
 to other flavor of coercions or also to other cast representations.
-
-\todo[inline]{JS: The above is too short of a description of that related
-work.}
-\todo[inline]{KC: I am actually very confused by \citet{garcia2014deriving}.
-They stated that ``Theorems 8.1 and 8.3 can be generalised for other choices
-of dynamic semantics by applying the correspondence described
-through the paper starting with a different set of coercion artefacts.''.
-However they didn't give a generalization and it is unclear to me over what
-their system is parameterized (cast representations? apply-coercion and seq?.}
-\todo[inline]{JS: your comment above says what you should say
-  (except the part about your confusion). Say it in a matter-of-fact
-way, and not a derogitory way.}
-\todo[inline]{KC: updated.}
 
@@
 \CBMachine\ and \SMachine{C}.
+A general description of the proof is in the Appendix.
 
@@
 \end{lemma}
-\todo[inline]{KC: wouldn't it be great if I can describe the main ideas of the proof?}
-\todo[inline]{JS: Yes, that would be great.}
-\todo[inline]{KC: that is possibly only if we steal some pages from elsewhere.
-The paper limit is 25 (excluding bib) and we have used 30 now.
-https://etaps.org/2021/call-for-papers}
-\todo[inline]{KC: [IMPORTANT]}
 
@@
 
-\todo[inline]{JS: I'd recommend moving this subsection before that of
-  LazyD because a reader is more likely to be familiar with Lazy UD.}
-\todo[inline]{KC: Updated.}
-
 % Hypercoercions for the \LUD\ blame tracking strategy have the same syntax
@@
 label to blame. The forth and last line is straightforward recursion.
-
-\todo[inline]{KC: I need a better name for \compatibletailhead{t}{h},
-  any suggestion from Jeremy?}
-\todo[inline]{JS: how about $\sim$}
-\todo[inline]{KC: sounds good}
 
@@
 \todo[inline]{KC: should we cite the place where ``Prior presentations'' locate?}
+
 The translation function \translate{\ccast{S}{l}{T}} is defined in 
@@
 
+\todo[inline]{KC: The general idea of Lemma~\ref{lem:weak-bisimulation}}
+
+Lemma~\ref{lem:weak-bisimulation} is proved by case analysis on \bisims{s_1}{s_1'}{T}.
+Function call is the most interesting case. In this case the function value in
+\CMachine{B}
+must be of the form 
+\[
+v_1 = \vfuncc{
+		\vfuncc{
+			\vfunc{x}{S_1}{e}{E}
+		}{S_1}{T_1}{l_1}{S_2}{T_2}
+		\ldots
+	}{S_{n-1}}{T_{n-1}}{l_{n-1}}{S_n}{T_n}
+\]
+By induction of the sequence of casts, we know \scont{v_2}{\Kcons{\FappOX{v_1}}{K}} will
+transition to
+\[
+\begin{array}{l}
+\mlet{v_2}{\applyCast{v_2}{\ccast{S_n}{\bar{l}}{S_{n-1}}}}{} \\
+\ldots \\
+\mlet{v_2}{\applyCast{v_2}{\ccast{S_2}{\bar{l}}{S_1}}}{} \\
+\sexpr{e}{E[x:=v_2]}{
+	\Kcons{\Fcast{\ccast{T_1}{l}{T_2}}}{
+	    \ldots
+	    \Kcons{\Fcast{\ccast{T_{n-1}}{l}{T_n}}}{K}}
+}
+\end{array}
+\]
+% Assuming \bisimv{v_1}{v_1'}{\Pfunc{S_n}{T_n}} and \bisimv{v_2}{v_2'}{S_n}.
+As for \SMachine{C}, the function value must be of the form
+\[
+v_1' = \ecast{\vfunc{x}{S}{e}{E'}}{\Pfunc{c}{d}}
+\]
+where
+\[
+\begin{array}{l}
+\bisimc{(\ccast{S_n}{\bar{l}}{S_{n-1}} \ldots \ccast{S_2}{\bar{l}}{S_1})}{c}{S_n}{S_1} \\
+\bisimc{(\ccast{T_1}{l}{T_1} \ldots \ccast{T_{n-1}}{l}{T_n})}{d}{T_1}{T_n} \\
+\end{array}
+\]
+By the definition of \applyContName\ we know \applyCont{v_2'}{\Kcons{\FappOX{v_1'}}{K}} will
+transition to
+\[
+\begin{array}{l}
+\mlet{v_2'}{\denote{c}(v_2')}{} \\
+\sexpr{e}{E'[x:=v_2']}{\extCont{d}{K'}}
+\end{array}
+\]
+Intuitively, we need to show the sequence of let bindings in \CMachine{B}
+bisimulate the single let binding in \SMachine{C}, and that the two 
+extended continuations bisimulate. Both of them are straightforward to
+proof.
+
 \end{document}

### 2020-10-13 paper.tex
minor edits in Abstract

@@
 %
-\authorrunning{F. Author et al.}
+\authorrunning{Lu et al.}
 % First names are abbreviated in the running head.
@@
 % Problem
-However, this technique imposes unnecessary burden to proof writer
+This technique imposes unnecessary burden in proving such theorems
 because a considerable portion of the semantics is irrelevant to
@@
 To isolate cast representations from the remaining part of 
-implementations, we present a abstract data type, namely Cast ADT,
+semantics, we present a abstract data type, namely Cast ADT,
 that captures interface functions a cast representations typically 

### 2020-10-14 paper.tex
slim down abstract to reduce page num to 25

@@
 coercions in normal forms and threesomes.
-These cast representations shall be proved not changing the overall
+A correct cast representations shall be proved not changing the overall
 behavior of language implementations except saving space.
 Existing proofs typically go through a bisimulation between
-a space-efficient semantics, which use a specific cast representation,
-and the definitional but inefficient semantics \citep{Siek:2010:TWB:1706299.1706342,Siek:2015:BCT:2737924.2737968}.
+the language semantics and a space-efficient one 
+\citep{Siek:2010:TWB:1706299.1706342,Siek:2015:BCT:2737924.2737968}.
 % Problem
-This technique imposes unnecessary burden in proving such theorems
-because a considerable portion of the semantics is irrelevant to
-casts.
+The similarity of these proofs suggests that people should be able
+to prove correctness for a cast representation by proving it holds
+certain properties.
 % Solution
-To isolate cast representations from the remaining part of 
-semantics, we present a abstract data type, namely Cast ADT,
+We present an abstract data type, namely Cast ADT,
 that captures interface functions a cast representations typically 
-includes, and an abstract machine parameterized over Cast ADTs.
-Our generic dynamic semantics comes with generic theorems,
+provides, and an abstract machine parameterized over Cast ADTs.
+Our abstract machine comes with generic theorems,
 % Why is our solution a step forward
@@
 bisimulate the single let binding in \SMachine{C}, and that the two 
-extended continuations bisimulate. Both of them are straightforward to
-proof.
+extended continuations bisimulate each other. The first part follows from
 

### 2020-10-14 paper.tex
Refine appendix
remove the last subsection in related work because the subsection is too short and not very informative.

@@
 (Subsection~\ref{subsec:parameterized-dynamics}),
-proofs of correctness of cast representations
-(Subsection~\ref{subsec:related-work-other-proofs}),
-and relationship between hypercoercions and other cast representations
-(Subsection~\ref{subsec:related-work-other-cast-reprs}).
+and proofs of correctness for cast representations
+(Subsection~\ref{subsec:related-work-other-proofs}).
+% and relationship between hypercoercions and other cast representations
+% (Subsection~\ref{subsec:related-work-other-cast-reprs}).
 
@@
 
-\subsection{Other Cast Representations}
-\label{subsec:related-work-other-cast-reprs}
-
-Hypercoercions is inspired by coercions in normal form and supercoercions
-and ends up having a symmetrical definition similar to threesomes.
+% \subsection{Other Cast Representations}
+% \label{subsec:related-work-other-cast-reprs}
+
+% Hypercoercions is inspired by coercions in normal form and supercoercions
+% and ends up having a symmetrical definition similar to threesomes.
 
@@
 
-\paragraph{Syntax}
-
 \todo[inline]{KC: is this the right place to mention that in Agda
 code we use de Bruijn indexes?}
+
+\paragraph{Syntax}
 
@@
 extended continuations bisimulate each other. The first part follows from 
+the properties of Cast ADT (Definition~\ref{def:cast-rep}) and the premise that 
+cast applications preserve the bisimulation relation. The second part
+is straightforward to prove.
 

### 2020-10-14 paper.tex
mention de Bruijn indexes
shortened and revised the abstract, other minor edits to get page count down to 25

@@
 coercions in normal forms and threesomes.
-A correct cast representations shall be proved not changing the overall
-behavior of language implementations except saving space.
-Existing proofs typically go through a bisimulation between
-the language semantics and a space-efficient one 
+% Problem
+The proofs of correctness of these cast representations are
+challenging, involving a bisimulation between the language semantics
+and a space-efficient implementation
 \citep{Siek:2010:TWB:1706299.1706342,Siek:2015:BCT:2737924.2737968}.
-% Problem
-The similarity of these proofs suggests that people should be able
-to prove correctness for a cast representation by proving it holds
-certain properties.
+The prospect of mechanizing these proofs is even more daunting.
 % Solution
-We present an abstract data type, namely Cast ADT,
-that captures interface functions a cast representations typically 
-provides, and an abstract machine parameterized over Cast ADTs.
-Our abstract machine comes with generic theorems,
-% Why is our solution a step forward
-with which the correctness proofs can be done by just proving 
-properties of a specific Cast ADT.
+In this paper we present a framework in Agda that reduces the cost of
+mechanized proofs of correctness for cast representations.
+
+%% The abstract is too long... I wrote the following but I'm now
+%% cutting it. No need for that much detail here. -Jeremy
+%% We present
+%% an abstract data type, the Cast ADT, that defines an interface for
+%% cast representations and we specify which properties are necessary for
+%% a Cast ADT to be correct. We then define an abstract machine
+%% parameterized over Cast ADTs and prove its correctness.  A user of our
+%% framework proves the correctness of their cast representation by
+%% implementing the Cast ADT, proving that it satisfies the correctness
+%% properties, and then instantiating our generic theorem.
+
+%% A correct cast representations shall be proved not changing the overall
+%% behavior of language implementations except saving space.
+%% Existing proofs typically go through a 
+%% % Problem
+%% The similarity of these proofs suggests that people should be able
+%% to prove correctness for a cast representation by proving it holds
+%% certain properties.
+%% % Solution
+%% We present an abstract data type, namely Cast ADT,
+%% that captures interface functions a cast representations typically 
+%% provides, and an abstract machine parameterized over Cast ADTs.
+%% Our abstract machine comes with generic theorems,
+%% % Why is our solution a step forward
+%% with which the correctness proofs can be done by just proving 
+%% properties of a specific Cast ADT.
 % %
@@
 
-We have successfully applied our new approach to the proofs of
-correctness for two space-efficient cast representations from the
-literature
+We apply our framework to obtain proofs of correctness for two
+space-efficient cast representations from the literature
 \citep{Siek:2010:TWB:1706299.1706342,siek2012interpretations,Siek:2015:BCT:2737924.2737968}
@@
 representations
-\citep{Garcia:2013:CTB:2500365.2500603,siek2012interpretations}.  We
-also present a new cast representation, hypercoercions, that is more
-friendly to mechanized meta-theory and consumes less memory than
+\citep{Garcia:2013:CTB:2500365.2500603,siek2012interpretations}.
+Finally, we present a new cast representation, named hypercoercions,
+that is more friendly to mechanization and consumes less memory than
 coercions in normal forms. We prove correctness for two variants of
-hypercoercions.
+hypercoercions using our framework.
 
@@
 
-\todo[inline]{KC: is this the right place to mention that in Agda
-code we use de Bruijn indexes?}
-
 \paragraph{Syntax}
@@
 Subsection~\ref{sec:S-correct}.
+
+\todo[inline]{KC: is here the right place to mention that in Agda
+code we use de Bruijn indexes?}
+In the Agda code we use de Bruijn indices instead of named variables.
 
@@
 \end{itemize}
-The bits for blame labels represent an index into a table of blame information.
-In the event that a program requires too many blame labels, then the 
-implementation
-can fallback to using the heap-allocated structure for more
-coercions.
+The bits for blame labels represent an index into a table of blame
+information.  If a program requires too many blame labels, then the
+implementation can fallback to using the heap-allocated structure for
+more coercions.
 \end{itemize}
@@
 %
-The framework includes abstract data types for cast representations
-(Cast ADT and its refinements Lazy D Cast ADT and \LUD\ \CastADT), a
-parameterized abstract machine \SMachine{C}, a theorem stating that
+The framework includes abstract data types for cast representations,
+%(Cast ADT and its refinements Lazy D Cast ADT and \LUD\ \CastADT)
+a parameterized abstract machine \SMachine{C}, a theorem stating that
 \SMachine{C} is equivalent to \LDMachine\ when $C$ is a Lazy D Cast
